### 2018-09-13 RSP_Paper/RSP_paper.tex
Newly initialized repo

\pdfoutput=1
\documentclass[iop, apjl, twocolappendix, numberedappendix]{emulateapj}
%\usepackage{newtxtext,newtxmath}
\usepackage[T1]{fontenc}
%\usepackage{ae,aecompl}
\usepackage{float}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{txfonts}
\usepackage{ulem}
\usepackage{xspace}
\usepackage[colorlinks=true,urlcolor=blue,linkcolor=blue,citecolor=blue]{hyperref}
%\usepackage{nccmath}
\usepackage[utf8]{inputenc}
\newcommand{\fhat}[1]{\expandafter\hat#1}
\newcommand{\fbar}[1]{\expandafter\bar#1}
\newcommand\fnurl[2]{%
  \href{#2}{#1}\footnote{\url{#2}}%
}
\def\rs{r_{\rm s}}
\def\rhos{\rho_{\rm s}}
\def\se{s_{\rm e}}
\def\ftrans{f_{\rm trans}}
\def\rhog{\rho_{\rm g}}
\def\rhoginner{\rho_{\rm g}^{\rm inner}}
\def\rhogouter{\rho_{\rm g}^{\rm outer}}
\def\rt{r_{\rm t}}
\def\rout{r_{\rm out}}
\def\mpch{h^{-1}{\rm Mpc}}
\def\msunh{h^{-1}{\rm M_{\odot}}}
\shorttitle{Splashback radius of Planck-SZ clusters}
\shortauthors{Zürcher, More}

\begin{document}

\title{The Splashback Radius of Planck-SZ clusters}

\author{
Dominik Zürcher \altaffilmark{1, 2}
Surhud More \altaffilmark{1, 3}, 
}
\affil{
$^{1}$Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), \\ 
$^{2}$Department of Physics, ETH Zurich, Wolfgang Pauli Strasse 27, 8093 Zurich, Switzerland\\
$^{3}$The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa, Chiba 277-8583\\
}

\begin{abstract}
We present evidence for the existence of the splashback radius
in galaxy clusters selected using the Sunyaev-Zeldovich effect.
We show that the deprojected cross-correlation of galaxy clusters
found in the Planck survey with galaxies detected photometrically in
the Pan-STARRS survey, shows a sharp steepening feature (a
logarithmic slope steeper than $-3$), which we associate with the
splashback radius.  We infer the three-dimensional splashback radius
for the SZ cluster sample to be $r_{\rm sp}=1.81_{-0.33}^{+0.28}$ $\mpch$,
where the cluster sample has an average halo mass $M_{\rm
500c}=3.0\times10^{14}\msunh$ at an average redshift of $z=0.18$.
The inferred value of the splashback radius is consistent with the
expected location for dark matter halos in the standard cold dark
matter paradigm. However, given the limited precision of our
measurements, we cannot conclusively rule out the smaller splashback
radius measured so far in the literature for photometrically
selected galaxy clusters. We show that the splashback radius does
not depend upon the galaxy magnitude for galaxies fainter than
$M_i-5\log h=-19.44$, and is present at a consistent location in
both red and blue galaxy populations. The presence of the splashback radius in
color-separated galaxy distributions could potentially be used to put lower limits on the
quenching timescales for galaxies. Further, we record a strong increase 
in the fraction of red galaxies that is associated with the splashback radius.

\end{abstract}

%\begin{keywords}
%galaxies:clusters:general -- galaxies:halos -- methods:observational -- cosmology:dark matter -- cosmology:large-scale structure of Universe -- cosmology:observations
%\end{keywords}

\section{Introduction}
\label{sec:Introduction}

The density distribution of matter within dark matter halos shapes
the potential well in which galaxies form and grow. Therefore, the
structure of these dark matter halos has been extensively studied
both theoretically as well as in numerical simulations \citep[see
e.g.,][]{gunn1972infall, fillmore1984self, bertschinger1985self,
navarro1997universal, moore1999dark}. Studies with numerical
simulations show that the density profiles of dark matter halos
within their virial radii are roughly self-similar and follow the
Navarro-Frenk-White (NFW) profile \citep{navarro1997universal},
which asymptotes to a slope of $-1$ in the inner regions and $-3$ at
large radii. There has been intense debate in the literature about
the exact form of the density profile 
\citep[e.g.,][]{navarro2004inner}, the value of the asymptotic inner slope,
as well as the outskirts and boundaries of dark matter halos
\citep{cuesta2008virialized, more2011overdensity, diemer2013pseudo}.

The recent study of \citet{diemer2014dependence} has sparked a
renewed interest in understanding the structure of dark matter halos
on scales beyond the typical virial radii.
\citet{diemer2014dependence} investigated the outskirts of dark
matter halos in numerical simulations and found the existence of a
physical feature, namely a sharp steepening in the density
distributions of dark matter halos, which is not captured by
commonly used functional forms such as the NFW profile. They showed
that even for halos of the same mass, the position of the feature
changes depending upon the mass accretion rate of the halos. A simple
theoretical toy model to explain this feature was presented by
\citet{adhikari2014splashback}. They showed that the feature
observed by \citet{diemer2014dependence} results from the  piling up
of recently accreted dark matter particles at the apocenters of
their orbits, and its location corresponds to the last density
caustic in the self-similar models of secondary infall
\citep{fillmore1984self, bertschinger1985self, lithwick2011self}.
They coined the term ``splashback radius`` for this feature. Their
toy model also naturally explains the accretion rate dependence --
faster accreting halos have smaller splashback radii.

The interpretation of the accretion rate dependence is
straightforward. Due to the continuous change of the gravitational
potential of the halo, depending on its accretion rate, the kinetic
energy of a recently accreted dark matter particle, gained during
its infall onto the cluster, does not suffice to climb the deepened
potential well completely again, but instead it ``splashes back`` at
a distance that depends on the recent deepening of the potential
well.

Subsequently, \citet{more2015splashback} studied the
growth rate of dark matter halos at low redshift and showed that
pseudo-evolution, caused by the ill-definition of the halo boundary
through the virial radius, accounts for nearly all of the apparent
growth of galaxy-sized halos and can also account for a substantial
fraction of the growth of cluster-sized halos
\citep{diemer2013pseudo}. They suggested the use of the splashback
radius as a natural boundary for dark matter halos and explored its
consequences for the inferred boundaries and growth rates of the
halos.  It was found that depending on the accretion rate of the
halo, the splashback radius may lie well beyond the commonly used
virial radius. For quickly accreting halos the splashback radius is
expected to occur at $\approx 0.8-1$ $r_{\mathrm{200m}}$ and at
$\approx 1.5$ $r_{\mathrm{200m}}$ for slowly accreting halos
\citep{more2015splashback}.

Given the mass of the halo, the location of the splashback radius
constitutes a direct probe of the halo accretion rate. Motivated by
these studies, \citet{more2016detection} tried to detect this
feature in observations. Using the optically selected Sloan Digital
Sky Survey RedMaPPer galaxy cluster catalog
\citep{rykoff2014redmapper}, and by cross-correlating it with the
SDSS photometric galaxy sample, \citet{more2016detection} found evidence
for the steepening of the dark matter density profile, and therefore
the splashback radius of this sample of galaxy clusters (later
corroborated by including further models for mis-centering by
\citet{baxter2017halo}). Somewhat surprisingly,
\citet{more2016detection} found that the location of the splashback
radius was inconsistent with that expected from numerical
simulations of dark matter by about $20\pm5$\%. Although they
investigated potential systematic issues, they did not have access
to mock cluster catalogs which could mimic the selection effects of
optically-identified clusters. \citet{busch2017assembly} used a
simplified optical cluster selection algorithm on the Millennium
simulation, and pointed out that optical clusters can be heavily
affected by projection issues, and could potentially introduce
systematics in the inference of the splashback radius, as well as
halo assembly bias. The existence of projection effects in the
optical cluster catalog in the context of halo assembly bias was 
also demonstrated by \citet{zu2016level}.

\citet{umetsu2017lensing} used Xray selected clusters to look for
the splashback radius using the weak lensing signal, however
stacking issues and the low signal-to-noise ratio remains a significant
hurdle. \citet{chang2017splashback} find evidence for the splashback
radius in the weak lensing signal, but their analysis was again done
using optically selected clusters in the Dark energy survey
\citep{dark2005dark}. Regardless of the projection issues present in
the optical cluster catalog, there is some inherent circularity
present in the logic of using photometric galaxies to select
clusters as over-densities in a given aperture, and then using the
same photometric sample of galaxies to look for the splashback
radius. There is a possibility that the aperture used to select the
cluster catalogs could be imprinted in a non-trivial way on the
measured number density profiles of clusters.

In this work, we move away from the optical cluster selection and
explore the use of SZ selected cluster catalogs. While the SZ
selected clusters can also be susceptible to systematic selection
effects, the scales on which the SZ signal is measured and the
cluster selection is performed is much smaller than the expected
location of the splashback radius. Therefore, we do not expect major
systematic biases due to the selection process. We use this sample
to explore the evidence for the splashback radius in observations.
Due to the low signal-to-noise ratio of the weak lensing signal, we
perform our analysis using cross-correlation of galaxies with
clusters instead. The SDSS sample used by \citet{more2016detection}
was deep enough such that biases in the location of the splashback
radius due to dynamical friction effects were expected to be small.
Nevertheless, we use galaxy samples, which are even fainter by
$0.5-1$ magnitudes compared to those used by
\citet{more2016detection}.

Given that the splashback radius represents a true halo boundary,
the observations of the splashback radius can be used to study a
variety of galaxy formation questions. Such as questions 
regarding the timescales and the spatial scales within
which star forming galaxies quench after they fall into the cluster
potential. Answers to those questions are important to understand 
the evolution of satellite galaxies in massive galaxy clusters. 
If blue galaxies quench before
they complete a single orbit, then they are not expected to show a
splashback feature in their density distribution. In pursuit of this
question, we also explore the dependence of the cluster-galaxy
cross-correlations separately for the red and blue galaxies and
explore their relative contributions to the overall density profile.

This paper is organized as follows: Section~\ref{sec:Methods} starts
by introducing the data, namely the cluster and the galaxy catalogs
as well as the methods that are used to derive the results which are
presented in visual and tabular form and  discussed in
Section~\ref{sec:Results}. We outline the steps that will be taken
in future works in Section~\ref{sec:Future} and finally we summarize
our findings in Section~\ref{sec:Conclusions} and provide a short
outlook on what needs yet to be done. Throughout the paper, we use a
flat $\Lambda$CDM cosmology with $\Omega_{\rm m}=0.27$ to convert
redshifts and angles into cosmological distances. Also, we denote 
three-dimensional distances by $r$ and projected distances by $R$.

\section{Data and Methods}
\label{sec:Methods}
The methodology we adopt for locating the splashback radius closely
follows \citet{more2016detection}. We perform a cross-correlation
between SZ selected galaxy clusters with photometric galaxies in
order to assess the existence and location of the splashback radius.
We describe the data sets we use and our methodology in this
section.

\subsection{Cluster catalog}
\label{sec:clusters}
The baryonic component of a galaxy cluster is dominated by the hot,
ionized  intra-cluster medium (ICM), which is gravitationally bound
within the cluster. The cosmic microwave background (CMB) photons
that pass through the cluster inverse Compton scatter off the hot
electrons and gain energy. This effect is known as the thermal
Sunyaev-Zeldovich (SZ) effect
\citep{sunyaev1970small,sunyaev1980velocity}. The effect has a
characteristic frequency dependence and results in an intensity
decrease below 220 GHz and an associated increase at higher
frequencies. The multiple frequency channels on the Planck satellite
allow a detection of galaxy clusters using the SZ effect
\citep{collaboration2016planck}. As part of the 2015 Data Release of
the Planck mission, the second Planck Catalogue of Sunyaev-Zeldovich
Sources (PSZ2) was made available to the community. The PSZ2 catalog
contains detections based on  three different techniques
\citep{ade2016planck}, and the union of these catalogs has in total
1653 galaxy clusters, of which 1203 clusters have been confirmed by
cross-matching to other galaxy clusters from external data sets. 
\begin{table}
    \centering
    \caption{Comparison of the PSZ2 cluster catalog
    against the RedMaPPer cluster catalog used by
\citet{more2016detection}. The values of the mass estimates
$M_{\mathrm{500c}}$, $M_{\mathrm{200m}}$, redshifts $z$ and expected
splashback radii $r^{\mathrm{3D,theo}}_{\mathrm{sp}}$ represent the
catalog averages. The redshifts for both catalogs are given from the
survey. For the RedMaPPer catalog the $M_{\mathrm{200m}}$ mass
estimates were obtained from gravitational lensing and for the PSZ2
catalog the $M_{\mathrm{500c}}$ estimates were calculated from the
survey parameters using the scaling relation between the integrated
Compton Y-parameter $Y_{500c}$ and $M_{500c}$ as found by
\citet{ade2014planck}. The missing mass estimates as well as the
expected values of the splashback radii were calculated using the
Python package COLOSSUS \citep{diemer2017colossus}. The predictions
for the splashback radii $r^{\mathrm{3D,theo}}_{\mathrm{sp}}$ is
given in comoving units.}
    \label{tab:cluster_catalogs} 
    \begin{tabular}{ccc}
    \hline 
    & RedMaPPer & PSZ2 \\
    \hline 
    $z$ & 0.24 & 0.177 \\
    \hline 
    \# objects & 8643 & 596\\
    \hline
    $M_{\mathrm{500c}}$ [$h^{-1}10^{14} $M$_{\sun}$] & 0.9 & 3.0 \\
    \hline
    $M_{\mathrm{200m}}$ [$h^{-1}10^{14} $M$_{\sun}$] & 1.8 & 6.2\\ 
    \hline
    $r^{\mathrm{3D,theo}}_{\mathrm{sp}}$ [$h^{-1}$ Mpc] & 1.37 & 1.89 \\
    \hline
    \end{tabular} 
\end{table}
\begin{table*}
    \centering
    \caption{Summary and comparison of the properties of the galaxy catalogs used in this work as well as the SDSS catalog used in \citet{more2016detection}.}
    \label{tab:galaxy_catalogs}
    \begin{tabular}{ccccc}
    \hline 
    & SDSS & PS 21 & PS 21.5 & PS 22 \\ 
    \hline 
    depth [mag] & 21.00 & 21.00 & 21.50 & 22.00\\ 
    \hline 
    eff. area [deg$^2$] & $\approx$ 10'000 & 21'148 & 20'586 & 15'689\\ 
    \hline 
    \# objects & 57'181'113 & 93'772'329 & 123'188'529 & 105'809'113 \\
    \hline
    objects/deg$^2$ & 5718 & 4434 & 5984 & 6744\\ 
    \hline
    \end{tabular} 
\end{table*}
\begin{table*}
    \centering
    \caption{Summary of the priors used in the MCMC sampling
procedure. The MCMC chains are constrained using flat priors or
normal priors on some of the fitting parameters. This table lists
the ranges of the flat priors and the central positions as well as
the scales of the normal priors ( format: center | scale ),
respectively.}
    \label{tab:priors}
    \begin{tabular}{ccccccccccc}
    \hline 
    & $\log_{10}(\rho_{\mathrm{s}})$ & $\log_{10}(\alpha)$ & $\log_{10}(r_{\mathrm{s}})$ & $\rho_0$ & $s_{\mathrm{e}}$ & $\log_{10}(r_{\mathrm{t}})$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ & $f_{\rm min}$ & $\sigma$\\ 
    \hline 
    Prior Type & None & Normal & Flat & None & None & Flat & Normal & Normal & Normal & Normal\\ 
    \hline 
    Prior Range & - & $\log_{10}(0.2)| 1.2$ & [0.1,5.0] & - & - & [0.1,5.0] & $\log_{10}(6.0) | 0.4$ & $\log_{10}(4.0) | 0.4$ & $0.15 | 0.21$ & $0.41 | 0.3$\\
    \hline
    \end{tabular} 
\end{table*}

The 1-$\sigma$ errors on the cluster positions are $\sim1.6\arcmin$
and the estimated purity of the catalog has a lower limit of 83\%
(probability that a detection corresponds to a real object). The
integrated Compton Y-parameter $Y_{500c}$ of each of the clusters
are also provided. Based on the scaling relation between $Y_{500c}$
and $M_{500c}$ \citep{ade2014planck} the mass estimates $M_{500c}$
of the clusters are calculated
\citep{adam2016planck,collaboration2016planck}. The PSZ2 union
cluster catalog is publicly available from the \fnurl{\textit{Planck
Legacy Archive}}{https://pla.esac.esa.int/pla/\# home}.

We restrict ourselves to the redshift range $0.03 \leq z \leq 0.33$
in order to mimic the redshift range used by
\citet{more2016detection}. Due to the large beam size of the Planck
satellite, the cluster positions as reported in the catalog may be
mis-centered from the true centers of the galaxy clusters. We perform
a visual inspection of Pan-STARRS images taken around the detected
galaxy clusters in order to locate the nearest, brightest cluster
galaxy (BCG). We regard the position of the BCG as the true cluster
location, under the assumption that the BCG is located at the true,
gravitational center. Due to this crude assumption, we additionally 
include the effects of a possible, remaining mis-centering of the 
cluster positions in our model for the two-dimensional correlation 
function (see Section~\ref{sec:mis-centering}). 
The final sample that we use consists of 596
galaxy clusters and is about an order of magnitude smaller compared
to the sample used in \citet{more2016detection}. The sample we use
in this paper has an average redshift of 0.177, and an average
cluster mass $M_{500c}$ of about $3.0 \cdot 10^{14}
h^{-1}$M$_{\sun}$. In Table~\ref{tab:cluster_catalogs} we compare
the main properties of the cluster catalog used in this work to that
used by \citet{more2016detection}. The sky positions of the clusters
can be found in Figure~\ref{fig:planck_fig} in
Appendix~\ref{sec:figures}.

\citet{kosyra2015environment} found no evidence for a significant
correlation between the density of Planck detections and the
weighted average noise of all Planck channels at $z<0.5$. Since we
restrict ourselves to $z<0.33$, we utilize the selection mask of the
PSZ2 union catalog in order to construct a random galaxy cluster
catalog, which is roughly one order of magnitude larger than the
original catalog. The redshifts of these random objects are drawn
from the parent cluster catalog in order to match the redshift
distribution of the original cluster catalog.

\subsection{Galaxy catalog}
\label{sec:galaxies}
The Panoramic Survey Telescope and Rapid Response System
(Pan-STARRS) is a wide-field astronomical imaging and data
processing facility operated by the University of Hawaii's Institute
for Astronomy \citep{kaiser2002pan,kaiser2010pan}. We use data from
the 3$\pi$ Steradian Survey carried out with this facility, which
was released as part of Data Release 1 (DR1). The survey covers the
entire sky north of $\delta=-31\degr$ (in ICRS coordinates) in five
broadband filters ($g_{\mathrm{P1}}, r_{\mathrm{P1}},
i_{\mathrm{P1}}, z_{\mathrm{P1}}, y_{\mathrm{P1}}$) with multiple
pointings. The mean 5$\sigma$ point source limiting sensitivities
amount to (23.3, 23.2, 23.1, 22.3, 21.4) magnitudes for the
individual bands, respectively.

For the visual inspection and centering of the clusters, we use the
Pan-Starrs $gri$ \textit{stack} images around each cluster position.
The galaxy catalog is obtained from the  \textit{StackObjectThin}
table, which is publicly available on the \fnurl{\textit{Barbara A.
Mikulski Archive for Space Telescopes}
(MAST)}{http://archive.stsci.edu/}. To select only objects detected
with acceptable precision we restrict our search to those objects
which have been flagged as \textit{BestDetection}s. We further
restrict the catalog to objects flagged as
\textit{PrimaryDetection}s in order to select unique objects. This
is necessary since the survey is divided into overlapping
\textit{projectioncells} and \textit{skycells}.

The magnitudes of the selected objects are then corrected for the
extinction caused by the dust present in the Milky Way. This is done
using the \fnurl{mwdust}{https://github.com/jobovy/mwdust} Python
module provided by \citet{bovy2016galactic}. The extinction
correction is performed using a dust map combining the measurements
of \citet{marshall2006modelling}, \citet{green2015three} and
\citet{drimmel2003three}. Only objects with an extinction corrected
$i_{\mathrm{P1}}$ band Kron magnitude brighter than 22.0 are
selected from the catalog. This results in a galaxy catalog
consisting out of 1'155'285'728 objects. Starting from this catalog
three different sub-catalogs named PS 21, PS 21.5 and PS 22 with a
survey depth of 21.0, 21.5 and 22.0 magnitudes, respectively are
constructed.

As mentioned in the description of the Pan-STARRS survey by
\citet{chambers2016pan} there is a significant variation in the
depth of the 3$\pi$ Steradian survey even on small scales. In order
to avoid choosing objects in shallow regions of the survey the
minimal observed Kron magnitude in the $i_{\mathrm{P1}}$ band in
each \textit{skycell} is recorded and only objects in skycells with
a minimal observed Kron magnitude of 21.0, 21.5 and 22.0 or brighter
are selected depending on the corresponding catalog. Since most of
the shallow regions lie in the galactic plane, we mask out the
region at low galactic latitudes $|b|<20\degr$. The resultant
HEALPix maps showing the excluded areas on the sky can be found in
Figure~\ref{fig:heal_map}. We further disregard objects in bad
pixel regions as indicated by the $i_{\mathrm{P1}}$ band
\textit{stack.mask} images.

At this point of the analysis, our object catalogs contain both
galaxies and stars. The 3$\pi$ Steradian Survey provides both the
Kron and PSF model based magnitudes for each object. These
magnitudes are expected to be similar for stars while the Kron
magnitudes are brighter for galaxies. Therefore, we flag all objects
with a value of $i_{\mathrm{P1,PSF}} - i_{\mathrm{P1,Kron}}< 0.05$
as stars \citep{farrow2013pan}. Despite this cut, bright, close-by
stars at magnitudes brighter than 13.5 tend to be classified as
extended objects \citep{chambers2016pan}. To avoid contamination of
the galaxy catalog due to such bright stars, we further remove all
objects with $i_{\mathrm{P1,PSF}} < 15.0$. Since there are very few
galaxies at such low magnitudes this does not introduce a selection
bias. We list the main characteristics of the galaxy catalogs we
have used in Table~\ref{tab:galaxy_catalogs}.

\subsection{Estimation of the spatial density profile}
\label{sec:estimators}

We use the Davis-Peebles estimator \citep{davis1983survey} to
compute the cross-correlation between our galaxy clusters and
galaxies. This estimator can be written as
\begin{equation}
\xi_{\rm 2D}(R) = \frac{\rm D_1D_2-R_1D_2}{\rm R_1D_2}\,
\end{equation}
where D$_1$D$_2$ and R$_1$D$_2$ are the normalized numbers of
cluster-galaxy pairs and cluster randoms-galaxy pairs at a given
comoving projected separation $R$. The subtraction of the signal
around random cluster positions gets rid of the uncorrelated pairs
and allows us to estimate the projected cross-correlation.

Given the flux limited galaxy catalog that we use, we expect to
observe more correlated galaxies in galaxy clusters that lie closer
to us, but with much fainter absolute magnitudes. To avoid
such biases with redshift of the clusters we restrict ourselves to
galaxies with absolute magnitudes brighter than a certain magnitude
limit, which depends on the depth of the used galaxy catalog. We
make the assumption that the galaxies reside at the redshift of the
cluster in question. The used magnitude limits are (-19.44, -18.94
and -18.44) for the catalogs PS 21, PS 21.5 and PS 22, respectively.

We use the functional form of \citet{diemer2014dependence} in order
to model our two-dimensional correlation function measurements. This
functional form consists of an inner Einasto profile and an outer
power law profile connected by a smooth transition
\begin{align}
\xi_{\rm 3D}(r) &= \rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r) + \rho_{\mathrm{out}}(r)\,, \\
\rho_{\mathrm{in}}(r)&=\rho_{\mathrm{s}}\exp\left( -\frac{2}{\alpha}\left[ \left( \frac{r}{r_{\mathrm{s}}}\right)^{\alpha}-1 \right] \right)\,,\\
\rho_{\mathrm{out}}(r)&=\rho_{\mathrm{0}}\left( \frac{r}{r_{\mathrm{out}}}\right)^{-s_{\mathrm{e}}} \,,\label{eq:model} \\
f_{\mathrm{trans}}(r)&=\left( 1+\left( \frac{r}{r_{\mathrm{t}}} \right)^{\beta} \right)^{-\gamma/ \beta}\,,
\label{eq:dk14}
\end{align}
where $r$ indicates the three-dimensional radial distance from the
halo center \citep{diemer2014dependence}. We model the
two-dimensional correlation function, $\xi_{\rm 2D}$ as an integral
over the three-dimensional correlation function
\begin{equation}
\xi_{\rm (2D,0)}(R)=\frac{1}{R_{\rm max}}\int^{R_{\mathrm{max}}}_0 \xi_{\rm 3D}(\sqrt{R^2+x^2}) dx \,
\label{eq:surface}
\end{equation}
where we adopt $R_{\mathrm{max}}=40$ $h^{-1}$Mpc for the maximum projection
length. Variations of this length do not change the location of the
splashback radius appreciably as tested in
\citet{more2016detection}. The functional form adopted in
Equation~\ref{eq:dk14} has nine model parameters,
$\rho_{\mathrm{s}}, \alpha, r_{\mathrm{s}}, r_{\mathrm{out}},
\rho_{\mathrm{0}}, s_{\mathrm{e}}, r_{\mathrm{t}}, \beta$ and
$\gamma$. Given the perfect degeneracy between the parameters
$r_{\mathrm{out}}$ and $\rho_{\rm o}$, we fix $r_{\mathrm{out}}=1.5$ $
h^{-1}$Mpc.

\paragraph{Modelling cluster mis-centering}
\label{sec:mis-centering}
Mis-centering of the central cluster positions can heavily affect 
the small-scale correlation function on scales smaller than the typical mis-centering distance. 
Although, the splashback radius is located at much larger scales, 
the change of the inner part of the correlation function can alter the model fit significantly. Mis-centering effects are not expected to change the location of the splashback feature but they can in principle decrease the significance of the evidence for the splashback feature \citep{baxter2017halo}.

The mass dependence of the exact mis-centering fractions are not
well understood and mis-centering effects are therefore difficult to model \citep{Skibba:2011, Hoshino:2015}. We follow the approach outlined in \citet{baxter2017halo} to take the effects of a possible mis-centering of a fraction of the cluster positions 
into account by modelling the influence on the two-dimensional correlation function.

Denoting the fraction of mis-centered clusters in the sample with $f_{\rm mis}$ we relate
the correlation function $\xi_{\rm 2D}(R)$ that is affected by the mis-centering of the clusters to the correlation function
unaffected by mis-centering $\xi_{\rm (2D,0)}(R)$ by

\begin{equation} 
\xi_{\rm 2D}(R) = (1-f_{\rm mis})\xi_{\rm (2D,0)}(R)+f_{\rm mis}\xi_{\rm (2D,mis)}(R)
\label{eq:full}
\end{equation}

where the contribution of the mis-centered clusters to the correlation function is captured by $\xi_{\rm (2D,mis)}$. 
We model the mis-centered component $\xi_{\rm (2D,mis)}$ as

\begin{equation}
\xi_{\rm (2D,mis)}(R)=\int_0^\infty \mathrm{d}R_{\rm mis} P(R_{\rm mis})\xi_{\rm (2D,mis)}(R|R_{\rm mis})
\end{equation}

where we assign a probability $P(R_{\rm mis})$ that a cluster is mis-centered by a comoving distance $R_{\rm mis}$.
The contribution $\xi_{\rm (2D,mis)}(R|R_{\rm mis})$ from a cluster mis-centered by a distance $R_{\rm mis}$ 
relates to the unaffected correlation function $\xi_{\rm (2D,0)}$ as

\begin{equation}
\xi_{\rm (2D,mis)}(R|R_{\rm mis})=\int_0^{2\pi}\frac{\mathrm{d}\theta}{2\pi}\xi_{\rm (2D,0)}\left(\sqrt{R^2+R_{\rm mis}^2+2RR_{\rm mis}\cos{\theta}}\right)
\end{equation}

according to \citet{yang2006weak} and \citet{johnston2007cross}. Following \citet{simet2016weak} we model the mis-centering probability 
$P(R_{\rm mis})$ as a Rayleigh distribution:

\begin{equation}
P(R_{\rm mis})=\frac{R_{\rm mis}}{\sigma^2}\exp{\left( -\frac{R_{\rm mis}^2}{2\sigma^2}\right)}
\end{equation}

Therefore, the mis-centered contribution is fully characterized by the two parameters $f_{\rm mis}$ and the witdh 
of the mis-centering probability distribution $\sigma$.
\newline

We cross-match our SZ selected cluster sample with the X-Ray selected ACCEPT cluster sample \citep{cavagnolo2009vizier}.
Assuming the ACCEPT clusters to lay at the true gravitational cluster centers we construct Gaussian priors
for the two mis-centering model parameters $f_{\rm mis}$ and $\sigma$ from the comparison of the 
two samples. The central values as well as the scales of the priors are listed in Table~\ref{tab:priors}.

Including mis-centering our model is described by ten model parameters.
We infer the posterior distributions of those parameters by fitting the model for the two-dimensional correlation
function affected by mis-centering to the measured two-dimensional correlation signal. 
We use the affine invariant Markov Chain Monte Carlo sampler of \citet{goodman2010ensemble} as
implemented in the parallel python package {\it emcee} by
\citet{foreman2013emcee}. We adopt priors similar to
\citet{more2016detection} on some of our parameters based on the
expectations of their values from numerical simulations, but double
the scales of the normal priors compared to their work (see
Table~\ref{tab:priors}). The central value for the prior on $\alpha$
is deduced from mass estimates \citep{gao2008redshift}, whereas the
central values on the priors of $\beta$ and $\gamma$ were
recommended by \citet{diemer2014dependence}.

The splashback radius for galaxy cluster scale halos is consistent
with the location of the steepest logarithmic slope of the density
profile. We estimate the steepest slope of both the two-dimensional
and the three-dimensional cross-correlation function. The two
locations of the steepest slope are expected to be different by
about 20\% for typical cluster halo parameters
\citep{diemer2014dependence, more2016detection}.

\subsection{Separation of red and blue galaxies}
\label{sec:Color}

We are also interested in measuring the cluster-galaxy
cross-correlations for the blue and the red galaxy samples
separately. We use a $g_{\mathrm{P1}}-r_{\mathrm{P1}}$ color cut
which varies with the redshift of the clusters in order to account
for the k-corrections, which cannot be computed individually for
each galaxy. We regard a galaxy as red if
$g_{\mathrm{P1}}-r_{\mathrm{P1}} > 0.65 + 3.04$ $(z_{\mathrm{clu}} -
0.1)$ and as blue otherwise. Depending upon the cluster redshift
under consideration the same galaxy may be considered red or blue. Our
method avoids the use of uncertain photometric redshifts to derive
k-corrections \citep[cf.][]{baxter2017halo}. We will study the
cross-correlations to derive the splashback radii for these galaxy
populations separately, as well as the fractional
contributions of the red and the blue galaxies to the total density profile
as a function of radius.

\section{Results}
\label{sec:Results}
\subsection{Cluster-galaxy cross-correlations}
The measurements of the two-dimensional cluster-galaxy
cross-correlations are shown as black points with error bars in the
left column of Figure~\ref{fig:2D_graphs}. The different rows
correspond to the three different absolute magnitude limits that we
have used to select all the galaxies when calculating the
cross-correlations. The cross-correlation signal is clearly detected
in all three measurements and the corresponding signal-to-noise
ratios of the measurements are listed in Table~\ref{tab:snr}.

We fit these measurements with our parametric model in Equation~\ref{eq:full}
and compute the posterior distribution of the model parameters 
as described in Section~\ref{sec:estimators}. The
median of the MCMC fit is indicated by the central solid line, while
the shaded area marks the 68\% credible interval for the fit. The
median values of the posterior distributions of the parameters along
with their 68\% confidence intervals are listed in
Table~\ref{tab:fit_parameters} along with their minimal, reduced
$\chi^2$ values. The two-dimensional posterior distributions for
each pair of parameters are shown in Figures~\ref{fig:corner_21},
\ref{fig:corner_21.5} and \ref{fig:corner_22} for the three absolute
magnitude limits, respectively.

\begin{figure}
    \includegraphics[scale=0.65]{2D_graphs.pdf}
\caption{The estimates of the two-dimensional cross-correlation
signals (black dots) are shown in the left column. The colored
curves show the two-dimensional model fits of the functional
form in Equation~\ref{eq:surface}. The magnitude limit applied to the galaxy
catalog is indicated in each row along with the signal-to-noise ratio (SNR). 
The vertical, shaded regions indicate the estimates of the locations of 
steepest slope of the profiles as estimated from the corresponding minima of the
derivative profiles, which are shown in the right column. For
comparison, the location of the $r_{\mathrm{200m}}$ radius as
calculated from the average cluster sample properties is indicated
by the black, dotted lines.}
   \label{fig:2D_graphs}
\end{figure}

\begin{figure}
    \includegraphics[scale=0.65]{3D_graphs.pdf}
\caption{The estimates of the three-dimensional cross-correlation
signals are shown in the left column. The colored curves show the
model fits of the functional form in Equation~\ref{eq:model}. The magnitude
limit applied on the galaxy catalog is indicated in each row along with 
the signal-to-noise ratio (SNR). The vertical, shaded regions indicate the 
estimates of the splashback radii as estimated from the corresponding minima 
of the derivative profiles, which are shown in the right column. For comparison, 
the location of the $r_{\mathrm{200m}}$ radius as calculated from the
average cluster sample properties is indicated by the black, dotted
lines.}
   \label{fig:3D_graphs} 
\end{figure}

\begin{table}
    \centering
    \caption{We list the signal to noise ratios (SNRs) of our
different estimates of the two-dimensional cross-correlation
obtained by using the different galaxy samples. For comparison: The SNR
achieved by \citet{more2016detection} is 263.0. It is much higher
due to size of the cluster sample used in their study.}
    \label{tab:snr}
    \begin{tabular}{cccc}
    \hline
    gal cat & PS 21 & PS 21.5 & PS 22 \\ 
    \hline
    \hline
   SNR & 42.4 & 43.3 & 30.9 \\
    \hline
    \end{tabular} 
\end{table}

\begin{table*}
    \centering
    \caption{We list our findings for the fitting parameters obtained from cross-correlating the galaxy cluster sample with the different galaxy catalogs. For each parameter estimate the median as well as the 16\% and 84\% quantiles of the posterior distribution are given. We also list the estimated locations of the steepening feature in the two-dimensional cross-correlation signal ($R_{\mathrm{sp}}^{\mathrm{2D}}$) as well as the three-dimensional splashback radius ($r_{\mathrm{sp}}^{\mathrm{3D}}$). In the last column the minimal, reduced $\chi^2$ value of the model fit is indicated. The two-dimensional posterior distributions of the fitting parameters are displayed in 
Figure~\ref{fig:corner_21} up to Figure~\ref{fig:cornerblue}.}
    \label{tab:fit_parameters}
    \begin{tabular}{cccccccccccccc}
    \hline 
gal cat & $\log_{10}(\rho_{\mathrm{s}})$ & $\log_{10}(\alpha)$ & $\log_{10}(r_{\mathrm{s}})$ & $\rho_{\mathrm{0}}$ & $s_{\mathrm{e}}$ & $\log_{10}(r_{\mathrm{t}})$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ & $R_{\rm sp}^{\rm 2D}$& $r_{\rm sp}^{\rm 3D}$& $\chi^2/\nu$ \\
\hline 
\hline 
PS 21 & $-0.92_{-0.56}^{+0.50}$ & $-1.19_{-0.21}^{+0.22}$ & $0.31_{-0.26}^{+0.29}$ & $0.0130_{-0.0083}^{+0.0062}$ & $0.72_{-0.22}^{+0.27}$ & $0.103_{-0.110}^{+0.056}$ & $0.85_{-0.36}^{+0.27}$ & $0.28_{-0.19}^{+0.12}$ & $1.35_{-0.12}^{+0.13}$ & $1.76_{-0.33}^{+0.29}$ & $0.511$ \\
\hline
PS 21.5 & $-0.91_{-0.48}^{+0.51}$ & $-0.98_{-0.18}^{+0.16}$ & $0.28_{-0.28}^{+0.26}$ & $0.0084_{-0.0060}^{+0.0041}$ & $0.53_{-0.23}^{+0.27}$ & $0.086_{-0.112}^{+0.051}$ & $0.78_{-0.34}^{+0.26}$ & $0.25_{-0.18}^{+0.12}$ & $1.30_{-0.10}^{+0.10}$ & $1.81_{-0.33}^{+0.28}$ & $0.178$ \\
\hline
PS 22 & $-0.99_{-0.46}^{+0.49}$ & $-0.90_{-0.17}^{+0.16}$ & $0.27_{-0.27}^{+0.26}$ & $0.0058_{-0.0052}^{+0.0027}$ & $0.43_{-0.29}^{+0.26}$ & $0.114_{-0.252}^{+0.076}$ & $0.71_{-0.38}^{+0.27}$ & $0.27_{-0.33}^{+0.16}$ & $1.33_{-0.17}^{+0.13}$ & $1.96_{-0.45}^{+0.37}$ & $0.264$ \\
\hline 
PS 21.5 (R) & $0.17_{-0.50}^{+1.03}$ & $-0.95_{-0.34}^{+0.44}$ & $-0.21_{-0.56}^{+0.26}$ & $0.0073_{-0.0084}^{+0.0040}$ & $0.59_{-0.38}^{+0.34}$ & $0.18_{-0.35}^{+0.22}$ & $0.52_{-0.41}^{+0.26}$ & $0.29_{-0.32}^{+0.23}$ & $1.20_{-0.12}^{+0.14}$ & $2.03_{-0.38}^{+0.38}$ & $1.194$ \\
\hline
PS 21.5 (B) & $-0.83_{-0.44}^{+0.49}$ & $-0.71_{-0.18}^{+0.19}$ & $0.24_{-0.30}^{+0.26}$ & $0.0112_{-0.0062}^{+0.0048}$ & $0.63_{-0.18}^{+0.23}$ & $0.28_{-0.20}^{+0.14}$ & $0.55_{-0.25}^{+0.16}$ & $0.44_{-0.33}^{+0.25}$ & $1.53_{-0.13}^{+0.13}$ & $2.30_{-0.23}^{+0.24}$ & $0.603$ \\
\hline
    \end{tabular} 
\end{table*}

\begin{figure*}
\centering{
  \includegraphics[scale=0.8]{derivatives.pdf}}
\caption{We show the distributions of the logarithmic derivatives of
the three-dimensional cross-correlation signals at the location of
the splashback radius. In the left panel the distributions of the
derivatives of the full profiles are shown, whereas only the inner
halo term (namely $\rho_{\mathrm{in}}f_{\mathrm{trans}}$) is
considered in the right panel.}
   \label{fig:derivatives} 
\end{figure*}
\begin{figure*}
\centering{
    \includegraphics[scale=0.8]{splashback.pdf}}
\caption{Shown are the posterior distributions of the inferred
locations of steepest slope of the two- and three dimensional
cross-correlation signals. On the left side the distributions of the
locations of the two-dimensional steepening feature
($R_{\mathrm{sp}}^{\mathrm{2D}}$) are shown, whereas the
distributions of the three-dimensional counterparts
($r_{\mathrm{sp}}^{\mathrm{3D}}$) are shown on the right. The
magnitude limit applied to the galaxy catalogs is indicated for each
distribution. Note that the colors of the distributions match with
the colors used in Figure~\ref{fig:2D_graphs} and
Figure~\ref{fig:3D_graphs}. For comparison, the location of the virial
radius $r_{\mathrm{200m}}$ as calculated from the average cluster
sample properties is indicated by the black, dotted lines.}
   \label{fig:splashback} 
\end{figure*}
\begin{figure}
    \includegraphics[scale=0.65]{color_separated.pdf}
\caption{\textit{Top row: } The two-dimensional cross-correlations
of the red and blue galaxy populations as inferred by
cross-correlating the cluster sample with the color-separated
subsamples that were extracted from the PS 21.5 galaxy catalog are
shown in the left panel, whereas the associated derivative profiles
are shown on the right. The vertical, shaded bands indicate the
locations of steepest slope of the cross-correlation signal as
inferred from the two subsamples, whereas the black, dashed lines
indicate the upper and lower bounds of the same feature but as
estimated from the full PS 21.5 galaxy catalog. \textit{Bottom row:
} We show the three-dimensional cross-correlations as
inferred by cross-correlating the cluster sample with the
color-separated galaxy subsamples, as well as the corresponding
splashback radii (indicated by the colored, vertical bands) and
their derivative profiles. Here, the black, dashed lines indicate
upper and lower bounds of the three-dimensional splashback radius
corresponding to the full PS 21.5 galaxy sample.}
   \label{fig:color_curve} 
\end{figure}

\begin{figure}
    \includegraphics[width= \columnwidth]{color_fraction.pdf}
\caption{Fractional contributions of the red and blue galaxy
populations to the total galaxy number density. We show the
locations of the splashback radii associated with the two subsamples
with the colored, vertical bands and the upper and lower bounds of
the splashback radius obtained from the full PS 21.5 catalog with
the black, dashed lines.}
   \label{fig:color_fraction} 
\end{figure}
The right panels in Figure~\ref{fig:2D_graphs} show the
corresponding analytical derivatives of the two-dimensional
cross-correlations and the 68\% confidence interval based on our
model fits. The logarithmic derivatives show a distinct steepening
feature at around $1.3-1.5~\mpch$. The figure shows that the
location of the steepest slope does not change appreciably when the
magnitude limit is changed, even though we use a sample which is one
magnitude deeper than $M_{\rm i}-5\log h=-19.44$. The 68\%
confidence interval of the location of the steepest slope is
indicated by the vertical, shaded region. We also show the location
of the virial radius $r_{\mathrm{200m}}$ based on the Planck SZ mass estimate 
as a black, dotted line in each panel.

We use the posterior distributions of our model parameters to infer
the three-dimensional cross-correlation and its logarithmic
derivative. These inferences along with the corresponding 68\%
confidence intervals are presented in Figure~\ref{fig:3D_graphs},
maintaining the same color scheme as in Figure~\ref{fig:2D_graphs}
for ease of comparison. The three-dimensional cross-correlations
also show significant steepening in each of the cases that we have
explored, reaching logarithmic derivatives steeper than $-3$. The
inferred 68\% confidence regions for the locations of the steepest
slope of the three-dimensional cross-correlations are shown with
vertical, shaded regions in each panel. The posterior
distributions of the locations of the steepest slope in the
two-dimensional and three-dimensional cross-correlations can be
found in the left hand and the right hand panels of
Figure~\ref{fig:splashback}, respectively. The estimates of the splashback radii
for each of the samples are listed in Table~\ref{tab:fit_parameters}
and our results show that the location of the splashback radius does
not depend upon the sample once we use galaxies fainter than $M_{\rm
i}-5\log h=-19.44$. Our measurements have an accuracy of $\sim$15\%.

Following \citet{baxter2017halo}, we also present the values of the
logarithmic derivatives at the location of the steepest slope for
the total three-dimensional cross-correlations, as well as those for
the inner halo term in the left and right hand panels of
Figure~\ref{fig:derivatives}, respectively. The logarithmic slope of the 
cross-correlation is significantly steeper than $-3$ at the location 
of the splashback radius, making it difficult to
be reproduced by classical fitting functions like the NFW profile,
which reach such slopes only asymptotically and even that only
without the presence of the outer 2-halo term. This provides
evidence for the existence of the splashback feature.

We perform a preliminary comparison of the measurements with
expectations from cold dark matter models. The average halo mass of
the PSZ2 clusters as estimated from the Sunyaev-Zeldovich signal
is $M_{\rm 500c}=3.0\times10^{14}$ $\msunh$. We convert this mass
estimate to $M_{\rm 200m}=6.2\times10^{14}$ $\msunh$ using the average
concentration mass relation of halos following
\citet{HuKravtsov:2003}. Given the average mass and redshift of our
cluster sample, we calculate the expected splashback radius to be
$1.89$ $\mpch$. We base this estimate on the fitting functions
presented in \citet{more2015splashback}. The splashback radius we
find for the three samples is consistent with this expectation,
although we can not rule out $\sim 18\%$ deviations in either directions,
given our large error bars.

Next we present our measurements of the projected and
three-dimensional cross-correlations of red and blue galaxies
satisfying $M_{i}-5\log h<-18.94$ with our SZ-selected cluster
sample in the top and bottom left hand panels of
Figure~\ref{fig:color_curve}, respectively. The shaded regions show
the 68\% confidence intervals from our fits. The vertical, shaded
bands with different colors indicate the 68\% confidence regions of
the locations of the steepest slope of the two- and the
three-dimensional cross-correlations. The black dashed lines show
these ranges for the entire galaxy sample without regard to color.
The best fit parameters as well as the inferred splashback radii are
listed in Table~\ref{tab:fit_parameters}. The right hand
panels show the corresponding inferred logarithmic derivatives. We
see that the red galaxies have a steeper cross-correlation profile
than the blue galaxies. Although there is a tendency for the red
galaxies to have a smaller splashback radius, the differences we see
are not statistically significant given the current errors. The
slopes of the three-dimensional cross-correlations reach values
steeper than -3 at the splashback radius.

Nevertheless, the fact that we detect the splashback radius for blue
galaxies is significant. The implication of this result is that
there needs to be a reasonable fraction of blue galaxies that fall
into the cluster and continue to stay blue even after reaching their
apocenters. Star forming galaxies in models which quench their star
formation on a timescale shorter than the orbital time scale, are
not expected to show the presence of the splashback radius. A
quantitative exploration of the implications is beyond the scope of
this work, but will be followed up in the future.

In Figure~\ref{fig:color_fraction}, we show the fractional
contributions of the red and blue galaxies to the total,
three-dimensional cross-correlation \footnote{The fractions are
obtained by performing an appropriate number density weighting.}.
The red galaxies dominate the central parts of the galaxy clusters
but become sub-dominant as we move further away from the centers of the 
clusters. We see a sharp increase of the fractional contribution of
red galaxies below the splashback radius. On scales larger than the
splashback radius, the populations are consistent with a constant
fraction of $\approx 55\%$ blue and $\approx 45\%$ red galaxies.

\section{Future work}
\label{sec:Future}

As it can be seen from Table~\ref{tab:snr}, the signal-to-noise
ratio of our measurement is lower when using the PS 22 catalog
compared to the other two estimates. This has two causes: Firstly,
the sky-coverage of the PS 22 catalog is $\approx$ 25\% lower than
for PS 21 and PS 21.5 since more regions had to be excluded due to
the survey depth being too low in those regions. Therefore, some
clusters from the PSZ2 catalog are missed when the PS 22 catalog is
exploited, which reduces the statistics. Secondly, as we consider
fainter galaxies, the contamination from background galaxies is
increased. This requires a better estimate of the uncorrelated
background component. A more precise estimation of the uncorrelated
background contamination would be possible by using a random galaxy
catalog in addition to the random cluster sample. This would allow
to use the more sophisticated Landy \& Szalay estimator
\citep{landy1993bias} to perform the background subtraction.

Another approach to increase the statistics of the measurements would be to increase the redshift range in which clusters are being considered. We chose $0.03 \leq z \leq 0.33$ in order to keep the analysis comparable to \citet{more2016detection}. However, this cut reduces the cluster sample size. Increasing the redshift range has its own limitations, though. It would be required to use a brighter magnitude limit for galaxies, which reduces the number of galaxies that can be used to infer the cross-correlation signal. This results in a trade-off and we could investigate the optimal redshift range. Alternatively, other cluster samples that do not rely on optical cluster finding such as Xray based surveys might serve as independent and larger cluster samples. 
Another plausible approach would be to consider a smaller region of
the sky, meaning also less clusters but with a deeper field of view,
such as in the case of the Hyper Suprime-Cam at Subaru Telescope,
which will survey $\approx 1400$ deg$^2$ of the sky and achieve a
depth of 26.2 magnitudes \citep{takada2010subaru}.

Lastly, but most importantly, the investigation of any systematics
which might originate from the SZ selection of the Planck clusters
is beyond the scope of the current work. We caution that there may
be residual systematics in the selection which could affect the
interpretation of our measurements. We will investigate such
selection systematics with the help of hydrodynamical simulations.

\section{Conclusions}
\label{sec:Conclusions}
The splashback radius of dark matter halos is a unique observational
probe of the mass accretion rate of dark matter halos. Although the
splashback radius has been well-characterized in simulations, the
observational evidence for the splashback radius presented using
optical cluster catalogs has come under intense scrutiny. In this
work, we tackle this issue by searching for evidence of the
splashback radius in galaxy clusters found by the Planck surveyor using
the thermal Sunyaev-Zeldovich effect. The use of this sample avoids
the circularity of using photometric galaxy catalogs to identify
clusters as well as to detect the splashback radius.

We cross-correlate these clusters with photometric galaxies from the
Pan-STARRS survey to obtain the two-dimensional cross-correlation
function and search for evidence for the splashback feature.
Additionally, we divided our galaxy catalog into two subsamples of
red and blue galaxies and investigated the cross-correlations of the
two subsamples with the clusters, separately.

Our main findings can be summarized as follows:
\begin{itemize}
\item We detect a clear signature of a steepening feature in the
cross-correlation of Planck SZ clusters with Pan-STARRS
galaxies. The steepest logarithmic slopes that we find in our cross-correlation
signals are steeper than $-3$, and would hence be poorly fit by the
NFW profile. We associate this feature with the splashback feature.
\item The location of the inferred splashback radius is $r_{\rm
sp}=1.81_{-0.33}^{+0.28}$ $\mpch$, which is consistent with expectations
from numerical simulations for
halos of an average mass $M_{\rm 500c}=3.0\times10^{14}\msunh$ at an
average redshift of $z=0.18$ in a collision-less dark matter Universe. 
However, given the errors we cannot
currently rule out $\sim18\%$ deviations from these expectations.
\item We find that the location of the steepest slope does not
strongly depend on the magnitude of the galaxy samples we use, once
we go fainter than $M_i-5\log h=-19.44$.
\item By separately studying the cross-correlation of red and blue
galaxies with the clusters, we present evidence for the presence of
the splashback feature in both populations. This implies that the
star formation of a sizable number of blue galaxies does not get
quenched during their first orbit through the halo.
\item We also detect a sharp increase in the fraction of red
galaxies associated with the splashback radius. 
\end{itemize}

Our curated galaxy catalogs from the Pan-STARRS survey for different
depths and the corresponding masks are available and can be send
upon request.

\section*{Acknowledgements}
DZ is grateful to Kavli IPMU for its hospitality during this
research project. SM is supported by a grant-in-aid by the Japan
Society for Promotion of Science (JSPS), grant number 16H01089.
The Pan-STARRS1 Surveys (PS1) and the PS1 public science archive
have been made possible through contributions by the Institute for
Astronomy, the University of Hawaii, the Pan-STARRS Project Office,
the Max-Planck Society and its participating institutes, the Max
Planck Institute for Astronomy, Heidelberg and the Max Planck
Institute for Extraterrestrial Physics, Garching, The Johns Hopkins
University, Durham University, the University of Edinburgh, the
Queen's University Belfast, the Harvard-Smithsonian Center for
Astrophysics, the Las Cumbres Observatory Global Telescope Network
Incorporated, the National Central University of Taiwan, the Space
Telescope Science Institute, the National Aeronautics and Space
Administration under Grant No. NNX08AR22G issued through the
Planetary Science Division of the NASA Science Mission Directorate,
the National Science Foundation Grant No. AST-1238877, the
University of Maryland, Eotvos Lorand University (ELTE), the Los
Alamos National Laboratory, and the Gordon and Betty Moore
Foundation.

Based on observations obtained with Planck
(http://www.esa.int/Planck), an ESA science mission with instruments
and contributions directly funded by ESA Member States, NASA, and
Canada.  Some of the results in this paper have been derived using
the HEALPix (K.M. Górski et al., 2005, ApJ, 622, p759) package

\bibliographystyle{mnras}
\bibliography{RSP_library}

\appendix

\section{Sky maps}
\label{sec:figures}
We present the sky locations of the SZ selected clusters from the PSZ2
catalog that were used in our study in Figure~\ref{fig:planck_fig}.
The purple areas mark the masked out regions as defined by the union
selection function of the PSZ2 catalog. The sky maps in
Figure~\ref{fig:heal_map} show the survey masks of our three galaxy
catalogs. All sky maps presented in this section use the ICRS
coordinate system.

\begin{figure}
\centering{
    \includegraphics[scale=0.8]{Planck_pres.png}}
\caption{Sky map showing the sky positions of the used clusters as
selected from the PSZ2 catalog. In total 596 clusters have been
selected. The purple areas mark the regions that are excluded by the
union survey selection function. Note that all clusters with
$\delta<-31\degr$ have been removed since this region is not covered
by the Pan-STARRS 3$\pi$ Steradian survey. The ICRS coordinate
system is used.}
    \label{fig:planck_fig} 
\end{figure}

\begin{figure*}
    \includegraphics[width= \textwidth]{heal_maps.png}
\caption{Sky maps displaying the masked out regions of the used
galaxy catalogs extracted from the Pan-STARRS 3$\pi$ Steradian
survey in purple. The ICRS coordinate system is used.}
   \label{fig:heal_map} 
\end{figure*}

\section{Cornerplots}
\label{sec:cornerplots}
In Figures \ref{fig:corner_21} to \ref{fig:cornerblue} we present
the two-dimensional posterior distributions for each pair of the
fitting parameters corresponding to the functional
form in Equation~\ref{eq:full}. We obtained the distributions by  using the
affine invariant Markov Chain Monte Carlo sampler of
\citet{goodman2010ensemble} as implemented in the parallel python
package {\it emcee} by \citet{foreman2013emcee}.
\begin{figure*}
    \includegraphics[width= \textwidth]{corner21.pdf}
\caption{The two-dimensional posterior distributions of each pair of
the fitting parameters corresponding to the functional
form in Equation~\ref{eq:full}. We cross-correlated PSZ2 galaxy clusters with
galaxies form the PS 21 galaxy catalog to establish this figure.}
   \label{fig:corner_21} 
\end{figure*}
\begin{figure*}
    \includegraphics[width= \textwidth]{corner215.pdf}
\caption{The two-dimensional posterior distributions of each pair of
the fitting parameters corresponding to the functional
form in Equation~\ref{eq:full}. We cross-correlated PSZ2 galaxy clusters with
galaxies form the PS 21.5 galaxy catalog to establish this figure.}
   \label{fig:corner_21.5} 
\end{figure*}
\begin{figure*}
    \includegraphics[width= \textwidth]{corner22.pdf}
\caption{The two-dimensional posterior distributions of each pair of
the fitting parameters corresponding to the functional
form in Equation~\ref{eq:full}. We cross-correlated PSZ2 galaxy clusters with
galaxies form the PS 22 galaxy catalog to establish this figure.}
   \label{fig:corner_22} 
\end{figure*}
\begin{figure*}
    \includegraphics[width= \textwidth]{cornerred.pdf}
\caption{The two-dimensional posterior distributions of each pair of
the fitting parameters corresponding to the functional
form in Equation~\ref{eq:full}. We cross-correlated PSZ2 galaxy clusters with
galaxies form the PS 21.5 galaxy catalog. Only the galaxies labeled
as red were used.}
   \label{fig:cornerred} 
\end{figure*}
\begin{figure*}
    \includegraphics[width= \textwidth]{cornerblue.pdf}
\caption{The two-dimensional posterior distributions of each pair of
the fitting parameters corresponding to the functional
form in Equation~\ref{eq:full}. We cross-correlated PSZ2 galaxy clusters with
galaxies form the PS 21 galaxy catalog. Only the galaxies labeled as
blue were used.}
   \label{fig:cornerblue} 
\end{figure*}

\label{lastpage}
\end{document}

### 2018-09-13 RSP_Report/RSP_Report.tex
Newly initialized repo

\documentclass[a4paper,fleqn,usenatbib]{mnras}
\usepackage{newtxtext,newtxmath}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{nccmath}
\usepackage[utf8]{inputenc}
\newcommand{\fhat}[1]{\expandafter\hat#1}
\newcommand{\fbar}[1]{\expandafter\bar#1}
\newcommand\fnurl[2]{%
  \href{#2}{#1}\footnote{\url{#2}}%
}

\title[Splashback radius in Pan-STARRS / Planck-SZ data]{Detection of the Splashback Radius by Cross-Correlation of Pan-STARRS and Planck-SZ data}

\author[D. Zürcher]{
D. Zürcher,$^{1}$\thanks{E-mail: dominikz@student.ethz.ch}
Supervisor: S. More,$^{2}$
Co-Supervisor: A. Refregier $^{3}$
\\
$^{1}$Department of Chemistry and Applied Biosciences, ETH Zurich, Vladimir-Prelog-Weg 1, 8093 Zurich, Switzerland\\
$^{2}$Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), \\ The University
of Tokyo, 5-1-5 Kashiwanoha, Kashiwa, Chiba 277-8583\\
$^{3}$Department of Physics, ETH Zurich, Wolfgang Pauli Strasse 27, 8093 Zurich, Switzerland\\
\\
Master's Thesis\\
In partial fulfillment of the requirements for the Master of Science ETH in Interdisciplinary Sciences 
}

% These dates will be filled out by the publisher
%\date{Accepted XXX. Received YYY; in original form ZZZ}

\pubyear{2018}

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.
\end{abstract}

\begin{keywords}
galaxies:clusters:general -- galaxies:halos -- methods:observational -- cosmology:dark matter -- cosmology:large-scale structure of Universe -- cosmology:observations
\end{keywords}

\section{Introduction}
Being one of the major and most promising probes in modern cosmology, the understanding of structure formation is getting a lot of attention from the observational, as well as from the theoretical side. In the standard framework of structure formation galaxies form via dissipative processes of baryons falling into the gravitational potential wells of dark matter clumps, so called halos\citep{rees1977cooling,white1978core,fall1980formation,blumenthal1984formation}. To infer constrains on the cosmological parameters from observations of the large scale galaxy distribution a profound understanding of the processes converting baryons into stars, as well as the growth rates of the halos is needed. Especially the scaling relation between the luminosity of galaxies and the dark matter halos associated with them have to be known in order to understand the process of structure formation \citep{kravtsov2004dark}. While the understanding of the scaling relation requires both; knowledge of the production of stars in the halos as well as the growth rate of the halos themselves, we only focus on the later in this work.

\citet{diemer2014dependence} studied the outskirts of the mass profiles of dark matter halos, which received only little attention in past studies compared to the inner regions of the halos. They showed, that classical fitting functions such as the Navarro-Frenk-White or the Einasto profile fail to describe the outer parts of the mass profiles as inferred from N-body simulations. Particularly they found a sharp steepening of the profile around the virial radius $r \approx R_{\mathrm{200m}}$, which is not modeled correctly by those fitting functions. They proposed a new fitting function consisting of an inner Einasto profile and an outer power law profile connected by a smooth transition
\begin{align}
\rho(r)=\rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r) + \rho_{\mathrm{out}}(r) 
\label{eq:model} \\
\rho_{\mathrm{in}}(r)=\rho_s\exp\left( -\frac{2}{\alpha}\left[ \left( \frac{r}{r_s}\right)^{\alpha}-1 \right] \right) \\
f_{\mathrm{trans}}(r)=\left( 1+\left( \frac{r}{r_t} \right)^{\beta} \right)^{-\gamma/ \beta} \\
\rho_{\mathrm{out}}(r)=\rho_0\left( \frac{r}{r_{out}}\right)^{-s_e}
\end{align}
where $r$ indicates the three dimensional radial distance from the halo center \citep{diemer2014dependence}.

In a follow up study \citet{adhikari2014splashback} proposed a simple theoretical model, which is able to accurately reproduce the sharp steepening found by Diemer and Kravtsov before. They argued that caustics arise in triaxial collapses of dark matter due to a pile up of the orbits of multiple particles at a similar radius. Such caustics most frequently appear close to the apocenters of the orbits due to the radial velocity being very small at that point, which causes the particles to spend a longer time there \citep{lithwick2011self}. The outermost caustic of a halo is associated with the first apoapsis of the most recently accreted particles. Those particles underwent a first collapse meaning that they passed through the center of the halo just once. This phenomenon is termed splashback effect and the radius corresponding to the density drop after the outermost caustic has been named splashback radius correspondingly. The location of the splashback radius depends mainly on the accretion rate $\Gamma$ of the halo, but shows a small redshift dependence due to the influence of $\Omega_{\mathrm{m}}$ . At lower redshifts $\Omega_{\mathrm{m}}$ decreases quickly leading to a smaller matter background density, which causes the halo to accrete less matter per time. Therefore the potential well deepens less quickly while the particles are traveling on their orbits and the splashback radius shifts towards larger radii. On the other hand, a higher accretion rate leads to a quicker deepening of the potential well of the halo, causing the splashback radius to occur at smaller radii. Therefore, the location of the splashback radius can be used to infer the accretion rate of a halo \citep{adhikari2014splashback}.

Motivated by the collapse model of a spherical top-hat over-density the outer boundary of a halo is usually defined as a radius $R_\Delta$ enclosing a region with an over-density of $\Delta$ or more with respect to a certain reference density $\Delta_{\mathrm{ref}}$, where the lower bound of the required over-density is given from the virialization criterion \citep{gunn1972infall}. However, \citet{diemer2013pseudo} found that such a boundary definition can lead to pseudo-evolution of the halo mass, meaning an apparent growth of the halo mass that is caused only by the evolution of the reference density with redshift and not by a physical accretion of mass onto the halo. Using simulations they showed that pseudo evolution accounts for nearly all of the apparent growth between $z=1$ and $0$ of galaxy-sized halos and can also account for a substantial fraction of the growth of cluster-sized halos \citep{diemer2013pseudo}. Further, \citet{diemer2013pseudo} realized that a new definition for the boundary of halos is required which must not suffer from pseudo-evolution. \citet{more2015splashback} proposed to use the newly discovered splashback radius as such an alternative definition. They found that depending on the accretion rate of the halo, the splashback radius may lay well beyond the commonly used virial radius. For slowly accreting halos the splashback radius is expected to occur at $\approx 0.8-1$ $R_{\mathrm{200m}}$ and at $\approx 1.5$ $R_{\mathrm{200m}}$ for quickly accreting halos \citep{more2015splashback}.

Using data from the Sloan Digital Sky Survey (SDSS) Data Release 8 (DR8) photometric galaxy catalog \citet{more2016detection} were able to confirm the existence of the splashback radius in observations. \citet{more2016detection} used galaxy clusters identified from the SDSS DR8 catalog by the redMaPPer algorithm \citep{rykoff2014redmapper,rozo2015redmapper}. The galaxy clusters were divided into two subsamples with the same redshift and mass distributions but different internal distributions of the galaxies within the halos. The same division has already been used by \citet{miyatake2016evidence} before and the samples have been shown to have different large-scale clustering amplitudes. By studying the stacked surface density profiles of the galaxy clusters \citet{more2016detection} detect a sharp steepening in both subsamples providing strong evidence for the existence of the splashback effect. Due to the splashback radius appearing at different locations in the two subsamples it was concluded that the two samples inherit different accretion rates implying different assembly histories. Therefore, halo assembly bias has been detected meaning that the clusters differ in their large scale distribution while having the same masses but different assembly histories \citep{more2016detection}.

\citet{more2016detection} compared their findings with simulations by utilizing the MultiDark-Planck II N-body simulation \citep{klypin2016multidark}. The comparison showed that the splashback radii detected for both subsamples are too small and also that the detected halo assembly bias signal is larger than expected from the simulation. Using the same N-body simulation once more \citet{more2016detection} explored several systematic effects which could lead to such deviations. However, none of the investigated, systematic effects can account for the discrepancies found in the data. However, \citet{more2016detection} noted that they cannot completely rule out the influence of effects originating from weak lensing as well as projections and optical cluster finding: The weak lensing signal is used in order to infer the masses $M_{\mathrm{200m}}$ and radii $R_{\mathrm{200m}}$ of the clusters. However, miscalibrations of the observable halo mass relations by weak lensing cannot be ruled out with today's data. In addition the weak lensing mass estimate is based solely on the projected mass distribution of the cluster. Therefore, different clusters might have different three-dimensional mass distributions although they possess the same weak lensing signal. Further, the identification of the central galaxy in a cluster is performed by the redMaPPer algorithm. This process of optical cluster finding is known to be affected by mis-centering. Mis-centering refers to the algorithm picking the wrong galaxy to be the central galaxy, or to the displacement of the central galaxy from the potential minimum of the cluster. Ruling out the influence of those systematic effects, with the discrepancy in the position of the splashback radius still remaining, would clear the path for new physical insights: Firstly, such a finding might point towards higher accretion rates of matter onto halos than expected from the standard cosmological model so far \citep{adhikari2016observing}. Alternatively, the introduction of anisotropic dark matter self-interactions into the dark matter model could account for the discrepancy while still obeying the bounds imposed by sub-halo evaporation \citep{kahlhoefer2013colliding}. Both explanations impose interesting challenges for the standard cosmological model and may point towards new physics\citep{more2016detection}.

In this work the influence of the effects mentioned above is removed by using an independent catalog of galaxy clusters, namely the second Planck Catalogue of Sunyaev-Zeldovich Sources (PSZ2), which is part of the 2015 data release of the Planck mission. The used catalog consists out of 1653 clusters detected by the Planck satellite  \citep{collaboration2016planck} by the use of the Sunyaev-Zeldovich effect. The estimate of the positions as well as the cluster masses are not affected by the effects mentioned above. As for the galaxies, the $3\upi$ Steradian survey, which is part of the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) Data Release 1 (DR1) is utilized \citep{chambers2016pan}. A similar analysis as in \citep{more2016detection} is carried out and new methods are being explored.

This paper is organized as follows: Section 2 starts by introducing the data, namely the cluster and the galaxy catalog as well as the methods that are used to derive the results which are presented in visual and tabular form and shortly discussed in Section 3. The results and their implications are discussed in great detail in Section 4 and finally we summarize our findings in Section 5 and provide a short outlook on what has yet to be done.

\section{Data and Methods}
In order to carry out the analysis described by \citet{more2016detection} two datasets are required. Firstly, a cluster catalog is needed. In \citet{more2016detection} this catalog is obtained from the SDSS DR8 sample using the RedMaPPer cluster finding algorithm. Here it is substituted by the larger PSZ2 catalog, which does not suffer from the systematic effects mentioned in the last section. On the other hand, the galaxy catalog, being the SDSS DR8 catalog in \citet{more2016detection}, is replaced by the larger and deeper Pan-STARRS DR1 catalog. In this section the used catalogs are described and the methods that are exploit are introduced.

\subsection{Cluster catalog}
\label{sec:clusters}
The dominant, baryonic component of a galaxy cluster is the hot, ionized  intra-cluster medium (ICM) which is trapped within the cluster. Via inverse Compton scattering the ICM can increase the energy of photons originating from the cosmic microwave background (CMB) that pass through the cluster. This effect is known as the thermal Sunyaev-Zeldovich (SZ) effect \citep{sunyaev1970small,sunyaev1980velocity}. The imprint of the effect on the CMB is best visible in the X-Ray range above 220 GHz. The High Frequency Instrument (HFI) of the Planck satellite is suited perfectly to observe the sky at this frequency \citep{collaboration2016planck}. Having, imaged the whole sky with an angular resolution and frequency coverage that was never achieved by any previous mission, the Planck satellite launched on May 14th 2009 was able to produce the largest SZ-selected sample of galaxy clusters yet. Being part of the 2015 Data Release of the Planck mission the second Planck Catalogue of Sunyaev-Zeldovich Sources (PSZ2) counts 1653 galaxy cluster detections, of which 1203 have been confirmed by cross-matching with other galaxy clusters from external data sets. The 67\% error radius of the cluster positions is $1.5\arcmin$ and the estimated purity of the catalog has a lower limit of 83\% (probability that a detection corresponds to a real object) \citep{adam2016planck,collaboration2016planck}. The PSZ2 catalog is publicly available from the \fnurl{\textit{Planck Legacy Archive}}{https://pla.esac.esa.int/pla/\# home}.

From the 1653 objects in the catalog only those with a redshift $0.03 \leq z \geq 0.33$ are chosen in order to reproduce the same conditions as in \citet{more2016detection}. As discussed extensively in \citet{more2016detection} already, galaxy cluster positions are often affected by misplacement. To avoid biases caused by such misplacements, images from the Pan-STARRS DR1 survey centered at the galaxy cluster positions are inspected visually. Assuming that the center of the cluster coincides with the position of the brightest cluster galaxy (BCG) the positions are adjusted manually. The final sample then consists out of 596 galaxy clusters which is small compared to a sample size of 8643 clusters as used by \citet{more2016detection}. The average redshift of the sample lies at 0.177 and the median at 0.179 whereas the average cluster mass amounts to $4.335 \cdot 10^{14} $M$_{\sun}$ with a median of $4.143 \cdot 10^{14} $M$_{\sun}$. Table~\ref{tab:cluster_catalogs} shows a comparison of the major properties of the two different cluster catalogs as used in this work and in \citet{more2016detection}. See Figure~\ref{fig:planck_fig} in Appendix~\ref{sec:figures} for a HEALPix map showing the cluster positions as well as the survey selection function \citep{2005ApJ...622..759G}.

Assuming the presence of a foreground and background population of clusters in the data a random cluster catalog is required to remove the effects of such a contamination (see Section~\ref{sec:estimators}). Exploiting the selection function of the PSZ2 survey which is also publicly available on the \fnurl{\textit{Planck Legacy Archive}}{https://pla.esac.esa.int/pla/\# home} a random galaxy sample composed of 8470 objects is constructed. The redshifts of the objects are drawn randomly from the redshifts of the actual cluster catalog in order to reproduce the same redshift distribution.

\begin{table}
    \centering
    \caption{Comparison of the PSZ2 cluster catalog against the RedMaPPer catalog used by \citet{more2016detection}. The values of the mass estimates $M_{\mathrm{500c}}$, $M_{\mathrm{200m}}$, redshifts $z$ and expected splashback radii $r^{\mathrm{3D,theo}}_{\mathrm{sp}}$ represent the catalog averages. The conversions of the masses as well as the calculation of the expected splashback radii was performed using the Python package COLOSSUS \citep{diemer2017colossus}.}
    \label{tab:cluster_catalogs} 
    \begin{tabular}{|c|c|c|c|}
    \hline 
    & RedMaPPer & PSZ2 & MCXC \\ 
    \hline 
    $z$ & 0.24 & 0.177 & \\ 
    \hline 
    \# objects & 8643 & 596 & \\ 
    \hline
    $M_{\mathrm{500c}}$ [$10^{14} $M$_{\sun}$] & 1.0 & 4.3 & \\ 
    \hline
    $M_{\mathrm{200m}}$ [$10^{14} $M$_{\sun}$] & 1.8 & 8.6 & \\ 
    \hline
    $r^{\mathrm{3D,theo}}_{\mathrm{sp}}$ [h$^{-1}$ Mpc] & 1.10 & 1.73 & \\ 
    \hline
    \end{tabular} 
\end{table}

\subsection{Galaxy catalog}
\label{sec:galaxies}
The Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) is a wide-field astronomical imaging and data processing facility operated by the University of Hawaii's Institute for Astronomy \citep{kaiser2002pan,kaiser2010pan}. The data for the Data Release 1 (DR1) was gathered using a single 1.8 meter dish telescope equipped with a 1.4 gigapixel camera, which is located on Maui. We use the 3$\upi$ Steradian Survey which is part of the DR1. The survey covers the sky north of $\delta=-31\degr$ (ICRS) in five broadband filters ($g_{\mathrm{P1}}, r_{\mathrm{P1}}, i_{\mathrm{P1}}, z_{\mathrm{P1}}, y_{\mathrm{P1}}$). In order to obtain deeper images the survey stacks pictures taken from 2009-06-02 until 2014-03-31. The achieved, band-dependent depth amounts to (23.3, 23.2, 23.1, 22.3, 21.4) magnitudes for the individual bands, respectively. Further, the magnitude of the objects is determined up to a standard deviation of 7-12 mmag depending on the band and the position of the objects is measured with a standard deviation of $\Delta ra=2.3\arcsec$ and $\Delta \delta=1.7\arcsec$. The Pan-STARRS survey uses a modification of the Budavari rings tessellation pattern to organize the data. The sky is split into rings with their middles spaced $4 \degr$ apart in declination space. Each ring is then divided into \textit{projectioncells} where the number of \textit{projectioncells} in each ring varies with declination. Notice that the \textit{projectioncells} overlap at some points. Having a size of roughly $4\degr$x$4\degr$, the \textit{projectioncells} are very large and inconvenient for the end user to handle. Therefore, they are further subdivided into 10x10 \textit{skycells}, each with a size of roughly $0.4\degr$x$0.4\degr$ which overlap by $60\arcsec$ (120 pixels) on each side in order to prevent splitting of objects. The survey has a global pixel scale of $0.25\arcsec$ \citep{chambers2016pan}.

The 3$\upi$ Steradian Survey consists out of multiple data products and not all of them are used in this work. Image-wise, we use the polychromatic \textit{stack} images to perform the visual correction of the cluster center locations and the \textit{stack.mask} images to disregard objects laying in bad pixel regions. Data-wise, we extract the galaxy catalog from the \textit{StackObjectThin} table. The data table is publicly available on the \fnurl{\textit{Barbara A. Mikulski Archive for Space Telescopes} (MAST)}{http://archive.stsci.edu/}. We select only objects with the \textit{BestDetection} flag attached to them indicating that they have been detected with acceptable accuracy. Due to the splitting of the survey in \textit{projectioncells} and \textit{skycells} and the induced overlapping of the cells, objects may show up in multiple cells and are therefore listed multiple times in the data table. Therefore, we keep only objects with the \textit{PrimaryDetection} flag attached which avoids counting the same object multiple times.

The magnitudes of the selected objects are then corrected for the extinction caused by the dust present in the Milky Way. This is done using the \fnurl{mwdust}{https://github.com/jobovy/mwdust} Python module provided by \citet{bovy2016galactic}. The extinction correction is performed using a dust map combining the measurements of \citet{marshall2006modelling}, \citet{green2015three} and \citet{drimmel2003three}. Only objects with an extinction corrected magnitude up to 22.0 as measured in the $i_{P1}$ band are selected from the catalog. After this procedure, the extracted galaxy counts exactly 1'155'285'728 objects. Starting from this catalog three different sub-catalogs named PS 21, PS 21.5 and PS 22 with a survey depth of 21.0, 21.5 and 22.0 magnitude, respectively are constructed.

As mentioned in the description of the Pan-STARRS survey by \citet{chambers2016pan} there is a significant variation in the depth of the 3$\upi$ Steradian survey even on small scales. In order to avoid choosing objects in shallow regions of the survey the minimal observed Kron magnitude in the $i_{\mathrm{P1}}$ band in each \textit{skycell} is recorded and only objects in skycells with a minimal observed Kron magnitude of 21.0, 21.5 and 22.0 or higher are selected depending on the corresponding catalog. Since most of the shallow regions lay in the galactic plane the whole region with $-20.0 < b < 20.0$ in galactic coordinates is excluded on top of that. The HEALPix maps showing the excluded areas on the sky are included in Appendix~\ref{sec:heal_maps}. To disregard objects laying in bad pixel regions caused for example by nearby, bright stars or camera artifacts a masking procedure is performed using the \textit{stack.mask} objects.

Since the Pan-STARRS survey contains galaxies and stars alike a star-galaxy separation has to be applied. Therefore, a simple cut in the PSF - Kron magnitude space in the $i_{\mathrm{P1}}$ band is used. All objects with a value of $i_{\mathrm{P1,PSF}} - i_{\mathrm{P1,Kron}}> 0.05$ are considered to be galaxies and all other objects are disregarded. As pointed out by \citet{farrow2013pan} this separation does a fairly good job. Bright, close-by stars tend to be classified as extended objects, therefore stars are often classified as galaxies by such a selection at magnitudes below 13.5 \citep{chambers2016pan}. To avoid contamination of the data with bright stars all objects with a $i_{\mathrm{P1,PSF}} < 15.0$ are disregarded. Since there are basically no galaxies at such low magnitudes this does not introduce a selection bias. In Table~\ref{tab:galaxy_catalogs} the major properties of the extracted galaxy catalogs are summarized and compared to the SDSS catalog as used in \citet{more2016detection}.

%(describe properties / expectations)
%Catalogs are publicly available???

Since it has to be assumed that there is a contamination by foreground and background galaxies present a random galaxy catalog is required (see Section~\ref{sec:estimators}). The random catalog is created by uniformly generating objects on the unit sphere and disregarding all objects laying in those regions that have been excluded in the galaxy catalog as well. Therefore, for each galaxy catalog a corresponding random catalog is generated.

\begin{table*}
    \centering
    \caption{Summary and comparison of the properties of the galaxy catalogs used in this work as well as the SDSS catalog used in \citet{more2016detection}.}
    \label{tab:galaxy_catalogs}
    \begin{tabular}{|c|c|c|c|c|}
    \hline 
    & SDSS & PS 21 & PS 21.5 & PS 22 \\ 
    \hline 
    depth [mag] & 21.43 & 21.00 & 21.50 & 22.00\\ 
    \hline 
    eff. area [deg$^2$] & $\approx$ 10'000 & 19'515 & 20'586 & 15'689\\ 
    \hline 
    \# objects & 57'181'113 & 87'985'151 & 123'188'529 & 105'809'113 \\
    \hline
    objects/deg$^2$ & 5718 & 4509 & 5984 & 6744\\ 
    \hline
    \end{tabular} 
\end{table*}

\subsection{Estimation of the spatial density profile}
\label{sec:estimators}
The splashback radius manifests itself as a sharp steepening in the spatial density profile of a dark matter halo. Unfortunately, such profiles are not directly accessible by todays measurements. However, in the standard paradigm of structure formation it is assumed that galaxies track the underlying dark matter distribution since they form from baryonic matter falling into the potential wells created by the dark matter \citep{rees1977cooling,white1978core,fall1980formation,blumenthal1984formation}. Therefore, I shall use the radial galaxy distribution as a proxy for the dark matter distribution of a halo. A further complication arises by the fact that only the projected galaxy distribution within a halo is accessible as a projection of the three dimensional distribution onto a projection plane perpendicular to the line of sight. Therefore, the three dimensional model given in Equation~\ref{eq:model} needs to be integrated along the line of sight in order to obtain a model for the surface density profile:
\begin{equation}
\xi(R)=2\int^{x_{max}}_0 \rho(\sqrt{R^2+x^2}) dx 
\label{eq:surface}
\end{equation}
where we adopt $x_{\mathrm{max}}=40 $ h$^{-1}$Mpc for the maximum projection length as suggested by \citet{more2016detection}. The surface density profile $\xi(R)$ depends on the projected radius $R$, which is defined as the projection of the three dimensional, radial distance from the cluster center onto the projection plane.

To obtain a measurement of the surface density profile from the data the cluster catalog is cross-correlated with the galaxy catalog. In order for a galaxy to be associated with a certain cluster the projected radial distance from the cluster center position must be  $\leq$ 10 h$^{-1}$ Mpc. Notice that since the clusters in the catalog span a large redshift range there will be a selection bias originating from systematically detecting more faint galaxies in low redshift clusters. To avoid such systematics a galaxy's magnitude m$_{\mathrm{gal}}$ must fulfill the following constraint to be considered as being part of a cluster at redshift z$_{\mathrm{clu}}$:
\begin{equation}
m_{\mathrm{gal}} < m_{\mathrm{lim}} - 5 \log_{10} \left( \frac{D(z_{\mathrm{clu}})}{D(z_{\mathrm{max}})} \frac{1+z_{\mathrm{max}}}{1+z_{\mathrm{clu}}}  \right)
\label{eq:constraint}
\end{equation}
where the function $D(z)$ determines the comoving distance to an object at redshift $z$. Further $z_{\mathrm{max}}$ is the maximal redshift of the cluster catalog (0.33 in our case) and $m_{\mathrm{lim}}$ indicates the depth of the galaxy catalog in consideration in magnitudes (being 21.0, 21.5 and 22.0, respectively) \citep{more2016detection}.
The assignment of the galaxies to the clusters requires to perform a range search which is done using the Python module \fnurl{splashpipe}{https://github.com/surhudm/splashpipe} which exploits a k-d tree algorithm to do so . The assigned galaxies are then binned into 8 equally spaced radial bins ranging from 0.1 h$^{-1}$ Mpc to 10 h$^{-1}$ Mpc.

We expect a correlation between clusters and galaxies if they are at the same redshift. However, at the same time it has to be assumed that there will also be a population of uncorrelated galaxies present consisting of higher or lower redshift galaxies that are not associated with the cluster in question. The same holds true for the cluster population as well. Such contaminations can be estimated by the use of random catalogs modeling the uncorrelated component of the two-point cross-correlation function. Following the discussion outlined in \citet{kerscher2000comparison} We shall introduce how the two-point correlation function can be estimated taking into consideration the contaminations mentioned above.

Let us define a counting function $P_{(X,Y)}(D)$, that counts how many objects from the catalog $Y$ can be found at a distance $D$ from any object in catalog $X$ (or vice versa)
\begin{equation}
P_{(X,Y)}(D)=\sum_{x \in X} \sum_{y \in Y} \Phi_D(x,y)
\end{equation}
where 
\begin{equation}
  \Phi_D(x,y) = \left.
  \begin{cases}
    0, & \text{for } d(x,y)<D-\Delta \\
    1, & \text{for }  D-\Delta \leq d(x,y) \leq D+\Delta \\
    0, & \text{for } d(x,y)>D+\Delta
  \end{cases}\right.
\end{equation}
with $d(x,y)$ being the separation between the two objects $x$ and $y$. Since, $X \neq Y$ holds at all times in this work (no auto-correlations of catalogs considered) the normalized counting function can be defined as 
\begin{equation}
P^{\mathrm{N}}_{(X,Y)}(D)=\frac{P_{(X,Y)}(D)}{N_X N_Y}
\end{equation}
with $N_X$ and $N_Y$ being the total number of objects residing in the catalogs $X$ and $Y$, respectively. 
Recalling that we would like to cross-correlate clusters with galaxies we identify one of the catalogs with the cluster catalog (say $X$) and the other one with the galaxy catalog (say $Y$). Further, we note that we are considering the projected, radial separation of objects. Therefore, let us replace the general separation $D$ by the projected, radial distance $R$. For either of the two catalogs we have two choices at hand; namely the actual catalog (further denoted as D) and the corresponding random catalog (further denoted as R) leading to four different counting functions that cross-correlate all the different catalogs; $P^{\mathrm{N}}_{\mathrm{(D,D)}}(R)$,$P^{\mathrm{N}}_{\mathrm{(D,R)}}(R)$,$P^{\mathrm{N}}_{\mathrm{(R,D)}}(R)$,$P^N_{\mathrm{(R,R)}}(R)$.
Starting from those normalized counting functions estimators of the two-point correlation function can be constructed. With the two-point correlation function of galaxies being one of the main statistical tools in cosmology, a vast number of such estimators can be found in the literature. We use the Davis \& Peebles estimator ($\fhat{\xi_{\mathrm{DP}}(r)}$ ; \citep{davis1983survey} ; DP) which corrects only for the contamination stemming from the uncorrelated galaxies and the more sophisticated Landy \& Szalay estimatior ($\fhat{\xi_{\mathrm{LS}}(r)}$ ; \citep{landy1993bias} ; LS) which also exploits the random cluster catalog in order to remove the contamination from back- and foreground clusters as well
\begin{align}
\fhat{\xi_{\mathrm{DP}}(R)}=\frac{P^{\mathrm{N}}_{\mathrm{(D,D)}}(R)}{P^{\mathrm{N}}_{\mathrm{(D,R)}}(R)}-1\\
\fhat{\xi_{\mathrm{LS}}(R)}=\frac{P^{\mathrm{N}}_{\mathrm{(D,D)}}(R)-P^{\mathrm{N}}_{\mathrm{(D,R)}}(R)-P^{\mathrm{N}}_{\mathrm{(R,D)}}(R)+P^{\mathrm{N}}_{\mathrm{(R,R)}}(R)}{P^{\mathrm{N}}_{\mathrm{(R,R)}}(R)}
\end{align}
Hence, we have constructed two estimators for the surface density $\xi(R)$. To estimate the covariance of the calculated surface density profile a jackknife re-sampling approach is taken \citep{efron1982jackknife}. The clusters are subdivided into 21 different jackknife samples. The random clusters are subdivided in the same fashion. In each jackknife bin the redshifts of the random clusters are drawn from the redshifts of the actual clusters in that bin such that the random clusters in each bin inherit the same redshift distribution as their real counterparts. Doing so we construct a set of 30 jackknife estimates for the surface density function
\begin{equation}
\fhat{\xi^{\mathrm{Jack}}_j (R)}=\frac{1}{n-1}\sum^n_{i=1,i\neq j} \fhat{\xi_i (R)}
\end{equation}
where $j \in \{1,..,30\}$ and $n=30$. The $\fhat{\xi_i (R)}$ are the estimates of the surface density function as inferred when considering only the clusters in the jackknife sample $i$. The average $\fbar{\xi(R)}$ and the covariance $\mathrm{Cov}(R_1,R_2)$ of the surface density function are then constructed as
\begin{equation}
\fbar{\xi(R)}=\frac{1}{n}\sum_{j=1}^n \fhat{\xi^{\mathrm{Jack}}_j (R)}
\end{equation}
and 
\begin{equation}
\mathrm{Cov}(R_1,R_2)=\frac{n-1}{n}\sum_{j=1}^n (\fhat{\xi^{\mathrm{Jack}}_j (R_1)} - \fbar{\xi(R_1)}) \cdot (\fhat{\xi^{\mathrm{Jack}}_j (R_2)} - \fbar{\xi(R_2)}).
\end{equation}
Exploiting this analysis for each one of the three catalogs with depth 21.0, 21.5 and 22.0 magnitude, respectively we obtain six different estimates of the surface density distribution in total.

\subsection{Locating the splashback radius}
\label{sec:MCMC}
Having an estimate of the surface density function at hand we now turn to the problem of inferring the location of the splashback radius. With that goal in mind we fit the model for the surface density profile given in Equation~\ref{eq:surface} to the estimated profile. Fixing $r_{\mathrm{out}}=1.5 $ h$^{-1}$Mpc due to its full degeneracy with the parameter $\rho_0$ this task involves fitting a model with eight free parameters namely $\rho_s, \alpha, r_s, \rho_0, s_e, r_t, \beta$ and $\gamma$. 
Performing a simple Least Square fit we obtain the set of parameter values as shown in Table~\ref{tab:inits}. We use the Python implementation \textit{emcee} \citep{foreman2013emcee} of the affine invariant Markov Chain Monte Carlo (MCMC) sampler of Goodman \& Weare to sample from the posterior distributions of the model parameters \citep{goodman2010ensemble}. Twenty MCMC chains are being run for 50'000 iterations each where the Least Square fitting parameters listed in Table~\ref{tab:inits} serve as their initial parameters. 
The priors constraining the MCMC chains during the runs are listed in Table~\ref{tab:priors}. We adapt similar priors as in the work of \citet{more2016detection} but increase the scales of the normal priors allowing the chains to explore a larger fraction of the parameter space.
Several statistical tests are performed to confirm the convergence of the MCMC chains. The tests and their results are presented in Appendix~\ref{sec:convergence}. Given the posterior distributions of the model parameters an estimate of the three dimensional model as given in Equation~\ref{eq:model} can be constructed as well. 
Being located at the steepest logarithmic slope of the density profile two different estimates of the splashback radius can be inferred; a projected splashback radius $R_{\mathrm{sp}}^{\mathrm{2D}}$ is obtained from the location of the steepening feature in the two dimensional surface density and a three dimensional, physical splashback radius $r^{\mathrm{3D}}_{\mathrm{sp}}$ is inferred from the three dimensional density profile alike. Note that according to \citet{diemer2014dependence} those two estimates are expected to differ from each other.
Since the analytical models are known we derive the analytical expressions of the projected as well as the three dimensional logarithmic derivatives of the models using simple algebra to be
\begin{align}
\frac{dlog(\xi )}{dlog(R)}=\frac{-1}{\int_0^{z_{\mathrm{max}}}\rho (y)dz} \int_0^{z_{\mathrm{max}}}\frac{R^2}{y}\left[ h(y)+ \frac{s_e}{y}\rho_{\mathrm{out}}(y)\right]dz   \\
\frac{dlog(\rho)}{dlog(r)}=-\frac{r}{\rho(r)}h(r)-s_e\frac{\rho_{\mathrm{out}}(r)}{\rho(r)}
\end{align}
where
\begin{align}
y(R,z)=\sqrt{R^2+z^2} \\
h(x)=\rho_{\mathrm{in}}(x) \cdot f_{\mathrm{trans}}(x) \left( 2\frac{x^{\alpha -1}}{r_s^{\alpha }}+\gamma \frac{x^{\beta -1}}{r_t^{\beta }}\frac{1}{1+\left( \frac{x}{r_t}\right)^{\beta }} \right)
\end{align}
and interpret their minima as the location of the projected and three dimensional splashback radius, respectively.

\begin{table*}
    \centering
    \caption{Illustration of the fitting parameters for the different surface density profiles obtained using a Least Square fit. These values also serve as the initial parameters for the MCMC chains.}
    \label{tab:inits}
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
    \hline 
    clu & depth & estimator& $\log_{10}(\rho_s)$ & $\log_{10}(\alpha)$ & $\log_{10}(r_s)$ & $\log_{10}(\rho_0)$ & $s_e$ & $\log_{10}(r_t)$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ \\ 
    \hline 
    PSZ2 & 21.0 & DP & -2.3 & -1.00 & 0.69 & -2.91 & 0.73 & 0.16 & 0.51 & 0.48 \\ 
    \hline 
     PSZ2 & 21.0 & LS & -1.23 & -1.03 & 0.69 & -1.76 & 0.84 & 0.15 & 0.53 & 0.47\\ 
    \hline 
    PSZ2 & 21.5 & DP & -2.21 & -1.00 & 0.578 & -2.23 & 1.05 & 0.122 & 0.648 & 0.49\\ 
    \hline 
    PSZ2 & 21.5 & LS & -1.34 & -1.04 & 0.69 & -1.37 & 1.04 & 0.13 & 0.63 & 0.51\\ 
    \hline 
    PSZ2 & 22.0 & DP & -2.43 & -1.03 & 0.69 & -2.80 & 0.61 & -0.019 & 0.72 & 0.21\\
    \hline
    PSZ2 & 22.0 & LS & -1.36 & 1.06 & 0.69 & -1.31 & 0.16 & -0.024 & 0.77 & 0.16\\
    \hline
    MCXC & 21.0 & LS & -2.37 & -1.08 & 0.56 & -2.52 & 1.52 & 0.0049 & 0.51 & 0.41 \\
    \hline
    MCXC & 21.5 & LS & -2.73 & -1.06 & 0.69 & -2.33 & 1.74 & 0.16 & 0.42 & 0.79\\
    \hline
    MCXC & 22.0 & LS & -2.18 & -0.99 & 0.39 & -2.89 & 0.99 & -0.042 & 0.56 & 0.35\\
    \hline
    \end{tabular} 
\end{table*}

\begin{table*}
    \centering
    \caption{Summary of the priors used in the MCMC sampling procedure. The MCMC chains are constrained using flat priors or normal priors on some of the fitting parameters. The table lists the ranges of the flat priors and the scales of the normal priors, respectively.}
    \label{tab:priors}
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
    \hline 
    & $\log_{10}(\rho_s)$ & $\log_{10}(\alpha)$ & $\log_{10}(r_s)$ & $\log_{10}(\rho_0)$ & $s_e$ & $\log_{10}(r_t)$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ \\ 
    \hline 
    %$\mathrm{Var}_{\mathrm{init}}$ & 0.8 & 0.030 & 0.058 & $4.7\cdot10^{-6}$ & $3.8\cdot10{-7}$ & 0.0088 & 0.25 & 0.0078\\ 
    %\hline 
    Prior Type & None & Normal & Flat & None & None & Flat & Normal & Normal\\ 
    \hline 
    Prior Range & - & 1.2 & [0.1,5.0] & - & - & [0.1,5.0] & 0.4 & 0.4\\
    \hline
    \end{tabular} 
\end{table*}

\subsection{Deprojection}
\label{sec:Deprojection}
At the time being, there is usually no spectroscopic data available for the single galaxies residing in a cluster. Therefore, the spatial mass distribution is normally not directly recoverable from the projected, angular distribution as it is measured in observations. We overcome this shortcoming by using a background-subtraction procedure and by integrating our mass density profile along the line of sight such that it can describe a projected distribution as well. However, in this procedure we need to assume spherical symmetry of the cluster and the fitting of the two dimensional profile is computationally much more involved than the direct fitting of the three dimensional density profile would be. Therefore, as an alternative approach, we follow the method outlined in eisenstein2003deprojecting to directly recover the spatial distribution of the galaxies in the cluster without having to perform the troublesome two dimensional fitting procedure. Generally speaking the deprojection algorithm weights the galaxy counts in the different radial bins with a function depending on the chosen window function. The procedure is outlined in detail in Section~\ref{sec:deprojection_math}. Due to lack of statistics we did not take masking and boundary effects into account but the procedure to do so is also described in Section~\ref{sec:deprojection_math}. Instead of the 8 radial bins used in the standard procedure 50 bins are being used in the deprojection method since it has been found that the increasingly faster increase in number density with radius at large radii can lead to unphysical, negative galaxy counts if the binsize is too large. Only when the binsize is chosen to be sufficiently small such that this effect does not occur physical results can be obtained.

\subsection{Separation of red and blue galaxies (incomplete)}
\label{sec:Color}
describe what is done and to which purpose
not exactly clear

\section{Results}
\subsection{Density Profiles}

The top row of Figure~\ref{fig:2D_graphs} displays the calculated estimates of the surface density profiles. The three panels correspond to different survey depths, where the depth increases from left to right. Each panel shows two different sets of data-points; one of which is constructed using the DP estimator and the other one by exploiting the more sophisticated LS estimator. The signal to noise ratios (SNRs) of the different sets of data points are listed in Table~\ref{tab:snr}. We note that the amplitude of the profile is arbitrary and scales with the number of clusters and galaxies in the sample. Therefore, only the shape of the profile carries physical information. The projected model as given in Equation~\ref{eq:surface} is fitted to each set of data-points by using the MCMC procedure as outlined in Section~\ref{sec:MCMC}. Several tests were ran to assess the convergence of the MCMC chains. The specific tests are outlined in Section~\ref{sec:convergence}. The solid lines indicate the median of the fits whereas the lower and upper dashed curves correspond to the 16\% and 84\% quantiles, respectively. As the surface density drops further away from the center of the cluster the goodness of the fits decreases. We note that the shapes of all the profiles are similar and that they do not vary significantly with survey depth or the choice of the estimator. In the bottom row of Figure~\ref{fig:2D_graphs} the analytical derivatives of the two dimensional model fits shown in the upper row are displayed. The corresponding vertical lines indicate the radius of the minimal derivative where once more the solid line is located at the median radius and the dashed lines indicate the 16\% and 84\% quantiles, respectively. The values of the parameters of the fitted model, namely $\rho_s, \alpha, r_s, s_e, \rho_0, r_t, \beta$ and $\gamma$ as well as the reduced $\chi^2$ values are listed in Table~\ref{tab:fit_parameters}.

Having obtained the fitting parameters from the two dimensional model fit, the three dimensional density profile is easily obtained by inserting the parameters into the model described by Equation~\ref{eq:model}. As such, the top row in Figure~\ref{fig:3D_graphs} displays the fitted three dimensional profiles. The colors of the profiles shown in Figure~\ref{fig:3D_graphs} correspond to the colors used in Figure~\ref{fig:2D_graphs}. As in Figure~\ref{fig:2D_graphs} the bottom row shows the corresponding derivatives of the upper profiles and the locations of the minima are highlighted. Again, solid lines indicate the median and the dashed lines show the 16\% and the 84\% quantiles. We notice the similarity of the profile shapes.

\begin{figure*}
    \includegraphics[width= \textwidth]{2D_graphs.pdf}
\caption{\textit{Top row: }The estimates of the surface density profiles including the fitted models. The fitted curves indicate the median as well as the 16\% and 84\% quantiles of the model fits. The survey depth of the galaxy catalog increases from left to right (indicated by mag$_{limit}$) and each panel shows two different estimates of the correlation signal using the DP and LS estimator, respectively. The colored vertical lines indicate the median and 16\% and 84\% quantiles of the location of steepest slope of the profiles as estimated from the minima of the derivatives which are shown in the bottom row. The lightgrey vertical line indicates the location of the R$_{200m}$ radius for comparison. \textit{Bottom row: } The analytical derivatives of the corresponding surface density profiles shown in the top row are displayed. As in the upper panels median, 16\% and 84\% quantiles are given.}
   \label{fig:2D_graphs}
\end{figure*}

\begin{figure*}
    \includegraphics[width= \textwidth]{3D_graphs.pdf}
\caption{\textit{Top row: }The three dimensional density profiles as obtained from the estimates of the fitting parameters obtained through the MCMC procedure. The curves indicate the median (solid lines) as well as the 16\% and 84\% quantiles of the model fit (dashed lines). The survey depth of the galaxy catalog increases from left to right (indicated by mag$_{limit}$) and each panel shows two different estimates of the correlation signal using the DP and LS estimator, respectively. The colored vertical lines indicate the median and 16\% and 84\% quantiles of the location of steepest slope of the profiles as estimated from the minima of the derivatives which are shown in the bottom row. The lightgrey vertical line indicates the location of the R$_{200m}$ radius for comparison. \textit{Bottom row: } The analytical derivatives of the corresponding density profiles shown in the top row are displayed. As in the upper panels median, 16\% and 84\% quantiles are given.}
   \label{fig:3D_graphs} 
\end{figure*}

\begin{figure*}
    \includegraphics[width= \textwidth]{XR_curves.pdf}
\caption{\textit{Top row: }The estimates of the surface density profiles including the fitted models. The fitted curves indicate the median as well as the 16\% and 84\% quantiles of the model fits. The survey depth of the galaxy catalog increases from left to right (indicated by mag$_{limit}$) and each panel shows two different estimates of the correlation signal using the DP and LS estimator, respectively. The colored vertical lines indicate the median and 16\% and 84\% quantiles of the location of steepest slope of the profiles as estimated from the minima of the derivatives which are shown in the bottom row. The lightgrey vertical line indicates the location of the R$_{200m}$ radius for comparison. \textit{Bottom row: } The analytical derivatives of the corresponding surface density profiles shown in the top row are displayed. As in the upper panels median, 16\% and 84\% quantiles are given.}
   \label{fig:XR_graphs}
\end{figure*}

\begin{table*}
    \centering
    \caption{fit parameters (incomplete)}
    \label{tab:fit_parameters}
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
    \hline 
    clu & depth & est & $\log_{10}(\rho_s)$ & $\log_{10}(\alpha)$ & $\log_{10}(r_s)$ & $\log_{10}(\rho_0)$ & $s_e$ & $\log_{10}(r_t)$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ & $\chi^2/\nu$ \\ 
    \hline 
    \hline
  PSZ2 & 21 & DP & $-0.48^{+0.30}_{-0.33}$ & $-0.49^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $8.3^{+3.6}_{-2.5}$ \\ 
    \hline 
  PSZ2 & 21 & LS & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ \\ 
    \hline 
   PSZ2 & 21.5 & DP & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ \\
    \hline
   PSZ2 & 21.5 & LS & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ \\
    \hline
   PSZ2 & 22 & DP & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ \\
    \hline
   PSZ2 & 22 & LS & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ \\
    \hline
   MCXC & 21 & DP & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ \\
    \hline
   MCXC & 21.5 & DP & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ \\
    \hline
   MCXC & 22 & DP & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ & $-0.48^{+0.30}_{-0.33}$ \\
    \hline
    \end{tabular} 
\end{table*}

\begin{table}
    \centering
    \caption{We list the signal to noise ratios (SNRs) of the different sets of data-points. For comparison: The SNR achieved by \citet{more2016detection} is 263. It is much higher due to size of the cluster sample used in their study.}
    \label{tab:snr}
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
    \hline
    clu & PSZ2 & PSZ2 & PSZ2 & PSZ2 & PSZ2 & PSZ2 & MCXC & MCXC & MCXC\\  
    \hline 
    depth & 21 & 21 & 21.5 & 21.5 & 22 & 22 & 21 & 21.5 & 22\\ 
    \hline
   est & DP & LS & DP & LS & DP & LS & DP & DP & DP\\ 
    \hline 
   SNR & 23.2 & 16.2 & 20.3 & 16.5 & 17.5 & 13.3 & & &\\ 
    \hline
    \end{tabular} 
\end{table}

\subsection{Location of the Splashback radius}
Using the estimates of the fitting parameters obtained from the MCMC procedure the posterior distributions of the locations of the splashback radii as inferred from the different datasets are obtained. The histograms are shown in Figure~\ref{fig:splashback}, where the panels on the left display the posterior distributions of the projected splashback radius and the right panels the distributions of the three dimensional, physical counterparts. The top row shows the results as inferred by using the DP estimator whereas the LS estimator was used in the lower panels. The survey depth is indicated for each distribution and the used color code corresponds to the code used in Figure~\ref{fig:2D_graphs} and Figure~\ref{fig:3D_graphs}. The inferred medians as well as the 16\% and 84\% quantiles of the distributions are listed in Table~\ref{tab:splashbacks}. 
The choice of the estimator does not influence the location of the splashback radius, as it was already visible from the shapes of the density profiles above. But increasing the survey depth shifts the location to smaller radii. This trend is visible for the two and three dimensional splashback radii. It can also be observed that the constraints on the projected splashback radius are more stringent than on its three dimensional counterparts.

\begin{figure*}
    \includegraphics[width= \textwidth]{splashback.pdf}
\caption{Shown are the posterior distributions of the inferred locations of the splashback radii. On the left side the distributions of the projected splashback radii are shown whereas the distributions of the three dimensional counterparts are shown on the right. In the top row the DP estimator is used but the LS estimator is exploited to obtain the distributions in the lower panels. The numbers attached to the distributions indicate the survey depth of the galaxy catalog. Note that the colors of the distributions match with the colors used in Figure~\ref{fig:2D_graphs} and Figure~\ref{fig:3D_graphs}. For reference, the R$_{200m}$ radius is indicated in each panel with a lightgrey, vertical, dashed line.}
   \label{fig:splashback} 
\end{figure*}

\begin{figure*}
    \includegraphics[width= \textwidth]{xr_splashback.pdf}
\caption{Shown are the posterior distributions of the inferred locations of the splashback radii. On the left side the distributions of the projected splashback radii are shown whereas the distributions of the three dimensional counterparts are shown on the right. In the top row the DP estimator is used but the LS estimator is exploited to obtain the distributions in the lower panels. The numbers attached to the distributions indicate the survey depth of the galaxy catalog. Note that the colors of the distributions match with the colors used in Figure~\ref{fig:2D_graphs} and Figure~\ref{fig:3D_graphs}. For reference, the R$_{200m}$ radius is indicated in each panel with a lightgrey, vertical, dashed line.}
   \label{fig:splashback} 
\end{figure*}

\begin{table}
    \centering
    \caption{We list the findings of the splashback radii (incomplete)}
    \label{tab:splashbacks}
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
    \hline
    clu & PSZ2 & PSZ2 & PSZ2 & PSZ2 & PSZ2 & PSZ2 & MCXC & MCXC & MCXC \\ 
    \hline 
    depth & 21 & 21 & 21.5 & 21.5 & 22 & 22 & 21 & 21.5 & 22\\ 
    \hline
   est & DP & LS & DP & LS & DP & LS & DP & DP & DP\\ 
    \hline 
   R$_{sp}^{2D}$ & LS & & & & & & & &\\ 
    \hline 
   r$_{sp}^{3D}$ & DP & & & & & & & &\\
    \end{tabular} 
\end{table}

\subsection{Deprojection}
In Figure~\ref{fig:deprojection} the estimates of the three dimensional density profiles as obtained from the alternative deprojection algorithm described in Section~\ref{sec:Deprojection} are presented. The deprojection method was exploited for each one of the three galaxy catalogs. The survey depth increases from left to right. The density profiles obtained by the standard MCMC fitting procedure outlined above are added to the data-points for better comparison. One can observe that the data points agree well with the density profiles obtained from the standard procedure on scales below 2 h$^{-1}$ Mpc but possess an overshoot on larger scales.

\begin{figure*}
    \includegraphics[width= \textwidth]{deprojection.pdf}
\caption{The data-points indicate the estimates of the three dimensional density profiles as inferred by using the deprojection algorithm outlined in Section~\ref{sec:Deprojection}. Additionally, the density profiles as obtained by using the DP estimator and the standard MCMC fitting procedure are shown for comparison. The survey depth increases from left to right and is indicated by mag$_{limit}$.}
   \label{fig:deprojection} 
\end{figure*}

\subsection{Separation of red and blue galaxies (incomplete)}

\section{Discussion (incomplete)}

\subsection{Density profiles}

why are shapes different?
compare with redmapper
as expected? splashback feature visible?

\subsection{Location of the Splashback radius}
show $splash_comp$
show derivatives
why is rsp different for each sample
why different from redmapper
measurements consistent?
measurements consistent with theory?
do max derivatives make sense (reference to paper)

\begin{figure}
    \includegraphics[width= \columnwidth]{splash_comp.pdf}
\caption{bla}
   \label{fig:splash_comp} 
\end{figure}

\subsection{Deprojection}

Do rhos differ? Why?
does deprojection work?
how to imporove?

\subsection{Separation of red and blue galaxies}
why different?
expected result?

\section{Conclusions}

The last numbered section should briefly summarise what has been done, and describe
the final conclusions which the authors draw from their work.

\section*{Acknowledgements}
The Pan-STARRS1 Surveys (PS1) and the PS1 public science archive have been made possible through contributions by the Institute for Astronomy, the University of Hawaii, the Pan-STARRS Project Office, the Max-Planck Society and its participating institutes, the Max Planck Institute for Astronomy, Heidelberg and the Max Planck Institute for Extraterrestrial Physics, Garching, The Johns Hopkins University, Durham University, the University of Edinburgh, the Queen's University Belfast, the Harvard-Smithsonian Center for Astrophysics, the Las Cumbres Observatory Global Telescope Network Incorporated, the National Central University of Taiwan, the Space Telescope Science Institute, the National Aeronautics and Space Administration under Grant No. NNX08AR22G issued through the Planetary Science Division of the NASA Science Mission Directorate, the National Science Foundation Grant No. AST-1238877, the University of Maryland, Eotvos Lorand University (ELTE), the Los Alamos National Laboratory, and the Gordon and Betty Moore Foundation.

Based on observations obtained with Planck (http://www.esa.int/Planck), an ESA science mission with instruments and contributions directly funded by ESA Member States, NASA, and Canada.

Some of the results in this paper have been derived using the HEALPix (K.M. Górski et al., 2005, ApJ, 622, p759) package

\bibliographystyle{mnras}
\bibliography{RSP_library}

\newpage

\appendix

\section{Additional Figures}
\label{sec:figures}

\begin{figure}
    \includegraphics[width= \columnwidth]{Planck_pres.png}
\caption{HEALPix map showing the used cluster positions as selected from the PSZ2 catalog. In total 596 clusters have been selected. The violet area marks the region that is excluded by the survey selection function. Note that all clusters with $\delta<-31\degr$ have been removed since this region is not covered by the Pan-STARRS 3$\upi$ Steradian survey. The ICRS coordinate system is used.}
    \label{fig:planck_fig} 
\end{figure}

\begin{figure*}
    \includegraphics[width= \textwidth]{heal_maps.png}
\caption{HEALPix map showing the disregarded regions of the Pan-STARRS 3$\upi$ Steradian survey in violet. The lower magnitude limit is 21.0, 21.5 and 22.0 respectively and ICRS coordinates are used.}
   \label{fig:heal_map} 
\end{figure*}

\section{Convergence of MCMC chains}
\label{sec:convergence}
Three different methods are exploited in order to assess the convergence of the MCMC chains. Firstly, the general behavior of the chains is monitored and it is checked that they are well behaved, meaning that they converge to a common point in the parameter space, at least visually. With the same goal in mind the autocorrelations of the chains are calculated and it is assured that the autocorrelations are monotonically decreasing as the chains grow.

The second method involves performing a statistical test, named after Geweke \citet{geweke1991evaluating} which relies on methods from spectral analysis to address the issues of biases and variance alike. Imagine attempting to estimate the mean of a function $f$ which depends on the simulated parameter $\theta$. After $n$ iterations of the chain the estimate of the mean becomes
\begin{equation}
\bar{f}_n=\frac{\sum_{i=1}^n f(\theta^{(i)})}{n}
\end{equation}
and Geweke states that the asymptotic variance of that estimator yields $S^G(0)/n$, where $S^G(0)$ indicates the spectral density at frequency 0. The Geweke statistic is calculated by using two subsamples of the simulated parameter set. Geweke suggests taking the first 10\% of the iterations as the first sample $n_A$ and the last 50\% of the iterations to be the second sample $n_B$. Note that $n_A/n + n_B/n < 1$ to assure asymptotic independence of the two parts of the chain. For both subsets the estimate of the mean is calculated yielding $\bar{f}(\theta)_A$ and $\bar{f}(\theta)_B$, respectively. Further, the corresponding asymptotic variances are calculated as well to obtain $S^G_A(0)/n_A$ and $S^G_B(0)/n_B$, respectively. Geweke's convergence diagnostic is than constructed as
\begin{equation}
Z_{(A,B)}=\frac{\bar{f}(\theta)_A-\bar{f}(\theta)_B}{n_A^{-1}S^G_A(0)-n_B^{-1}S^G_B(0)},
\end{equation}
which approaches a standard normal distribution according to the central limit theorem if the samples are being drawn from a stationary distribution. Geweke argues that the convergence statistic may be used to determine how many of the initial steps must be regarded as burn-in steps and therefore must be disregarded \citet{cowles1996markov}.

Lastly, the Heidelberger and Welch test is performed \citep{heidelberger1983simulation}. The test combines approaches from spectral analysis with a convergence test by \citet{schruben1983optimal} designed to detect non-stationarity in a simulated set of parameters. Denoting the jth simulated parameter value in the chain as $\theta_j$ and the total number of iterations in the chain as $n$ the statistic $B_n(t)$ is calculated as
\begin{equation}
B_n(t)=\frac{T_{[nt]}-[nt]\bar{\theta}}{\sqrt{nS(0)}} , 0 \leq t \leq 1
\end{equation}
where $[.]$ indicates the floor function and
\begin{align}
T_k=\sum_{j=1}^k \theta_j \\
\bar{\theta}=\frac{\sum_{j=1}^n \theta_j}{n}
\end{align}
and $S(0)$ indicates the spectral density at frequency 0 once again. The claim is that if convergence of the chain is given, meaning that a stationary distribution is reached the statistic $B_n(t)$ is approximately distributed as a Browninan bridge. The Cramer-von Mises statistic 
\begin{equation}
\int_0^1 B_n(t)^2 dt
\end{equation}
may than be used as a test statistic to test if $B_n(t)$ tracks a Brownian bridge and therefore to test the hypothesis of convergence of the underlying chain \citep{cowles1996markov}.

Note that, as highlighted by \citet{cowles1996markov}, there exists no universally reliable tool to assure the convergence of a MCMC chain. Instead, it is advisable to use a variety of different tools that are aimed at doing so. Therefore, even though the chains seem to converge according to the statistical tests exploited, the tests may fail and the chains did not converge after all \citep{cowles1996markov}.

The statistical tests mentioned above have been carried out using the \fnurl{py-coda}{https://github.com/surhudm/py-coda} package which provides a python wrapper of some of the tools included in the CODA package in R \citep{coda}. 
\section{Deprojection of the surface density profile}
\label{sec:deprojection_math}
We follow the procedure outlined by \citet{eisenstein2003deprojecting} to construct an estimator which can recover the spatial density profile from the observed surface density profile. The projected angular galaxy distribution $\Sigma(R)$ of a cluster can be found from the spatial distribution $\rho(r)$ by integration along the line of sight as
\begin{equation}
\Sigma(R)=\int_{-\infty}^{\infty} \rho(\sqrt{R^2+Z^2})dZ. \label{eq:c1}
\end{equation}
It is known that the integral in Equation~\ref{eq:c1} can be inverted as an Abel integral to obtain
\begin{equation}
\rho(r) = -\frac{1}{\pi} \int_{r}^{\infty} \frac{d\Sigma}{dR}\frac{dR}{\sqrt{R^2-r^2}}. \label{eq:c2}
\end{equation}
Involving a derivative of the measured quantity $\Sigma(R)$ this integral is very noisy and therefore difficult to compute in practice. To overcome this we consider measuring $\Sigma(R)$ only as an integral weighted by as window function $W(r)$, where the choice of $W(r)$ can be used to pick up the number of galaxies in a radial bin. Therefore, $\Sigma(R)$ is approximated by the galaxy count $\Delta$ as  
\begin{equation}
\Delta N = \int_{0}^{\infty} W(r) \rho(r) 4 \pi r^2 dr.
\end{equation}
We proceed by using Equation~\ref{eq:c2} and partial integration as
\begin{align}
\Delta N &=& \int_{0}^{\infty} W(r) \left[ \frac{-1}{\pi} \int_{r}^{\infty} \frac{d\Sigma}{dR}\frac{dR}{\sqrt{R^2-r^2}} \right] 4 \pi r^2 dr  \label{eq:rho} \\
&=& -\frac{1}{\pi} \int_{0}^{\infty} dR \frac{d\Sigma}{dR} \int_{0}^{R} 4 \pi r^2 W(r) \frac{dr}{\sqrt{R^2-r^2}}\\
&=& -4 \int_{0}^{\infty} dR \frac{d\Sigma}{dR} \int_{0}^{R} W(r) \frac{r^2 dr}{\sqrt{R^2-r^2}} \\
&=& -4 \int_{0}^{\infty} dR \frac{d\Sigma}{dR} G(R)\\
&=& 4 \int_{0}^{\infty} dR \frac{dG}{dR} \Sigma(R) \label{eq:parts}\\
&=& 4 \int_{0}^{\infty} dR \frac{dG}{dR} \sum_i \frac{\delta_{\rm D}(R-R_i)}{2\pi R_i} \label{eq:discrete} \\
&=& \sum \frac{2}{\pi R_i} \left.\frac{dG}{dR}\right|_{R_i}
\end{align}
where we replaced the angular distribution by a discrete sum over the single galaxies in the sample located at projected radii $R_i$ from the cluster center and we defined
\begin{equation}
G(R) = \int_{0}^{R} W(r) \frac{r^2 dr}{\sqrt{R^2-r^2}}.
\end{equation}
Let us parametrize the three dimensional distance as $r=R \sin(\theta)$ yielding
\begin{align}
G(R) &=& \int_{0}^{\pi/2} W(R\sin\theta) \frac{R^2 \sin^2\theta R \cos\theta d\theta}{R\cos\theta}\\
&=& \int_{0}^{\pi/2} W(R\sin\theta) R^2 \sin^2\theta  d\theta.
\end{align}
Now let us consider a radial bin $r\in[a, b]$, thus $W(r)=\Theta(r-a) - \Theta(r-b)$, where $\Theta$ is the Heaviside step function. In this case we have three regimes for any given radius $R$; (i) $R<a$, (ii) $R\in[a, b]$, (iii) $R>b$. Let us deal with each of these cases separately.

\paragraph{Case (i): $R<a$}
In case (i), $\forall \theta\in[0, \pi/2]$, $W(R\sin\theta)=0$. Therefore, $G(R)=0$ and hence the derivative is zero.

\paragraph{Case (ii): $R\in[a,b]$}
In case (ii), $W(R\sin\theta)$ is non-zero $\forall \theta\in[\theta_{\rm min}, \pi/2]$, where $R\sin\theta_{\rm min}=a$. Therefore, the integral for G(R) reduces to
\begin{eqnarray}
G(R) &=& \int_{\theta_{\rm min}}^{\pi/2} R^2 \sin^2\theta  d\theta \\
&=& \frac{R^2}{2} \left[\theta-\sin\theta\cos\theta\right]_{\theta_{\rm min}}^{\pi/2}\\
&=& \frac{R^2}{2} \left[ \frac{\pi}{2} - (\theta_{\rm min}-\sin\theta_{\rm min}\cos\theta_{\rm min})  \right] \\
\frac{dG}{dR} &=& R  \frac{\pi}{2} -  R  \left[\tan^{-1}\left(\frac{x/R}{\sqrt{1-x^2/R^2}}\right) - \frac{x/R}{\sqrt{1-x^2/R^2}}\right]_a \nonumber \\
&=& R \left[ \frac{\pi}{2} - f(a) \right] \\
\frac{2}{\pi R}\frac{dG}{dR} &=& 1 - \frac{2}{\pi} f(a)
\end{eqnarray}
where we defined
\begin{equation}
f(x)=\tan^{-1}\left(\frac{x/R}{\sqrt{1-x^2/R^2}}\right) - \frac{x/R}{\sqrt{1-x^2/R^2}}
\end{equation}

\paragraph{Case (iii): $R>b$}
In case (iii), $W(R\sin\theta)$ is non-zero $\forall \theta\in[\theta_{\rm min}, \theta_{\rm max}]$, where $R\sin\theta_{\rm min}=a$, and $R\sin\theta_{\rm max}=b$. Therefore, the integral for G(R) reduces to
\begin{eqnarray}
G(R) &=& \int_{\theta_{\rm min}}^{\theta_{\rm max}} R^2 \sin^2\theta  d\theta \\
&=& \frac{R^2}{2} \left[\theta-\sin\theta\cos\theta\right]_{\theta_{\rm min}}^{\theta_{\rm max}}\\
&=& \frac{R^2}{2} \left[\sin^{-1}\left(\frac{x}{R}\right) - \frac{x}{R}\sqrt{1-\frac{x^2}{R^2}} \right]_{a}^{b} \\
&=& \left[\frac{R^2}{2} \sin^{-1}\left(\frac{x}{R}\right) - \frac{x}{2}\sqrt{R^2-x^2} \right]_{a}^{b} \\
\frac{dG}{dR} &=& \left[R  \sin^{-1}\left(\frac{x}{R}\right) - \frac{1}{2} \frac{x}{\sqrt{1-x^2/R^2}} - \frac{x}{2}\frac{1}{\sqrt{1-x^2/R^2}}\right]_a^b\\
\frac{dG}{dR} &=& R  \left[\sin^{-1}\left(\frac{x}{R}\right) - \frac{x/R}{\sqrt{1-x^2/R^2}}\right]_a^b\\
\frac{dG}{dR} &=& R  \left[\tan^{-1}\left(\frac{x/R}{\sqrt{1-x^2/R^2}}\right) - \frac{x/R}{\sqrt{1-x^2/R^2}}\right]_a^b \\
&=& R [f(b) - f(a)] \\
\frac{2}{\pi R}\frac{dG}{dR} &=& \frac{2}{\pi} [ f(b) - f(a)]
\end{eqnarray}

\subsection{Masking and survey boundaries}
The surface area normalization in Eq.~\ref{eq:discrete} assumes that the entire annulus at radius $R_i$ around a given cluster lays within the survey area. But this may not be true due to masking effects or survey boundaries. In this case the normalization is modified to be
\begin{equation}
\Sigma(R) = \sum_i \frac{1}{2\pi\phi(R)} \delta_{\rm D}(R-R_i),
\end{equation}
where $\phi(R)$ is the fraction of the annulus that lays within the survey area.

\bsp
\label{lastpage}
\end{document}

### 2018-09-13 RSP_Report/RSP_Report_v2.tex
Newly initialized repo

--- 2018-09-13 RSP_Paper/RSP_paper.tex
@@
 \shorttitle{Splashback radius of Planck-SZ clusters}
-\shortauthors{Zürcher, More}
+\shortauthors{Zürcher, More \& Refregier}
+\slugcomment{Master's Thesis:
+In partial fulfillment of the requirements for the Master of Science ETH in Interdisciplinary Sciences}
 
@@
 \author{
-Dominik Zürcher \altaffilmark{1, 2}
-Surhud More \altaffilmark{1, 3}, 
+D. Zürcher \altaffilmark{1, 2}
+Surhud More \altaffilmark{2, 3, 5}, 
+A. Refregier \altaffilmark{4, 6}
 }
 \affil{
-$^{1}$Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), \\ 
-$^{2}$Department of Physics, ETH Zurich, Wolfgang Pauli Strasse 27, 8093 Zurich, Switzerland\\
-$^{3}$The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa, Chiba 277-8583\\
+$^{1}$Department of Chemistry and Applied Biosciences, ETH Zurich, Vladimir-Prelog-Weg 1, 8093 Zurich, Switzerland;{\tt dominikz@student.ethz.ch}\\
+$^{2}$Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), \\ 
+${^3}$The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa, Chiba 277-8583\\
+$^{4}$Department of Physics, ETH Zurich, Wolfgang Pauli Strasse 27, 8093 Zurich, Switzerland\\
+${^5}$Supervisor\\
+${^6}$Co-supervisor\\
 }
 
+%\pubyear{2018}
+
+%\begin{document}
+%\label{firstpage}
+%\pagerange{\pageref{firstpage}--\pageref{lastpage}}
+%\maketitle
+
 \begin{abstract}
+%Being a unique observational probe for the mass accretion rate of
+%dark matter halos the splashback radius has been well-modeled by the
+%use of numerical simulations. However, although its signature has
+%been found using optical cluster catalogs, discrepancies from the
+%simulations were noted and the plausibility of the detections were
+%questioned. We overcome those caveats by using SZ selected clusters
+%from the Planck survey. By cross-correlation with galaxies from the
+%Pan-STARRS survey we construct the two-dimensional galaxy cluster -
+%galaxy cross-correlation signal. We detect a clear steepening in the
+%signal, which is steeper than $-3$ and poorly modeled by the NFW
+%profile. The feature is found at a location consistent with the
+%expectations. The uncertainty on the location of the splashback
+%radius is recorded as $\sim 15$\%. We also study the
+%cross-correlation of red and blue galaxies, separately and find
+%evidence for the existence of the splashback feature in both
+%populations. Further, we record a strong increase in the fraction of
+%red galaxies that is associated with the splashback radius.
+
 We present evidence for the existence of the splashback radius
@@
 splashback radius.  We infer the three-dimensional splashback radius
-for the SZ cluster sample to be $r_{\rm sp}=1.81_{-0.33}^{+0.28}$ $\mpch$,
+for the SZ cluster sample to be $r_{\rm sp}=1.85_{-0.30}^{+0.26}$ $\mpch$,
 where the cluster sample has an average halo mass $M_{\rm
@@
 faster accreting halos have smaller splashback radii.
+
+%The interpretation of the dependence on accretion rate is straightforward and can be explained by the dynamics of a dark matter particle falling down and subsequently climbing out of a changing potential well of the dark matter halo.
+The dark matter particle will gain kinetic energy as it falls down the potential well.
+However if the potential well grows during this time, then the particle does not have enough energy to climb out of it.
+This results in the reduction of the apocenter of its orbit, and hence the splashback radius.
+The faster the accretion rate, the deeper the potential well gets, the smaller the splashback radius.
 
@@
 
+%The correct interpretation of observations of large scale structures in the universe requires accurate, theoretical predictions for the structure of dark matter halos as they form in a cold dark matter scenario.
+Therefore, a large efford has been made in the past decades to predict the density profiles of dark matter halos starting with \citet{gunn1972infall} who used a simple top hat model to describe the collapse of the halos.
+However, cosmolgical simulations revealed that the collapse of the halos are rather triaxial than spherically symmetric and therefore more complicated than expected \citep{klypin1983three}.
+The NFW profile named after its inventors \citet{navarro1997universal} became one of the most popular models taking into account the triaxial nature of the collapse.
+It was found that the profiles of dark matter halos exhibit a monotonical steepening at larger radii \citep{huss1999universal}.
+This behaviour is badly described by the NFW profile which inherits an asymptotic slope of -3 at large radii, since \citet{navarro1997universal} focused on the description of the inner part of the dark matter halos.
+Instead, a more accurate desription has been found through the Einasto profile (e.g., \citep{navarro2004inner}).
+%Most of the studies on dark matter halo profiles focused on the inner regions of halos since these are more easily probed by the observable galaxy distributions (e.g., \citep{moore1999dark}).
+However, through X-Ray and Sunyeaev-Zeldovich surveys as well as weak gravitational lensing studies the mass distribution of the outskirts of the halos become more and more accesible \citep{diemer2014dependence}.
+Therefore, \citet{diemer2014dependence} investigated the outer regions of the dark matter halos in order to provide more accurate models for the description of the outskirts of the halos which are necessary for the correct interpretation of such observations.
+They showed, that the classical fitting functions such as the NFW or the Einasto profile fail to describe the outer parts of the mass profiles as inferred from N-body simulations.
+Particularly they found a sharp steepening of the profile around the virial radius $r \approx r_{\mathrm{200m}}$, which is not modeled correctly by those fitting functions and they argue that the local steepening is caused by a caustic formed by recently accreated particles which passed through the pericenter of their orbit just once since their infall onto the cluster.
+They proposed a new fitting function consisting of an inner Einasto profile and an outer power law profile connected by a smooth transition
+%\begin{align}
+%\rho(r) &= \rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r) + \rho_{\mathrm{out}}(r)\,, \\
+%\rho_{\mathrm{in}}(r)&=\rho_{\mathrm{s}}\exp\left( -\frac{2}{\alpha}\left[ \left( \frac{r}{r_{\mathrm{s}}}\right)^{\alpha}-1 \right] \right)\,,\\
+%\rho_{\mathrm{out}}(r)&=\rho_{\mathrm{0}}\left( \frac{r}{r_{\mathrm{out}}}\right)^{-s_{\mathrm{e}}} \,,\label{eq:model} \\
+%f_{\mathrm{trans}}(r)&=\left( 1+\left( \frac{r}{r_{\mathrm{t}}} \right)^{\beta} \right)^{-\gamma/ \beta}\,,
+%\label{eq:dk14}
+%\end{align}
+%where $r$ indicates the three dimensional radial distance from the halo center \citep{diemer2014dependence}.
+
+%In a follow up study \citet{adhikari2014splashback} derived a simple theoretical model from first principles explaining the presence of the local steepening found by \citet{diemer2014dependence}.
+They base their work on the ideas developed by \citet{diemer2014dependence} and \citet{fillmore1984self}.
+They argue that caustics arise in triaxial collapses of dark matter due to a pile up of the orbits of multiple particles at a similar radius.
+Such caustics most frequently appear close to the apocenters of the orbits due to the radial velocity being very small at that point, which causes the particles to spend a longer time there \citep{lithwick2011self}.
+The outermost caustic of a halo is associated with the first apoapsis of the most recently accreted particles.
+Those particles underwent a first collapse meaning that they passed through the center of the halo just once.
+This phenomenon is termed splashback effect and the radius corresponding to the density drop after the outermost caustic has been named splashback radius correspondingly.
+
+%The location of the splashback radius strongly depends on the accretion rate $\Gamma$ of the halo.
+The interpretation of the dependence on $\Gamma$ is straightforward: Imagine a dark matter particle which passed through the center of the halo just once and is on its way back towards larger radii.
+If the gravitaional potential of the halo would be static the particle would inherit enough kinetic energy to climb the potential and leave the halo again.
+However, since the halo keeps on accreating matter while the particle moves away from the center, its gravitational potential well deepens and the dark matter particle will not be able to climb the potential completely but instead "splashes back" towards the center of the halo.
+The deepening of the potential during the particle's journey depends on the amount of the accreated material and therefore on the value of $\Gamma$.
+Hence, a larger $\Gamma$ leads to a smaller splashback radius.
+This means that the location of the splashback radius can be used to infer the accretion rate of a halo \citep{adhikari2014splashback}
+
+%Similarly, the redshift dependence arises through the influence of the values of the cosmological paramerters $\Omega_m$ and $\Omega_{\Lambda}$ on the amount of material that can be accreated onto the halo during the time that the particle requires to travels outwards from the center again.
+At lower redshifts $\Omega_m$ decreases quickly as $\Omega_{\Lambda}$ becomes more dominant.
+Therefore, the mean background density $\bar{\rho}_m$ of the universe decreases quickly as well and the halo can only accreate less and less material which slows down the deepening of the potential well and increases the splashback radius \citep{adhikari2014splashback}.
+
+%Motivated by the collapse model of a spherical top-hat over-density the outer boundary of a halo is usually defined as a radius $R_\Delta$ enclosing a region with an over-density of $\Delta$ or more with respect to a certain reference density $\rho_{\mathrm{ref}}$, where the lower bound of the required over-density is given from the virialization criterion at the time of the virialization of the halo \citep{gunn1972infall}.
+However, \citet{diemer2013pseudo} found that such a boundary definition can lead to pseudo-evolution of the halo mass, meaning an apparent growth of the halo mass that is caused only by the evolution of the reference density with redshift and not by a physical accretion of mass onto the halo.
+Using simulations they showed that pseudo evolution accounts for nearly all of the apparent growth between $z=1$ and $0$ of galaxy-sized halos and can also account for a substantial fraction of the growth of cluster-sized halos \citep{diemer2013pseudo}.
+Further, \citet{diemer2013pseudo} realized that a new definition for the boundary of halos is required which must not suffer from pseudo-evolution.
+\citet{more2015splashback} proposed to use the newly discovered splashback radius as such an alternative definition.
+They found that depending on the accretion rate of the halo, the splashback radius may be well beyond the commonly used virial radius.
+For quickly accreting halos the splashback radius is expected to occur at $\approx 0.8-1$ $r_{\mathrm{200m}}$ and at $\approx 1.5$ $r_{\mathrm{200m}}$ for slowly accreting halos \citep{more2015splashback}.
+
+%Cross-correlating the Sloan Digital Sky Survey (SDSS) Data Release 8 (DR8) photometric galaxy catalog with clusters identified from the SDSS DR8 catalog by the redMaPPer algorithm \citep{rykoff2014redmapper,rozo2015redmapper} \citet{more2016detection} presented evidence for the existence of the splashback radius in observations.
+By studying the stacked surface density profiles of the galaxy clusters they detected a sharp steepening providing strong evidence for the existence of the splashback effect.
+
+%\citet{more2016detection} compared their findings with simulations by utilizing the MultiDark-Planck II N-body simulation \citep{klypin2016multidark}.
+The comparison showed that the splashback radii detected are smaller than expected from the simulation.
+They explored several systematic effects which could lead to such deviations.
+However, none of the investigated, systematic effects can account for the discrepancies found in the data.
+
 Given that the splashback radius represents a true halo boundary,
@@
 cross-matching to other galaxy clusters from external data sets. 
+%what 3 techniques???
 \begin{table}
@@
     \label{tab:priors}
-    \begin{tabular}{ccccccccccc}
-    \hline 
-    & $\log_{10}(\rho_{\mathrm{s}})$ & $\log_{10}(\alpha)$ & $\log_{10}(r_{\mathrm{s}})$ & $\rho_0$ & $s_{\mathrm{e}}$ & $\log_{10}(r_{\mathrm{t}})$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ & $f_{\rm min}$ & $\sigma$\\
-    \hline 
-    Prior Type & None & Normal & Flat & None & None & Flat & Normal & Normal & Normal & Normal\\ 
-    \hline 
-    Prior Range & - & $\log_{10}(0.2)| 1.2$ & [0.1,5.0] & - & - & [0.1,5.0] & $\log_{10}(6.0) | 0.4$ & $\log_{10}(4.0) | 0.4$ & $0.15 | 0.21$ & $0.41 | 0.3$\\
+    \begin{tabular}{ccccccccc}
+    \hline 
+    & $\log_{10}(\rho_{\mathrm{s}})$ & $\log_{10}(\alpha)$ & $\log_{10}(r_{\mathrm{s}})$ & $\rho_0$ & $s_{\mathrm{e}}$ & $\log_{10}(r_{\mathrm{t}})$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ \\ 
+    \hline 
+    %$\mathrm{Var}_{\mathrm{init}}$ & 0.8 & 0.030 & 0.058 & $4.7\cdot10^{-6}$ & $3.8\cdot10{-7}$ & 0.0088 & 0.25 & 0.0078\\ 
+    %\hline 
+    Prior Type & None & Normal & Flat & None & None & Flat & Normal & Normal\\ 
+    \hline 
+    Prior Range & - & $\log_{10}(0.2)| 1.2$ & [0.1,5.0] & - & - & [0.1,5.0] & $\log_{10}(6.0) | 0.4$ & $\log_{10}(4.0) | 0.4$\\
     \hline
@@
 satellite, the cluster positions as reported in the catalog may be
-mis-centered from the true centers of the galaxy clusters. We perform
+mis-centered from the true center of the galaxy clusters. We perform
 a visual inspection of Pan-STARRS images taken around the detected
@@
 location, under the assumption that the BCG is located at the true,
-gravitational center. Due to this crude assumption, we additionally 
-include the effects of a possible, remaining mis-centering of the 
-cluster positions in our model for the two-dimensional correlation 
-function (see Section~\ref{sec:mis-centering}). 
-The final sample that we use consists of 596
+gravitational center. The final sample that we use consists of 596
 galaxy clusters and is about an order of magnitude smaller compared
@@
 and -18.44) for the catalogs PS 21, PS 21.5 and PS 22, respectively.
+
+%However, at the same time it has to be assumed that there will also be a
+%population of uncorrelated galaxies present consisting of higher or lower
+%redshift galaxies that are not associated with the cluster in question. The
+%same holds true for the cluster population as well. Such contaminations can be
+%estimated by the use of random catalogs modeling the uncorrelated component of
+%the two-point cross-correlation function. We outline this procedure in
+%Section~\ref{sec:est_surf_den}.  Exploiting this analysis for each one of the
+%three catalogs with depth 21.0, 21.5 and 22.0 magnitude, respectively we obtain
+%three different estimates of the surface density distribution in total.
+
+%The splashback radius manifests itself as a sharp steepening in the spatial density profile of a dark matter halo.
+Unfortunately, such profiles are not directly accessible through measurements.
+However, in the standard paradigm of structure formation it is assumed that galaxies track the underlying dark matter distribution since they form from baryonic matter falling into the potential wells created by the dark matter \citep{rees1977cooling,white1978core,fall1980formation,blumenthal1984formation}.
+Therefore, we use the radial galaxy distribution as a proxy for the dark matter distribution of a halo.
+A further complication arises by the fact that only the projected galaxy distribution within a halo is accessible as a projection of the three dimensional distribution onto a projection plane perpendicular to the line of sight.
+Therefore, the three dimensional model given in Equation~\ref{eq:model} needs to be integrated along the line of sight in order to obtain a model for the surface density profile:
 
@@
 \begin{equation}
-\xi_{\rm (2D,0)}(R)=\frac{1}{R_{\rm max}}\int^{R_{\mathrm{max}}}_0 \xi_{\rm 3D}(\sqrt{R^2+x^2}) dx \,
+\xi_{\rm 2D}(R)=\frac{1}{R_{\rm max}}\int^{R_{\mathrm{max}}}_0 \xi_{\rm 3D}(\sqrt{R^2+x^2}) dx \,
 \label{eq:surface}
@@
 $r_{\mathrm{out}}$ and $\rho_{\rm o}$, we fix $r_{\mathrm{out}}=1.5$ $
-h^{-1}$Mpc.
-
-\paragraph{Modelling cluster mis-centering}
-\label{sec:mis-centering}
-Mis-centering of the central cluster positions can heavily affect 
-the small-scale correlation function on scales smaller than the typical mis-centering distance. 
-Although, the splashback radius is located at much larger scales, 
-the change of the inner part of the correlation function can alter the model fit significantly.
-Mis-centering effects are not expected to change the location of the splashback feature but they can in principle decrease the significance of the evidence for the splashback feature \citep{baxter2017halo}.
-
-The mass dependence of the exact mis-centering fractions are not
-well understood and mis-centering effects are therefore difficult to model \citep{Skibba:2011, Hoshino:2015}.
-We follow the approach outlined in \citet{baxter2017halo} to take the effects of a possible mis-centering of a fraction of the cluster positions
-into account by modelling the influence on the two-dimensional correlation function.
-
-Denoting the fraction of mis-centered clusters in the sample with $f_{\rm mis}$ we relate
-the correlation function $\xi_{\rm 2D}(R)$ that is affected by the mis-centering of the clusters to the correlation function
-unaffected by mis-centering $\xi_{\rm (2D,0)}(R)$ by
-
-\begin{equation} 
-\xi_{\rm 2D}(R) = (1-f_{\rm mis})\xi_{\rm (2D,0)}(R)+f_{\rm mis}\xi_{\rm (2D,mis)}(R)
-\label{eq:full}
-\end{equation}
-
-where the contribution of the mis-centered clusters to the correlation function is captured by $\xi_{\rm (2D,mis)}$. 
-We model the mis-centered component $\xi_{\rm (2D,mis)}$ as
-
-\begin{equation}
-\xi_{\rm (2D,mis)}(R)=\int_0^\infty \mathrm{d}R_{\rm mis} P(R_{\rm mis})\xi_{\rm (2D,mis)}(R|R_{\rm mis})
-\end{equation}
-
-where we assign a probability $P(R_{\rm mis})$ that a cluster is mis-centered by a comoving distance $R_{\rm mis}$.
-The contribution $\xi_{\rm (2D,mis)}(R|R_{\rm mis})$ from a cluster mis-centered by a distance $R_{\rm mis}$ 
-relates to the unaffected correlation function $\xi_{\rm (2D,0)}$ as
-
-\begin{equation}
-\xi_{\rm (2D,mis)}(R|R_{\rm mis})=\int_0^{2\pi}\frac{\mathrm{d}\theta}{2\pi}\xi_{\rm (2D,0)}\left(\sqrt{R^2+R_{\rm mis}^2+2RR_{\rm mis}\cos{\theta}}\right)
-\end{equation}
-
-according to \citet{yang2006weak} and \citet{johnston2007cross}. Following \citet{simet2016weak} we model the mis-centering probability 
-$P(R_{\rm mis})$ as a Rayleigh distribution:
-
-\begin{equation}
-P(R_{\rm mis})=\frac{R_{\rm mis}}{\sigma^2}\exp{\left( -\frac{R_{\rm mis}^2}{2\sigma^2}\right)}
-\end{equation}
-
-Therefore, the mis-centered contribution is fully characterized by the two parameters $f_{\rm mis}$ and the witdh 
-of the mis-centering probability distribution $\sigma$.
-\newline
-
-We cross-match our SZ selected cluster sample with the X-Ray selected ACCEPT cluster sample \citep{cavagnolo2009vizier}.
-Assuming the ACCEPT clusters to lay at the true gravitational cluster centers we construct Gaussian priors
-for the two mis-centering model parameters $f_{\rm mis}$ and $\sigma$ from the comparison of the 
-two samples. The central values as well as the scales of the priors are listed in Table~\ref{tab:priors}.
-
-Including mis-centering our model is described by ten model parameters.
-We infer the posterior distributions of those parameters by fitting the model for the two-dimensional correlation
-function affected by mis-centering to the measured two-dimensional correlation signal. 
-We use the affine invariant Markov Chain Monte Carlo sampler of \citet{goodman2010ensemble} as
+h^{-1}$Mpc and infer the posterior distribution of the remaining
+eight parameters from the measurements. We use the affine invariant
+Markov Chain Monte Carlo sampler of \citet{goodman2010ensemble} as
 implemented in the parallel python package {\it emcee} by
@@
 
+%where the function $D(z)$ determines the comoving distance to an object at redshift $z$.
+Further $z_{\mathrm{max}}$ is the maximal redshift of the cluster catalog (0.33 in our case) and $m_{\mathrm{lim}}$ indicates the depth of the galaxy catalog in consideration in magnitudes (being 21.0, 21.5 and 22.0, respectively) \citep{more2016detection}.
+%The assigned galaxies are then binned into 8 equally spaced radial bins ranging from 0.1 h$^{-1}$ Mpc to 10 h$^{-1}$ Mpc.  
+%
+%We expect a correlation between clusters and galaxies if they are at the same redshift.
+However, at the same time it has to be assumed that there will also be a population of uncorrelated galaxies present consisting of higher or lower redshift galaxies that are not associated with the cluster in question.
+The same holds true for the cluster population as well.
+Such contaminations can be estimated by the use of random catalogs modeling the uncorrelated component of the two-point cross-correlation function.
+We outline this procedure in Section~\ref{sec:est_surf_den}.
+%Exploiting this analysis for each one of the three catalogs with depth 21.0, 21.5 and 22.0 magnitude, respectively we obtain three different estimates of the surface density distribution in total.
+%
+%\subsection{Locating the splashback radius}
+%\label{sec:MCMC}
+%Having an estimate of the surface density function at hand we now turn to the problem of inferring the location of the splashback radius.
+With that goal in mind we fit the model for the surface density profile given in Equation~\ref{eq:surface} to the estimated profile.
+Fixing $r_{\mathrm{out}}=1.5 $ h$^{-1}$Mpc due to its full degeneracy with the parameter $\rho_{\mathrm{0}}$ this task involves fitting a model with eight free parameters namely $\rho_{\mathrm{s}}, \alpha, r_{\mathrm{s}}, \rho_{\mathrm{0}}, s_{\mathrm{e}}, r_{\mathrm{t}}, \beta$ and $\gamma$.
+%Performing a simple Least Square fit we obtain the set of parameter values as shown in Table~\ref{tab:inits}.
+We use the Python implementation \textit{emcee} \citep{foreman2013emcee} of the affine invariant Markov Chain Monte Carlo (MCMC) sampler of Goodman \& Weare to sample from the posterior distributions of the model parameters \citep{goodman2010ensemble}.
+Twenty MCMC chains are being run for 50'000 iterations each where the Least Square fitting parameters listed in Table~\ref{tab:inits} serve as their initial parameters.
+%The priors constraining the MCMC chains during the runs are listed in Table~\ref{tab:priors}.
+We adapt similar priors as in the work of \citet{more2016detection} but increase the scales of the normal priors allowing the chains to explore a larger fraction of the parameter space.
+The central value for the prior on $\alpha$ is deduced from mass estimates from weak lensing \citep{gao2008redshift} whereas the cenral values for the priors of $\beta$ and $\gamma$ were recommended by \citet{diemer2014dependence}.
+%Several statistical tests are performed to confirm the convergence of the MCMC chains.
+The tests and their results are presented in Appendix~\ref{sec:convergence}.
+Given the posterior distributions of the model parameters an estimate of the three dimensional model as given in Equation~\ref{eq:model} can be constructed as well.
+%We define the splashback radius as being located at the steepest logarithmic slope of the density profile.
+For each measurement two different estimates of the splashback radius can be inferred; a projected splashback radius $R_{\mathrm{sp}}^{\mathrm{2D}}$ is obtained from the location of the steepening feature in the two dimensional surface density and a three dimensional, physical splashback radius $r^{\mathrm{3D}}_{\mathrm{sp}}$ is inferred from the three dimensional density profile alike.
+Note that according to \citet{diemer2014dependence} those two estimates are expected to differ from each other.
+%Since the analytical models are known we derive the analytical expressions of the projected as well as the three dimensional logarithmic derivatives of the models using simple algebra to be
+%\begin{align}
+%\frac{\mathrm{d}\log(\xi )}{\mathrm{d}\log(R)}=\frac{-1}{\int_0^{z_{\mathrm{max}}}\rho (y)\mathrm{dz}} \int_0^{z_{\mathrm{max}}}\frac{R^2}{y}\left[ h(y)+ \frac{s_{\mathrm{e}}}{y}\rho_{\mathrm{out}}(y)\right]\mathrm{dz}   \\
+%\frac{\mathrm{d}\log(\rho)}{\mathrm{d}\log(r)}=-\frac{r}{\rho(r)}h(r)-s_{\mathrm{e}}\frac{\rho_{\mathrm{out}}(r)}{\rho(r)}
+%\end{align}
+%where
+%\begin{align}
+%y(R,z)=\sqrt{R^2+z^2} \\
+%h(x)=\rho_{\mathrm{in}}(x) \cdot f_{\mathrm{trans}}(x) \left( 2\frac{x^{\alpha -1}}{r_{\mathrm{s}}^{\alpha }}+\gamma \frac{x^{\beta -1}}{r_{\mathrm{t}}^{\beta }}\frac{1}{1+\left( \frac{x}{r_{\mathrm{t}}}\right)^{\beta }} \right)
+%\end{align}
+%and interpret their minima as the location of the projected and three dimensional splashback radius, respectively.
+
+%\subsection{Deprojection}
+%\label{sec:Deprojection}
+%At the time being, there is usually no spectroscopic data available for the single galaxies residing in a cluster.
+Therefore, the spatial mass distribution is normally not directly recoverable from the projected, angular distribution as it is measured in observations.
+We overcome this shortcoming by using a background-subtraction procedure and by integrating our mass density profile along the line of sight such that it can describe a projected distribution as well.
+However, in this procedure we need to assume spherical symmetry of the cluster and the fitting of the two dimensional profile is computationally much more involved than the direct fitting of the three dimensional density profile would be.
+Therefore, as an alternative approach, we follow the method outlined in \citet{eisenstein2003deprojecting} to directly recover the spatial distribution of the galaxies in the cluster without having to perform the troublesome two dimensional fitting procedure.
+Generally speaking the deprojection algorithm weights the galaxy counts in the different radial bins with a function depending on the chosen window function.
+The procedure is outlined in detail in Section~\ref{sec:deprojection_math}.
+Due to lack of statistics we did not take masking and boundary effects into account but the procedure to do so is also described in Section~\ref{sec:deprojection_math}.
+
 \subsection{Separation of red and blue galaxies}
 \label{sec:Color}
+%Early studies have already revealed that quiescent, red sequence galaxies are found predominantely in the dense, inner regions of halos (e.g.
+\citep{oemler1974systematic}) and correlations between the galaxy properties and their small-scale environement, namely their host dark matter halos have been discovered \citep{blanton2009physical}.
+From a physcial perspective those correlations can be explained by quenching of the galaxies, which refers to the transition of an active star-forming, blue galaxy to a quiescent, red sequence galaxy.
+Several mechanisms influence the timescale and efficiency of the quenching; As a galaxy falls into a dark matter halo the stong gravitational forces not only prevent the galaxy from accreting but even strip dark matter from the galaxy's own halo (e.g.
+\citep{dekel2003galactic}).
+Moreover, the extended gas in the galaxy can be heated and stripped off as well which eventually diminishes the replenishment of the gas used up in the galaxy by star formation, a process that is referred to as 'strangulation' or 'starvation' \citep{larson1980evolution}.
+In an even more extreme case ram pressure can cause the gas to be stripped off from the galaxy's disc directly (e.g.
+\citep{chung2009vla};\citep{gunn1972infall}).
+As such processes happen mainly in the denser regions of the halo one expects to see an increase of red sequence galaxies on scales smaller than the splashback radius since galaxies located outside of the splashback radius are likely to be on their first infall onto the cluster \citep{baxter2017halo}.
+Other theories suggest that the color of the galaxy is unaffected by the environement of the galaxy but correlates only with the time of accretion of the galaxy onto the halo \citep{hearin2015beyond}.
+In this case one would still expect an increase in the red fraction below the splashback radius since the percentage of galaxies that have been splashed back at least once and therefore spent a considerable amount of time in the halo is significantly increased \citep{baxter2017halo}.
+%We investigate if such a correlation between the increase of the red fraction of galaxies and the splashback radius holds true by creating two galaxy subsamples from our main galaxy catalog, one containing red and the other containing blue galaxies, and studying their relative contributions to the overall density profile.
 
@@
 \label{sec:Results}
+%We present the results of our studies in this section.
+All the best fit values represent medians, whereas upper error limits indicate 84\% quantiles and lower limits 16 \% quantiles.
+The shaded bands in the figures spand the range from the 16\% quantile lower bound up to the 84\% quantile upper bound as well.
 \subsection{Cluster-galaxy cross-correlations}
@@
 
-We fit these measurements with our parametric model in Equation~\ref{eq:full}
+We fit these measurements with our parametric model in Equation~\ref{eq:surface}
 and compute the posterior distribution of the model parameters 
@@
     \hline
+    %clu & PSZ2 & PSZ2 & PSZ2 & PSZ2 & PSZ2 & PSZ2 & MCXC & MCXC & MCXC\\  
+    %\hline 
     gal cat & PS 21 & PS 21.5 & PS 22 \\ 
@@
     \hline
-   SNR & 42.4 & 43.3 & 30.9 \\
+   SNR & 42.4 & 43.3 & 30.9 \\%& 16.5 & 17.5 & 13.3 & & &\\ 
     \hline
@@
     \hline 
-gal cat & $\log_{10}(\rho_{\mathrm{s}})$ & $\log_{10}(\alpha)$ & $\log_{10}(r_{\mathrm{s}})$ & $\rho_{\mathrm{0}}$ & $s_{\mathrm{e}}$ & $\log_{10}(r_{\mathrm{t}})$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ & $R_{\rm sp}^{\rm 2D}$& $r_{\rm sp}^{\rm 3D}$& $\chi^2/\nu$ \\
-\hline 
-\hline 
-PS 21 & $-0.92_{-0.56}^{+0.50}$ & $-1.19_{-0.21}^{+0.22}$ & $0.31_{-0.26}^{+0.29}$ & $0.0130_{-0.0083}^{+0.0062}$ & $0.72_{-0.22}^{+0.27}$ & $0.103_{-0.110}^{+0.056}$ & $0.85_{-0.36}^{+0.27}$ & $0.28_{-0.19}^{+0.12}$ & $1.35_{-0.12}^{+0.13}$ & $1.76_{-0.33}^{+0.29}$ & $0.511$ \\
-\hline
-PS 21.5 & $-0.91_{-0.48}^{+0.51}$ & $-0.98_{-0.18}^{+0.16}$ & $0.28_{-0.28}^{+0.26}$ & $0.0084_{-0.0060}^{+0.0041}$ & $0.53_{-0.23}^{+0.27}$ & $0.086_{-0.112}^{+0.051}$ & $0.78_{-0.34}^{+0.26}$ & $0.25_{-0.18}^{+0.12}$ & $1.30_{-0.10}^{+0.10}$ & $1.81_{-0.33}^{+0.28}$ & $0.178$ \\
-\hline
-PS 22 & $-0.99_{-0.46}^{+0.49}$ & $-0.90_{-0.17}^{+0.16}$ & $0.27_{-0.27}^{+0.26}$ & $0.0058_{-0.0052}^{+0.0027}$ & $0.43_{-0.29}^{+0.26}$ & $0.114_{-0.252}^{+0.076}$ & $0.71_{-0.38}^{+0.27}$ & $0.27_{-0.33}^{+0.16}$ & $1.33_{-0.17}^{+0.13}$ & $1.96_{-0.45}^{+0.37}$ & $0.264$ \\
-\hline 
-PS 21.5 (R) & $0.17_{-0.50}^{+1.03}$ & $-0.95_{-0.34}^{+0.44}$ & $-0.21_{-0.56}^{+0.26}$ & $0.0073_{-0.0084}^{+0.0040}$ & $0.59_{-0.38}^{+0.34}$ & $0.18_{-0.35}^{+0.22}$ & $0.52_{-0.41}^{+0.26}$ & $0.29_{-0.32}^{+0.23}$ & $1.20_{-0.12}^{+0.14}$ & $2.03_{-0.38}^{+0.38}$ & $1.194$ \\
-\hline
-PS 21.5 (B) & $-0.83_{-0.44}^{+0.49}$ & $-0.71_{-0.18}^{+0.19}$ & $0.24_{-0.30}^{+0.26}$ & $0.0112_{-0.0062}^{+0.0048}$ & $0.63_{-0.18}^{+0.23}$ & $0.28_{-0.20}^{+0.14}$ & $0.55_{-0.25}^{+0.16}$ & $0.44_{-0.33}^{+0.25}$ & $1.53_{-0.13}^{+0.13}$ & $2.30_{-0.23}^{+0.24}$ & $0.603$ \\
+gal cat & $\log_{10}(\rho_{\mathrm{s}})$ & $\log_{10}(\alpha)$ & $\log_{10}(r_{\mathrm{s}})$ & $\rho_{\mathrm{0}}\cdot 10^{5}$ & $s_{\mathrm{e}}$ & $\log_{10}(r_{\mathrm{t}})$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ & $R_{\mathrm{sp}}^{\mathrm{2D}}$ & $r_{\mathrm{sp}}^{\mathrm{3D}}$ & $\chi^2/\nu$ \\
+\hline 
+\hline 
+PS 21 & $-2.93_{-0.50}^{+0.44}$ & $-1.06_{-0.18}^{+0.14}$ & $0.35_{-0.24}^{+0.27}$ & $17.9_{-8.6}^{+7.5}$ & $0.78_{-0.19}^{+0.24}$ & $0.123_{-0.122}^{+0.051}$ & $0.74_{-0.31}^{+0.21}$ & $0.35_{-0.21}^{+0.13}$ & $1.384_{-0.096}^{+0.088}$ & $1.86_{-0.26}^{+0.25}$ & $1.524$ \\
+\hline
+PS 21.5 & $-2.93_{-0.45}^{+0.45}$ & $-0.95_{-0.16}^{+0.13}$ & $0.32_{-0.25}^{+0.25}$ & $10.3_{-6.5}^{+4.7}$ & $0.56_{-0.22}^{+0.25}$ & $0.095_{-0.115}^{+0.045}$ & $0.74_{-0.32}^{+0.24}$ & $0.27_{-0.19}^{+0.12}$ & $1.323_{-0.086}^{+0.080}$ & $1.85_{-0.30}^{+0.26}$ & $0.285$ \\
+\hline
+PS 22 & $-2.95_{-0.44}^{+0.49}$ & $-0.91_{-0.17}^{+0.14}$ & $0.28_{-0.27}^{+0.25}$ & $6.2_{-5.1}^{+2.8}$ & $0.41_{-0.28}^{+0.25}$ & $0.094_{-0.190}^{+0.060}$ & $0.76_{-0.36}^{+0.29}$ & $0.24_{-0.27}^{+0.14}$ & $1.31_{-0.14}^{+0.11}$ & $1.90_{-0.40}^{+0.32}$ & $0.211$ \\
+\hline
+PS 21.5(R) & $-2.17_{-0.58}^{+0.86}$ & $-1.03_{-0.33}^{+0.33}$ & $-0.02_{-0.46}^{+0.31}$ & $8.3_{-8.8}^{+4.4}$ & $0.59_{-0.37}^{+0.34}$ & $0.09_{-0.32}^{+0.13}$ & $0.53_{-0.32}^{+0.23}$ & $0.27_{-0.32}^{+0.20}$ & $1.22_{-0.10}^{+0.12}$ & $1.94_{-0.34}^{+0.32}$ & $1.361$ \\
+\hline
+PS 21.5(B) & $-2.90_{-0.38}^{+0.38}$ & $-0.64_{-0.14}^{+0.12}$ & $0.34_{-0.24}^{+0.24}$ & $12.7_{-6.5}^{+5.5}$ & $0.61_{-0.18}^{+0.23}$ & $0.26_{-0.20}^{+0.13}$ & $0.48_{-0.16}^{+0.12}$ & $0.44_{-0.30}^{+0.23}$ & $1.505_{-0.089}^{+0.091}$ & $2.29_{-0.20}^{+0.19}$ & $1.132$ \\
 \hline
@@
 find for the three samples is consistent with this expectation,
-although we can not rule out $\sim 18\%$ deviations in either directions,
+although we can not rule out $15\%$ deviations in either directions,
 given our large error bars.
+
+%\subsection{Location of the Splashback radius}
+%Using the estimates of the fitting parameters obtained from the MCMC procedure the posterior distributions of the locations of the splashback radii as inferred from the different datasets are obtained.
+The distributions are shown in Figure~\ref{fig:splashback}, where the panel on the left displays the posterior distribution of the projected splashback radius ($R_{\mathrm{sp}}^{\mathrm{2D}}$) and the right panel the distributions of the three dimensional, physical counterparts ($r_{\mathrm{sp}}^{\mathrm{3D}}$).
+%The top row shows the results as inferred by using the DP estimator whereas the LS estimator was used in the lower panels.
+%The survey depth is indicated for each distribution and the colors correspond to the colors already used in Figure~\ref{fig:2D_graphs} and Figure~\ref{fig:3D_graphs}.
+The estimates of the splashback radii are listed in Table~\ref{tab:splashbacks}.
+%We notice a weak anti-correlation between survey depth and the location of $R_{\mathrm{sp}}^{\mathrm{2D}}$.
+However, the trend is no longer visible in the posterior distributions for $r_{\mathrm{sp}}^{\mathrm{3D}}$.
 
@@
 splashback radius, the populations are consistent with a constant
-fraction of $\approx 55\%$ blue and $\approx 45\%$ red galaxies.
+fraction of $\approx 70\%$ blue and $\approx 30\%$ red galaxies.
+%\subsection{Deprojection}
+%In Figure~\ref{fig:deprojection} the estimate of the three dimensional density profile as obtained from the alternative deprojection algorithm described in Section~\ref{sec:Deprojection} is presented.
+The deprojection method was exploited for the PS 21.5 catalog.
+The density profile obtained by the standard MCMC fitting procedure outlined above is added to the data-points for better comparison.
+One can observe that the deprojection algorithm manages to reproduce the density profile obtained by the standard procedure very well on scales below 2 h$^{-1}$ Mpc but experiences an overshoot on larger scales.
+
+%\begin{figure}
+%   \includegraphics[width= \columnwidth]{deprojection.pdf}
+%\caption{The data-points indicate the estimate of the three dimensional density profile as inferred by using the deprojection algorithm outlined in Section~\ref{sec:Deprojection} on the PS 21.5 galaxy sample.
+Additionally, the density profile obtained by exploiting the PS 21.5 galaxy catalog and the standard MCMC fitting procedure are shown for comparison.}
+%   \label{fig:deprojection} 
+%\end{figure}
+%\newpage
 
@@
 
+%Further, by comparison of the estimates of the splashback radius listed in Table~\ref{tab:splashbacks} with the expectation of $1.89 $ h$^{-1}$ Mpc for the three dimensional, physical splashback radius $r_{\mathrm{sp}}^{\mathrm{3D}}$ we can conclude that our results are in agreement with the theoretical prediction.
+On the contrary, we can not confirm the discrepancy between the theoretical and observed location of the splashback radius that was found by \citet{more2016detection} when correlating optically selected clusters with SDSS galaxies.
+
+%From the comparison in Figure~\ref{fig:3D_graphs} we can conclude that the choice of the depth of the catalog does not alter the shapes of the density profiles significantly nor does it change the location of the splashback radius in a systematic manner.
+
+% Move into future work section:
 As it can be seen from Table~\ref{tab:snr}, the signal-to-noise
@@
 \citep{landy1993bias} to perform the background subtraction.
+% (see Section~\ref{sec:est_surf_den}).
 
@@
 Alternatively, other cluster samples that do not rely on optical cluster finding such as Xray based surveys might serve as independent and larger cluster samples.
+%We are considering to use the meta-catalog of X-ray detected clusters of galaxies (MCXC) which combines sevaral X-Ray based cluster catalogs for further investigations.
+The catalog is based on the ROSAT All-Sky survey \citep{voges1999rosat}.
 Another plausible approach would be to consider a smaller region of
@@
 depth of 26.2 magnitudes \citep{takada2010subaru}.
+
+%We present the result of our attempt to deproject the surface density profile in Figure~\ref{fig:deprojection}.
+We achieve good agreement between the standard and the deprojection procedure on scales below $2$ h$^{-1}$ Mpc but record a significant disagreement on larger scales.
+Therefore, we conclude that the general procedure is working but requires improvement.
+We suspect that including effects from masking and survey boundaries into the deprojection algorithm could improve the agreement.
+The procedure to do so is outlined in Section~\ref{sec:deprojection_math} but was not implemented so far.
+
+% I do not agree with this paragraph. I will tell you why later on.
+%From Figure~\ref{fig:color_fraction} we can confirm that the splashback feature is strongly associated with a sharp increase in the red fraction as it was observed by \citet{baxter2017halo} before.
+On the contrary, \citet{baxter2017halo} find that the density profile of the blue population reaches a constant logarithmic derivative of -1.5 at large radii outside of the splashbak radius, as it would be expected for purely in-falling material.
+This is not reproduced in our study where the density profile of the blue population flattens out further and reaches logarithmic derivatives below -1.
+We propose that this deviation from a purely in-falling population of galaxies might be caused by group preprocessing: preprocessing referrs to a situation where a galaxy is in-falling onto a large halo but has been acrreated onto a smaller subhalo before which itself is being accreated onto the larger halo at the time of observation.
+In such a scenario, the galaxy seems to be on its first in-fall but has actually passed through the central part of a smaller subhalo before \citep{fujita2004pre}.
+Therefore, the quenching of the galaxy started earlier and it might have already changed to a red sequence galaxy before reaching the splashback radius of the large halo.
+It was found by \citet{wetzel2013galaxy} that such galaxies make up for at least 30\% of the quiescent galaxies in a cluster which can increase to over 50\% for massive clusters above $10^{14} M_{\sun}$.
+Since mainly massive clusters are studied in this work we expect a large contribution from preprocessed galaxies which could explain the discrepancy from \citet{baxter2017halo}.
+We note that our investigations on the distributions of the blue and red subpopulations are far from complete.
+A thorough study would have to take into account the different masses and velocities of the individual galaxies in order to get a more precise picture.
+We note as well that we used a very simple, idealistic way to separate the galaxy catalog in subsamples relying on only two photometric bands and that a considering more bands might improve the results.
+
+% Already included before.
+%Although, we find good agreement with the theory it would be premature to jump to conclusions about the nature of the splashback radius from this study.
+Due to the small cluster sample used in this work we achieve much lower statistic than \citet{more2016detection}.
+As evident from Table~\ref{tab:splashbacks} our estimates of the splashback radii suffer from relative errors of $\approx$ 15\%.
+
+In our work, we have assumed that the brightest central galaxy
+resides at rest with respect to the center of the dark matter halo.
+The mass dependence of the exact mis-centering fractions are not
+well understood \citep{Skibba:2011, Hoshino:2015}.
+\citet{baxter2017halo} have shown that mis-centering effects could
+in principle decrease the significance of the evidence for the
+splashback radius, but do not affect the location of the splashback
+radius, significantly. Nevertheless we plan to pursue models
+including mis-centering to fit to our measurements.
+
+%Apart, from statistical errors there are also multiple systematic sources of errors that have to be investigated more thoroughly before we can draw any definitive conclusions from our results: Although, the central cluster positions have been adjusted manually it can not be guaranteed that the corrected positions are at the actual centers of the clusters.
+Firstly, the visual inspection is prone to human error of course and secondly it is assumed that the gravitational center of the cluster lays at the same position as the brightest central galaxy, which might not be true in general.
+The effect of such misplacements might be investigated by artificially displace some subsample of the clusters and study the influence on the location of the splashback radius.
+
+% This is irrelevant because the stars are not correlated with the galaxy clusters, so should drop out.
+%Regarding the galaxy catalog, the exploited star-galaxy separation is of very simplistic nature and the extracted catalog might still suffer from contaminations from stars.
+It might be worth to consider a more sophisticated separation method.
+
+% This is very commonly known, so not necessary to be stated.
+%Some tests outlined in Section~\ref{sec:convergence} have been exploited to investigate the mixing behavior and convergence of the MCMC chains used in the fitting procedure as described in Section~\ref{sec:MCMC}.
+However, it has to be noted that there is no mathematical tool available, that can confirm the convergence of MCMC chains without fail.
+Therefore, although the performed tests suggest that the chains are convergent we can not exclude that they may have not reached a static distribution.
 
@@
 
+%By using an independent cluster sample that was not obtained by optical cluster finding, we manage to observe the splashback radius at the expected location.
+
 We cross-correlate these clusters with photometric galaxies from the
@@
 two subsamples with the clusters, separately.
+
+%Subsequently, we searched for the signature of the splashback feature in the cross-correlation signals.
+We also separated the extracted galaxy catalog on color into a subsample of red and one of blue galaxies and studied their radial distributions in the halos.
 
@@
 \item The location of the inferred splashback radius is $r_{\rm
-sp}=1.81_{-0.33}^{+0.28}$ $\mpch$, which is consistent with expectations
+sp}=1.85_{-0.30}^{+0.26}$ $\mpch$, which is consistent with expectations
 from numerical simulations for
@@
 However, given the errors we cannot
-currently rule out $\sim18\%$ deviations from these expectations.
+currently rule out $\sim15\%$ deviations from these expectations.
 \item We find that the location of the steepest slope does not
@@
 we go fainter than $M_i-5\log h=-19.44$.
+% Explore dynamical friction effects by going even two magnitudes brighter later.
+%Hence, we conclude that the discrepancy found by \citet{more2016detection} is caused by systematics originating from the optical cluster finding algorithm
 \item By separately studying the cross-correlation of red and blue
@@
 galaxies associated with the splashback radius. 
+%clear correlation between the location of the splashback feature and an associated sharp increase in the red fraction.
+Further, we record indications pointing towards the group preprocessing scenario.
+% \item We made a first attempt to deproject the two dimensional correlation signal.
+We find good agreement between the deprojected signal and the three dimensional profile obtained from the standard algorithm on scales up to 2 h$^{-1}$ Mpc, from which we conclude that the method works, basically.
+However, we note a strong disagreement on larger scales, which we suspect to originate from the missing correction for masking and survey border effects.
 \end{itemize}
@@
 upon request.
+
+%As it is noted in Section~\ref{sec:Discussion} there is still need for further investigation and improvement.
+We plan on utilizing the meta-catalog of X-ray detected clusters of galaxies (MCXC) which is based on the ROSAT All-Sky survey \citep{voges1999rosat} as yet another independent cluster sample.
+Also, the systematic biases stemming from the selection of clusters through the Sunyaev-Zeldovich effect have to be clarified.
+To that goal, performing hydrodynamic simulations might have to be considered.
+Further, the use of random galaxies would improve the estimation of the uncorrelated background component and increase the sensitivity espicially when using faint galaxies.
+Interesting results regarding the formation history of galaxies in clusters were found.
+However, the correct interpretation of those results requires further, more detailed studies.
+Having obtained a very good agreement between the deprojection algorithm and the standard procedure exploited we are confident that the remaining discrepancy can be diminished by further improvement of the algorithm, such as accounting for masking and survey boundaries.
 
@@
 
+%\section{Convergence of MCMC chains
+%\label{sec:convergence}
+%Three different methods are exploited in order to assess the convergence of the MCMC chains.
+Firstly, the general behavior of the chains is monitored and it is checked that they are well behaved, meaning that they converge to a common point in the parameter space, at least visually.
+With the same goal in mind the autocorrelations of the chains are calculated and it is assured that the autocorrelations are monotonically decreasing as the chains grow.
+
+%The second method involves performing a statistical test, named after Geweke \citet{geweke1991evaluating} which relies on methods from spectral analysis to address the issues of biases and variance alike.
+Imagine attempting to estimate the mean of a function $f$ which depends on the simulated parameter $\theta$.
+After $n$ iterations of the chain the estimate of the mean becomes
+%\begin{equation}
+%\bar{f}_n=\frac{\sum_{i=1}^n f(\theta^{(i)})}{n}
+%\end{equation}
+%and Geweke states that the asymptotic variance of that estimator yields $S^G(0)/n$, where $S^G(0)$ indicates the spectral density at frequency 0.
+The Geweke statistic is calculated by using two subsamples of the simulated parameter set.
+Geweke suggests taking the first 10\% of the iterations as the first sample $n_{\mathrm{A}}$ and the last 50\% of the iterations to be the second sample $n_{\mathrm{B}}$.
+Note that $n_{\mathrm{A}}/n + n_{\mathrm{B}}/n < 1$ to assure asymptotic independence of the two parts of the chain.
+For both subsets the estimate of the mean is calculated yielding $\bar{f}(\theta)_{\mathrm{A}}$ and $\bar{f}(\theta)_{\mathrm{B}}$, respectively.
+Further, the corresponding asymptotic variances are calculated as well to obtain $S^G_{\mathrm{A}}(0)/n_{\mathrm{A}}$ and $S^G_{\mathrm{B}}(0)/n_{\mathrm{B}}$, respectively.
+Geweke's convergence diagnostic is than constructed as
+%\begin{equation}
+%Z_{\mathrm{(A,B)}}=\frac{\bar{f}(\theta)_{\mathrm{A}}-\bar{f}(\theta)_{\mathrm{B}}}{n_{\mathrm{A}}^{-1}S^G_{\mathrm{A}}(0)-n_{\mathrm{B}}^{-1}S^G_{\mathrm{B}}(0)},
+%\end{equation}
+%which approaches a standard normal distribution according to the central limit theorem if the samples are being drawn from a stationary distribution.
+Geweke argues that the convergence statistic may be used to determine how many of the initial steps must be regarded as burn-in steps and therefore must be disregarded \citet{cowles1996markov}.
+
+%Lastly, the Heidelberger and Welch test is performed \citep{heidelberger1983simulation}.
+The test combines approaches from spectral analysis with a convergence test by \citet{schruben1983optimal} designed to detect non-stationarity in a simulated set of parameters.
+Denoting the jth simulated parameter value in the chain as $\theta_j$ and the total number of iterations in the chain as $n$ the statistic $B_n(t)$ is calculated as
+%\begin{equation}
+%B_n(t)=\frac{T_{[nt]}-[nt]\bar{\theta}}{\sqrt{nS(0)}} , 0 \leq t \leq 1
+%\end{equation}
+%where $[.]$ indicates the floor function and
+%\begin{align}
+%T_k=\sum_{j=1}^k \theta_j \\
+%\bar{\theta}=\frac{\sum_{j=1}^n \theta_j}{n}
+%\end{align}
+%and $S(0)$ indicates the spectral density at frequency 0 once again.
+The claim is that if convergence of the chain is given, meaning that a stationary distribution is reached the statistic $B_n(t)$ is approximately distributed as a Browninan bridge.
+The Cramer-von Mises statistic
+%\begin{equation}
+%\int_0^1 B_n(t)^2 dt
+%\end{equation}
+%may than be used as a test statistic to test if $B_n(t)$ tracks a Brownian bridge and therefore to test the hypothesis of convergence of the underlying chain \citep{cowles1996markov}.
+
+%Note that, as highlighted by \citet{cowles1996markov}, there exists no universally reliable tool to assure the convergence of a MCMC chain.
+Instead, it is advisable to use a variety of different tools that are aimed at doing so.
+Therefore, even though the chains seem to converge according to the statistical tests exploited, the tests may fail and the chains did not converge after all \citep{cowles1996markov}.
+
+%The statistical tests mentioned above have been carried out using the \fnurl{py-coda}{https://github.com/surhudm/py-coda} package which provides a python wrapper of some of the tools included in the CODA package in R \citep{coda}.
+
+%\section{Deprojection of the surface density profile}
+%\label{sec:deprojection_math}
+%We follow the procedure outlined by \citet{eisenstein2003deprojecting} to construct an estimator which can recover the spatial density profile from the observed surface density profile.
+The projected angular galaxy distribution $\Sigma(R)$ of a cluster can be found from the spatial distribution $\rho(r)$ by integration along the line of sight as
+%\begin{equation}
+%\Sigma(R)=\int_{-\infty}^{\infty} \rho(\sqrt{R^2+Z^2})\mathrm{dZ}. \label{eq:c1}
+%\end{equation}
+%It is known that the integral in Equation~\ref{eq:c1} can be inverted as an Abel integral to obtain
+%\begin{equation}
+%\rho(r) = -\frac{1}{\pi} \int_{r}^{\infty} \frac{\mathrm{d}\Sigma}{\mathrm{d}R}\frac{\mathrm{d}R}{\sqrt{R^2-r^2}}. \label{eq:c2}
+
+%\end{equation}
+%Involving a derivative of the measured quantity $\Sigma(R)$ this integral is very noisy and therefore difficult to compute in practice.
+To overcome this we consider measuring $\Sigma(R)$ only as an integral weighted by as window function $W(r)$, where the choice of $W(r)$ can be used to pick up the number of galaxies in a radial bin.
+Therefore, $\Sigma(R)$ is approximated by the galaxy count $\Delta$ as
+%\begin{equation}
+%\Delta N = \int_{0}^{\infty} W(r) \rho(r) 4 \pi r^2 dr.
+%\end{equation}
+%We proceed by using Equation~\ref{eq:c2} and partial integration as
+%\begin{align}
+%\Delta N &=& \int_{0}^{\infty} W(r) \left[ \frac{-1}{\pi} \int_{r}^{\infty} \frac{d\Sigma}{dR}\frac{dR}{\sqrt{R^2-r^2}} \right] 4 \pi r^2 dr  \label{eq:rho} \\
+%&=& -\frac{1}{\pi} \int_{0}^{\infty} dR \frac{d\Sigma}{dR} \int_{0}^{R} 4 \pi r^2 W(r) \frac{dr}{\sqrt{R^2-r^2}}\\
+%&=& -4 \int_{0}^{\infty} dR \frac{d\Sigma}{dR} \int_{0}^{R} W(r) \frac{r^2 dr}{\sqrt{R^2-r^2}} \\
+%&=& -4 \int_{0}^{\infty} dR \frac{d\Sigma}{dR} G(R)\\
+%&=& 4 \int_{0}^{\infty} dR \frac{dG}{dR} \Sigma(R) \label{eq:parts}\\
+%&=& 4 \int_{0}^{\infty} dR \frac{dG}{dR} \sum_i \frac{\delta_{\rm D}(R-R_i)}{2\pi R_i} \label{eq:discrete} \\
+%&=& \sum \frac{2}{\pi R_i} \left.\frac{dG}{dR}\right|_{R_i}
+%\end{align}
+%where we replaced the angular distribution by a discrete sum over the single galaxies in the sample located at projected radii $R_i$ from the cluster center and we defined
+%\begin{equation}
+%G(R) = \int_{0}^{R} W(r) \frac{r^2 dr}{\sqrt{R^2-r^2}}.
+%\end{equation}
+%Let us parametrize the three dimensional distance as $r=R \sin(\theta)$ yielding
+%\begin{align}
+%G(R) &=& \int_{0}^{\pi/2} W(R\sin\theta) \frac{R^2 \sin^2\theta R \cos\theta d\theta}{R\cos\theta}\\
+%&=& \int_{0}^{\pi/2} W(R\sin\theta) R^2 \sin^2\theta  d\theta.
+%\end{align}
+%Now let us consider a radial bin $r\in[a, b]$, thus $W(r)=\Theta(r-a) - \Theta(r-b)$, where $\Theta$ is the Heaviside step function.
+In this case we have three regimes for any given radius $R$; (i) $R<a$, (ii) $R\in[a, b]$, (iii) $R>b$.
+Let us deal with each of these cases separately.
+
+%\paragraph{Case (i): $R<a$}
+%In case (i), $\forall \theta\in[0, \pi/2]$, $W(R\sin\theta)=0$. Therefore, $G(R)=0$ and hence the derivative is zero.
+
+%\paragraph{Case (ii): $R\in[a,b]$}
+%In case (ii), $W(R\sin\theta)$ is non-zero $\forall \theta\in[\theta_{\rm min}, \pi/2]$, where $R\sin\theta_{\rm min}=a$. Therefore, the integral for G(R) reduces to
+%\begin{eqnarray}
+%G(R) &=& \int_{\theta_{\rm min}}^{\pi/2} R^2 \sin^2\theta  d\theta \\
+%&=& \frac{R^2}{2} \left[\theta-\sin\theta\cos\theta\right]_{\theta_{\rm min}}^{\pi/2}\\
+%&=& \frac{R^2}{2} \left[ \frac{\pi}{2} - (\theta_{\rm min}-\sin\theta_{\rm min}\cos\theta_{\rm min})  \right] \\
+%\frac{dG}{dR} &=& R  \frac{\pi}{2} -  R  \left[\tan^{-1}\left(\frac{x/R}{\sqrt{1-x^2/R^2}}\right) - \frac{x/R}{\sqrt{1-x^2/R^2}}\right]_a \nonumber \\
+%&=& R \left[ \frac{\pi}{2} - f(a) \right] \\
+%\frac{2}{\pi R}\frac{dG}{dR} &=& 1 - \frac{2}{\pi} f(a)
+%\end{eqnarray}
+%where we defined
+%\begin{equation}
+%f(x)=\tan^{-1}\left(\frac{x/R}{\sqrt{1-x^2/R^2}}\right) - \frac{x/R}{\sqrt{1-x^2/R^2}}
+%\end{equation}
+
+%\paragraph{Case (iii): $R>b$}
+%In case (iii), $W(R\sin\theta)$ is non-zero $\forall \theta\in[\theta_{\rm min}, \theta_{\rm max}]$, where $R\sin\theta_{\rm min}=a$, and $R\sin\theta_{\rm max}=b$.
+Therefore, the integral for G(R) reduces to
+%\begin{eqnarray}
+%G(R) &=& \int_{\theta_{\rm min}}^{\theta_{\rm max}} R^2 \sin^2\theta  d\theta \\
+%&=& \frac{R^2}{2} \left[\theta-\sin\theta\cos\theta\right]_{\theta_{\rm min}}^{\theta_{\rm max}}\\
+%&=& \frac{R^2}{2} \left[\sin^{-1}\left(\frac{x}{R}\right) - \frac{x}{R}\sqrt{1-\frac{x^2}{R^2}} \right]_{a}^{b} \\
+%&=& \left[\frac{R^2}{2} \sin^{-1}\left(\frac{x}{R}\right) - \frac{x}{2}\sqrt{R^2-x^2} \right]_{a}^{b} \\
+%\frac{dG}{dR} &=& \left[R  \sin^{-1}\left(\frac{x}{R}\right) - \frac{1}{2} \frac{x}{\sqrt{1-x^2/R^2}} - \frac{x}{2}\frac{1}{\sqrt{1-x^2/R^2}}\right]_a^b\\
+%\frac{dG}{dR} &=& R  \left[\sin^{-1}\left(\frac{x}{R}\right) - \frac{x/R}{\sqrt{1-x^2/R^2}}\right]_a^b\\
+%\frac{dG}{dR} &=& R  \left[\tan^{-1}\left(\frac{x/R}{\sqrt{1-x^2/R^2}}\right) - \frac{x/R}{\sqrt{1-x^2/R^2}}\right]_a^b \\
+%&=& R [f(b) - f(a)] \\
+%\frac{2}{\pi R}\frac{dG}{dR} &=& \frac{2}{\pi} [ f(b) - f(a)]
+%\end{eqnarray}
+
+%\subsection{Masking and survey boundaries}
+%The surface area normalization in Eq.~\ref{eq:discrete} assumes that the entire annulus at radius $R_i$ around a given cluster lays within the survey area.
+But this may not be true due to masking effects or survey boundaries.
+In this case the normalization is modified to be
+%\begin{equation}
+%\Sigma(R) = \sum_i \frac{1}{2\pi\phi(R)} \delta_{\rm D}(R-R_i),
+%\end{equation}
+%where $\phi(R)$ is the fraction of the annulus that lays within the survey area.
+
+%%% \section{Estimating the surface density profile}
+%%% \label{sec:est_surf_den}
+%%% Following the discussion outlined in \citet{kerscher2000comparison} we shall introduce how the two-point correlation function can be estimated taking into consideration the contaminations mentioned above.
+%%% Let us define a counting function $P_{\mathrm{(X,Y)}}(D)$, that counts how many objects from the catalog Y can be found at a distance $D$ from any object in catalog X (or vice versa)
+%%% \begin{equation}
+%%% P_{\mathrm{(X,Y)}}(D)=\sum_{x \in X} \sum_{y \in Y} \Phi_{\mathrm{D}}(x,y)
+%%% \end{equation}
+%%% where 
+%%% \begin{equation}
+%%%   \Phi_{\mathrm{D}}(x,y) = \left.
+%%%   \begin{cases}
+%%%     0, & \text{for } d(x,y)<D-\Delta \\
+%%%     1, & \text{for }  D-\Delta \leq d(x,y) \leq D+\Delta \\
+%%%     0, & \text{for } d(x,y)>D+\Delta
+%%%   \end{cases}\right.
+%%% \end{equation}
+%%% with $d(x,y)$ being the separation between the two objects $x$ and $y$.
+Since, X $\neq$ Y holds at all times in this work (no auto-correlations of catalogs considered) the normalized counting function can be defined as
+%%% \begin{equation}
+%%% P^{\mathrm{N}}_{\mathrm{(X,Y)}}(D)=\frac{P_{\mathrm{(X,Y)}}(D)}{N_{\mathrm{X}} N_{\mathrm{Y}}}
+%%% \end{equation}
+%%% with $N_{\mathrm{X}}$ and $N_{\mathrm{Y}}$ being the total number of objects residing in the catalogs X and Y, respectively. 
+%%% Recalling that we would like to cross-correlate clusters with galaxies we identify one of the catalogs with the cluster catalog (say X) and the other one with the galaxy catalog (say Y).
+Further, we note that we are considering the projected, radial separation of objects.
+Therefore, let us replace the general separation $D$ by the projected, radial distance $R$.
+For either of the two catalogs we have two choices at hand; namely the actual catalog (further denoted as D) and the corresponding random catalog (further denoted as R) leading to four different counting functions that cross-correlate all the different catalogs; $P^{\mathrm{N}}_{\mathrm{(D,D)}}(R)$,$P^{\mathrm{N}}_{\mathrm{(D,R)}}(R)$,$P^{\mathrm{N}}_{\mathrm{(R,D)}}(R)$,$P^N_{\mathrm{(R,R)}}(R)$.
+%%% Starting from those normalized counting functions estimators of the two-point correlation function can be constructed.
+With the two-point correlation function of galaxies being one of the main statistical tools in cosmology, a vast number of such estimators can be found in the literature.
+We use the Davis \& Peebles estimator ($\fhat{\xi_{\mathrm{DP}}(r)}$ ; \citep{davis1983survey} ; DP) which estimates the uncorrelated component by using only a random sample for one of the samples (clusters in our case).
+A more sophisticated choice would be the Landy \& Szalay estimatior ($\fhat{\xi_{\mathrm{LS}}(r)}$ ; \citep{landy1993bias} ; LS) which exploits two random samples, one for each catalog
+%%% \begin{align}
+%%% \fhat{\xi_{\mathrm{DP}}(R)}=\frac{P^{\mathrm{N}}_{\mathrm{(D,D)}}(R)}{P^{\mathrm{N}}_{\mathrm{(D,R)}}(R)}-1\\
+%%% \fhat{\xi_{\mathrm{LS}}(R)}=\frac{P^{\mathrm{N}}_{\mathrm{(D,D)}}(R)-P^{\mathrm{N}}_{\mathrm{(D,R)}}(R)-P^{\mathrm{N}}_{\mathrm{(R,D)}}(R)+P^{\mathrm{N}}_{\mathrm{(R,R)}}(R)}{P^{\mathrm{N}}_{\mathrm{(R,R)}}(R)}
+%%% \end{align}
+%%% Hence, we have constructed two estimators for the surface density $\xi(R)$.
+To estimate the covariance of the calculated surface density profile a jackknife re-sampling approach is taken \citep{efron1982jackknife}.
+The clusters are subdivided into 21 different jackknife samples.
+The random clusters are subdivided in the same fashion.
+In each jackknife bin the redshifts of the random clusters are drawn from the redshifts of the actual clusters in that bin such that the random clusters in each bin inherit the same redshift distribution as their real counterparts.
+Doing so we construct a set of 30 jackknife estimates for the surface density function
+%%% \begin{equation}
+%%% \fhat{\xi^{\mathrm{Jack}}_j (R)}=\frac{1}{n-1}\sum^n_{i=1,i\neq j} \fhat{\xi_i (R)}
+%%% \end{equation}
+%%% where $j \in \{1,..,30\}$ and $n=30$.
+The $\fhat{\xi_i (R)}$ are the estimates of the surface density function as inferred when considering only the clusters in the jackknife sample $i$.
+The average $\fbar{\xi(R)}$ and the covariance $\mathrm{Cov}(R_1,R_2)$ of the surface density function are then constructed as
+%%% \begin{equation}
+%%% \fbar{\xi(R)}=\frac{1}{n}\sum_{j=1}^n \fhat{\xi^{\mathrm{Jack}}_j (R)}
+%%% \end{equation}
+%%% and 
+%%% \begin{equation}
+%%% \mathrm{Cov}(R_1,R_2)=\frac{n-1}{n}\sum_{j=1}^n (\fhat{\xi^{\mathrm{Jack}}_j (R_1)} - \fbar{\xi(R_1)}) \cdot (\fhat{\xi^{\mathrm{Jack}}_j (R_2)} - \fbar{\xi(R_2)}).
+%%% \end{equation}
+
 \section{Cornerplots}
@@
 fitting parameters corresponding to the functional
-form in Equation~\ref{eq:full}. We obtained the distributions by  using the
+form in Equation~\ref{eq:model}. We obtained the distributions by  using the
 affine invariant Markov Chain Monte Carlo sampler of
@@
 the fitting parameters corresponding to the functional
-form in Equation~\ref{eq:full}. We cross-correlated PSZ2 galaxy clusters with
+form in Equation~\ref{eq:model}. We cross-correlated PSZ2 galaxy clusters with
 galaxies form the PS 21 galaxy catalog to establish this figure.}
@@
 the fitting parameters corresponding to the functional
-form in Equation~\ref{eq:full}. We cross-correlated PSZ2 galaxy clusters with
+form in Equation~\ref{eq:model}. We cross-correlated PSZ2 galaxy clusters with
 galaxies form the PS 21.5 galaxy catalog to establish this figure.}
@@
 the fitting parameters corresponding to the functional
-form in Equation~\ref{eq:full}. We cross-correlated PSZ2 galaxy clusters with
+form in Equation~\ref{eq:model}. We cross-correlated PSZ2 galaxy clusters with
 galaxies form the PS 22 galaxy catalog to establish this figure.}
@@
 the fitting parameters corresponding to the functional
-form in Equation~\ref{eq:full}. We cross-correlated PSZ2 galaxy clusters with
+form in Equation~\ref{eq:model}. We cross-correlated PSZ2 galaxy clusters with
 galaxies form the PS 21.5 galaxy catalog. Only the galaxies labeled
@@
 the fitting parameters corresponding to the functional
-form in Equation~\ref{eq:full}. We cross-correlated PSZ2 galaxy clusters with
+form in Equation~\ref{eq:model}. We cross-correlated PSZ2 galaxy clusters with
 galaxies form the PS 21 galaxy catalog. Only the galaxies labeled as

### 2018-09-13 BCG_correction/download.sh

@@ -1,0 +1,15 @@
+#! /bin/bash
+
+HTTP_FILE = 'PS_https.dat'
+NAME_FILE = 'PS_names.dat'
+OUTDIR = './orignial_picuters'
+
+
+LINES=$(wc -l < ../${NAME_FILE})
+
+for (( c=1; c<=$LINES; c++ ))
+do 
+    HTTP=`cat ../${HTTP_FILE} | head -$c | tail -1`
+    NAME=`cat ../${NAME_FILE} | head -$c | tail -1`
+    wget $HTTP -w 2 --random-wait -O ${OUTDIR}/${NAME} 
+done

### 2018-09-13 BCG_correction/edge_correction.py

@@ -1,0 +1,58 @@
+# Completes pictures located on edges of skycells
+import os
+import numpy as np
+from glob import glob
+import numpy as np
+import sys
+sys.path.insert(0,'../toolbox')
+import tools
+import frogress
+
+
+if __name__=="__main__":
+
+    indir = "./Pan-STARRS_Pics/original_pictures/" #Input directory containing downloaded pictures
+    outdir = "./Pan-STARRS_Pics/edge_corrected/" #Output directory for corrected pictures
+    conf_path = "configfile.csv" #Output file of the readin process
+    it = 0 #Pictures to skip
+
+
+    picnames = glob(indir+"*") 
+    names, ras, decs, widths, heights, pros, skys, outs = tools.edge_check(picnames, conf_path)
+    print("There are %s objects that need to be corrected" % names.size)
+
+    np.savetxt(outdir + "names.txt", names, fmt = '%.s')
+    np.savetxt(outdir + "ras.txt", ras)
+    np.savetxt(outdir + "decs.txt", decs)
+    np.savetxt(outdir + "widths.txt", widths)
+    np.savetxt(outdir + "heights.txt", heights)
+    np.savetxt(outdir + "pros.txt", pros)
+    np.savetxt(outdir + "skys.txt", skys)
+    np.savetxt(outdir + "outs.txt", outs)
+
+    names = np.genfromtxt(outdir + "names.txt", dtype=str)
+    ras = np.genfromtxt(outdir + "ras.txt")
+    decs = np.genfromtxt(outdir + "decs.txt")
+    widths = np.genfromtxt(outdir + "widths.txt")
+    heights = np.genfromtxt(outdir + "heights.txt")
+    pros = np.genfromtxt(outdir + "pros.txt")
+    skys = np.genfromtxt(outdir + "skys.txt")
+    outs = np.genfromtxt(outdir + "outs.txt")
+
+    names = names[it:]
+    ras = ras[it:]
+    decs = decs[it:]
+    widths = widths[it:]
+    heights = heights[it:]
+    pros = pros[it:]
+    skys = skys[it:]
+    outs = outs[it:]
+
+
+    for j in range(len(names)):
+            names[j] = str(outdir) + str(os.path.basename(names[j]))
+
+    for i in frogress.bar(range(len(names))):
+            tools.edge_correct(names[i],pros[i],skys[i],ras[i],decs[i],outs[i],widths[i],heights[i],indir,outdir)
+
+

### 2018-09-13 BCG_correction/readin.py

@@ -1,0 +1,229 @@
+#Reads original Planck cluster catalog and gets Pan-STARRS picture-names
+# coding=utf-8
+import pandas as pd
+import sys
+sys.path.insert(0,'../toolbox')
+import tools
+import numpy as np
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+from astropy.io import fits
+
+
+def dec2deg(sign, hd, min, sec):
+    """
+    Converts declination to degrees
+
+    Parameters
+    ----------
+    hd : int
+    degrees
+    m : int
+    arcminutes
+    s : float
+    arcseconds
+
+    Returns
+    -------
+    hd : float
+    A decimal number
+
+    """
+    return sign*(np.absolute(hd) + min/60.0 + sec/3600.0)
+
+def ra2deg(hd, min, sec):
+    """
+    Converts ra to degrees
+
+    Parameters
+    ----------
+    hd : int
+    hours
+    m : int
+    minutes
+    s : float
+    seconds
+
+    Returns
+    -------
+    hd : float
+    A decimal number
+
+        """
+    return (np.float(hd) + min/60.0 + sec/3600.0)*360./24.
+
+def convert_ra_from_list(listobj):
+    hd = float(listobj[0])
+    mts = float(listobj[1])
+    sec = float(listobj[2])
+    return ra2deg(hd, mts, sec)
+
+
+def convert_dec_from_list(listobj):
+    #sign = float(spl[0][0:1]+"1")
+    sign = np.sign(float(listobj[0]+"1"))
+    hd = float(listobj[0][1:])
+    mts = float(listobj[1])
+    sec = float(listobj[2])
+    return dec2deg(sign, hd, mts, sec)
+
+
+def read_Planck(inputfile, output_full):
+    #Reading FITS data into npy table
+    print("Reading data from original catalog")
+    hdulist = fits.open(inputfile)
+    head = hdulist[0].header
+    body = hdulist[1].data
+    full = pd.DataFrame(body)
+    full.to_csv(output_full, index=False)
+    cols = hdulist[1].columns
+    data = np.zeros((1,8))
+    length = body['INDEX'][-1]
+
+    ra = np.asarray(body['RA'])
+    dec = np.asarray(body['DEC'])
+    redshift = np.asarray(body['REDSHIFT'])
+    mass = np.asarray(body['MSZ'])
[…]

### 2018-09-13 BCG_correction/show.py

@@ -1,0 +1,169 @@
+#! coding=utf8
+#Surhud's Library for getting the coordinates from clicking on picture
+import numpy as np
+import matplotlib
+import matplotlib.image as mpimg
+matplotlib.use("TkAgg")
+import pylab as pl
+import pandas
+from glob import glob
+import sys
+import astropy.wcs as wcs
+import numpy as np
+from astropy.coordinates import SkyCoord
+import csv
+
+def get_ra_dec(x, y, proj):
+    c = SkyCoord.from_pixel(x, y, proj, origin=0)
+    return c.ra.degree, c.dec.degree
+
+pixscale=0.25/3600
+
+def construct_wcs_alt(ra0, dec0, width, height):
+    """Construct world coordinate system."""
+    w = wcs.WCS(naxis=2)
+    w.wcs.crpix = [0.5 * (width + 1), 0.5 * (height + 1)]
+    radiusx = 0.5 * width * pixscale
+    cdeltx = np.rad2deg(np.tan(np.deg2rad(radiusx))) / (0.5 * (width - 1))
+    radiusy = 0.5 * height * pixscale
+    cdelty = np.rad2deg(np.tan(np.deg2rad(radiusy))) / (0.5 * (height - 1))
+    w.wcs.cdelt = [cdeltx, cdelty]
+    w.wcs.crval = [ra0, dec0]
+    w.wcs.ctype = ["RA---TAN", "DEC--TAN"]
+    w.wcs.cunit = ['deg', 'deg']
+    return w
+
+
+def construct_wcs(ra0, dec0, radius, width):
+    proj = wcs.WCS()
+    proj.naxis = [width, width]
+
+    proj.wcs.ctype = ['RA---TAN', 'DEC--TAN']
+    proj.wcs.cunit = ['deg', 'deg']
+    proj.wcs.crval = [ra0, dec0]
+
+    crpix = 0.5 * (width + 1)
+    proj.wcs.crpix = [crpix, crpix]
+    proj.tunit = ['prob deg-2']
+    
+    cdelt = np.rad2deg(np.tan(np.deg2rad(radius))) / (0.5 * (width - 1))
+    proj.wcs.cdelt = [-cdelt, cdelt]
+
+    proj.wcs.radesys = 'ICRS'
+
+    return proj
+
+def get_params(fname):
+    print(fname.split("&"))
+    ra, dec, width, height = fname.split("&")
+    ra = float(ra.split("=")[1])
+    dec = float(dec.split("=")[1])
[…]

### 2018-09-13 Mest/10_run_conversion.sh

@@ -1,0 +1,6 @@
+#PBS -lnodes=1:ppn=1,walltime=48:00:00
+#PBS -N MCMC_1
+#PBS -q tiny
+cd /home/dominik.zuercher/Documents/RSP_Pro/Mest
+python conversion_stats.py --modded 1 --type_ "Planck_PS_21_reloaded" --add "_best"  >output1.log 2>&1
+

### 2018-09-13 Mest/1_MLE_finder.py

@@ -1,0 +1,336 @@
+#! coding=utf8
+import sys
+sys.path.insert(0,'/home/dominik.zuercher/Documents/RSP_Pro/toolbox')
+import tools
+import scipy.integrate as integrate
+import scipy.special as special
+from scipy.optimize import fmin
+import numpy as np
+import pandas as pd
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt 
+import corner
+import emcee
+from scipy.linalg import inv
+
+
+def MLE_procedure(type_, mc):
+    input_dir = "/work/dominik.zuercher/Output/splashpipe/"+type_
+    output_dir = "/work/dominik.zuercher/Output/Mest/"+type_
+    data = pd.read_csv("%s/xi_2d.dat" % (input_dir), header = None, sep = ' ')
+    cov_data = pd.read_csv("%s/xi_2d_cov.dat" % (input_dir), header = None, sep = ' ')
+    data = np.asarray(data.values)
+    cov = np.asarray(cov_data.values)
+
+    rr = data[:,0]
+    yy = data[:,1]
+    yy_err = data[:,2]
+    idx = (data[:,0] > 0.0) & (data[:,0] < radmax) #radial cut
+    rr = rr[idx]
+    yy = yy[idx]
+    yy_err = yy_err[idx]
+    cov = np.transpose(cov[idx])[idx]
+    invcov = inv(cov)
+    if diag == True:
+        invcov = np.diag(np.diag(invcov))
+    """
+    fig = plt.figure(1)
+    plt.matshow(cov)
+    plt.colorbar()
+    plt.savefig("%s/%s_covariance.pdf" % (input_dir, type_))
+    rij = np.zeros_like(cov)
+    for i in range(cov.shape[0]):
+        for j  in range(cov.shape[1]):
+            rij[i,j] = cov[i,j]/np.sqrt(cov[i,i]*cov[j,j])
+
+    fig = plt.figure(2)
+    plt.matshow(rij)
+    plt.colorbar()
+    plt.savefig("%s/%s_covmod.pdf" % (input_dir, type_))
+    """
+    if (type_=='Planck_PS_21.5_reloaded') & (mc==False):
+        rhos=-1.
+        alpha=np.log10(0.2)
+        rs=0.2
+        rho0=0.03
+        se=1.2
+        rt=0.4
+        beta=np.log10(4.0)
[…]

### 2018-09-13 Mest/2_run_mcmc.sh

@@ -1,0 +1,7 @@
+#PBS -lnodes=1:ppn=28,walltime=48:00:00
+#PBS -N MCMC_1
+#PBS -q mini
+cd /home/dominik.zuercher/Documents/RSP_Pro/Mest
+module load mpi/mpich-x86_64
+mpirun python mcmc_sampler.py --steps 100000 --prevrun 29 --size 28 --type_ "Planck_PS_21.5_blue_spline" --add "_best"  >/work/dominik.zuercher/Output/Mest/logs/output_blue.log 2>&1
+

### 2018-09-13 Mest/3_combine_parameters.sh

@@ -1,0 +1,38 @@
+#! /bin/bash
+
+function combine_chains {
+    OUTDIR="/work/dominik.zuercher/Output/Mest"
+    OutFileName="${OUTDIR}/$1/chainstate_full.txt"
+    rm $OutFileName
+    base="${OUTDIR}/$1/chainstates/chainstate_${1}_${prior}"
+    if [ $mc -eq 1 ]
+    then
+        echo "bla"
+        base=$base'_mc'
+    fi
+    for i in {1..100}
+    do
+        filename=${base}_${i}.txt
+        echo $filename
+        if [ "$filename"  != "$OutFileName" ] 
+        then
+            cat $filename >>  $OutFileName
+        fi
+    done
+}
+
+
+##########################
+#Main
+##########################
+
+types='Planck_PS_21.5_blue_spline Planck_PS_21.5_red_spline'
+prior='best'
+mc=1
+
+for type in $types
+do
+    combine_chains $type 
+done
+
+

### 2018-09-13 Mest/4_calc_stats.sh

@@ -1,0 +1,7 @@
+#PBS -lnodes=35:ppn=28,walltime=48:00:00
+#PBS -N calc_stats_1
+#PBS -q large
+cd /home/dominik.zuercher/Documents/RSP_Pro/Mest
+module load mpi/mpich-x86_64
+mpirun python mcmc_calc_stats.py --type_ "Planck_PS_21.5_red_spline" --add "_best"  > /work/dominik.zuercher/Output/Mest/logs/output_calc_red.log 2>&1
+

### 2018-09-13 Mest/5_combine_MCMC_data.sh

@@ -1,0 +1,29 @@
+#! /bin/bash
+
+function combine_data {
+    OUTDIR="/work/dominik.zuercher/Output/Mest"
+    OutFileName="${OUTDIR}/$1/Data_full.txt"
+    rm $OutFileName
+    base="${OUTDIR}/$1/data_parts/MCMC_data"
+    for i in {0..979}
+    do
+        filename=${base}_${i}.txt
+        echo $filename
+        if [ "$filename"  != "$OutFileName" ]
+        then
+            cat $filename >>  $OutFileName
+        fi
+    done
+}
+
+##########################
+#Main
+##########################
+prior='best'
+types='Planck_PS_21.5_red_spline Planck_PS_21.5_blue_spline'
+for type in $types
+do
+    combine_data $type 
+done
+
+

### 2018-09-13 Mest/6_extractor.py

@@ -1,0 +1,76 @@
+import sys
+sys.path.insert(0,'/home/dominik.zuercher/Documents/RSP_Pro/toolbox')
+import tools
+import scipy.integrate as integrate
+import scipy.special as special
+import numpy as np
+import pandas as pd
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import corner
+import frogress
+
+
+def correct_chain(type_,add,modded=False):
+    #Read calculated values
+    print("Reading MCMC_data...")
+    
+    if modded==False:
+        value_array=pd.read_csv("%s/%s/Data_full.txt" % (output_dir, type_), sep=' ',header=None,error_bad_lines=False)
+    else:
+        value_array=pd.read_csv("%s/%s/Data_full_modded.txt" % (output_dir, type_), sep=' ',header=None,error_bad_lines=False)
+
+    value_array=np.asarray(value_array.values)
+    #Read chains
+    print("Reading chains...")
+    if modded==False:
+        samples=np.loadtxt("%s/%s/chainstate_full.txt" % (output_dir, type_))
+
+    else:
+        data = pd.read_csv("%s/%s/chainstate_full_modded.txt" % (output_dir, type_), sep=' ',header=None,error_bad_lines=False)
+
+    samples=samples.astype(float)
+    #Find broken chains (do visual inspection of chain file and come up with criterion)
+    print("Removing broken chains...")
+    if broken_walker!=None:
+	broken_walkers=[broken_walker+i*nwalkers for i in range(steps)]
+	#Remove broken chains
+	value_array=np.delete(value_array,broken_walkers,axis=0)
+	samples=np.delete(samples,broken_walkers,axis=0)
+
+    #Find nan values from rhodev_array
+    print("Search and remove NAN entries...")
+    rhodev_array=value_array[:,rsteps*3:rsteps*4]
+    fix=np.isnan(rhodev_array)
+    row=np.invert(np.any(fix,axis=1))
+    print("Found %d NAN derivatives" % (value_array.shape[0] - np.sum(row)) )
+
+    #Remove nan value entries from rhodev_array
+    value_array=value_array[row,:]
+
+    print("Saving modded MCMC_data...")
+    np.savetxt("%s/%s/Data_full_modded.txt" % (output_dir, type_), value_array)
+
+    samples=samples.astype(float)
+    print("Saving modded chains...")
[…]

### 2018-09-13 Mest/7_calculate_color_fractions.py

@@ -1,0 +1,61 @@
+import numpy as np
+import pandas as pd
+
+
+def calc_color_frac(red_type, blue_type, add, output_dir):
+
+    if mc == True:
+	add += "_mc"
+    print("Sort according to miscentering parameters...")
+    red_parameter_array=pd.read_csv("%s/%s/chainstate_full_modded.txt" % (output_dir, red_type), sep=' ',header=None,error_bad_lines=False,usecols=[8,9])
+
+    blue_parameter_array=pd.read_csv("%s/%s/chainstate_full_modded.txt" % (output_dir, blue_type), sep=' ',header=None,error_bad_lines=False,usecols=[8,9])
+
+
+    red_parameter_array=np.asarray(red_parameter_array)
+    blue_parameter_array=np.asarray(blue_parameter_array)
+
+    print("Ordering")
+    red_order=np.lexsort((red_parameter_array[:,0],red_parameter_array[:,1]))
+    blue_order=np.lexsort((blue_parameter_array[:,0],blue_parameter_array[:,1]))
+
+    print("Reading Data arrays...")
+    red_data_array=pd.read_csv("%s/%s/Data_full_modded.txt" % (output_dir, red_type), sep=' ',header=None,error_bad_lines=False,usecols=range(rsteps,rsteps*2))
+
+    blue_data_array=pd.read_csv("%s/%s/Data_full_modded.txt" % (output_dir, blue_type), sep=' ',header=None,error_bad_lines=False,usecols=range(rsteps,rsteps*2))
+
+    red_rho_array=np.asarray(red_data_array.values)
+    blue_rho_array=np.asarray(blue_data_array.values)
+
+    print("Reordering arrays...")
+    red_rho_array=red_rho_array[red_order,:]
+    blue_rho_array=blue_rho_array[blue_order,:]
+
+    red_frac=red_rho_array[red_cutoff:]/(blue_rho_array[blue_cutoff:]+red_rho_array[red_cutoff:])
+    blue_frac=blue_rho_array[blue_cutoff:]/(blue_rho_array[blue_cutoff:]+red_rho_array[red_cutoff:])
+
+    red_fracs = np.asarray(map(lambda v: (v[1], v[2]-v[1], v[1]-v[0]), zip(*np.percentile(red_frac, [16, 50, 84], axis=0))))
[…]

### 2018-09-13 Mest/8_calculate.py

@@ -1,0 +1,112 @@
+import sys
+sys.path.insert(0,'/home/dominik.zuercher/Documents/RSP_Pro/toolbox')
+import tools
+import scipy.integrate as integrate
+import scipy.special as special
+import numpy as np
+import pandas as pd
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import corner
+import frogress
+
+
+
+def cal_procedure(type_,add,modded=False):
+
+    #Reading data
+    if modded==False:
+        data_array=pd.read_csv("%s/%s/Data_full.txt" % (output_dir, type_), sep=' ',header=None,error_bad_lines=False)
+    else:
+        data_array=pd.read_csv("%s/%s/Data_full_modded.txt" % (output_dir, type_), sep=' ',header=None,error_bad_lines=False)
+
+    print("Read")
+    data_array=np.asarray(data_array.values)
+    sigma_array=data_array[:,0:rsteps]
+    rho_array=data_array[:,rsteps:rsteps*2]
+    dev_array=data_array[:,rsteps*2:rsteps*3]
+    rhodev_array=data_array[:,rsteps*3:rsteps*4]
+    rsp2d_array=data_array[:,rsteps*4]
+    rsp2d_array=rsp2d_array.reshape((rsp2d_array.size,1))
+    rsp3d_array=data_array[:,rsteps*4+1]
+    rsp3d_array=rsp3d_array.reshape((rsp3d_array.size,1))
+    chisquare_array=data_array[:,rsteps*4+2]
+    chisquare_array=chisquare_array.reshape((chisquare_array.size,1))
+    maxrhodev_array=data_array[:,rsteps*4+3]
+    maxrhodev_array=maxrhodev_array.reshape((maxrhodev_array.size,1))
+    maxinnerrhodev_array=data_array[:,rsteps*4+4]
+    maxinnerrhodev_array=maxinnerrhodev_array.reshape((maxinnerrhodev_array.size,1))
+
+
+    #Calculating percentile values
+    sigmas = np.asarray(map(lambda v: (v[1], v[2]-v[1], v[1]-v[0]), zip(*np.percentile(sigma_array, [16, 50, 84], axis=0))))
+    print("sigmas done")
[…]

### 2018-09-13 Mest/9_visualizer.py

@@ -1,0 +1,197 @@
+import sys
+sys.path.insert(0,'/home/dominik.zuercher/Documents/RSP_Pro/toolbox')
+import tools
+import scipy.integrate as integrate
+import scipy.special as special
+import numpy as np
+import pandas as pd
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import corner
+import frogress
+import matplotlib.cm as cm
+
+
+def vis_procedure(ndim,type_,add,modded=False,mc=False):
+    if mc==True:
+        ndim+=2
+    #Reading data
+    dat=pd.read_csv("%s/%s/xi_2d.dat" % (input_dir, type_), header=None,sep=' ')
+
+    dat = np.asarray(dat.values)
+    rr = dat[:,0]
+    yy = dat[:,1]
+    yy_err = dat[:,2]
+
+    idx = (dat[:,0] > 0.1) & (dat[:,0] < 10.0)
+    rr=rr[idx]
+    yy=yy[idx]
+    yy_err=yy_err[idx]
+    rrange=np.linspace(rr[0],rr[-1],rsteps)
+
+    plotdat=pd.read_csv("%s/%s/plotsave.dat" % (output_dir, type_) ,sep=' ',header=None)
+    plotdat=np.asarray(plotdat.values)
+    sigmas=plotdat[0:rsteps,:]
+    rhos=plotdat[rsteps:rsteps*2,:]
+    devs=plotdat[rsteps*2:rsteps*3,:]
+    rhodevs=plotdat[rsteps*3:rsteps*4,:]
+
+    splashdat=pd.read_csv("%s/%s/values.dat" % (output_dir, type_),sep=' ',header=None)
+    splashdat=np.asarray(splashdat.values)
+    rsp2ds=splashdat[0,:]
+    rsp3ds=splashdat[1,:]
+    chisquares=splashdat[2,:]
+    maxrhodevs=splashdat[3,:]
+    maxinnerrhodevs=splashdat[4,:]
+
+    #Plotting graphs
+    f, axarr = plt.subplots(ncols=2,nrows=2)
+    axarr[0,0].errorbar(rr, yy, yy_err, fmt=".")
+    axarr[0,0].plot(rrange,sigmas[:,0],'r-',label="MCMC fit")
[…]

### 2018-09-13 Mest/conversion_stats.py

@@ -1,0 +1,54 @@
+#! coding=utf8
+import numpy as np
+import pandas as pd
+import sys
+sys.path.insert(0,'/home/dominik.zuercher/Documents/RSP_Pro/toolbox')
+import tools
+from py_coda import read_pycoda,mcmc
+import argparse
+
+
+def calc_stats(type_, add, modded = False, nwalkers = 28):
+    if modded==False:
+        chain = np.loadtxt("%s/chains/%s%s/chainstate_%s%s.txt" % (output_dir, type_, add, type_, add))
+    else:
+        chain = np.loadtxt("%s/chains/%s%s/chainstate_%s%s_modded.txt" % (output_dir, type_, add, type_, add))
+    chain = chain.reshape((steps, nwalkers, ndim))
+    flatchain = chain.reshape((-1, ndim))
+    np.savetxt("%s/chains/%s%s/flatchain_%s%s.txt" % (output_dir, type_, add, type_, add), flatchain)
+
+    params = np.loadtxt("paramnames.in", dtype = str)
+    print("Read")
+    for num in range(nwalkers):
+	chain = flatchain[num::20,:]
+	mcmcobj = mcmc(params, chain, thin = 1)
+
+	mcmcobj.geweke(backend = "Agg", savefig = "%s/output/%s%s/%s%s_%s_" % (output_dir, type_, add, type_, add, num),fp="%s/output/%s%s/%s%s_%s_geweke.dat" % (output_dir, type_, add, type_, add, num))
+
+	statfile = open("%s/output/%s%s/%s%s_%s_stats.dat" % (output_dir, type_, add, type_, add, num), "w+")
+	mcmcobj.get_stats(fp = statfile)
+	statfile.close()
+
+	mcmcobj.plot_traces(backend = "Agg", savefig = "%s/output/%s%s/%s%s_%s_" % (output_dir, type_, add, type_, add, num))
+	mcmcobj.heidelberger_welch(fp = "%s/output/%s%s/%s%s_%s_heidelberg_welch.dat" % (output_dir, type_, add, type_, add, num))
+	mcmcobj.plot_autocorr(backend = "Agg", savefig = "%s/output/%s%s/%s%s_%s_" % (output_dir, type_, add, type_, add))
+
+
+
+if __name__ == "__main__":
+
+    output_dir = "/work/dominik.zuercher/Output/Mest"
+
+    steps = 100000
+    ndim = 8
+    nwalkers  = 28
+
[…]

### 2018-09-13 Mest/mcmc_calc_stats.py

@@ -1,0 +1,131 @@
+#! coding=utf8
+import numpy as np
+import pandas as pd
+import emcee
+from emcee.utils import MPIPool, sample_ellipsoid
+import sys
+sys.path.insert(0,'/home/dominik.zuercher/Documents/RSP_Pro/toolbox')
+import tools
+import functools
+import subprocess
+import argparse
+import subprocess as sub
+from subprocess import call
+
+
+def MCMC_calc_stats(ndim,rank,type_,add,mc):
+    call("mkdir -p %s/%s/data_parts" % (output_dir, type_), shell = 1)
+    if mc==True:
+        add=add+"_mc"
+        ndim+=2
+    #Reading of the data
+    print("Doing "+str(type_)+" with prior "+str(add))
+    data = pd.read_csv("%s/%s/xi_2d.dat" % (input_dir, type_), header=None, sep = ' ')
+    cov_data = pd.read_csv("%s/%s/xi_2d_cov.dat" % (input_dir, type_), header=None, sep = ' ')
+
+    data = np.asarray(data.values)
+    rr = data[:,0]
+    yy = data[:,1]
+    yy_err = data[:,2]
+    idx = (data[:,0] > 0.1) & (data[:,0] < radmax)
+    cov = np.asarray(cov_data.values)
+    cov=np.transpose(cov[idx])[idx]
+    rr=rr[idx]
+    yy=yy[idx]
+    yy_err=yy_err[idx]
+    rrange=np.linspace(rr[0],rr[-1],rsteps)
+
+    inv_cov=np.linalg.inv(cov)
+    if diag==True:
+        inv_cov=np.diag(np.diag(inv_cov))
+
+    chunky=int(steps/size)
+    rest=steps-chunky*size
+    mini=chunky*rank
+    maxi=chunky*(rank+1)
+    if rank>=(size-1)-rest:
+        maxi+=1+rank-(size-1-rest)
+        mini+=rank-(size-1-rest)
+    if rank==size-1:
+        maxi=steps
+    mini=int(mini)
+    maxi=int(maxi)
+
+    sigma_array = np.zeros((1,rrange.size))
+    rho_array = np.zeros((1,rrange.size))
+    dev_array=np.zeros((1,rrange.size))
+    rhodev_array=np.zeros((1,rrange.size))
+    rsp2d_array=np.zeros((1,1))
+    rsp3d_array=np.zeros((1,1))
[…]

### 2018-09-13 Mest/mcmc_sampler.py

@@ -1,0 +1,183 @@
+#! coding=utf8
+import numpy as np
+import pandas as pd
+import emcee
+from emcee.utils import MPIPool, sample_ellipsoid
+import sys
+sys.path.insert(0,'/home/dominik.zuercher/Documents/RSP_Pro/toolbox')
+import tools
+import functools
+import subprocess
+import argparse
+from subprocess import call
+
+
+
+def MCMC_procedure(type_, add, prevrun, mc = False):
+    if mc == True:
+        add = add + "_mc"
+
+    #Reading of the data
+    print("Doing %s with prior %s" % (type_, add))
+    data = pd.read_csv("%s/%s/xi_2d.dat" % (input_dir, type_), header = None, sep = ' ')
+    cov_data = pd.read_csv("%s/%s/xi_2d_cov.dat" % (input_dir, type_), header = None, sep = ' ')
+    if mc == False:
+        mlep = pd.read_csv(output_dir + "/" + type_ +"/MLE_parameters.txt", header = None)
+    else:
+        mlep = pd.read_csv(output_dir + "/" + type_ + "/MLE_parameters_mc.txt", header = None)
+
+    data = np.asarray(data.values)
+    rr = data[:,0]
+    yy = data[:,1]
+    yy_err = data[:,2]
+    idx = (data[:,0] > 0.1) & (data[:,0] < radmax)
+    cov = np.asarray(cov_data.values)
+    cov = np.transpose(cov[idx])[idx]
+    rr = rr[idx]
+    yy = yy[idx]
+    yy_err = yy_err[idx]
+    rrange = np.linspace(rr[0], rr[-1], rsteps)
+
+    mlep = np.asarray(mlep.values).reshape(mlep.size)
+
+    inv_cov = np.linalg.inv(cov)
+    if diag == True:
+        inv_cov = np.diag(np.diag(inv_cov))
+
+    #Initialize parallization
+    pool = MPIPool(loadbalance = True)
+
+    #Check for previousruns and draw inital parameters around MLE 
+    if pool.is_master():
+        call("mkdir -p %s/%s/chainstates" % (output_dir, type_), shell = 1)
+        call("mkdir -p %s/%s/pos" % (output_dir, type_), shell = 1)
+        if prevrun != 0:
+            p0 = np.loadtxt("%s/%s/pos/pos_%s%s_%s.dat" % (output_dir, type_, type_, add, prevrun))
+        else:
+            rhos_mle = mlep[0]
[…]

### 2018-09-13 Mest/percentiler.py

@@ -1,0 +1,135 @@
+from scipy.linalg import inv
+import sys
+sys.path.insert(0,'/home/dominik.zuercher/Documents/RSP_Pro/toolbox')
+import tools
+import pandas as pd
+import numpy as np
+from copy import deepcopy
+from mpi4py import MPI
+comm = MPI.COMM_WORLD
+rank = comm.rank
+size = comm.size
+
+
+type='Planck_PS'
+est='DR'
+
+
+def procedure(rank):
+	
+	ndim=8
+	steps=50000
+	nwalkers=42
+	runnum=50
+	
+	data = np.genfromtxt("/work/dominik.zuercher/MCMC_Store/chains/"+str(type)+"/chainstate_"+str(runnum)+".txt")
+	samples = data.reshape((nwalkers,steps,ndim))
+
+        chunky=int(steps/size)
+        rest=steps-chunky*size
+        mini=chunky*rank
+        maxi=chunky*(rank+1)
+        if rank>=(size-1)-rest:
+                maxi+=1+rank-(size-1-rest)
+                mini+=rank-(size-1-rest)
+        if rank==size-1:
+                maxi=steps-1
+        mini=int(mini)
+        maxi=int(maxi)
+	
+	data = pd.read_csv("/work/dominik.zuercher/DataStore/corr-pairs/"+str(type)+"/"+str(type)+"_plot("+str(est)+").dat", header=None, sep = ' ')
+	cov_data = pd.read_csv("/work/dominik.zuercher/DataStore/corr-pairs/"+str(type)+"/"+str(type)+"_plot_cov("+str(est)+").dat", header=None, sep = ' ')
+	data = np.asarray(data.values)
+	cov = np.asarray(cov_data.values)
+	cov=np.diag(np.diag(cov))
+	rr = data[:,0]
+	yy = data[:,1]
+	yy_err = data[:,2]
+
+	idx = (data[:,0] > 0.1) & (data[:,0] < 10.0)
+	rr=rr[idx]
+	yy=yy[idx]
+	yy_err=yy_err[idx]
+	cov=np.transpose(cov[idx])[idx]
+	invcov=inv(cov)
+
+	rrange=np.linspace(rr[0],rr[-1],200)
+	sigma_array = np.zeros((1,rrange.size))
+	rho_array = np.zeros((1,rrange.size))
+	dev_array=np.zeros((1,rrange.size))
+	rhodev_array=np.zeros((1,rrange.size))
+	#dev2_array=np.zeros((1,rrange.size))
[…]

### 2018-09-13 Pan-Starrs/1_run_preparator1.sh

@@ -1,0 +1,7 @@
+#PBS -lnodes=25:ppn=28,walltime=10:00:00
+#PBS -N preparator
+#PBS -q large
+cd /home/dominik.zuercher/Documents/RSP_Pro/Pan-Starrs
+module load mpi/mpich-x86_64
+echo "Started!!!"
+mpirun python PS_preparator.py --step 1 --mag_lim 22 --indir "/work/dominik.zuercher/DataStore/Pan-Starrs/original/split_deep" --outdir "/work/dominik.zuercher/DataStore/Pan-Starrs/PS_parts1/parts" >output1.txt 2>&1

### 2018-09-13 Pan-Starrs/2_combine_part1.sh

@@ -1,0 +1,7 @@
+#PBS -lnodes=1:ppn=28,walltime=48:00:00
+#PBS -N PS_combiner
+#PBS -q small
+cd /home/dominik.zuercher/Documents/RSP_Pro/Pan-Starrs/
+module load mpi
+mpirun ./combine_part1.sh >output.log 2>&1
+

### 2018-09-13 Pan-Starrs/3_run_preparator_part2.sh

@@ -1,0 +1,7 @@
+#PBS -lnodes=30:ppn=28,walltime=10:00:00
+#PBS -N preparator
+#PBS -q large
+cd /home/dominik.zuercher/Documents/RSP_Pro/Pan-Starrs
+module load mpi/mpich-x86_64
+echo "Started!!!"
+mpirun python PS_preparator.py --step 2 --mag_lim 21 --indir "/work/dominik.zuercher/DataStore/Pan-Starrs/PS_parts1/finished" --outdir "/work/dominik.zuercher/DataStore/Pan-Starrs/PS_parts2/parts" >output2.txt 2>&1

### 2018-09-13 Pan-Starrs/4_combine_part2.sh

@@ -1,0 +1,14 @@
+#! /bin/bash
+INDIR="/work/dominik.zuercher/DataStore/Pan-Starrs/PS_parts2/parts"
+OUTDIR="/work/dominik.zuercher/DataStore/Pan-Starrs"
+
+OutFileName="${OUTDIR}/PS_star_catalog.csv" # Fix the output name
+rm $OutFileName # Reset a counter
+for filename in "${INDIR}/*"
+do        
+    if [ "$filename"  != "$OutFileName" ] ;      # Avoid recursion 
+    then
+        tail -n+2 $filename >>  $OutFileName # Append from the 2nd line each file
+    fi
+done
+

### 2018-09-13 Pan-Starrs/5_remove_multiples.sh

@@ -1,0 +1,4 @@
+#! /bin/bash
+DIR="/work/dominik.zuercher/DataStore/Pan-Starrs"
+uniq -f5 "${DIR}/PS_catalog.csv" > "${DIR}/PS_catalog_deep_fin_stripped.csv"
+echo "multiples printed"

### 2018-09-13 Pan-Starrs/PS_preparator.py

@@ -1,0 +1,156 @@
+#Requires a splitted version of the PS catalog
+import numpy as np
+import pandas as pd
+import healpy as hp
+from operator import itemgetter, attrgetter, methodcaller
+import sys
+sys.path.insert(0,'/home/dominik.zuercher/Documents/RSP_Pro/toolbox')
+import tools
+import os
+from glob import glob
+import argparse
+
+
+def preparation1(rank):
+    print("Reading original PS catalog...")
+    catalog=pd.read_csv("%s/split_deep_part_%s.csv" % (catalog_dir, rank), delimiter = ',', names=['id','pro','sky','ira','idec','iPSFMag','iKronMag','SDSS_i_avg'], usecols = [0,1,2,5,7,9,11,16], header = None, dtype = {'id':str})
+    print("Throw away stars...")
+
+    catalog = catalog.loc[catalog.pro != -999.0]
+    catalog = catalog.loc[catalog.sky != -999.0]
+    catalog = catalog.loc[catalog.ira != -999.0]
+    catalog = catalog.loc[catalog.idec != -999.0]
+    catalog = catalog.loc[catalog.iPSFMag != -999.0]
+    catalog = catalog.loc[catalog.iKronMag != -999.0]
+    catalog = catalog.loc[catalog.SDSS_i_avg != -999.0]
+    
+    try:
+        catalog['mag'] = catalog["iKronMag"].values - catalog["SDSS_i_avg"].values
+    except:
+        print("Broken " + str(rank))
+        print(catalog["SDSS_i_avg"])
+    catalog['iPSFMag'] = np.asarray(catalog["iPSFMag"].values) - np.asarray(catalog["SDSS_i_avg"].values)
+
+    newcat = catalog[((catalog["iPSFMag"] - catalog['mag']) > 0.05) & (catalog['iPSFMag'] > 15.0) & (catalog['mag'] <= mag_lim)]
+    #For star catalog production
+    #newcat = catalog[((catalog["iPSFMag"] - catalog['mag']) < 0.05) & (catalog['mag'] <= 21.5)]
+
+    #Get rid of unnecessary columns
+    del newcat['iKronMag']
+    del newcat['iPSFMag']
+    del newcat['SDSS_i_avg']
+
+    print("Throw away objects in bad skycells (low mag limit or no mask available)...")
+    bads = hp.read_map("%s/bads_%s.fits" % (mask_path, mag_lim))
+
[…]

### 2018-09-13 Pan-Starrs/add_random_magnitude.py

@@ -1,0 +1,41 @@
+#Adds a random magnitude to the random catalogs (needed if chunked version of randoms is used)
+import sys
+import pandas as pd
+import numpy as np
+from mpi4py import MPI
+comm=MPI.COMM_WORLD
+rank=comm.rank
+size=comm.size
+mag_limit = sys.argv[1]
+
+def add_mag(rank,mag_limit):
+    print("Reading random chunk")
+    dfrand = pd.read_csv("Chunked_randoms/PS_randoms_%s.dat%03d.dat"%(mag_limit,rank),sep=",",names=["ra","dec","pro","sky"])
+
+    randsize=len(dfrand.ra.values)
+
+    np.random.seed()
+    chunkrandom=np.random.randint(0,980)
+
+    print("Reading galaxy chunk")
+    df = pd.read_csv("../Chunked_galaxies/PS_catalog_%s.csv%03d.dat"%(mag_limit,chunkrandom),names=["mag"],usecols=[4])
+
+    np.random.seed()
+    linerandoms=np.random.randint(0,len(df.mag.values),size=randsize)
+    
+    print("Drawing random magnitudes")
+    randmags=df.mag[linerandoms]
+    dfrand['mag']=randmags.values
+
+    print("Saving")
+    dfrand.to_csv("Chunked_randoms_magnitudes/PS_randoms_%s.dat%03d.dat"%(mag_limit,rank),sep=',',index=False,header=False)
+
+
+
+
+########################
+#MAIN
+########################
+
+add_mag(rank,mag_limit)
+

### 2018-09-13 Pan-Starrs/combine_part1.sh

@@ -1,0 +1,37 @@
+#! /bin/bash
+
+DIR="/work/dominik.zuercher/DataStore/Pan-Starrs/PS_parts1/"
+OFFSET=635
+SIZE=28
+
+
+TOTAL=$(((2643 - $OFFSET) / $SIZE))
+MIN=$(( $OFFSET + $OMPI_COMM_WORLD_RANK * $TOTAL ))
+MAX=$(( $OFFSET + ($OMPI_COMM_WORLD_RANK + 1) * $TOTAL - 1 ))
+
+rm "${DIR}finished/*"
+if [ "$OMPI_COMM_WORLD_RANK" == 27 ];
+        then
+        MAX=2643
+        fi
+echo "$MIN"
+echo "$MAX"
+for cell in $(seq $MIN $MAX);
+do
+
+OutFileName="${DIR}finished/PS_cell_${cell}.dat"                       # Fix the output name
+rm $OutFileName
+i=0 # Reset a counter
+for filename in "${DIR}parts/PS_cell_${cell}_rank*.dat";
+        do
+        if [ "$filename"  != "$OutFileName" ] ;      # Avoid recursion 
+                then
+                cat $filename >>  $OutFileName # Append from the 2nd line each file
+                i=$(( $i + 1 ))                        # Increase the counter
+        fi
+        done
+
+echo "${cell} done"
+
+done
+

### 2018-09-13 Pan-Starrs/reconstruct.py

@@ -1,0 +1,14 @@
+import sys
+import frogress
+
+base_name = "/work/dominik.zuercher/DataStore/Pan-Starrs/Chunked_randoms/PS_randoms_21.5"
+Outdir = "/work/dominik.zuercher/DataStore/Pan-Starrs"
+
+name_list = [base_name + "/PS_randoms_21.5.dat%03d.dat" % i for i in range(0,980)]
+fw = open(Outdir + "/PS_randoms_21.5_reconstructed.dat", "w+")
+for name in frogress.bar(name_list):
+    with open(name, "r") as f:
+	for line in f:
+	    fw.write(line)
+    f.close()
+fw.close()

### 2018-09-13 Pan-Starrs/run_mag_add.sh

@@ -1,0 +1,8 @@
+#PBS -lnodes=35:ppn=28,walltime=10:00:00
+#PBS -N 1_Planck_PS_redux
+#PBS -q large
+
+cd $PBS_O_WORKDIR
+pwd
+module load mpi/mpich-x86_64
+mpirun python add_random_magnitude.py 22 > output.log 2>&1 

### 2018-09-13 Pan-Starrs/split.py

@@ -1,0 +1,20 @@
+import sys
+
+Catalog = "/work/dominik.zuercher/DataStore/Pan-Starrs/Catalogs/PS_catalog_22.csv"
+
+Outdir = "/work/dominik.zuercher/DataStore/Pan-Starrs/Chunked_galaxies/PS_catalog_22/PS_catalog.csv"
+lines_per_file = 80972 #Number of lines in Catalog/980 and roundup
+
+with open(Catalog, "r") as f:
+    itern = 0
+    fnum = 0
+    for line in f:
+        if itern==0:
+            if fnum!=0:
+                fw.close()
+            print "Writing fnum", fnum
+            fw = open("%s" % Outdir + "%03d" % fnum,"w")
+            fnum = fnum + 1
+        fw.write(line)
+        itern = itern + 1
+        itern = itern%lines_per_file

### 2018-09-13 casjobs/download.sh

@@ -1,0 +1,12 @@
+#!/bin/bash
+
+#Downloads extracted files from casjobs Database
+
+OUTDIR="./output"
+NAME_BASE="part"
+
+for c in {0..48};
+do
+     HTTP="ps1images.stsci.edu/datadelivery/outgoing/casjobs/csv/${NAME_BASE}_${c}.csv"
+     wget $HTTP -w 2 --random-wait -O "${OUTDIR}/${NAME_BASE}_$c"
+done

### 2018-09-13 casjobs/query_generator.sh

@@ -1,0 +1,29 @@
+#!/bin/bash
+#Generates configuration files for the SQL queries to access the casjobs Database
+#Splits the query into 49 pieces
+#Requires dust data as dust_data object in MyDB
+OUTDIR="./queries"
+
+for i in {0..48};
+do
+    min=$((69+$i*3))
+    max=$((69+($i+1)*3))
+    
+    if [ "$i" -eq "48" ]
+    then
+	min=213
+	max=215
+    fi
+
+    echo "select objid,projectionID,skyCellID,primaryDetection,bestDetection,ira,iraErr,idec,idecErr,rPSFMag,rPSFMagErr,rKronMag,rKronMagErr,gPSFMag,gPSFMagErr,gKronMag,gKronMagErr,iPSFMag,iPSFMagErr,iKronMag,iKronMagErr,iinfoflag, iinfoflag2, iinfoflag3, SDSS_i_avg
+    from PanSTARRS_DR1.StackObjectThin o,
+    Mydb.dust_data d
+    where o.objid between 1E15*$min and 1E15*$max
+    and o.primaryDetection=1
+    and o.bestDetection=1
+    and o.projectionID=d.procell
+    and d.skycell=o.skyCellID
+    and o.iKronMag between 0.0 and 22.0+d.SDSS_i_avg
+    into mydb.deep_$i" > ${OUTDIR}/query_$i.sql
+
+done

### 2018-09-13 casjobs/sql_procedure.sh

@@ -1,0 +1,14 @@
+#!/bin/bash
+
+#Submits SQL jobs to the casjobs server to extract data from the catalog to downloadable files.
+
+NAME_BASE="part"
+Q_DIR="./queries"
+
+for i in {0..48};
+do
+    java -jar casjobs.jar run -t 'PANSTARRS_DR1/720' -n "${NAME_BASE}_$i" -f "${Q_DIR}/query_$i.sql"
+    java -jar casjobs.jar extract -b "${NAME_BASE}_$i" -type CSV 
+    sleep 15m        
+    java -jar casjobs.jar execute -n 'Dropper' "drop table ${NAME_BASE}_$i"
+done

### 2018-09-13 change_mass.py

@@ -1,0 +1,58 @@
+###Calculates theoretical expecations for splashback radii of the clusters
+from colossus.cosmology import cosmology
+from colossus.halo import concentration
+from colossus.halo.mass_defs import changeMassDefinition
+import colossus.halo.splashback as sb
+
+h = 0.7 #Hubble parameter
+cosmology.setCosmology('bolshoi')
+
+
+def calc_stats(mass, redshift, mass_definition = "200m"):
+    if mass_definition == "200m":
+        M200m = mass
+        c200m = concentration.concentration(M200m, mass_definition, redshift)
+        M500c, R500c, c500c = changeMassDefinition(M200m, c200m, redshift,'200m', '500c', profile = 'nfw')
+    elif mass_definition == "500c":
+        M500c = mass
+	c500c = concentration.concentration(M500c, '500c', redshift)
+        M200m, R200m, c200m = changeMassDefinition(M500c, c500c, redshift,'500c', '200m')
+
+    Rsp = sb.splashbackRadius(redshift, '200m', M = M200m)[0]*(1 + redshift)
+    return M200m, M500c, R200m, Rsp
+
+
+if __name__=="__main__":
+   
+    #RedMaPPer
+    mass = 1.8e14
+    redshift = 0.24
+    M200m, M500c, R200m = calc_stat(mass, redshift, mass_defintion)
+    print("RedMaPPer:")
+    print("######################################")
+    print("R200m is: %E kpc/h" % R200m)
+    print("M500c is %E Msol/h and M200m is %E Msol/h" % (M500c, M200m))
+    print("The splashback radius is: %f kpc/h" % Rsp)
+    print("######################################")
+
+    #SZ
+    mass = 4.3e14*h
+    redshift = 0.177
+    M200m, M500c, R200m = calc_stat(mass, redshift, mass_defintion)
+    print("SZ:")
+    print("######################################")
+    print("R200m is: %E kpc/h" % R200m)
+    print("M500c is %E Msol/h and M200m is %E Msol/h" % (M500c, M200m))
+    print("The splashback radius is: %f kpc/h" % Rsp)
+    print("######################################")
+
+    #XR
+    mass = 2.3e14*h
+    redshift = 0.186
+    M200m, M500c, R200m = calc_stat(mass, redshift, mass_defintion)
+    print("XR:")
+    print("######################################")
+    print("R200m is: %E kpc/h" % R200m)
[…]

### 2018-09-13 cluster_manipulate/jackadder.py

@@ -1,0 +1,19 @@
+# Adds a Jackknife bin to each cluster in the catalog. 
+# Use for normal and random cluster sample
+
+import pandas
+import numpy as np
+
+
+if __name__ == "__main__":
+
+    Njack = 102 #Number of Jackknife bins
+    catalog_in = "catalog.dat"
+    catalog_out = "new_catalog.csv"
+
+
+    data = pandas.read_csv(catalog_in, sep = ' ')
+    number = data.RA.values.size
+    jacks = np.random.randint(Njack, size = number)
+    data["jackreg"] = jacks
+    data.to_csv(catalog_out, index = False)

### 2018-09-13 cluster_manipulate/redshift_assigner.py

@@ -1,0 +1,38 @@
+# Assigns a redshift to the random clusters.
+# Only use on random cluster sample
+# Only use after jackknife bin has been assigned
+# Requires running splashpipe on normal cluster catalog first
+
+import numpy as np 
+import pandas as pd
+
+catalog_in = "randoms.csv"
+distribution_dir = "./Normal" #Path to the redshift_distribution files generated by the splashpipe procedure
+output = "randoms_new.csv"
+
+
+def assign_reds(catalog_in, distribution_dir, catalog_out):
+    data = pd.read_csv(catalog_in, sep = ",")
+    jackregs = data.jackreg.values
+    jackregs = np.asarray(jackregs)
+    redshifts = np.zeros(0)
+
+    for i, jack in enumerate(jackregs):
+        array = np.genfromtxt("%s/redshift_distribution_%s.txt" % ( distribution_dir, int(jack) )
+        if array.size==0:
+            print("No point in this bin !!!!")
+            redshift = -99
+        else:
+            if array.size==1:
+                redshift = array
+            else:
+                number = np.random.randint(array.size, size = 1)
+                redshift = array[number]
+        redshifts = np.append(redshifts, redshift)
+    data["REDSHIFT"] = redshifts
+    data.to_csv(catalog_out, index=False, header=['RA','DEC','REDSHIFT','jackreg'])
+
+
+if __name__=="__main__":
+   assign_reds(input_,distribution,output)
+   print("Done")

### 2018-09-13 cluster_manipulate/splitter.py

@@ -1,0 +1,372 @@
+# Splits the cluster catalog into jackknife bins based on their locations on the sky
+# Each bin contains a similiar number of clusters
+
+import numpy as np
+import pandas as pd
+import matplotlib
+matplotlib.use("Agg")
+import matplotlib.pyplot as plt
+import matplotlib.cm as cm
+
+
+def fullsplit(vals, regions):
+    splits = np.asarray(np.array_split(vals, regions))
+    middles = np.zeros(0)
+    for it in range(splits.shape[0] - 1):
+        middle = np.median(np.append(splits[it], splits[it+1]))
+	middles = np.append(middles, middle)
+    return np.append(np.append(-40.0, middles), 360.0), splits
+
+
+def get_north_lines(npoints):
+    nras = npoints[:,0]
+    ndecs = npoints[:,1]
+
+    sortid = np.argsort(nras)
+    nras = np.take(nras, sortid)
+    ndecs = np.take(ndecs, sortid)
+
+    nralines, nrasplits = fullsplit(nras, 7)
+    totlength = 0
+    argdecsplits = np.zeros(7, dtype = object)
+    for i in range(nrasplits.shape[0]):
+	length = nrasplits[i].size
+        new = length + totlength
+        argdecsplits[i] = np.sort(ndecs[totlength:new])
+        totlength = new
+
+    north = np.zeros((8 + 1, 1))
+    for i, part in enumerate(argdecsplits):
+        declines, decsplits = fullsplit(part, 8)
+        declines = declines.reshape((declines.size, 1))
+        north = np.hstack((north, declines))
+    north = north[:,1:]
+    return nralines, north
+
+
+def get_south_lines(spoints):
+    sras = spoints[:,0]
+    #shift to patch southern part together
+    sras = np.mod(np.add(sras, 100.0), 360.0)
+    sdecs = spoints[:,1]
+
+    sortid = np.argsort(sras)
+    sras = np.take(sras, sortid)
+    sdecs = np.take(sdecs, sortid)
+
+    sralines, srasplits = fullsplit(sras, 6)
+
+    totlength = 0
[…]

### 2018-09-13 cluster_manipulate/visualizer.py

@@ -1,0 +1,34 @@
+# Plots a map of the (random) cluster positions
+
+import healpy as hp
+import numpy as np
+import pandas as pd
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+from astropy import units as uwell
+from astropy.coordinates import SkyCoord
+
+
+cat_path = "catalog.csv"
+rand_cat_path = "random_catalog.csv"
+sel_func_path =" HFI_PCCS_SZ-selfunc-union-survey_R2.08.fits"
+title = "Planck Clusters"
+out_path = "Planck_scatter.pdf"
+
+
+if __name__=="__main__":
+    catalog = pd.read_csv(cat_path)
+    random_catalog = pd.read_csv(rand_cat_path)
+
+    ra = np.asarray(catalog["RA"].values)
+    dec = np.asarray(catalog["DEC"].values)
+    rand_ra = np.asarray(random_catalog["RA"].values)
+    rand_dec = np.asarray(random_catalog["DEC"].values)
+
+    seln_func = hp.read_map(sel_func_path)
+    hp.visufunc.mollview(seln_func, title = title, coord=["G","C"])
+    hp.projscatter(ra, dec, lonlat=True, s = 3, c = 'r')
+    #hp.projscatter(rand_ra, rand_dec, lonlat=True, s = 3, c = 'b')
+    hp.graticule()
+    plt.savefig(out_path)

### 2018-09-13 depth_analysis/1_run_produce_bad_map.sh

@@ -1,0 +1,6 @@
+#PBS -lnodes=6:ppn=28,walltime=48:00:00
+#PBS -N Separator
+#PBS -q small
+cd /home/dominik.zuercher/Documents/RSP_Pro/depth_analysis
+module load mpi/mpich-x86_64
+mpirun python produce_bad_map.py --part 1 --mag_cut 21 --outfile_1 "bad_borders.csv" > output.txt 2>&1

### 2018-09-13 depth_analysis/2_run_produce_bad_map.sh

@@ -1,0 +1,6 @@
+#PBS -lnodes=6:ppn=28,walltime=48:00:00
+#PBS -N Separator
+#PBS -q small
+cd /home/dominik.zuercher/Documents/RSP_Pro/depth_analysis
+module load mpi/mpich-x86_64
+mpirun python produce_bad_map.py --part 2 --mag_cut 21 --outfile_1 "bad_borders.csv" --outdir_2 "pix_parts" > output.txt 2>&1

### 2018-09-13 depth_analysis/3_combiner.sh

@@ -1,0 +1,16 @@
+OutFileName="bad_pixels.dat"
+INDIR="./pix_parts/"
+
+rm $OutFileName
+i=0                           # Reset a counter
+for filename in "${INDIR}*";
+        do
+        echo $i;
+        if [ "$filename"  != "$OutFileName" ] ;      # Avoid recursion 
+        then
+                cat $filename >> $OutFileName
+                #tail -n+2 $filename >>  $OutFileName # Append from the 2nd line each file
+                i=$(( $i + 1 ))                        # Increase the counter
+        fi
+        done
+

### 2018-09-13 depth_analysis/4_run_produce_bad_map.sh

@@ -1,0 +1,6 @@
+#PBS -lnodes=6:ppn=28,walltime=48:00:00
+#PBS -N Separator
+#PBS -q small
+cd /home/dominik.zuercher/Documents/RSP_Pro/depth_analysis
+module load mpi/mpich-x86_64
+mpirun python produce_bad_map.py --part 3 --mag_cut 21 --infile_3 "bad_pixels.dat" --outdir_3 "." > output.txt 2>&1

### 2018-09-13 depth_analysis/5_run_produce_full_map.sh

@@ -1,0 +1,6 @@
+#PBS -lnodes=1:ppn=28,walltime=48:00:00
+#PBS -N Separator
+#PBS -q tiny
+cd /home/dominik.zuercher/Documents/RSP_Pro/depth_analysis
+module load mpi/mpich-x86_64
+mpirun python produce_full_map.py --mid_directory "mask_pix_parts" >output.txt 2>&1

### 2018-09-13 depth_analysis/6_mask_combiner.sh

@@ -1,0 +1,14 @@
+OutFileName="bad_mask_pixels.dat"
+INDIR="./mask_pix_parts/"
+rm $OutFileName
+i=0                           # Reset a counter
+for filename in "${INDIR}*";
+        do
+        echo $i;
+        if [ "$filename"  != "$OutFileName" ] ;      # Avoid recursion 
+        then
+                cat $filename >> $OutFileName
+                i=$(( $i + 1 ))                        # Increase the counter
+        fi
+        done
+

### 2018-09-13 depth_analysis/produce_bad_map.py

@@ -1,0 +1,252 @@
+#NOTE: The adding cuts part requires Numpy==1.13 since there is a bug in Numpy 1..14 causing Skycoord to fail if compiled with Python 2.7.5
+import healpy as hp
+import pandas as pd
+from astropy.table import Table
+import numpy as np 
+import frogress
+from astropy import units as uwell
+from astropy.coordinates import SkyCoord
+from itertools import product
+from astropy.io import fits
+import astropy.wcs as wcs
+import sys
+sys.path.insert(0,'/home/dominik.zuercher/Documents/RSP_Pro/toolbox')
+import tools
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import argparse
+
+
+
+def part1():
+    print("Reading dustmap...")
+    dust = pd.read_csv(dust_path, sep = ' ', usecols = [0,1,-1], names = ['procell','skycell','SDSS_i_avg'], header = None)
+    dustprocells = np.asarray(dust["procell"].values).astype(int)
+    dustskycells = np.asarray(dust["skycell"].values).astype(int)
+    dust_avg = np.asarray(dust["SDSS_i_avg"].values)
+
+    print("Reading Mag lim catalog")
+    data = Table.read(cut_path, format = 'fits')
+    data = data.to_pandas()
+    skycells = np.asarray(data["skyCellID"].values).astype(int)
+    procells = np.asarray(data["projectionid"].values).astype(int)
+    mag = np.asarray(data["max_iKronMag"].values)
+
+    for ii in frogress.bar(range(skycells.shape[0])):
+        skycell = skycells[ii]
+        procell = procells[ii]
+        idx = np.where((dustprocell s== procell) & (dustskycells == skycell))[0]
+        if idx.size != 1:
+            print(idx, procell, skycell)
+            print("Failed")
+            break
+        if dust_avg[idx] > -20.0:
+            mag[ii] -= dust_avg[idx]	
+        else:
+            print("No Mask")
+            mag[ii] = 0.0
+    idx = (mag < mag_cut)
+    outpro = procells[idx]
+    outpro = outpro.reshape((outpro.size, 1))
+    outsky = skycells[idx]
+    outsky = outsky.reshape((outsky.size, 1))
+    inpu = np.hstack((outpro, outsky))
+
+    print("Calculating ra, dec borders...")
+    outpro = inpu[:,0]
[…]

### 2018-09-13 depth_analysis/produce_full_map.py

@@ -1,0 +1,119 @@
+#Produces an end-user mask meant for distribution 
+import sys
+sys.path.insert(0,'/home/dominik.zuercher/Documents/RSP_Pro/toolbox')
+import tools
+import healpy as hp
+import numpy as np
+import astropy.wcs as wcs
+from astropy.io import fits
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import frogress
+import argparse
+
+
+def part2(rank):
+
+    steps = 2643 - 635
+    chunky = int(steps/size)
+    rest = steps - chunky*size
+    mini = chunky*rank
+    maxi = chunky*(rank + 1)
+    if rank >= (size - 1) - rest:
+        maxi += 2 + rank - size + rest)
+        mini += rank - size + 1 + rest
+    if rank == size - 1:
+        maxi = steps + 1
+    mini += 635
+    maxi += 635
+    mini = int(mini)
+    maxi = int(maxi)
+
+
+    bad_pixels = np.zeros(0)
+    for pro in frogress.bar(range(mini, maxi)):
+        flag = False
+        for i in range(0, 100):
+             try:
+                 foohdu = fits.open("%s/mask_%04d.%3d0.fits" % (mask_directory, pro, i), ignore_missing_end = True)
+                 break
+             except:
+                 pass
+             if i == 99:
+                 flag = True
+        if flag == True:
+            continue
+        w = wcs.WCS(foohdu[1].header)
+        for sky in range(0, 100):
+            try:
+                mask = fits.open('%s/mask_%04d.%03d.fits' % (mask_directory, pro, sky), ignore_missing_end = True)
+                body = mask[1].data
+                width = body.shape[1]
+                height = body.shape[0]
+            except:
+                continue
+            #cut off borders of skycell
+            body = body[20:-20,20:-20]
+            badpix = np.where(body != 0)
+            bady = badpix[0]
+            badx = badpix[1]
+            bady += 20
+            badx += 20
+            world = w.all_pix2world(badx, bady, 0, ra_dec_order = True)
+            ra = np.radians(world[0])
+            dec = np.radians(np.subtract(90.0, world[1]))
+            pix = hp.pixelfunc.ang2pix(NSIDE, dec, ra)
+            pix = np.unique(pix)
+            pix = pix.astype(int)
+            bad_pixels = np.append(bad_pixels, pix)
+
[…]

### 2018-09-13 depth_analysis/single_cell_analysis.py

@@ -1,0 +1,108 @@
+#! coding=utf8
+from scipy.stats import linregress
+import numpy as np
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import glob
+import sys
+import sys
+sys.path.insert(0,'/home/dominik.zuercher/Documents/RSP_Pro/toolbox')
+import tools
+
+
+def lin_func(x, coeff):
+    return np.add(np.multiply(x, coeff[1]), coeff[0])
+
+
+if __name__ == "__main__": 
+    single_cell_path = "/work/dominik.zuercher/singlecell"
+    outpath = "./graphs"
+
+    num = sys.argv[1]
+
+    table = np.genfromtxt("%s/cell_%s" % (single_cell_path, num), dtype = str, delimiter = ',')[1:,:]
+
+    #Through away undefined measurments
+    select3 = np.where(table[:,7].astype(float) != -999.)[0]
+    table = table[select3,:]
+    select4 = np.where(table[:,14].astype(float) !=- 999.)[0]
+    table = table[select4,:]
+
+    print("The median of the magnitude is: %s" % +str(np.median(table[:,7].astype(np.float))))
+
+    #Through away multiply counted objects
+    pastid = 0
+    del_pos = np.zeros(0)
+    for i in range(0, table.shape[0]):
+        objid = table[i,0]
+        if objid == pastid:
+            del_pos = np.append(del_pos, i)
+        pastid = objid
+    table = np.delete(table, (del_pos), axis=0)
+    table = table.astype(np.float)
+
+    #Separate into galaxy matches and non-matches
+    nonfit_pos = tools.vec_hextest(list = table[:,11], hexvalues = flag1success, mode="neg")
+    fit_pos = tools.vec_hextest(list = table[:,11], hexvalues = flag1success, mode = "pos")
+    fit_exp = table[fit_pos,14]
+    nonfit_exp = table[nonfit_pos,14]
+    fit_mag = table[fit_pos,7].astype(float)
+    nonfit_mag = table[nonfit_pos,7].astype(float)
+
+    drop_index = np.zeros(0)
+    drop_bin = np.zeros(0)
+    for bin in range(0, np.max(table[:,14]).astype(int)):
+        act_exp_fit = np.zeros(0)
+        act_exp_nonfit = np.zeros(0)
+        act_mag_fit = np.zeros(0)
+        act_mag_nonfit = np.zeros(0)
+
[…]

### 2018-09-13 dust_correction/combiner.py

@@ -1,0 +1,30 @@
+#Combines extinction corrections from different filters into one file
+import pandas as pd
+import numpy as np
+import glob
+
+if __name__ == "__main__":
+
+    size = 980 #Number of processors used in get_dust.py
+    dust_dir = "./" #Directory containing the dust catalogs produced by get_dust.py
+    outfile = "test.dat"
+
+    output = np.zeros((1, 5))
+
+    for ii in range(size):
+        redfile = np.loadtxt(outdir + "redparts/dust_catalog_red_%s.csv" % ii)
+        greenfile = np.loadtxt(outdir + "greenparts/dust_catalog_green_%s.csv" % ii)
+        ifile = np.loadtxt(outdir + "ibandparts/dust_catalog_iband_%s.csv" % ii)
+        green = greenfile[:,2]
+        iband = ifile[:,2]
+        green = green.reshape(green.size,1)
+        iband = iband.reshape(iband.size,1)
+        foo = np.hstack((redfile, green, iband))
+        output = np.vstack((output, foo))
+
+    np.savetxt(outfile, output[1:,:])
+
+
+
+
+

### 2018-09-13 dust_correction/get_dust.py

@@ -1,0 +1,113 @@
+#Uses mwdust module to get the extinction corrections from MW dust. Run which each color band separately.
+#! coding=utf8
+#NOTE: In order for mwdust module to work require Python 2.7.5 and Numpy version 1.13 EXACTLY!!!
+
+import mwdust
+import matplotlib.pyplot as plt
+import numpy as np
+from astropy.io import fits
+from astropy import units as u
+from astropy.coordinates import SkyCoord
+import frogress
+import csv
+import sys
+sys.path.insert(0,'/home/dominik.zuercher/Documents/RSP_Pro/toolbox')
+import tools
+from glob import glob
+from mpi4py import MPI
+import os.path
+
+
+
+def procedure(rank, size):
+ 
+	steps = 2643.0 - 635.0
+	chunky = int(steps/size)
+        rest = steps - chunky*size
+        mini = chunky*rank
+        maxi = chunky*(rank + 1)
+        if rank >= (size - 1 - rest):
+                maxi += 2 + rank - size + rest
+		mini += rank - size + 1 + rest
+	mini += 635
+	maxi += 635
+	mini = int(mini)
+	maxi = int(maxi)
+
+        if color == "iband":
+            filter_ = "SDSS i"
+        elif color == "red":
+            filter_ = "SDSS r"
+        elif color == "green":
+            filter_ = "SDSS g"
+        else:
+            print("Defined filter not available. Choose red, green or iband")
+            return
+
+	imap = mwdust.Combined15(filter = filter_, sf10 = True)
+
+
+	print("Creating Grid...")
+	
+	foos = np.arange(mini, maxi, 1)
+	full = tools.create_grid(foos)
+	print("Kernel %s doing %s up to %s" % (rank, mini, maxi))
+	print("Calculating borders of the cells")
+	minras, maxras, mindecs, maxdecs = tools.get_centers(full[:,0], full[:,1], borders = True, maskdetect = True)
+
+	print("Using %s objects in Kernel %s" % (full.shape[0], rank))
+
+
+	print("Converting coordinates to galactic system")
+	idy = np.where(np.abs(minras + 99.0) < 0.0001))[0]
+	idy2 = np.where(np.abs(minras + 999.0) < 0.0001))[0]
+	idy = np.append(idy, idy2)
+	idy = np.unique(idy)
+	for it in idy:
+		minras[it] = 0.0
+		mindecs[it] = 0.0
[…]

### 2018-09-13 match_PS/combiner.py

@@ -1,0 +1,25 @@
+import pandas
+import glob
+import numpy as np
+
+
+if __name__ == "__main__":
+    input_dir = "/work/dominik.zuercher/Output/match_PS/spec_parts"
+    output_dir = "/work/dominik.zuercher/Output/match_PS"
+
+    zred=np.zeros(0)
+    red=np.zeros(0)
+    green=np.zeros(0)
+    red_PS=np.zeros(0)
+    green_PS=np.zeros(0)
+
+    for ii, fname in enumerate(glob.glob("%s/matched_???" % input_dir)):
+        print(fname)
+        dfnew = pandas.read_csv(fname, delim_whitespace=1, header=None,names=["zred","red","green","red_PS","green_PS"])
+        zred=np.append(zred,dfnew.zred.values)
+        red=np.append(red,dfnew.red.values)
+        green=np.append(green,dfnew.green.values)
+        red_PS=np.append(red_PS,dfnew.red_PS.values)
+        green_PS=np.append(green_PS,dfnew.green_PS.values)
+    np.savetxt("%s/matched_spec.dat" % output_dir, np.hstack((zred.reshape(zred.size,1),red.reshape(red.size,1),green.reshape(green.size,1),red_PS.reshape(red_PS.size,1),green_PS.reshape(green_PS.size,1))) )
+

### 2018-09-13 match_PS/fitting.py

@@ -1,0 +1,147 @@
+from scipy.interpolate import UnivariateSpline
+from  scipy.optimize import curve_fit
+import numpy as np
+import matplotlib
+matplotlib.use("Agg")
+import matplotlib.pyplot as plt
+import frogress
+
+def cut(red, ax = 0.65):
+    return ax + ((red - 0.1)*0.8/0.23)
+
+
+def double_gaussian(x, c1, mu1, sigma1, c2, mu2, sigma2):
+    res =   c1 * np.exp( - (x - mu1)**2.0 / (2.0 * sigma1**2.0) ) + c2 * np.exp( - (x - mu2)**2.0 / (2.0 * sigma2**2.0) )
+    return res
+
+
+def bin_redshifts(redshift, min_z, max_z, z_steps):
+
+    z_edges = np.linspace(min_z, max_z, num = z_steps)
+    bin_num = np.zeros(redshift.size)
+    for ii,z in frogress.bar(enumerate(redshift)):
+	it = 0
+        upper_z = z_edges[it]
+	while z > upper_z:
+	   it += 1
+	   upper_z = z_edges[it]
+	bin_num[ii] = it
+    return bin_num
+
+
+def get_cuts(color, bin_num, bins, z_steps):
+    cuts = np.zeros(z_steps-1)
+    for it in frogress.bar(range(1,z_steps)):
+        colors = color[bin_num == it]
+        hist, edges = np.histogram(colors, bins = bins)
+        try:
+            popt, pcov = curve_fit(double_gaussian, edges[:-1] + (edges[1] - edges[0])/2., hist)
+        except:
+            cuts[it-1] = -1000
+            continue
+        red_ind = np.argmax([popt[1], popt[4]])
+        if red_ind == 0:
+            red_mu = popt[1]
+            red_sigma = popt[2]
+        else:
+            red_mu = popt[4]
+            red_sigma = popt[5]
+        cut = red_mu - 3 * np.abs(red_sigma)
+        cuts[it - 1] = cut 
+
+        if (it % 10 == 0):
+            plt.figure(it / 10)
+            plt.hist(colors, bins = bins)
+            gr_range = edges[:-1] + (edges[1] - edges[0])/2.
+            plt.plot(gr_range, double_gaussian(gr_range, popt[0], popt[1], popt[2], popt[3], popt[4], popt[5]), 'k-', lw = 0.3)
[…]

### 2018-09-13 match_PS/match.py

@@ -1,0 +1,129 @@
+#Matches RedMaPPer spectroscopic galaxies with PS galaxies. Contains redshift (from RedMaPPer) and color (from PS)
+import scipy.spatial as kdtree
+import sys
+import numpy as np
+from astropy.io import fits as pyfits
+from astroML.crossmatch import crossmatch_angular
+import pandas
+from mpi4py import MPI
+
+
+def get_assigned_targets(cat, ps_cat):
+    ra_e = cat[:,0]
+    dec_e = cat[:,1]
+    X_e = np.empty((ra_e.size, 2), dtype = np.float64)
+    X_e[:, 0] = ra_e
+    X_e[:, 1] = dec_e
+
+    data_m = ps_cat
+
+    ra_m = data_m[:,0]
+    dec_m = data_m[:,1]
+    X_m = np.empty((ra_m.size, 2), dtype = np.float64)
+    X_m[:, 0] = ra_m
+    X_m[:, 1] = dec_m
+    print "Out of:", ra_m.size
+
+    max_radius = 0.3 / 3600  # 0.01 arcsec
+    dist, ind = crossmatch_angular(X_m, X_e, max_radius)
+    idx = (~np.isinf(dist))
+
+    return data_m[idx], dist, ind
+
+
+def with_kdtree(cat, ps_cat):
+    #Prepare cat
+    ra_e = cat[:,0]*np.pi/180.
+    dec_e = cat[:,1]*np.pi/180.
+    X_e = np.empty((ra_e.size, 3), dtype = np.float64)
+    X_e[:, 0] = np.cos(ra_e)
+    X_e[:, 1] = np.sin(dec_e)
+    X_e[:, 2] = np.cos(dec_e)
+
+    #Make kdtree
+    tree = kdtree.KDTree(X_e)
+
+    #Prepare ps_cat
+    data_m = ps_cat
+    ra_m = data_m[:,0]*np.pi/180.
+    dec_m = data_m[:,1]*np.pi/180.
+    X_m = np.empty((ra_m.size, 3), dtype = np.float64)
+    X_m[:, 0] = np.cos(ra_m)
+    X_m[:, 1] = np.sin(dec_m)
+    X_m[:, 2] = np.cos(dec_m)
+ 
+    max_radius = 0.3/3600*np.pi/180.0 #In arcsecs
+    dd, ii = tree.query(X_m, distance_upper_bound = max_radius) #dd = Distance between matched objects (inf if no match found), ii == Index of matched pair in cat, botth have length of ps_cat 
[…]

### 2018-09-13 match_PS/match_spec.py

@@ -1,0 +1,137 @@
+#Matches RedMaPPer spectroscopic galaxies with PS galaxies. Contains redshift (from RedMaPPer) and color (from PS)
+import scipy.spatial as kdtree
+import sys
+import numpy as np
+from astropy.io import fits as pyfits
+from astroML.crossmatch import crossmatch_angular
+import pandas
+from mpi4py import MPI
+
+
+def get_assigned_targets(cat, ps_cat):
+    ra_e = cat[:,0]
+    dec_e = cat[:,1]
+    X_e = np.empty((ra_e.size, 2), dtype = np.float64)
+    X_e[:, 0] = ra_e
+    X_e[:, 1] = dec_e
+
+    data_m = ps_cat
+
+    ra_m = data_m[:,0]
+    dec_m = data_m[:,1]
+    X_m = np.empty((ra_m.size, 2), dtype = np.float64)
+    X_m[:, 0] = ra_m
+    X_m[:, 1] = dec_m
+    print "Out of:", ra_m.size
+
+    max_radius = 0.3 / 3600  # 0.01 arcsec
+    dist, ind = crossmatch_angular(X_m, X_e, max_radius)
+    idx = (~np.isinf(dist))
+
+    return data_m[idx], dist, ind
+
+
+def with_kdtree(cat, ps_cat):
+    #Prepare cat
+    ra_e = cat[:,0]*np.pi/180.
+    dec_e = cat[:,1]*np.pi/180.
+    X_e = np.empty((ra_e.size, 3), dtype = np.float64)
+    X_e[:, 0] = np.cos(ra_e)
+    X_e[:, 1] = np.sin(dec_e)
+    X_e[:, 2] = np.cos(dec_e)
+
+    #Make kdtree
+    tree = kdtree.KDTree(X_e)
+
+    #Prepare ps_cat
+    data_m = ps_cat
+    ra_m = data_m[:,0]*np.pi/180.
+    dec_m = data_m[:,1]*np.pi/180.
+    X_m = np.empty((ra_m.size, 3), dtype = np.float64)
+    X_m[:, 0] = np.cos(ra_m)
+    X_m[:, 1] = np.sin(dec_m)
+    X_m[:, 2] = np.cos(dec_m)
+ 
+    max_radius = 0.3/3600*np.pi/180.0 #In arcsecs
+    dd, ii = tree.query(X_m, distance_upper_bound = max_radius) #dd = Distance between matched objects (inf if no match found), ii == Index of matched pair in cat, botth have length of ps_cat 
[…]

### 2018-09-13 match_PS/plotter_spec.py

@@ -1,0 +1,108 @@
+import matplotlib 
+matplotlib.use("Agg")
+import matplotlib.pyplot as plt
+import numpy as np
+
+def cut(red, ax = 0.8):
+    return ax + ((red - 0.1)*0.8/0.23)
+
+if __name__ == "__main__":
+
+    catalog = "/work/dominik.zuercher/Output/match_PS/matched_spec_new.dat"
+    output_dir = "/work/dominik.zuercher/Output/match_PS"
+
+
+    data = np.loadtxt(catalog)
+    redshift = data[:,0]
+    red = data[:,1]
+    green = data[:,2]
+    red_PS = data[:,3]
+    green_PS = data[:,4]
+    id_ = data[:,5]
+    id_PS = data[:,6]
+
+
+    rrange = np.linspace(0, 0.35, 1000)
+    yy0 = cut(rrange, 0.65)
+
+    #Calculate contaminations for mixed characterization (best estimate?)
+    #Falses
+    reds_below_cut = (id_ == False) & (green_PS - red_PS < 0.55 + redshift*((redshift - 0.1)*12) )
+    blues_above_cut = (id_ == True) & (green_PS - red_PS >= 0.55 + redshift*((redshift - 0.1)*12) )
+    #Rights
+    reds_above_cut = (id_ == False) & (green_PS - red_PS >= 0.55 + redshift*((redshift - 0.1)*12) )
+    blues_below_cut = (id_ == True) & (green_PS - red_PS < 0.55 + redshift*((redshift - 0.1)*12) )
+
+    print("Reds below cut: %s" % np.sum(reds_below_cut))
+    print("Blues below cut: %s" % np.sum(blues_below_cut))
+    print("Reds above cut: %s" % np.sum(reds_above_cut))
+    print("Blues above cut: %s" % np.sum(blues_above_cut))
+    plt.figure(1)
+    plt.scatter(redshift[id_ == True], green[id_ ==True] - red[id_ ==True], s = 0.01, color = 'b', label = "Blue")
+    plt.scatter(redshift[id_ == False], green[id_ == False] - red[id_==False], s = 0.01, color = 'r', label = "Red")
+
+    plt.plot(rrange, yy0, 'k-',lw=0.3, label="orig. cut")
+
+    plt.ylim([0,3])
+    plt.xlim([0,0.33])
+    plt.legend()
[…]

### 2018-09-13 match_PS/run_match.sh

@@ -1,0 +1,10 @@
+#!/bin/bash
+#PBS -lnodes=35:ppn=28,walltime=10:00:00
+#PBS -N match_PS
+#PBS -q large
+cd /home/dominik.zuercher/Documents/RSP_Pro/match_PS
+pwd
+module load mpi/mpich-3.2-x86_64
+
+mpirun python match_spec.py > /work/dominik.zuercher/Output/match_PS/logs/output_spec.log 2>&1
+

### 2018-09-13 match_PS/separate_spec.py

@@ -1,0 +1,20 @@
+import pandas as pd
+import numpy as np
+
+
+if __name__ == "__main__":
+
+    dir_ = "/work/dominik.zuercher/Output/match_PS"
+
+    spec_cat = "%s/matched_spec.dat" % dir_
+    data = pd.read_csv(spec_cat, delim_whitespace=1,header=None,names=["zred","red","green","red_PS","green_PS"])
+    cat = data.values
+    id_ = np.zeros(cat.shape[0])
+    id_ = (cat[:,2] - cat[:,1] <= 0.8 - 0.03*(cat[:,1] + 20.0)) #True if identified as blue and False if red
+    cat = np.hstack((cat,id_.reshape(id_.size,1))) 
+
+    id_ = np.zeros(cat.shape[0])
+    id_ = (cat[:,4] - cat[:,3] <= 0.8 - 0.03*(cat[:,3] + 20.0)) #True if identified as blue and False if red
+    cat = np.hstack((cat,id_.reshape(id_.size,1))) 
+    np.savetxt("%s/matched_spec_new.dat" % dir_,cat)
+

### 2018-09-13 match_Planck_Chandra/match.py

@@ -1,0 +1,139 @@
+#Matches Planck clusters to Chandra analogs in order to get miscentering assuming Chandra clusters at correct posisitons
+import numpy as np
+from astropy.io import fits as pyfits
+import pandas as pd
+
+def dec2deg(sign, hd, min, sec):
+    """
+    Converts declination to degrees
+
+    Parameters
+    ----------
+    hd : int
+    degrees
+    m : int
+    arcminutes
+    s : float
+    arcseconds
+
+    Returns
+    -------
+    hd : float
+    A decimal number
+
+    """
+    return sign*(np.absolute(hd) + min/60.0 + sec/3600.0)
+
+def ra2deg(hd, min, sec):
+    """
+    Converts ra to degrees
+
+    Parameters
+    ----------
+    hd : int
+    hours
+    m : int
+    minutes
+    s : float
+    seconds
+
+    Returns
+    -------
+    hd : float
+    A decimal number
+
+        """
+    return (np.float(hd) + min/60.0 + sec/3600.0)*360./24.
+
+def convert_ra_from_list(chandrara):
+    outframe=np.zeros(0)
+    for obj in chandrara:
+        splitra=obj.split(":")
+	hd = float(splitra[0])
+	mts = float(splitra[1])
+	sec = float(splitra[2])
+        outra = ra2deg(hd, mts, sec)
+        outframe=np.append(outframe,outra)
+    return outframe
+
+def convert_dec_from_list(chandradec):
+    outframe=np.zeros(0)
+    for obj in chandradec:
+        splitdec = obj.split(":")
+	sign = np.sign(float(splitdec[0]+"1"))
+	hd = float(splitdec[0])
+	mts = float(splitdec[1])
+	sec = float(splitdec[2])
+        outdec = dec2deg(sign, hd, mts, sec)
+        outframe=np.append(outframe,outdec)
+    return outframe
+
+def match(rra, ddec, xxra, xxdec,cut):
+	rra = np.pi/180.*rra
+    	ddec = np.pi/180.*ddec
+    	xx = np.cos(ddec)*np.cos(rra)
+    	yy = np.cos(ddec)*np.sin(rra)
+    	zz = np.sin(ddec)
+
+    	xxra = np.pi/180.*xxra
+    	xxdec = np.pi/180.*xxdec
+    	xxp = np.cos(xxdec)*np.cos(xxra)
+    	yyp = np.cos(xxdec)*np.sin(xxra)
[…]

### 2018-09-13 match_Planck_Chandra/miscentering_prior_est.py

@@ -1,0 +1,79 @@
+# Uses Chandra and Planck clusters to find prior values for miscentering parameters fmin and sigma
+import scipy.optimize as op
+import numpy as np
+import pandas as pd
+from astropy.cosmology import FlatLambdaCDM
+import astropy.units as u
+import matplotlib
+matplotlib.use("Agg")
+import matplotlib.pyplot as plt
+
+cosmo = FlatLambdaCDM(H0 = 70 * u.km / u.s / u.Mpc, Om0 = 0.3)
+
+def comoving_separation(z,theta):
+    theta = theta/3600
+    theta = theta*np.pi/180.0
+    dc = cosmo.comoving_distance(z) #comoving distance
+    da = dc/(1.0+z) #angular diameter distance
+    rp = theta*da #physical separation
+    rc = rp*(1.0+z) 
+    rc = rc*0.7 #Output in comoving h**-1 Mpc
+    return rc
+
+def rayleigh_distribution(R,sigma):
+    return R/sigma**2*np.exp(-R**2/(2*sigma**2))
+
+def lnlike(sigma,R,yy):
+    chisq = np.sum((yy - rayleigh_distribution(R,sigma))**2)
+    return -0.5*chisq
+
+def MLE_procedure(RR, yy, p0):
+    nll = lambda *args: -lnlike(*args)
+    result = op.minimize(nll, p0, args=(RR, yy))
+    return result["x"]
+
+
+
+if __name__=="__main__":
+
+    data = pd.read_csv("/work/dominik.zuercher/DataStore/Planck-SZ/30/Planck_corrected_matched.csv")
+    redshifts = data["REDSHIFT"].values
+    distances = data["Chandra_distance"].values
+    idx = distances > -10.0
+    distances = distances[idx]
+    redshifts = redshifts[idx]
+   
+    total=redshifts.size
+
+    lowcut = 0.25
+
+    com_dist = comoving_separation(redshifts,distances).value
+    idx = com_dist > lowcut
+    com_dist = com_dist[idx]
+
+    reduced=com_dist.size
+    fmin_est = float(reduced)/float(total)
+
+
+    hist, bin_edges = np.histogram(com_dist,density=True,bins=20)
+    bin_centers = (bin_edges[1:] - bin_edges[:-1])/2.0 + bin_edges[:-1]
+    idx = hist > 0
+    hist = hist[idx]
[…]

### 2018-09-13 random_generate/PS_random/1_random_generator_init.sh

@@ -1,0 +1,7 @@
+#PBS -lnodes=35:ppn=28,walltime=10:00:00
+#PBS -N random_generator
+#PBS -q large
+cd /home/dominik.zuercher/Documents/RSP_Pro/random_generate/PS_random
+module load mpi/mpich-x86_64
+echo "Started!!!" 
+mpirun python random_generator.py --init 1 --mag_cut 21 --outdir "/work/dominik.zuercher/DataStore/Pan-Starrs/Randoms/randoms/parts" >output.txt 2>&1

### 2018-09-13 random_generate/PS_random/2_run_combine_part1.sh

@@ -1,0 +1,7 @@
+#PBS -lnodes=1:ppn=28,walltime=48:00:00
+#PBS -N Random combiner
+#PBS -q small
+cd /home/dominik.zuercher/Documents/RSP_Pro/random_generate/PS_random/
+module load mpi
+mpirun ./combine_part1.sh >output.log 2>&1
+

### 2018-09-13 random_generate/PS_random/3_random_gnerator_main.sh

@@ -1,0 +1,7 @@
+#PBS -lnodes=35:ppn=28,walltime=10:00:00
+#PBS -N random_generator
+#PBS -q large
+cd /home/dominik.zuercher/Documents/RSP_Pro/random_generate/PS_random
+module load mpi/mpich-x86_64
+echo "Started!!!" 
+mpirun python random_generator.py --init 0 --mag_cut 21 --indir "/work/dominik.zuercher/DataStore/Pan-Starrs/Randoms/randoms/finished" --middir "/work/dominik.zuercher/DataStore/Pan-Starrs/Randoms/randoms2" --outdir "/work/dominik.zuercher/DataStore/Pan-Starrs/Randoms/randoms3" >output.txt 2>&1

### 2018-09-13 random_generate/PS_random/4_combine_part2.sh

@@ -1,0 +1,20 @@
+#! /bin/bash
+
+OUTDIR="/work/dominik.zuercher/DataStore/Pan-Starrs/Randoms/"
+INDIR="/work/dominik.zuercher/DataStore/Pan-Starrs/Randoms/randoms3/"
+
+OutFileName="${OUTDIR}PS_randoms_new.dat"
+
+
+rm $OutFileName
+i=0 # Reset a counter
+for filename in "${INDIR}*";
+do
+    if [ "$filename"  != "$OutFileName" ] ;      # Avoid recursion 
+    then
+        cat $filename >>  $OutFileName # Append from the 2nd line each file
+        i=$(( $i + 1 ))                        # Increase the counter
+	echo "$i"    
+    fi
+done
+

### 2018-09-13 random_generate/PS_random/combine_part1.sh

@@ -1,0 +1,38 @@
+#! /bin/bash
+
+OFFSET=635
+SIZE=28
+INDIR="/work/dominik.zuercher/DataStore/Pan-Starrs/Randoms/randoms/finished/"
+OUTDIR="/work/dominik.zuercher/DataStore/Pan-Starrs/Randoms/randoms/parts/"
+
+TOTAL=$(((2643 - $OFFSET) / $SIZE))
+MIN=$(( $OFFSET + $OMPI_COMM_WORLD_RANK * $TOTAL ))
+MAX=$(( $OFFSET + ($OMPI_COMM_WORLD_RANK + 1) * $TOTAL - 1 ))
+
+rm "${OUTDIR}*"
+if [ "$OMPI_COMM_WORLD_RANK" == 27 ];
+        then
+        MAX=2643
+        fi
+echo "$MIN"
+echo "$MAX"
+for cell in $(seq $MIN $MAX);
+do
+
+OutFileName="${OUTDIR}random_cell_${cell}.dat"                 
+
+rm $OutFileName
+i=0 # Reset a counter
+for filename in "${INDIR}random_cell_${cell}_rank*.dat";
+        do
+        if [ "$filename"  != "$OutFileName" ] ;      # Avoid recursion 
+                then
+                cat $filename >>  $OutFileName # Append from the 2nd line each file
+                i=$(( $i + 1 ))                        # Increase the counter
+        fi
+        done
+
+echo "${cell} done"
+
+done
+

### 2018-09-13 random_generate/PS_random/random_generator.py

@@ -1,0 +1,143 @@
+#! coding=utf8
+import numpy as np
+from astropy.io import fits
+from astropy.coordinates import SkyCoord
+from astropy import units as uwell
+import astropy.wcs as wcs
+import pandas as pd
+import matplotlib.pyplot as plt
+import math
+import healpy as hp
+import os
+import sys
+sys.path.insert(0,'/home/dominik.zuercher/Documents/RSP_Pro/toolbox')
+import tools
+import argparse
+from mpi4py import MPI
+from glob import glob
+
+
+def init_procedure(rank):	
+    total_randoms = int(total_num*4.0/3.0/size) #Randoms generated per thread
+
+    #Generate the random objects
+    ran_dec  = -1.0 + 2.*np.random.random(size = total_randoms)
+    ran_ra = 2.0*np.pi*np.random.random(size = total_randoms)
+    ran_dec = np.arccos(ran_dec)
+    print("generated")
+
+    #Throw away those in bad skycells using bads.fits mask
+    bads = hp.read_map("%s/bads_%s.fits" % (mask_path, mag_cut))
+
+    print("converting")
+    pix = hp.pixelfunc.ang2pix(NSIDE, ran_dec, ran_ra)
+    pixmask = (bads[pix] == 1)
+    ran_ra = ran_ra[pixmask]
+    ran_dec = ran_dec[pixmask]
+
+    print("selected")
+    ran_dec = np.degrees(np.pi/2.0 - ran_dec)
+    ran_ra = np.degrees(ran_ra)
+    output = np.hstack((ran_ra.reshape((ran_ra.size, 1)), ran_dec.reshape((ran_dec.size, 1))))
+    output = np.hstack((output, np.zeros((output.shape[0], 2))))
+    projectioncell = tools.decide_pro(output[:,0], output[:,1])
+
+    print("Decided on Projectioncell")
+    output[:,2] = projectioncell.reshape((output.shape[0],))
+    outdict = {key:np.zeros((1, 4)) for key in range(635, 2644)}
+
+    print("Writing Directory...")	
+    for j in range(output.shape[0]):
+        if j == int(output.shape[0]/4):
+            print("%s at 25%" % rank)
+        if j == int(output.shape[0]/2):
+            print("%s at 50%" % rank)
+        cell = output[j,2]
+        outdict[int(cell)] = np.vstack((outdict[int(cell)], output[j,:]))
+
+    print("Saving")
[…]

### 2018-09-13 random_generate/Planck_random/random_generator.py

@@ -1,0 +1,55 @@
+#! coding=utf8
+import numpy as np
+import healpy
+import pyfits
+import matplotlib.pyplot as plt
+from astropy import units as uwell
+from astropy.coordinates import SkyCoord
+
+
+if __name__=="__main__":
+
+    seln_func = healpy.read_map("/work/dominik.zuercher/DataStore/Planck-SZ/HFI_PCCS_SZ-selfunc-union-cosmolog_R2.08.fits") #Planck survey selection function
+    hdulist = pyfits.open("/work/dominik.zuercher/DataStore/Planck-SZ/HFI_PCCS_SZ-union_R2.08.fits") #Planck SZ catalog
+    redshift_lim = 0.33 #Upper redshift limit for clusters
+    Nsize = 10000 #Number of random clusters drawn
+    sel_fig = "selectionfunction.pdf"
+    bcg_fig = "onlyBCG.png"
+    dist_fig = "dist.png"
+    out_path = "/work/dominik.zuercher/DataStore/Planck-SZ/Planck_random_cosmo.csv"
+
+    data = hdulist[1].data
+    zred = data["redshift"]
+    idx = (zred != -1.)
+    zred = zred[idx]
+    idy = (zred <= 0.33)
+    zred = zred[idy]
+    mu_r = -1.0 + 2.*np.random.random(size = Nsize)
+    phi_r = 2.0*np.pi*np.random.random(size = Nsize)
+    theta_r = np.arccos(mu_r)
+
+    pix = healpy.pixelfunc.ang2pix(2048, theta_r, phi_r)
+    mask = (seln_func[pix] == 1) #Select only points within the seln_func
+    theta_r = theta_r[mask]
+    phi_r = phi_r[mask]
+    zred_r = zred[np.random.permutation(phi_r.size) % zred.size] #Produce 'random' redshifts
+
+    fig = plt.figure(1)
+    healpy.mollview(seln_func,norm = 'hist', cmap = 'PRGn')
+    fig.savefig(sel_fig)
+
+    fig = plt.figure(2)
+    healpy.mollview(seln_func, norm = 'hist', cmap = 'PRGn')
+    healpy.projscatter(planck_theta, planck_phi, s = 1, lw = 0)
+    fig.savefig(bcg_fig)
+
+    fig = plt.figure(3)
+    healpy.mollview(seln_func, norm = 'hist', cmap = 'PRGn')
[…]

### 2018-09-13 splashpipe/1_run_splashpipe.sh

@@ -1,0 +1,26 @@
+#!/bin/bash
+
+#PBS -lnodes=35:ppn=28,walltime=10:00:00
+#PBS -N Planck_PS
+#PBS -q large
+
+cd /home/dominik.zuercher/Documents/RSP_Pro/splashpipe
+pwd
+module load mpi/mpich-3.2-x86_64
+
+
+mpirun python mpi_splashback.py --rmax 50.0 --rmin 0.1 --rbin 15 --colored -1 --clusterdir "Planck" --galaxydir "Pan-Starrs_chunks" --magcut "21.5" --dirout "/work/dominik.zuercher/Output/splashpipe/Planck_PS_21.5_blue_spline/Clu=Norm_Gal=Norm" > /work/dominik.zuercher/Output/splashpipe/logs/output_1.dat 2>&1
+#mpirun python mpi_splashback.py --rmax 50.0 --rmin 0.1 --rbin 15 --colored -1 --clusterdir "Planck" --galaxydir "Pan-Starrs_chunks" --magcut "21.5" --dirout "/work/dominik.zuercher/Output/splashpipe/Planck_PS_21.5_blue_cut_9/Clu=Norm_Gal=Norm" > /work/dominik.zuercher/Output/splashpipe/logs/output_1.dat 2>&1
+
+
+#Old ones left for doc purposes
+#Deprojection
+#mpirun python mpi_splashback_galaxies.py --rmax 10.0 --rmin 0.1 --rbin 8 --random 0 --colored 0 --deproject 1 --clusterdir "Planck" --magcut "21.5" --dirout "reloaded/Planck_PS_21.5_deprojected" > output.log 2>&1 
+#Colored
+#mpirun python mpi_splashback_galaxies.py --rmax 50.0 --rmin 0.1 --rbin 15 --random 0 --colored -1 --clusterdir "Planck_random" --magcut "21.5" --dirout "reloaded/Planck_PS_21.5_blue_random" > output.log 2>&1 
+#mpirun python mpi_splashback_galaxies.py --rmax 50.0 --rmin 0.1 --rbin 15 --random 0 --colored -1 --clusterdir "Planck" --magcut "21.5" --dirout "debug_Planck_PS_21.5_blue" > output.log 2>&1 
[…]

### 2018-09-13 splashpipe/2_combiner.py

@@ -1,0 +1,26 @@
+import pandas
+import numpy as np
+import sys
+import glob
+from subprocess import call
+
+
+if __name__ == "__main__":
+
+    dire = sys.argv[1]
+
+    for ii, fname in enumerate(glob.glob(dire+"/???/pairs.dat")):
+	print fname
+	if ii==0:
+	    df = pandas.read_csv(fname, delim_whitespace=1, header=None, names=(["rr", "dd", "avr", "area"]), comment="#")
+	    #df_denom = pandas.read_csv(fname+".denom", delim_whitespace=1, header=None, names=(["denom"]), comment="#")
+	else:
+	    dfnew = pandas.read_csv(fname, delim_whitespace=1, header=None, names=(["rr", "dd", "avr", "area", "denom"]), comment="#")
+	    #df_denom_new = pandas.read_csv(fname+".denom", delim_whitespace=1, header=None, names=(["denom"]), comment="#")
+	    df.dd = df.dd + dfnew.dd
+	    #df_denom.denom = df_denom.denom + df_denom_new.denom
+    #df.join(df_denom)
+    #df = pandas.concat([df,df_denom],axis=1)
+    df.to_csv(dire+"/pairs.dat", index=False, header=False, sep=" ", float_format="%.6e")
+
+    call("cp %s/000/Ncluster_0.dat %s/Ncluster.dat"%(dire, dire), shell=True)

### 2018-09-13 splashpipe/3_consolidate.py

@@ -1,0 +1,67 @@
+import numpy as np
+import matplotlib
+matplotlib.use("Agg")
+import matplotlib.pyplot as pl
+import sys
+import palettable
+colors=palettable.colorbrewer.qualitative.Dark2_8.mpl_colors
+
+
+deproject=False
+
+directory = sys.argv[1]
+
+fname = directory + "/Clu=Norm_Gal=Norm/pairs.dat"
+ranname = directory + "/Clu=Ran_Gal=Norm/pairs.dat"
+
+rad, counts, avr, area = np.loadtxt(fname, usecols=(0, 1, 2, 3), unpack=1)
+r_arr = np.unique(rad)
+Nclu=np.loadtxt(directory+"/Clu=Norm_Gal=Norm/Ncluster.dat")
+Nclu = np.tile(Nclu, r_arr.size)
+
+if deproject==False:
+    foo=np.loadtxt(ranname, unpack=1)
+    rad, rancounts, avr, area, = np.loadtxt(ranname, usecols=(0, 1, 2, 3), unpack=1)
+    Nclu_ran=np.loadtxt(directory+"/Clu=Ran_Gal=Norm/Ncluster.dat")
+    Nclu_ran = np.tile(Nclu_ran, r_arr.size)
+
+Nrad = r_arr.size
+Njack = rad.size/Nrad
+r_arr = rad[0::Njack]
+xi = np.zeros(Nrad)
+xi_err = np.zeros(Nrad)
+xi_cov = np.zeros(Nrad*Nrad).reshape(Nrad, Nrad)
+logrdiff=(r_arr[1]-r_arr[0])
+r_arrbins = 10.0**np.append(r_arr, r_arr[-1]+logrdiff)
+shell = 4./3.*np.pi*(r_arrbins[1:]**3-r_arrbins[:-1]**3)
+
+if deproject:
+    xijack = counts/np.repeat(shell,Njack)-1.
+else:
+    xijack = counts/(rancounts*Nclu/Nclu_ran) - 1.0
+
+for i in range(r_arr.size):
+    xi[i] = np.mean(xijack[Njack*i:Njack*(i+1)])
+
+for i in range(r_arr.size):
+    begi = Njack*i
+    endi = Njack*(i+1)
+    for j in range(r_arr.size):
+        begj = Njack*j
+        endj = Njack*(j+1)
[…]

### 2018-09-13 splashpipe/build/lib.linux-x86_64-2.7/splashback.py

@@ -1,0 +1,149 @@
+# This file was automatically generated by SWIG (http://www.swig.org).
+# Version 2.0.10
+#
+# Do not make changes to this file unless you know what you are doing--modify
+# the SWIG interface file instead.
+
+
+
+from sys import version_info
+if version_info >= (2,6,0):
+    def swig_import_helper():
+        from os.path import dirname
+        import imp
+        fp = None
+        try:
+            fp, pathname, description = imp.find_module('_splashback', [dirname(__file__)])
+        except ImportError:
+            import _splashback
+            return _splashback
+        if fp is not None:
+            try:
+                _mod = imp.load_module('_splashback', fp, pathname, description)
+            finally:
+                fp.close()
+            return _mod
+    _splashback = swig_import_helper()
+    del swig_import_helper
+else:
+    import _splashback
+del version_info
+try:
+    _swig_property = property
+except NameError:
+    pass # Python < 2.2 doesn't have 'property'.
+def _swig_setattr_nondynamic(self,class_type,name,value,static=1):
+    if (name == "thisown"): return self.this.own(value)
+    if (name == "this"):
+        if type(value).__name__ == 'SwigPyObject':
+            self.__dict__[name] = value
+            return
+    method = class_type.__swig_setmethods__.get(name,None)
+    if method: return method(self,value)
+    if (not static):
+        self.__dict__[name] = value
+    else:
+        raise AttributeError("You cannot add attributes to %s" % self)
+
+def _swig_setattr(self,class_type,name,value):
+    return _swig_setattr_nondynamic(self,class_type,name,value,0)
+
+def _swig_getattr(self,class_type,name):
+    if (name == "thisown"): return self.this.own()
+    method = class_type.__swig_getmethods__.get(name,None)
+    if method: return method(self)
+    raise AttributeError(name)
+
+def _swig_repr(self):
+    try: strthis = "proxy of " + self.this.__repr__()
+    except: strthis = ""
+    return "<%s.%s; %s >" % (self.__class__.__module__, self.__class__.__name__, strthis,)
+
+try:
+    _object = object
+    _newclass = 1
+except AttributeError:
+    class _object : pass
+    _newclass = 0
+
+
+class dp(_object):
+    __swig_setmethods__ = {}
[…]

### 2018-09-13 splashpipe/calc_SNR.py

@@ -1,0 +1,60 @@
+import numpy as np
+import pandas as pd
+import scipy.linalg
+def calc_area(type_):
+   if type_=='Planck_PS_21':
+       randinit=1304704002
+       randafter=617205099
+   elif type_=='Planck_PS_22':
+       randinit=1155286477.0*4.0/3.0
+       randafter=585841750.0
+   elif type_=='Planck_PS_21.5':
+       randinit=1155286477.0*4.0/3.0
+       randafter=768660433
+   area=randafter/(randinit/(41253))
+   return area
+
+
+def calc_SNR(type_):
+    if type_=='surhud':
+        data=np.genfromtxt("/home/dominik.zuercher/Documents/RSP_Pro/Mest/redmap.dat")
+        cov_data = np.genfromtxt("/home/dominik.zuercher/Documents/RSP_Pro/Mest/redmap.cov")[:,0]
+        cov=cov_data.reshape((data[:,0].size,data[:,0].size))
+    else:
+	data = pd.read_csv("/home/dominik.zuercher/Documents/RSP_Pro_reload/splashpipe/reloaded/"+str(type_)+"/xi_2d.dat", header=None, sep = ' ')
+	cov_data = pd.read_csv("/home/dominik.zuercher/Documents/RSP_Pro_reload/splashpipe/reloaded/"+str(type_)+"/xi_2d_cov.dat", header=None, sep = ' ')
+        cov = np.asarray(cov_data.values)
+        data = np.asarray(data.values)
+
+    rr = data[:,0]
+    yy = data[:,1]
+    yy_err = data[:,2]
+
+    invcov=scipy.linalg.inv(cov)
+
+    SNR=np.sqrt(np.dot(yy,np.dot(invcov,yy)))
+    #SNR=np.sqrt(np.dot(yy.T, np.dot(invcov, yy)))
+    return SNR
+
+
+
+#Survey areas
+types=['Planck_PS_21','Planck_PS_22','Planck_PS_21.5']
+for type_ in types:
+    print("Effective survey area of "+str(type_)+" is "+str(calc_area(type_)))
+
+#SNRs
[…]

### 2018-09-13 splashpipe/calc_fractions.py

@@ -1,0 +1,99 @@
+import pandas
+import numpy as np
+import pylab as pl
+
+
+def get_sigma(dire, colors,Njack):
+    sigma = {}
+    xi_full={} 
+    xi_err_full={}
+    ratio={}
+    xi_ratio_full={} 
+    xi_err_ratio_full={}
+    for col in colors:
+        diree = dire+col
+        df = pandas.read_csv(diree+"/Clu=Norm_Gal=Norm/pairs.dat", delim_whitespace=1, header=None, names=(["Rp", "DD", "AVR", "Area"]))
+        Ncluster = np.loadtxt(diree+"/Clu=Norm_Gal=Norm/Ncluster.dat")
+        Ncluster = np.repeat(Ncluster, np.unique(df.Rp.values).size)
+
+        df_r = pandas.read_csv(diree+"/Clu=Ran_Gal=Norm/pairs.dat", delim_whitespace=1, header=None, names=(["Rp", "DR", "AVR", "Area"]))
+        Ncluster_r = np.loadtxt(diree+"/Clu=Ran_Gal=Norm/Ncluster.dat")
+        Ncluster_r = np.repeat(Ncluster_r, np.unique(df_r.Rp.values).size)
+
+        sigma[col] = df.DD.values/df.Area.values/Ncluster - df_r.DR.values/df_r.Area.values/Ncluster_r
+
+
+        Nrad=np.unique(df_r.Rp.values).size      
+        xi=np.zeros(np.unique(Nrad))
+        xi_err = np.zeros(Nrad)
+        xi_cov = np.zeros(Nrad*Nrad).reshape(Nrad, Nrad)
+
+	for i in range(Nrad):
+	    xi[i] = np.mean(sigma[col][Njack*i:Njack*(i+1)])
+
+	for i in range(Nrad):
+	    begi = Njack*i
+	    endi = Njack*(i+1)
+	    for j in range(Nrad):
+		begj = Njack*j
+		endj = Njack*(j+1)
+		xi_cov[i][j] = np.mean((sigma[col][begi:endi]-xi[i])*(sigma[col][begj:endj]-xi[j]))*(Njack-1.)
+	    xi_err[i] = xi_cov[i][i]**0.5
+        #np.savetxt("xi_2d%s.dat"% col, np.transpose([10.0**np.unique(df_r.Rp.values), xi, xi_err]))
[…]

### 2018-09-13 splashpipe/make_plots.py

@@ -1,0 +1,672 @@
+import pandas as pd
+import numpy as np
+import matplotlib
+matplotlib.use("Agg")
+import matplotlib.pyplot as plt
+import palettable 
+cm=palettable.colorbrewer.qualitative.Dark2_8.mpl_colors
+
+
+def assign_color(i,idx):
+    return cm[i]
+
+def assign_color_xr(i):
+    return cm[i*2]
+
+def curve_graphs(types):
+    f1, axarr1 = plt.subplots(ncols=2,nrows=3,figsize=(6,6))
+    f2, axarr2 = plt.subplots(ncols=2,nrows=3,figsize=(6,6))
+    i=0
+    shifts=np.asarray([1,1,1])
+    for type_ in types:
+	print("Doing %s",type_)
+	dr_dat = np.genfromtxt("%s/%s/xi_2d.dat" % (splash_directory, type_))
+
+	idx = (dr_dat[:,0] > 0.1) & (dr_dat[:,0] < 10.0)
+	rr=dr_dat[idx,0]
+	rrange=np.linspace(rr[0],rr[-1],rsteps)
+
+	dr_plotdat=pd.read_csv("%s/%s/plotsave.dat" % (est_directory, type_),sep=' ',header=None)
+	dr_plotdat=np.asarray(dr_plotdat.values)
+	dr_sigmas=dr_plotdat[0:rsteps,:]
+	dr_rhos=dr_plotdat[rsteps:rsteps*2,:]
+	dr_devs=dr_plotdat[rsteps*2:rsteps*3,:]
+	dr_rhodevs=dr_plotdat[rsteps*3:rsteps*4,:]
+
+	dr_splashdat=pd.read_csv("%s/%s/values.dat" % (est_directory, type_), sep=' ',header=None)
+	dr_splashdat=np.asarray(dr_splashdat.values)
+	dr_rsp2ds=dr_splashdat[0,:]
+	dr_rsp3ds=dr_splashdat[1,:]
+        
+        print("Data read")
+        print("Plotting...")
+
+	#Plot 2D data
+	axarr1[i,0].errorbar(dr_dat[:,0], dr_dat[:,1], dr_dat[:,2], fmt=".",capsize=2,c='k')
+
+	#Plot 2D MCMC fits
[…]

### 2018-09-13 splashpipe/mpi_splashback.py

@@ -1,0 +1,79 @@
+import sys
+print(sys.path)
+sys.path.insert(0, "install/lib64/python2.7/site-packages/")
+print(sys.path)
+import numpy as np
+import socket
+from mpi4py import MPI
+import mpi4py
+from splashback_aroundsource import run_pipeline
+import argparse
+import sys
+
+def getsource_dict(rank, size, magcut, colored, galaxydir):
+    d = {}
+    d["type"] = galaxydir
+    d["filetype"] = "ascii"
+    d["mag_limit"] = magcut
+    d["z_limit"] = 0.33
+    d["rank"] = rank
+    d["size"] = size
+    d["colored"] = colored
+    return d
+
+def getlens_dict(rank, size, magcut, Njack, clusterdir):
+    d = {}
+    d["type"] = clusterdir
+    d["zmin"] = 0.03
+    d["zmax"] = 0.33
+    d["Njack"] = Njack
+    d["mag_limit"] = magcut
+    d["rank"] = rank
+    d["size"] = size
+    return d
+
+if __name__ == "__main__":
+    comm = MPI.COMM_WORLD
+    rank = comm.rank
+    size = comm.size
+
+    parser = argparse.ArgumentParser(formatter_class=argparse.ArgumentDefaultsHelpFormatter)
+    parser.add_argument("--rmax", help="Max radius", type=float, default=10.0)
+    parser.add_argument("--rmin", help="Min radius", type=float, default=0.1)
+    parser.add_argument("--rbin", help="Radial bin", type=int, default=8)
+    parser.add_argument("--dirout", help="Directory", default="debug")
+    parser.add_argument("--random", help="To use random sources or not", type=int, default=0)
+    parser.add_argument("--colored", help="To use color code or not (0,1,-1)", type=int, default=0)
+    parser.add_argument("--magcut", help="Magnitude cut", default="21.5")
+    parser.add_argument("--clusterdir", help="Cluster directory", default="Planck")
+    parser.add_argument("--galaxydir", help="Galaxy directory", default="Pan-Starrs_chunks")
+    parser.add_argument("--deproject", help="Deproject or not (True or False)", type=bool, default=False)
+    parser.add_argument("--Njack", help="Number of Jackknife bins to use", default=30)
+
+    args = parser.parse_args()
+
+    ssample = getsource_dict(rank, size, args.magcut, args.colored, args.galaxydir)
[…]

### 2018-09-13 splashpipe/plot_combined_graphs.py

@@ -1,0 +1,130 @@
+import numpy as np
+import matplotlib
+matplotlib.use("Agg")
+import matplotlib.pyplot as plt
+import matplotlib.cm as cm
+
+
+def compare(ests,types,name,pres):
+    colors=np.linspace(0,1,int(len(ests)*len(types)))
+    if pres==True:
+        #shifts=np.linspace(1,10+(int(len(ests)*len(types))-1),int(len(ests)*len(types)))
+        shifts=[9]*(int(len(ests)*len(types)))
+        #shifts[0]+=10
+    else:
+        shifts=np.asarray([1]*int(len(ests)*len(types)))
+    fig=plt.figure(1)
+    ax = plt.subplot(111)
+    i=0
+    for type_ in types:
+        for est in ests:
+            if type_=='surhud':
+                dat=np.genfromtxt("/home/dominik.zuercher/Documents/RSP_Pro/Mest/redmap.dat")
+            elif "SDSS" in type_:
+                     dat=np.genfromtxt("/work/dominik.zuercher/DataStore/corr-pairs/Planck_SDSS/Planck_SDSS_plot("+str(est)+").dat")
+            else:
+                 try:
+                     dat=np.genfromtxt("/work/dominik.zuercher/DataStore/corr-pairs/"+str(type_)+"/"+str(type_)+"_plot("+str(est)+").dat")
+                 except:
+                     continue
+            print("-----------------------------------------")
+            print(type_,est)
+            print(dat)
+            print("-----------------------------------------")
+            if type_=='surhud':
+                ax.errorbar(dat[:,0], np.multiply(dat[:,1],0.1), np.multiply(dat[:,2],0.1), fmt=".",c=cm.nipy_spectral(colors[i]),capsize=2, alpha=1,label ="RedMaPPer") 
+            else:
+                ax.errorbar(dat[:,0], np.multiply(dat[:,1],shifts[i]), np.multiply(dat[:,2],shifts[i]), fmt=".",capsize=2,c=cm.nipy_spectral(colors[i]), alpha=0.8,label =str(type_)+" ("+str(est)+")")
+            i+=1
+    ax.set_title("Comparison")
+    ax.set_xscale("log")
+    ax.set_yscale("log")
+    ax.set_xlabel(r"$R$ ($h^{-1}$Mpc)")
+    ax.set_ylabel(r"$\xi^{\rm 2d}$ ($h^{-1}$Mpc)")
+    plt.legend()
[…]

### 2018-09-13 splashpipe/redshift_plotter.py

@@ -1,0 +1,19 @@
+import numpy as np
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+dirin="/work/dominik.zuercher/DataStore/corr-pairs/Planck_PS_21_rebin/Normal"
+full=np.zeros(0)
+for i in range(0,30):
+	normal=np.loadtxt(dirin+"/redshift_distribution_"+str(i)+".txt")
+        print(normal)
+        full=np.append(full,normal)
+        """
+	for rank in range(0,168):
+		data=np.load(dirin+"/save_random_"+str(rank)+"_"+str(i)+".npy")
+		fulldata=np.add(fulldata,data[0,:])
+	fulldatasum=fulldata[-1]
+	fulldata=np.divide(fulldata,fulldatasum)
+        """
+plt.hist(full)
+plt.savefig(dirin+"/redshift_dist.pdf")

### 2018-09-13 splashpipe/setup.py

@@ -1,0 +1,27 @@
+#!/usr/bin/env python
+
+"""
+setup.py file for splashpipe
+"""
+
+from distutils.core import setup, Extension
+import numpy
+
+splashback_module = Extension('_splashback',
+                          sources=['src/splashback.i', 'src/splashback.cpp', 'src/cosmology.cpp', 'src/haloes.cpp', 'src/powerspectrum.cpp', 'src/gauleg.cpp', 'src/kdtree2.cpp'],
+                          swig_opts=["-keyword","-c++"],
+                          libraries=['m','gsl','gslcblas', 'boost_system'],
+                          include_dirs=[numpy.get_include()],
+                          )
+
+setup (name        = 'splashpipe',
+      version     = '0.01',
+      author      = "Surhud More",
+      url         = "http://member.ipmu.jp/surhud.more/research",
+      author_email= "surhud.more@ipmu.jp",
+      description = """Splashback radius pipeline tools""",
+      ext_modules = [splashback_module],
+      license     = ['GPL'],
+      py_modules  = ["splashback"],
+      package_dir = { '':'src'},
+      )

### 2018-09-13 splashpipe/splashback_aroundsource.py

@@ -1,0 +1,144 @@
+import sys
+print(sys.path)
+sys.path.insert(0, "install/lib64/python2.7/site-packages/")
+print(sys.path)
+import splashback
+print("Look here:", splashback.__file__)
+import frogress
+import pandas
+import numpy as np
+import sys
+import pyfits
+import fitsio
+import argparse
+import yaml
+from splashback_select import lens_select, source_select
+from subprocess import call
+
+def run_pipeline(config):
+
+    rmin = config["rmin"]
+    rmax = config["rmax"]
+    rbin = config["rbin"]
+    dirout = config["dirout"]
+    randomsources = config["randomsources"]
+    colored = config["colored"]
+    deproject=config["deproject"]
+
+    if randomsources:
+        pairout = config["dirout"]+"/random_pairs.dat"
+    else:
+        pairout = config["dirout"]+"/pairs.dat"
+
+    # No race condition here as the file is written at the end
+    if not randomsources:
+        call("mkdir -p %s" % (config["dirout"]), shell=1)
+    else:
+        # Wait until directory is written
+        import os
+        import time
+        while not os.path.exists("./%s/" % (config["dirout"])):
+            time.sleep(1)
+    
+    mag_limit = float(config["source"]["mag_limit"])
+    z_limit = config["source"]["z_limit"]
+    
+    splashpipe = splashback.splashback(rmin, rmax, rbin, pairout, mag_limit, z_limit, config["lens"]["Njack"], deproject=deproject, colored=colored, verbose=False)
+    
+    # First get all the lens galaxy data
+    print(config["lens"])
+    ra, dec, zred, wt, jackreg = lens_select(config["lens"])
+
+    #counting jackknife regions
+    if "rank" in config["lens"]:
+        fp=open(config["dirout"]+"/Ncluster_"+str(config["lens"]["rank"])+".dat","w+")
+    else:
+        fp = open(config["dirout"]+"/Ncluster.dat", "w")
+    for ii in range(config["lens"]["Njack"]):
+        idx = (ii != jackreg)
+        fp.write("%d\n" % (np.sum(idx)))
+    fp.close()
+    splashpipe.allocate_lens_memory(ra.size)
+    for i in range(ra.size):
+        splashpipe.process_lens(ra[i], dec[i], zred[i], jackreg[i])
+    tree = splashpipe.finalize_lenses()
+    
+    # Ready to pounce on the source data, a million galaxies at a time
+    itern=0
[…]

### 2018-09-13 splashpipe/splashback_select.py

@@ -1,0 +1,395 @@
+import numpy as np
+import pyfits
+import pandas
+import sys
+import fitsio
+import glob
+
+def lens_select(lensargs):
+    np.random.seed(10)
+    Njack = lensargs['Njack']
+    rank = lensargs["rank"]
+    size = lensargs["size"]
+
+    if lensargs['type'] == "Planck":
+        df = pandas.read_csv("/work/dominik.zuercher/DataStore/Planck-SZ/Catalogs/%02d_bins/Planck_%02d_bins.csv" % (Njack, Njack))
+        ra = df["RA"].values
+        dec = df["DEC"].values
+        zred = df["REDSHIFT"].values
+        wt = ra/ra
+        jackreg = df["jackreg"].values
+
+        idx = (zred>lensargs["zmin"]) & (zred<=lensargs["zmax"])
+        ra = ra[idx]
+        dec = dec[idx]
+        zred = zred[idx]
+        wt = wt[idx]
+        jackreg = jackreg[idx]
+        jackreg=jackreg.astype(int)
+	sys.stdout.write("Selecting %d lenses \n" % (np.sum(idx)))
+        return ra, dec, zred, wt, jackreg
+
+    if (lensargs['type'] == "Planck_random"):
+        df = pandas.read_csv("/work/dominik.zuercher/DataStore/Planck-SZ/Randoms/%02d_bins/Planck_randoms_%02d_bins_%s.csv" % (Njack, Njack, str(lensargs["mag_limit"])), sep = ",")
+        ra = df["RA"].values
+        dec = df["DEC"].values
+        zred = df["REDSHIFT"].values
+        wt = ra/ra
+        jackreg = df["jackreg"].values
+        #rankarr = np.random.randint(size, size=ra.size)
+        #idx = (zred>lensargs["zmin"]) & (zred<=lensargs["zmax"]) & (rankarr==rank)
+        idx = (zred>lensargs["zmin"]) & (zred<=lensargs["zmax"])
+        ra = ra[idx]
+        dec = dec[idx]
+        zred = zred[idx]
+        wt = wt[idx]
+        jackreg = jackreg[idx]
+        jackreg=jackreg.astype(int)
+        sys.stdout.write("Selecting %d lenses \n" % (np.sum(idx)))
+        return ra, dec, zred, wt, jackreg
+
+    if lensargs['type'] == "redmapper":
[…]

### 2018-09-13 splashpipe/src/cosmology.cpp

@@ -1,0 +1,878 @@
+///Cosmology routines
+#include "cosmology.h"
+
+///Default constructor WMAP3 flat cosmology
+cosmology::cosmology()
+{
+    Omega0 = 0.238;
+    Omegab = 0.02233/pow(0.734,2.);
+    Omegak=0.0;
+    Omegal = 1.-Omega0-Omegak;
+    h      = 0.734 ;
+    theta  = 1.0093;///2.7;
+    sigma8 = 0.744;
+    ns     = 0.951;
+    w0     =-1.0;
+    wa     = 0.0;
+    xiNLzetamax=log10(8.0);
+    cfactor=1.0;
+    initialize();
+    if(verbose) std::cout<<"# Cosmo constructor 1 called\n";
+}
+
+/** Initialize the cosmology dependent routines
+ *  and output to the log
+ * */
+void cosmology::initialize()
+{
+    /// Initialize all constants required for the program
+    verbose=false;
+    mock=false;
+    takahashicorr=false;
+    peacockcorr=false;
+
+    kmpspMpctoGyr=977.813952;
+    gee=4.2994e-9;
+    c=299792.458;
+    e=2.71828183;
+
+    /// Numerical interpolation units for power spectra and correlations
+    kmin=-5.0;
+    kmax=8.0;
+    rmin=-5.0;
+    rmax=5.0;
+    kbins=161;
+
+    /// Numerical interpolation for ukofm
+    cmin=-1.0;
+    cmax=3.5;
+    krsmax= 8.0;
+    krsmin=-6.0;
+    Nuk = 100;
+
+    // Gauleg
+    N9_16 = 100;
+    N0_2p = 57;
+    Nsigma=100;
+    Ngf=1000;
+    Npower=1000;
+    Nxi=1000;
+    Nxibar=1000;
+
+
+    /// For initQk
+    hod_kmin=-4.0;
+    hod_kmax=7.5;
+
+    /// Initialize options
+    opt_mf=1;
+    opt_b=1;
+    opt_c=1;
+    opt_ps_L=1;
+    opt_ps_NL=1;
+
+    /// Initialize the time today
+    t0=Time(0.0);
+
+    /// Init z_glob
+    z_glob=0.0;
+    gf_glob=1.0;
+
+    /// Initialise the boolean variables
+    bool_init_Chi=false;
+    bool_initPS=false;
+    bool_init_PSL0=false;
+    bool_init_PSNL=false;
[…]

### 2018-09-13 splashpipe/src/cosmology.h

@@ -1,0 +1,586 @@
+#ifndef COSMOLOGY_H
+#define COSMOLOGY_H
+
+# include "cosmology.h"
+# include "gauleg.h"
+# include <cmath>
+# include <string>
+# include <iostream>
+# include <fstream>
+# include <gsl/gsl_integration.h>
+# include <gsl/gsl_sf.h>
+# include <gsl/gsl_math.h>
+# include <gsl/gsl_roots.h>
+# include <gsl/gsl_spline.h>
+# include <gsl/gsl_matrix.h>
+# include <gsl/gsl_odeiv.h>
+# include <gsl/gsl_errno.h>
+
+struct cosmo
+{
+    double  Om0,Omk,w0,wa,Omb,hval,th,s8,nspec,ximax,cfac;
+};
+
+struct gf_par{
+    double Omega0,OmegaL,w0,wa;
+};
+
+/// march_params object
+struct march_params
+{
+    double fac;
+};
+
+class cosmology;
+
+struct qk_params
+{
+    cosmology *cptr;
+    double *k;
+    double *z;
+    double *xmax;
+    int opt;
+};
+
+struct projwpk_params
+{
+    cosmology *cptr;
+    double *R;
+    double *z;
+    double *fkai;
+};
+
+/// Object to pass cosmology, cvir, Omega(z), Deltacrit(z)
+struct cDel_params
+{
+    cosmology *cptr;
+    double *cvir;
+    double *omegaz;
+    double *dcz;
+    double *Delta;
+};
+
+double dTime(double,void*);
+double dChi (double,void*);
+//double df3 (double,void*);
+double dneffint(double, void*);
+double dCint(double, void*);
+double findmvir(double, void*);
+double findksig(double, void*);
+double dxi_L(double, void*);
+double dPktest_L(double, void*);
+double dPktest_NL(double, void*);
+double dPktest_zetaNL(double, void*);
+double dxi_NL(double, void*);
+double E_sq(gf_par&, double&);
+double dE_sqdz(gf_par&,double&);
+void getall(gf_par&,double&,double&,double&,double&);
+double d2lnE_sqdz2(gf_par&,double&);
+int gf_func(double, const double[], double [], void*);
+int gf_jac(double, const double[], double*, double [], void*);
+double findrz(double x, void *params);
+class hod;
+double findzmax(double x, void *params);
+double dwpnl(double x, void* params);
+double dwpl(double x, void* params);
+double dQk(double,void*);
+
[…]

### 2018-09-13 splashpipe/src/haloes.cpp

@@ -1,0 +1,1161 @@
+/// Power spectrum routines part of cosmology class
+#include "cosmology.h"
+#include <gsl/gsl_sf_trig.h>
+
+
+/// Mass function wrapper
+double cosmology::nofm(double M, double z)
+{
+    double result;
+    if(opt_mf==1)
+    {
+        result=MF_TI10(M,z);
+    }else if(opt_mf==2)
+    {
+	result=MF_ST(M,z);
+    }else if(opt_mf==3)
+    {
+	result=MF_BH(M,z);
+    }else
+    {
+        std::cout<<"Mass function option not supported yet"<<std::endl;
+        exit(0);
+    }
+    return result;
+}
+
+/// Tinker et al. 2009 SO (350) mass function The mass function is in comoving coordinates.
+/// n(M) dM has the units of h^3 Mpc^{-3}
+double cosmology::MF_TI09_350(double M, double z)
+{
+    double sig=sqrt(varM_TH_num(M,z));
+    double dlogsigdlogm= 0.5*(log(varM_TH_num(0.99*M,z))-log(varM_TH_num(1.01*M,z)))/(log(0.99*M)-log(1.01*M));
+    double A0=0.206;
+    double sa0=1.54,b0=2.15,c0=1.31;
+    double Aofz=A0*pow(1.+z,-0.14);
+    double saofz=sa0*pow(1.+z,-0.06);
+    double alp350=pow(10.,-pow(0.75/log10(350.0/75.0),1.2));
+    double bofz=b0*pow(1.+z,-alp350);
+    double cofz=c0;
+    double fsig=Aofz*(pow(sig/bofz,-saofz)+1.)*exp(-cofz/pow(sig,2.));
+
+    return rho_crit_0*Omega0*fsig/pow(M,2.)*fabs(dlogsigdlogm);
+}
+
+/// Tinker et al. 2010 SO (200) mass function The mass function is in comoving coordinates.
+/// n(M) dM has the units of h^3 Mpc^{-3}
+double cosmology::MF_TI10(double M, double z)
+{
+    if(z!=z_glob){
+	setnew_z(z);
+    }
+    if(!init_Tink){
+	initTinker(z);
+    }
+
+    double dc=1.686;
+    double sig=sqrt(varM_TH_num(M,z));
+    double xnu=dc/sig;
+
+    // Note that the variance can be calced either at z=0.0 or z=z.
[…]

### 2018-09-13 splashpipe/src/kdtree2.cpp

@@ -1,0 +1,1145 @@
+//
+// (c) Matthew B. Kennel, Institute for Nonlinear Science, UCSD (2004)
+//
+// Licensed under the Academic Free License version 1.1 found in file LICENSE
+// with additional provisions in that same file.
+
+#include "kdtree2.h"
+
+#include <algorithm> 
+#include <iostream>
+
+namespace kdtree2 {
+// utility
+
+inline float squared(const float x, const float per) {
+    float y=fabs(x);
+  if(per>0.0){
+    if(y>per/2.) y=per-y;
+  }
+    return(y*y);
+}
+
+inline void swap(int& a, int&b) {
+  int tmp;
+  tmp = a;
+  a = b;
+  b = tmp; 
+}
+
+inline void swap(float& a, float&b) {
+  float tmp;
+  tmp = a;
+  a = b;
+  b = tmp; 
+}
+
+
+//
+//       KDTREERESULT implementation
+// 
+
+inline bool operator<(const KDTreeResult& e1, const KDTreeResult& e2) {
+  return (e1.dis < e2.dis);
+}
+
+//
+//       KDTREE2_RESULT_VECTOR implementation
+// 
+float KDTreeResultVector::max_value() {
+  return( (*begin()).dis ); // very first element
+}
+
+void KDTreeResultVector::push_element_and_heapify(KDTreeResult& e) {
+  push_back(e); // what a vector does.
+  push_heap( begin(), end() ); // and now heapify it, with the new elt.
+}
+float KDTreeResultVector::replace_maxpri_elt_return_new_maxpri(KDTreeResult& e) {
+  // remove the maximum priority element on the queue and replace it
+  // with 'e', and return its priority.
+  //
+  // here, it means replacing the first element [0] with e, and re heapifying.
+  
+  pop_heap( begin(), end() );
+  pop_back();
+  push_back(e); // insert new
+  push_heap(begin(), end() );  // and heapify. 
+  return( (*this)[0].dis );
+}
+
+//
+//        KDTREE2 implementation
+//
+
+// constructor
+KDTree::KDTree(KDTreeArray& data_in,KDTreePeriod& xp,int xN, int xdim, int bs, bool rearrange_in,int dim_in)
+  : the_data(data_in),
+    period(xp),
+    N  (xN ),
+    dim(xdim),
+    sort_results(false),
+    rearrange(rearrange_in), 
+    root(NULL),
+    data(NULL),
[…]

### 2018-09-13 splashpipe/src/kdtree2.h

@@ -1,0 +1,265 @@
+#ifndef __KDTREE2_H
+#define __KDTREE2_H
+
+//
+// (c) Matthew B. Kennel, Institute for Nonlinear Science, UCSD (2004)
+//
+// Licensed under the Academic Free License version 1.1 found in file LICENSE
+// with additional provisions in that same file.
+
+
+
+//
+// Implement a kd tree for fast searching of points in a fixed data base
+// in k-dimensional Euclidean space.
+//
+// 
+
+#include <vector>
+#include <algorithm>
+#include <cmath>
+#include <iostream>
+#include <cstdio>
+
+#include <boost/multi_array.hpp>
+#include <boost/array.hpp>
+namespace kdtree2 {
+typedef float * KDTreeArray;
+typedef boost::multi_array<float,1>             KDTreePeriod;
+typedef boost::const_multi_array_ref<float,2>   KDTreeROArray;  // read only ref
+
+
+typedef struct {
+  float lower, upper;
+} interval;
+
+
+// let the compiler know that this is a names of classes. 
+class KDTreeNode; 
+class SearchRecord;
+
+//
+// struct KDTreeResult
+// class  KDTreeResult
+//
+
+
+struct KDTreeResult {
+  // 
+  // the search routines return a (wrapped) vector
+  // of these. 
+  //
+public:
+  float dis;  // its square Euclidean distance
+  int idx;    // which neighbor was found
+}; 
+
+class KDTreeResultVector : public std::vector<KDTreeResult> {
+  // inherit a std::vector<KDTreeResult>
+  // but, optionally maintain it in heap form as a priority
+  // queue.
+public:
+
+  //  
+  // add one new element to the list of results, and
+  // keep it in heap order.  To keep it in ordinary, as inserted,
+  // order, then simply use push_back() as inherited
+  // via std::vector<> 
+
+  void push_element_and_heapify(KDTreeResult&);
+  float replace_maxpri_elt_return_new_maxpri(KDTreeResult&);
+
+  float max_value(); 
+  // return the distance which has the maximum value of all on list, 
+  // assuming that ALL insertions were made by
+  // push_element_and_heapify() 
+};
+
+
+//
+// class KDTree
+//
+// The main data structure, one for each k-d tree, pointing
+// to a tree of an indeterminate number of "KDTreeNode"s.
+//
+
+class KDTree {
+public: 
+  const KDTreeArray& the_data;   
+  // "the_data" is a reference to the underlying multi_array of the
[…]

### 2018-09-13 splashpipe/src/main.cpp

@@ -1,0 +1,35 @@
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <math.h>
+#include <iostream>
+#include <fstream>
+#include "splashback.h"
+#include <vector>
+#include <ctime>
+#include <cstring>
+#include <cmath>
+
+int main(int argc, char** argv)
+{
+    /*
+    cosmology a = cosmology(0.30, 0.0, -1.0, 0.0, 0.0476, 0.7, 2.726, 0.8, 0.96, log10(8.0), 1.0);
+    printf("%.7e\n",a.Dlofz(0.5));
+    */
+    splashback a = splashback(0.10, 10.0, 10, (char *)"debug.dat", 21.0, 0.33, 100, false, 0, true);
+    a.allocate_lens_memory(10000);
+    for (int i=0; i<100; i++){
+        for (int j=0; j<100; j++){
+            a.process_lens(i/100.*2*M_PI, j/100.*2*M_PI-M_PI, 0.5, i);
+        }
+    }
+    a.finalize_lenses();
+
+    for (int i=0; i<100; i++){
+        a.process_source(0.6*2*M_PI, 0.1*M_PI, 21.0, 0);
+    }
+
+    a.finalize_results();
+    a.finalize_results(true);
+}
+

### 2018-09-13 splashpipe/src/powerspectrum.cpp

@@ -1,0 +1,2742 @@
+/// Power spectrum routines part of cosmology class
+#include "cosmology.h"
+
+/// Linear Powerspectrum wrappers
+double cosmology::Delta2_L(double k,double z)
+{
+    double result;
+
+    if(opt_ps_L==1)
+    {
+        result=Delta2_EH(k, z);
+    } else
+    {
+        std::cout<<"Linear power spectrum option not supported yet."<<std::endl;
+        exit(0);
+    }
+
+    return result;
+
+}
+
+double cosmology::Pk_L(double k,double z)
+{
+    double result;
+
+    if(opt_ps_L==1)
+    {
+        result=Pk_EH(k, z);
+    } else
+    {
+        std::cout<<"Linear power spectrum option not supported yet."<<std::endl;
+        exit(0);
+    }
+
+    return result;
+
+}
+
+/// Nonlinear Powerspectrum wrappers
+double cosmology::Pk_NL(double k,double z)
+{
+    double result;
+
+    if(opt_ps_NL==1)
+    {
+        result=PkNL_S(k, z);
+    } else
+    {
+        std::cout<<"Non-linear power spectrum option not supported yet."<<std::endl;
+        exit(0);
+    }
+
+    return result;
+
+}
+
+double cosmology::Delta2_NL(double k,double z)
+{
+    double result;
+
+    if(opt_ps_NL==1)
+    {
+        result=Delta2NL_S(k, z);
+    } else
+    {
+        std::cout<<"Non-linear power spectrum option not supported yet."<<std::endl;
+        exit(0);
+    }
+
+    return result;
+
+}
+
+/// Initialize power spectrum variables Eisenstein and Hu 1998
+double cosmology::initPS_EH()
+{
+
+    double O0h2=Omega0*h*h;
+    double Obh2=Omegab*h*h;
+
+    if(verbose){
+    std::cout<<"# "<<"============================================================="<<std::endl;
+    std::cout<<"# "<<" O0h2="<<O0h2<<" "<<" Obh2="<<Obh2<<std::endl;
+    }
+
[…]

### 2018-09-13 splashpipe/src/splashback.cpp

@@ -1,0 +1,374 @@
+#include <fstream>
+#include <string>
+#include <vector>
+#include <sstream>
+#include <fstream>
+#include "splashback.h"
+#include "spline.h"
+
+splashback::splashback(float xrmin, float xrmax, int xrbins, char *xoutfile, float xmag_limit, float xzmax, int xNjack, bool xdeproject, int xcolored, bool xverbose)
+{
+    fprintf(stderr,"Using right code");
+    class_initialized=true;
+    rmin=xrmin;
+    rmax=xrmax;
+    rbins=xrbins;
+    logrmin=log10(rmin);
+    logrmax=log10(rmax);
+    logrdiff=(logrmax-logrmin)/rbins;
+    mag_limit=xmag_limit;
+    zmax = xzmax;
+    Njack=xNjack;
+    sprintf(outfile, "%s", xoutfile);
+
+    deproject=xdeproject;
+    verbose=xverbose;
+    colored=xcolored;
+
+    count_num=NULL;
+    denom_count_num=NULL;
+    Rarr=NULL;
+    count_num = (double *)calloc(rbins*Njack,sizeof(double));
+    Rarr = (double *)calloc(rbins+1, sizeof(double));
+    for (int i=0;i<=rbins;i++)
+    {
+        float rrmin = pow(10., logrmin + i*logrdiff);
+        Rarr[i] = rrmin;
+    }
+
+    // ========================================================
+    // Initialize cosmology
+    // ========================================================
+    cosmo=NULL;
+    cosmo = new cosmology(0.27,0.0,-1.0,0.0,0.0476,0.7,2.726,0.8,0.96,log10(8.0),1.0);
+    lenses_alloc=false;
+    lenses_finalized=false;
+    zredmin=1.E30;
+    zredmax=-1.E30;
+    gee = 4.2994e-9;
+    cee = 3.E5;
+    Dcomzmax = cosmo->Dcofz(double(zmax));
+
+    if (verbose){
+        fprintf(stderr, "Initialized cosmology, and delta sigma sum arrays\n");
+        fprintf(stderr, "Options passed rmin:%f rmax:%f rbins:%d outfile:%s \n", rmin, rmax, rbins, outfile);
+    }
+}
+
+splashback::~splashback(){
+    if (class_initialized){
+	free(Rarr);
+	free(count_num);
+	delete cosmo;
+    /*    */
+	class_initialized=false;
+    }
+    if (verbose){
[…]

### 2018-09-13 splashpipe/src/splashback.h

@@ -1,0 +1,72 @@
+#ifndef SPLASHBACK_H
+#define SPLASHBACK_H
+
+#include <iostream>
+#include <cstdlib>
+#include <cstdio>
+#include <ctime>
+#include <cmath>
+#include <fstream>
+#include "cosmology.h"
+#include "kdtree2.h"
+#include <vector>
+#include <ctime>
+#include <cstring>
+#include <cmath>
+#include <boost/multi_array.hpp>
+typedef boost::multi_array<float,1> array1dfloat;
+#include <boost/timer.hpp>
+
+class splashback;
+
+class splashback
+{
+    protected:
+        cosmology *cosmo;
+        bool verbose;
+        float rmin;
+        float rmax;
+        float logrmin;
+        float logrmax;
+        float logrdiff;
+        float mag_limit;
+        float zmax, Dcomzmax;
+        bool deproject;
+        int rbins;
+        int colored;
+        float *ra, *dec, *zred, *lam, *datacen, *c_lra, *s_lra, *c_ldec, *s_ldec, *Dcom, *maglimz, *wt;
+        double *Rarr;
+        int *jackreg;
+        int Ncen, Nfill;
+        float zredmin, zredmax, Dcommin;
+        double *count_num;
+        double *denom_count_num;
+        char outfile[1000];
+        char outfile_denom[1006];
+        boost::timer *timer;
+        long int Niter;
+        int Njack;
+        bool lenses_alloc, lenses_finalized;
+        array1dfloat xper;
+        int dim;
+        bool class_initialized;
+
+        double gee;
+        double cee;
+
+    public:
+        kdtree2::KDTree *tree;
+        //splashback();
+        splashback(float xrmin=0.5, float xrmax=15.0, int xrbins=15, char *xoutfile=(char *)"Debug.dat", float xmag_limit=25.0, float zmax=0.5, int Njack=25, bool deproject=false, int colored=0, bool verbose=false);
+        ~splashback();
+        int allocate_lens_memory(int xNcen);
+        int process_lens(float xra, float xdec, float xzred, int xjackreg, float wt=1.0);
+        int finalize_lenses();
+
+        int process_source(float sra, float sdec, float smag, bool disable_magcheck, float color=1.E30);
+        int finalize_results(bool writeok=false);
+        int test_searchrecord();
+        double deprojection_kernel(double x);
+};
+
+#endif

### 2018-09-13 splashpipe/src/splashback_wrap.cpp

@@ -1,0 +1,4769 @@
+/* ----------------------------------------------------------------------------
+ * This file was automatically generated by SWIG (http://www.swig.org).
+ * Version 2.0.10
+ * 
+ * This file is not intended to be easily readable and contains a number of 
+ * coding conventions designed to improve portability and efficiency. Do not make
+ * changes to this file unless you know what you are doing--modify the SWIG 
+ * interface file instead. 
+ * ----------------------------------------------------------------------------- */
+
+#define SWIGPYTHON
+#define SWIG_PYTHON_DIRECTOR_NO_VTABLE
+
+
+#ifdef __cplusplus
+/* SwigValueWrapper is described in swig.swg */
+template<typename T> class SwigValueWrapper {
+  struct SwigMovePointer {
+    T *ptr;
+    SwigMovePointer(T *p) : ptr(p) { }
+    ~SwigMovePointer() { delete ptr; }
+    SwigMovePointer& operator=(SwigMovePointer& rhs) { T* oldptr = ptr; ptr = 0; delete oldptr; ptr = rhs.ptr; rhs.ptr = 0; return *this; }
+  } pointer;
+  SwigValueWrapper& operator=(const SwigValueWrapper<T>& rhs);
+  SwigValueWrapper(const SwigValueWrapper<T>& rhs);
+public:
+  SwigValueWrapper() : pointer(0) { }
+  SwigValueWrapper& operator=(const T& t) { SwigMovePointer tmp(new T(t)); pointer = tmp; return *this; }
+  operator T&() const { return *pointer.ptr; }
+  T *operator&() { return pointer.ptr; }
+};
+
+template <typename T> T SwigValueInit() {
+  return T();
+}
+#endif
+
+/* -----------------------------------------------------------------------------
+ *  This section contains generic SWIG labels for method/variable
+ *  declarations/attributes, and other compiler dependent labels.
+ * ----------------------------------------------------------------------------- */
+
+/* template workaround for compilers that cannot correctly implement the C++ standard */
+#ifndef SWIGTEMPLATEDISAMBIGUATOR
[…]

### 2018-09-13 splashpipe/test_splines.cpp

@@ -1,0 +1,96 @@
+#include <iostream>
+#include <fstream>
+#include <string>
+#include <vector>
+#include <sstream>
+#include "spline.h"
+
+/*
+#include "./alglib/src/ap.h"
+//disable some irrelevant warnings
+#if (AE_COMPILER==AE_MSVC) && !defined(AE_ALL_WARNINGS)
+#pragma warning(disable:4100)
+#pragma warning(disable:4127)
+#pragma warning(disable:4611)
+#pragma warning(disable:4702)
+#pragma warning(disable:4996)
+#endif
+#include "./alglib/src/alglibinternal.h"
+#include "./alglib/src/alglibmisc.h"
+//#include "./alglib/src/diffequations.h"
+#include "./alglib/src/linalg.h"
+#include "./alglib/src/optimization.h"
+//#include "./alglib/src/solvers.h"
+#include "./alglib/src/statistics.h"
+#include "./alglib/src/dataanalysis.h"
+//#include "./alglib/src/specialfunctions.h"
+#include "./alglib/src/integration.h"
+//#include "./alglib/src/fasttransforms.h"
+#include "./alglib/src/interpolation.h"
+*/
+
+
+int main(){
+
+   std::string line, sub_1, sub_2;
+   std::istringstream os;
+   std::vector<double> redshifts, cuts;
+   double foo;
+   std::ifstream inputFile("/work/dominik.zuercher/Output/match_PS/spline_data.dat");
+
+   if (inputFile.is_open()){
+        while ( getline(inputFile, line) ){
+            sub_1 = line.substr(0, line.find(' '));
+            sub_2 = line.substr(line.find(' '));
+            os.str(sub_1);
+	    os >> foo;
+            redshifts.push_back(foo);
+	    os.str("");
+	    os.clear();
+            os.str(sub_2);
+	    os >> foo;
+            //std::cout<<x<<'\n';
+            cuts.push_back(foo);
+	    os.str("");
+	    os.clear();
+	}
+	inputFile.close();
+    }
+    
+    std::cout << "redshifts \n";
+    for (std::vector<double>::const_iterator i = redshifts.begin(); i != redshifts.end(); ++i){
+        std::cout << *i << ' ';
+    }
+    std::cout << "colors \n";
+    for (std::vector<double>::const_iterator i = cuts.begin(); i != cuts.end(); ++i){
[…]

### 2018-09-13 temp/combined_Mest_plots.py

@@ -1,0 +1,102 @@
+import sys
+sys.path.insert(0,'/home/dominik.zuercher/Documents/RSP_Pro/toolbox')
+import tools
+import scipy.integrate as integrate
+import scipy.special as special
+import numpy as np
+import pandas as pd
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import corner
+import frogress
+import matplotlib.cm as cm
+
+def make_plots(types):
+    
+    dat=pd.read_csv("%s/%s/xi_2d.dat" % (input_dir, types[0]), header=None,sep=' ')
+
+    dat = np.asarray(dat.values)
+    rr = dat[:,0]
+    yy = dat[:,1]
+    yy_err = dat[:,2]
+
+    idx = (dat[:,0] > 0.1) & (dat[:,0] < 10.0)
+    rr=rr[idx]
+    yy=yy[idx]
+    yy_err=yy_err[idx]
+    rrange=np.linspace(rr[0],rr[-1],rsteps)
+
+    f, axarr = plt.subplots(ncols=2,figsize=(30,15))
+
+    for ii, type_ in enumerate(types):
+	plotdat=pd.read_csv("%s/%s/plotsave.dat" % (output_dir, type_) ,sep=' ',header=None)
+	plotdat=np.asarray(plotdat.values)
+	sigmas=plotdat[0:rsteps,:]
+	rhos=plotdat[rsteps:rsteps*2,:]
+	devs=plotdat[rsteps*2:rsteps*3,:]
+	rhodevs=plotdat[rsteps*3:rsteps*4,:]
+
+	splashdat=pd.read_csv("%s/%s/values.dat" % (output_dir, type_),sep=' ',header=None)
+	splashdat=np.asarray(splashdat.values)
+	rsp2ds=splashdat[0,:]
+	rsp3ds=splashdat[1,:]
+	chisquares=splashdat[2,:]
+	maxrhodevs=splashdat[3,:]
+	maxinnerrhodevs=splashdat[4,:]
+
+
+	axarr[0].plot(rrange,devs[:,0],'-',label="MCMC derivative")
+	#axarr[1,0].plot(rrange,devs[:,0]+devs[:,1],'r--')
[…]

### 2018-09-13 temp/combined_profiles.py

@@ -1,0 +1,60 @@
+import sys
+sys.path.insert(0,'/home/dominik.zuercher/Documents/RSP_Pro/toolbox')
+import tools
+import scipy.integrate as integrate
+import scipy.special as special
+import numpy as np
+import pandas as pd
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import corner
+import frogress
+import matplotlib.cm as cm
+
+def make_plots(types):
+    
+
+    for ii, type_ in enumerate(types):
+	dat=pd.read_csv("%s/%s/xi_2d.dat" % (input_dir, type_), header=None,sep=' ')
+
+	dat = np.asarray(dat.values)
+	rr = dat[:,0]
+	yy = dat[:,1]
+	yy_err = dat[:,2]
+
+	idx = (dat[:,0] > 0.1) & (dat[:,0] < 10.0)
+	rr=rr[idx]
+	yy=yy[idx]
+	yy_err=yy_err[idx]
+	rrange=np.linspace(rr[0],rr[-1],rsteps)
+
+	plt.errorbar(rr,yy,yy_err,fmt=".",label="Cut %s" % str(ii+1))
+
+    plt.xlabel(r"$R$ ($h^{-1}$Mpc)")
+    plt.ylabel(r"$\xi^{\rm 2d}$ ($h^{-1}$Mpc)")
+    plt.xscale("log")
+    plt.yscale("log")
+    plt.legend()
+    plt.savefig("/work/dominik.zuercher/Output/temp/profiles_combined.pdf" )
+
+    print("Plot done")
+
+
+
+
+if __name__ == "__main__":
+
+    input_dir = "/work/dominik.zuercher/Output/splashpipe"
+    output_dir = "/work/dominik.zuercher/Output/Mest"
+
+    modded=True
+    mc=False
+
+    ndim=8
+    nwalkers=28 #98
+    nwalkers_modded=28
+    steps=100000
+    rsteps=25
+    types=['Planck_PS_21.5_blue_cut_1','Planck_PS_21.5_blue_cut_2','Planck_PS_21.5_blue_cut_3','Planck_PS_21.5_blue_cut_4','Planck_PS_21.5_blue_cut_5','Planck_PS_21.5_blue_cut_6','Planck_PS_21.5_blue_cut_7','Planck_PS_21.5_blue_cut_8','Planck_PS_21.5_blue_cut_9']
+    make_plots(types)

### 2018-09-13 toolbox/tool_test.py

@@ -1,0 +1,110 @@
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import sys
+sys.path.insert(0,'/home/dominik.zuercher/Documents/RSP_Pro/toolbox')
+import tools
+from scipy.linalg import inv
+import numpy as np
+import pandas as pd
+
+type_="Planck_PS_22"
+est="DR"
+#Reading the MLE values
+mlep = pd.read_csv("/home/dominik.zuercher/Documents/RSP_Pro/Mest/mles/MLE_parameters_"+str(type_)+"_"+str(est)+".txt", header=None)
+mlep = np.asarray(mlep.values).reshape(mlep.size)
+alpha_mle=mlep[1]
+rs_mle=mlep[2]
+rt_mle=mlep[5]
+beta_mle=mlep[6]
+gamma_mle=mlep[7]
+
+snr_red=263.0
+snr_sz=60.0 #SNR of Planck SZ
+incr=snr_red/snr_sz
+
+#get ranges for the new priors from the RedMaPPer errors
+#The structure is new_error= RedMaPPer_error * SNR_correction
+
+alpha_sigma=0.2*incr  # SZ_error= RedMaPPer_error/
+rs_sigma=0.27*incr
+rt_sigma=0.04*incr
+beta_sigma=0.1*incr
+gamma_sigma=0.14*incr
+
+over=3.0
+
+alpha_min=alpha_mle-over*alpha_sigma
+alpha_max=alpha_mle+over*alpha_sigma
+rs_min=rs_mle-over*rs_sigma
+rs_max=rs_mle+over*rs_sigma
+
+over_rt=over*6.0
+rt_min=rt_mle-over_rt*rt_sigma
+rt_max=rt_mle+over_rt*rt_sigma
+
+beta_min=beta_mle-over*beta_sigma
+beta_max=beta_mle+over*beta_sigma
+gamma_min=gamma_mle-over*gamma_sigma
+gamma_max=gamma_mle+over*gamma_sigma
+
+print("Alpha flat prior from: "+str(alpha_min)+" to "+str(alpha_max))
+print("rs flat prior from: "+str(rs_min)+" to "+str(rs_max))
+print("rt flat prior from: "+str(rt_min)+" to "+str(rt_max))
+print("Beta flat prior from: "+str(beta_min)+" to "+str(beta_max))
[…]

### 2018-09-13 toolbox/tools.py

@@ -1,0 +1,1837 @@
+#! coding=utf8
+import scipy.interpolate as spl
+import scipy.optimize as op
+import pandas as pd
+from astropy.io import fits
+import pkg_resources
+from astropy.cosmology import FlatLambdaCDM
+from astropy.coordinates import Angle
+from astropy.coordinates import SkyCoord
+import astropy.units as u
+import numpy as np
+import frogress
+import subprocess as sub
+from PIL import Image
+import matplotlib
+#import matplotlib.image as mpimg
+from scipy.ndimage import imread as mpimg
+import astropy.wcs as wcs
+import emcee
+import os
+import scipy.integrate as integrate
+from scipy.optimize import fmin
+from scipy.optimize import fminbound
+
+
+overlap=240
+pixscale = 0.25 #Pixelscale of the Pan-STARRS Survey in arcsec/pix
+cosmo = FlatLambdaCDM(H0 = 70 * u.km / u.s / u.Mpc, Om0 = 0.3) #Cosmology used
+
+
+#Exclusion criteria as inffered from the flags (not actually applied anywhere)
+#Flag 1 exclusions
+flag1fail=[2048,4096]
+#Flag 3 exclusions
+flag3fail=[8192]
+#Flag 1 galaxy marker (fits to aperature)
+flag1success=[2097152]
+
+
+resource_package = __name__  # Could be any module/package name
+resource_path = 'ps1grid.fits' # Do not use os.path.join(), see below
+gridfile = pkg_resources.resource_stream(resource_package, resource_path)
+gridlist = fits.open(gridfile,ignore_missing_end=True)
+
+
+def is_number(s):
+    """Checks if a string can be converted to a float."""
+    try:
+         float(s)
+         return True
+    except ValueError:
+         return False
+
+
+def pixcal(redshift, scalep=1):
+    """Calculates the number of pixels corresponding 
+    to a certain physical distance if considered at a 
+    certain redshift.
+    scalep : physical distance in Mpc
+    """
+    scale = scalep * u.Mpc
+    dist = cosmo.luminosity_distance(redshift)
+    theta = Angle(np.arctan(np.divide(scale,np.multiply(2, dist))), u.radian)
+    totang = np.multiply(2,theta.arcsecond)
+    num_of_pix = np.divide(totang,pixscale)
+    return num_of_pix.astype(int)
+
+
+def get_filenames(pros=[],skys=[],ra=[],dec=[],type="stack",filter='i'):
+    """Gets filename lines from the Pan-STARRS Archive.
[…]

### 2018-09-24 Mest/5_combine_MCMC_data.sh
Added matching to GAMA catalog

@@ -20,7 +20,7 @@ function combine_data {
 #Main
 ##########################
 prior='best'
-types='Planck_PS_21.5_red_spline'
+types='Planck_PS_21.5_red_hard_spline_no_mc Planck_PS_21.5_blue_hard_spline_no_mc'
 for type in $types
 do
     combine_data $type 

### 2018-09-24 match_PS_GAMA/combiner.py

@@ -1,0 +1,19 @@
+import pandas
+import glob
+import numpy as np
+
+
+if __name__ == "__main__":
+    input_dir = "/work/dominik.zuercher/Output/match_PS_GAMA/spec_parts"
+    output_dir = "/work/dominik.zuercher/Output/match_PS_GAMA"
+
+    zred=np.zeros(0)
+    color_PS=np.zeros(0)
+
+    for ii, fname in enumerate(glob.glob("%s/matched_???" % input_dir)):
+        print(fname)
+        dfnew = pandas.read_csv(fname, delim_whitespace=1, header=None,names=["zred","color_PS"])
+        zred=np.append(zred,dfnew.zred.values)
+        color_PS = np.append(color_PS,dfnew.color_PS.values)
+    np.savetxt("%s/matched_spec.dat" % output_dir, np.hstack((zred.reshape(zred.size,1),color_PS.reshape(color_PS.size,1))) )
+

### 2018-09-24 Paper_new/RSP_paper_new.tex
Readding Paper_new

--- 2018-09-13 RSP_Paper/RSP_paper.tex
@@
 color-separated galaxy distributions could potentially be used to put lower limits on the
-quenching timescales for galaxies. Further, we record a strong increase 
+quenching timescales for galaxies. Further, we record an increase 
 in the fraction of red galaxies that is associated with the splashback radius.
@@
 stacking issues and the low signal-to-noise ratio remains a significant
-hurdle. \citet{chang2017splashback} find evidence for the splashback
+hurdle. \citet{chang2017splashback} found evidence for the splashback
 radius in the weak lensing signal, but their analysis was again done
@@
 question, we also explore the dependence of the cluster-galaxy
-cross-correlations separately for the red and blue galaxies and
-explore their relative contributions to the overall density profile.
+cross-correlations separately for the red and blue galaxy populations 
+and explore their relative contributions to the overall density profile.
 
@@
 Python package COLOSSUS \citep{diemer2017colossus}. The predictions
-for the splashback radii $r^{\mathrm{3D,theo}}_{\mathrm{sp}}$ is
+for the splashback radii $r^{\mathrm{3D,theo}}_{\mathrm{sp}}$ are
 given in comoving units.}
@@
     \label{tab:priors}
-    \begin{tabular}{ccccccccccc}
-    \hline 
-    & $\log_{10}(\rho_{\mathrm{s}})$ & $\log_{10}(\alpha)$ & $\log_{10}(r_{\mathrm{s}})$ & $\rho_0$ & $s_{\mathrm{e}}$ & $\log_{10}(r_{\mathrm{t}})$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ & $f_{\rm min}$ & $\sigma$\\
-    \hline 
-    Prior Type & None & Normal & Flat & None & None & Flat & Normal & Normal & Normal & Normal\\ 
-    \hline 
-    Prior Range & - & $\log_{10}(0.2)| 1.2$ & [0.1,5.0] & - & - & [0.1,5.0] & $\log_{10}(6.0) | 0.4$ & $\log_{10}(4.0) | 0.4$ & $0.15 | 0.21$ & $0.41 | 0.3$\\
+    \begin{tabular}{ccccccccc}
+    \hline 
+    & $\log_{10}(\rho_{\mathrm{s}})$ & $\log_{10}(\alpha)$ & $\log_{10}(r_{\mathrm{s}})$ & $\rho_0$ & $s_{\mathrm{e}}$ & $\log_{10}(r_{\mathrm{t}})$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ \\ 
+    \hline 
+    Prior Type & None & Normal & Flat & None & None & Flat & Normal & Normal\\ 
+    \hline 
+    Prior Range & - & $\log_{10}(0.2)| 1.2$ & [0.1,5.0] & - & - & [0.1,5.0] & $\log_{10}(6.0) | 0.4$ & $\log_{10}(4.0) | 0.4$ \\
     \hline
@@
 gravitational center. Due to this crude assumption, we additionally 
-include the effects of a possible, remaining mis-centering of the 
+study the effects of a possible, remaining mis-centering of the 
 cluster positions in our model for the two-dimensional correlation 
-function (see Section~\ref{sec:mis-centering}). 
+function (see Appendix~\ref{sec:mis-centering}).
+
 The final sample that we use consists of 596
@@
 the main properties of the cluster catalog used in this work to that
-used by \citet{more2016detection}. The sky positions of the clusters
+used by \citet{more2016detection}. A map of the sky positions of the clusters
 can be found in Figure~\ref{fig:planck_fig} in
@@
 is necessary since the survey is divided into overlapping
-\textit{projectioncells} and \textit{skycells}.
+\textit{projectioncells} and \textit{skycells}, which causes some objects
+to be listed multiple times.
 
@@
 \begin{align}
-\xi_{\rm 3D}(r) &= \rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r) + \rho_{\mathrm{out}}(r)\,, \\
+\xi_{\rm 3D}(r) &= \rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r) + \rho_{\mathrm{out}}(r)\,, \label{eq:model} \\
 \rho_{\mathrm{in}}(r)&=\rho_{\mathrm{s}}\exp\left( -\frac{2}{\alpha}\left[ \left( \frac{r}{r_{\mathrm{s}}}\right)^{\alpha}-1 \right] \right)\,,\\
-\rho_{\mathrm{out}}(r)&=\rho_{\mathrm{0}}\left( \frac{r}{r_{\mathrm{out}}}\right)^{-s_{\mathrm{e}}} \,,\label{eq:model} \\
+\rho_{\mathrm{out}}(r)&=\rho_{\mathrm{0}}\left( \frac{r}{r_{\mathrm{out}}}\right)^{-s_{\mathrm{e}}} \,,\\
 f_{\mathrm{trans}}(r)&=\left( 1+\left( \frac{r}{r_{\mathrm{t}}} \right)^{\beta} \right)^{-\gamma/ \beta}\,,
@@
 \citet{more2016detection}. The functional form adopted in
-Equation~\ref{eq:dk14} has nine model parameters,
+Equation~\ref{eq:surface} has nine model parameters,
 $\rho_{\mathrm{s}}, \alpha, r_{\mathrm{s}}, r_{\mathrm{out}},
@@
 
-\paragraph{Modelling cluster mis-centering}
-\label{sec:mis-centering}
-Mis-centering of the central cluster positions can heavily affect 
-the small-scale correlation function on scales smaller than the typical mis-centering distance. 
-Although, the splashback radius is located at much larger scales, 
-the change of the inner part of the correlation function can alter the model fit significantly.
-Mis-centering effects are not expected to change the location of the splashback feature but they can in principle decrease the significance of the evidence for the splashback feature \citep{baxter2017halo}.
-
-The mass dependence of the exact mis-centering fractions are not
-well understood and mis-centering effects are therefore difficult to model \citep{Skibba:2011, Hoshino:2015}.
-We follow the approach outlined in \citet{baxter2017halo} to take the effects of a possible mis-centering of a fraction of the cluster positions
-into account by modelling the influence on the two-dimensional correlation function.
-
-Denoting the fraction of mis-centered clusters in the sample with $f_{\rm mis}$ we relate
-the correlation function $\xi_{\rm 2D}(R)$ that is affected by the mis-centering of the clusters to the correlation function
-unaffected by mis-centering $\xi_{\rm (2D,0)}(R)$ by
-
-\begin{equation} 
-\xi_{\rm 2D}(R) = (1-f_{\rm mis})\xi_{\rm (2D,0)}(R)+f_{\rm mis}\xi_{\rm (2D,mis)}(R)
-\label{eq:full}
-\end{equation}
-
-where the contribution of the mis-centered clusters to the correlation function is captured by $\xi_{\rm (2D,mis)}$. 
-We model the mis-centered component $\xi_{\rm (2D,mis)}$ as
-
-\begin{equation}
-\xi_{\rm (2D,mis)}(R)=\int_0^\infty \mathrm{d}R_{\rm mis} P(R_{\rm mis})\xi_{\rm (2D,mis)}(R|R_{\rm mis})
-\end{equation}
-
-where we assign a probability $P(R_{\rm mis})$ that a cluster is mis-centered by a comoving distance $R_{\rm mis}$.
-The contribution $\xi_{\rm (2D,mis)}(R|R_{\rm mis})$ from a cluster mis-centered by a distance $R_{\rm mis}$ 
-relates to the unaffected correlation function $\xi_{\rm (2D,0)}$ as
-
-\begin{equation}
-\xi_{\rm (2D,mis)}(R|R_{\rm mis})=\int_0^{2\pi}\frac{\mathrm{d}\theta}{2\pi}\xi_{\rm (2D,0)}\left(\sqrt{R^2+R_{\rm mis}^2+2RR_{\rm mis}\cos{\theta}}\right)
-\end{equation}
-
-according to \citet{yang2006weak} and \citet{johnston2007cross}. Following \citet{simet2016weak} we model the mis-centering probability 
-$P(R_{\rm mis})$ as a Rayleigh distribution:
-
-\begin{equation}
-P(R_{\rm mis})=\frac{R_{\rm mis}}{\sigma^2}\exp{\left( -\frac{R_{\rm mis}^2}{2\sigma^2}\right)}
-\end{equation}
-
-Therefore, the mis-centered contribution is fully characterized by the two parameters $f_{\rm mis}$ and the witdh 
-of the mis-centering probability distribution $\sigma$.
-\newline
-
-We cross-match our SZ selected cluster sample with the X-Ray selected ACCEPT cluster sample \citep{cavagnolo2009vizier}.
-Assuming the ACCEPT clusters to lay at the true gravitational cluster centers we construct Gaussian priors
-for the two mis-centering model parameters $f_{\rm mis}$ and $\sigma$ from the comparison of the 
-two samples. The central values as well as the scales of the priors are listed in Table~\ref{tab:priors}.
-
-Including mis-centering our model is described by ten model parameters.
+Therefore the model is described by eight model parameters.
 We infer the posterior distributions of those parameters by fitting the model for the two-dimensional correlation
-function affected by mis-centering to the measured two-dimensional correlation signal. 
+function to the measured two-dimensional correlation signal. 
 We use the affine invariant Markov Chain Monte Carlo sampler of \citet{goodman2010ensemble} as
@@
 
+Mis-centering of the central cluster positions can heavily affect 
+the small-scale correlation function on scales smaller than the typical mis-centering distance. 
+Although, the splashback radius is located at much larger scales, 
+the change of the inner part of the correlation function can alter the model fit significantly. 
+Mis-centering effects are not expected to change the location of the splashback feature 
+but they can in principle decrease the significance of the evidence for the splashback feature \citep{baxter2017halo}.
+We discuss the modelling of mis-centering and its effects on the inferred splashback radii in Appendix~\ref{sec:mis-centering}.
 \subsection{Separation of red and blue galaxies}
@@
 for the k-corrections, which cannot be computed individually for
-each galaxy. We regard a galaxy as red if
-$g_{\mathrm{P1}}-r_{\mathrm{P1}} > 0.65 + 3.04$ $(z_{\mathrm{clu}} -
-0.1)$ and as blue otherwise. Depending upon the cluster redshift
+each galaxy.
+
+We exploit the XXX SDSS galaxy sample to calibrate our color cut (cite ???).
+The SDSS galaxy sample is divided into a red and a blue galaxy population
+using the color cut XXX (cite???). By cross matching the sample with our Pan-STARRS
+catalog we can identify parts of the Pan-STARRS galaxies as red and blue galaxies,
+respectively. Additionally, we assign the photometric redshifts from the SDSS sample to
+the matched Pan-STARRS galaxies. The redshift dependent 
+$g_{\mathrm{P1}}-r_{\mathrm{P1}}$ color cut is then calibrated to exclude
+red galaxies from being characterized as blue galaxies at a confidence level of 3$\sigma$.
+
+Depending upon the cluster redshift
 under consideration the same galaxy may be considered red or blue. Our
@@
 \begin{figure}
-    \includegraphics[scale=0.65]{2D_graphs.pdf}
+    \includegraphics[scale=0.65]{2D_graphs_with_spline_no_mc.pdf}
 \caption{The estimates of the two-dimensional cross-correlation
@@
 
-\begin{figure}
-    \includegraphics[scale=0.65]{3D_graphs.pdf}
+\begin{figure*}
+    \centering
+    \includegraphics[scale=0.85]{3D_graphs_with_spline_no_mc.pdf}
 \caption{The estimates of the three-dimensional cross-correlation
-signals are shown in the left column. The colored curves show the
+signals are shown in the leftmost column. The colored curves show the
 model fits of the functional form in Equation~\ref{eq:model}. The magnitude
@@
 estimates of the splashback radii as estimated from the corresponding minima 
-of the derivative profiles, which are shown in the right column. For comparison, 
-the location of the $r_{\mathrm{200m}}$ radius as calculated from the
-average cluster sample properties is indicated by the black, dotted
+of the derivative profiles, which are shown in the column in the middle. The
+rightmost column shows the second derivative profiles in matching color.
+For comparison, the location of the $r_{\mathrm{200m}}$ radius as calculated 
+from the average cluster sample properties is indicated by the black, dotted
 lines.}
    \label{fig:3D_graphs} 
-\end{figure}
+\end{figure*}
 
@@
 obtained by using the different galaxy samples. For comparison: The SNR
-achieved by \citet{more2016detection} is 263.0. It is much higher
+achieved by \citet{more2016detection} is 263. It is much higher
 due to size of the cluster sample used in their study.}
@@
     \hline 
-gal cat & $\log_{10}(\rho_{\mathrm{s}})$ & $\log_{10}(\alpha)$ & $\log_{10}(r_{\mathrm{s}})$ & $\rho_{\mathrm{0}}$ & $s_{\mathrm{e}}$ & $\log_{10}(r_{\mathrm{t}})$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ & $R_{\rm sp}^{\rm 2D}$& $r_{\rm sp}^{\rm 3D}$& $\chi^2/\nu$ \\
-\hline 
-\hline 
-PS 21 & $-0.92_{-0.56}^{+0.50}$ & $-1.19_{-0.21}^{+0.22}$ & $0.31_{-0.26}^{+0.29}$ & $0.0130_{-0.0083}^{+0.0062}$ & $0.72_{-0.22}^{+0.27}$ & $0.103_{-0.110}^{+0.056}$ & $0.85_{-0.36}^{+0.27}$ & $0.28_{-0.19}^{+0.12}$ & $1.35_{-0.12}^{+0.13}$ & $1.76_{-0.33}^{+0.29}$ & $0.511$ \\
-\hline
-PS 21.5 & $-0.91_{-0.48}^{+0.51}$ & $-0.98_{-0.18}^{+0.16}$ & $0.28_{-0.28}^{+0.26}$ & $0.0084_{-0.0060}^{+0.0041}$ & $0.53_{-0.23}^{+0.27}$ & $0.086_{-0.112}^{+0.051}$ & $0.78_{-0.34}^{+0.26}$ & $0.25_{-0.18}^{+0.12}$ & $1.30_{-0.10}^{+0.10}$ & $1.81_{-0.33}^{+0.28}$ & $0.178$ \\
-\hline
-PS 22 & $-0.99_{-0.46}^{+0.49}$ & $-0.90_{-0.17}^{+0.16}$ & $0.27_{-0.27}^{+0.26}$ & $0.0058_{-0.0052}^{+0.0027}$ & $0.43_{-0.29}^{+0.26}$ & $0.114_{-0.252}^{+0.076}$ & $0.71_{-0.38}^{+0.27}$ & $0.27_{-0.33}^{+0.16}$ & $1.33_{-0.17}^{+0.13}$ & $1.96_{-0.45}^{+0.37}$ & $0.264$ \\
-\hline 
-PS 21.5 (R) & $0.17_{-0.50}^{+1.03}$ & $-0.95_{-0.34}^{+0.44}$ & $-0.21_{-0.56}^{+0.26}$ & $0.0073_{-0.0084}^{+0.0040}$ & $0.59_{-0.38}^{+0.34}$ & $0.18_{-0.35}^{+0.22}$ & $0.52_{-0.41}^{+0.26}$ & $0.29_{-0.32}^{+0.23}$ & $1.20_{-0.12}^{+0.14}$ & $2.03_{-0.38}^{+0.38}$ & $1.194$ \\
-\hline
-PS 21.5 (B) & $-0.83_{-0.44}^{+0.49}$ & $-0.71_{-0.18}^{+0.19}$ & $0.24_{-0.30}^{+0.26}$ & $0.0112_{-0.0062}^{+0.0048}$ & $0.63_{-0.18}^{+0.23}$ & $0.28_{-0.20}^{+0.14}$ & $0.55_{-0.25}^{+0.16}$ & $0.44_{-0.33}^{+0.25}$ & $1.53_{-0.13}^{+0.13}$ & $2.30_{-0.23}^{+0.24}$ & $0.603$ \\
+gal cat & $\log_{10}(\rho_{\mathrm{s}})$ & $\log_{10}(\alpha)$ & $\log_{10}(r_{\mathrm{s}})$ & $\rho_{\mathrm{0}}$ & $s_{\mathrm{e}}$ & $\log_{10}(r_{\mathrm{t}})$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ & $R_{\mathrm{sp}}^{\mathrm{2D}}$ & $r_{\mathrm{sp}}^{\mathrm{3D}}$ & $\chi^2/\nu$ \\
+\hline 
+\hline 
+PS 21 & $-2.93_{-0.50}^{+0.44}$ & $-1.06_{-0.18}^{+0.14}$ & $0.35_{-0.24}^{+0.27}$ & $0.000179_{-0.000086}^{+0.000075}$ & $0.78_{-0.19}^{+0.24}$ & $0.123_{-0.122}^{+0.051}$ & $0.74_{-0.31}^{+0.21}$ & $0.35_{-0.21}^{+0.13}$ &$1.384_{-0.096}^{+0.088}$&$1.86_{-0.26}^{+0.25}$& $1.524$ \\
+\hline
+PS 21.5 & $-2.93_{-0.45}^{+0.45}$ & $-0.95_{-0.16}^{+0.13}$ & $0.32_{-0.25}^{+0.25}$ & $0.000103_{-0.000065}^{+0.000047}$ & $0.56_{-0.22}^{+0.25}$ & $0.095_{-0.115}^{+0.045}$ & $0.74_{-0.32}^{+0.24}$ & $0.27_{-0.19}^{+0.12}$ &$1.323_{-0.086}^{+0.080}$&$1.85_{-0.30}^{+0.26}$& $0.285$ \\
+\hline
+PS 22 & $-2.95_{-0.44}^{+0.49}$ & $-0.91_{-0.17}^{+0.14}$ & $0.28_{-0.27}^{+0.25}$ & $0.000062_{-0.000051}^{+0.000028}$ & $0.41_{-0.28}^{+0.25}$ & $0.094_{-0.190}^{+0.060}$ & $0.76_{-0.36}^{+0.29}$ & $0.24_{-0.27}^{+0.14}$ &$1.31_{-0.14}^{+0.11}$&$1.90_{-0.40}^{+0.32} $&$0.211$ \\
+\hline
+PS 21.5 (R) & $-0.69_{-0.54}^{+0.55}$ & $-0.99_{-0.20}^{+0.17}$ & $0.24_{-0.31}^{+0.30}$ & $0.0092_{-0.0065}^{+0.0046}$ & $0.63_{-0.27}^{+0.30}$ & $0.157_{-0.171}^{+0.091}$ & $0.54_{-0.20}^{+0.16}$ & $0.36_{-0.26}^{+0.17}$ & $1.437_{-0.089}^{+0.099}$ & $2.13_{-0.21}^{+0.22}$ & $0.502$ \\
+\hline
+PS 21.5 (B) & $-1.00_{-0.24}^{+0.47}$ & $-0.31_{-0.15}^{+0.21}$ & $0.22_{-0.31}^{+0.19}$ & $0.0078_{-0.0047}^{+0.0036}$ & $0.52_{-0.21}^{+0.24}$ & $0.31_{-0.27}^{+0.29}$ & $0.61_{-0.44}^{+0.31}$ & $0.30_{-0.39}^{+0.29}$ & $1.43_{-0.13}^{+0.12}$ & $2.34_{-0.34}^{+0.33}$ & $1.355$ \\
 \hline
@@
 \centering{
-  \includegraphics[scale=0.8]{derivatives.pdf}}
+  \includegraphics[scale=0.8]{derivatives_with_spline_no_mc.pdf}}
 \caption{We show the distributions of the logarithmic derivatives of
@@
 \centering{
-    \includegraphics[scale=0.8]{splashback.pdf}}
+    \includegraphics[scale=0.8]{splashback_with_spline_no_mc.pdf}}
 \caption{Shown are the posterior distributions of the inferred
@@
 \begin{figure}
-    \includegraphics[scale=0.65]{color_separated.pdf}
-\caption{\textit{Top row: } The two-dimensional cross-correlations
+    \includegraphics[scale=0.65]{color_separated_2D_with_spline_no_mc.pdf}
+\caption{The two-dimensional cross-correlations
 of the red and blue galaxy populations as inferred by
@@
 indicate the upper and lower bounds of the same feature but as
-estimated from the full PS 21.5 galaxy catalog. \textit{Bottom row:
-} We show the three-dimensional cross-correlations as
+estimated from the full PS 21.5 galaxy catalog. }
+   \label{fig:color_curve_2D} 
+\end{figure}
+\begin{figure*}
+    \includegraphics[scale=0.75]{color_separated_3D_with_spline_no_mc.pdf}
+\caption{We show the three-dimensional cross-correlations as
 inferred by cross-correlating the cluster sample with the
@@
 splashback radii (indicated by the colored, vertical bands) and
-their derivative profiles. Here, the black, dashed lines indicate
+their first and second order derivative profiles. Here, the black, dashed lines indicate
 upper and lower bounds of the three-dimensional splashback radius
 corresponding to the full PS 21.5 galaxy sample.}
-   \label{fig:color_curve} 
-\end{figure}
-
+   \label{fig:color_curve_3D} 
+\end{figure*}
 \begin{figure}
-    \includegraphics[width= \columnwidth]{color_fraction.pdf}
+    \includegraphics[width= \columnwidth]{color_fraction_with_spline_no_mc.pdf}
 \caption{Fractional contributions of the red and blue galaxy
@@
 model fits. The logarithmic derivatives show a distinct steepening
-feature at around $1.3-1.5~\mpch$. The figure shows that the
+feature at around $1.3~\mpch$. The figure shows that the
 location of the steepest slope does not change appreciably when the
@@
 We use the posterior distributions of our model parameters to infer
-the three-dimensional cross-correlation and its logarithmic
-derivative. These inferences along with the corresponding 68\%
+the three-dimensional cross-correlation and its first and second order logarithmic
+derivatives. These inferences along with the corresponding 68\%
 confidence intervals are presented in Figure~\ref{fig:3D_graphs},
@@
 explored, reaching logarithmic derivatives steeper than $-3$. The
-inferred 68\% confidence regions for the locations of the steepest
+inferred 68\% confidence regions of the locations of the steepest
 slope of the three-dimensional cross-correlations are shown with
@@
 find for the three samples is consistent with this expectation,
-although we can not rule out $\sim 18\%$ deviations in either directions,
+although we can not rule out $\sim 15\%$ deviations in either directions,
 given our large error bars.
@@
 Next we present our measurements of the projected and
-three-dimensional cross-correlations of red and blue galaxies
+three-dimensional cross-correlations of the red and blue galaxy populations
 satisfying $M_{i}-5\log h<-18.94$ with our SZ-selected cluster
-sample in the top and bottom left hand panels of
-Figure~\ref{fig:color_curve}, respectively. The shaded regions show
+sample. The projected cross-correlations are presented in Figure~\ref{fig:color_curve_2D},
+whereas the three-dimensional counterparts are shown in 
+Figure~\ref{fig:color_curve_3D}. The shaded regions show
 the 68\% confidence intervals from our fits. The vertical, shaded
@@
 The best fit parameters as well as the inferred splashback radii are
-listed in Table~\ref{tab:fit_parameters}. The right hand
-panels show the corresponding inferred logarithmic derivatives. We
+listed in Table~\ref{tab:fit_parameters}. We
 see that the red galaxies have a steeper cross-correlation profile
-than the blue galaxies. Although there is a tendency for the red
+than the blue galaxies. Although there seems to be  a tendency for the red
 galaxies to have a smaller splashback radius, the differences we see
@@
 slopes of the three-dimensional cross-correlations reach values
-steeper than -3 at the splashback radius.
-
-Nevertheless, the fact that we detect the splashback radius for blue
-galaxies is significant. The implication of this result is that
+steeper than -2.5 at the splashback radius, which is difficult to model with
+traditional NFW profiles. We take the detection of those steepening features 
+as evidence for the existence of the splashback feature in both galaxy populations.
+The finding of the splashback feature in the blue population implicates that
 there needs to be a reasonable fraction of blue galaxies that fall
@@
 apocenters. Star forming galaxies in models which quench their star
-formation on a timescale shorter than the orbital time scale, are
-not expected to show the presence of the splashback radius. A
+formation on a timescale shorter than the orbital time scale are
+not expected to show presence of the splashback feature. A
 quantitative exploration of the implications is beyond the scope of
@@
 The red galaxies dominate the central parts of the galaxy clusters
-but become sub-dominant as we move further away from the centers of the 
-clusters. We see a sharp increase of the fractional contribution of
+but become less dominant as we move further away from the cluster center.
+We see an increase of the fractional contribution of
 red galaxies below the splashback radius. On scales larger than the
-splashback radius, the populations are consistent with a constant
-fraction of $\approx 55\%$ blue and $\approx 45\%$ red galaxies.
+splashback radius, the fractional contributions of the two populations become
+very similar.
 
@@
 
-Another approach to increase the statistics of the measurements would be to increase the redshift range in which clusters are being considered.
-We chose $0.03 \leq z \leq 0.33$ in order to keep the analysis comparable to \citet{more2016detection}.
-However, this cut reduces the cluster sample size.
-Increasing the redshift range has its own limitations, though.
-It would be required to use a brighter magnitude limit for galaxies, which reduces the number of galaxies that can be used to infer the cross-correlation signal.
-This results in a trade-off and we could investigate the optimal redshift range.
-Alternatively, other cluster samples that do not rely on optical cluster finding such as Xray based surveys might serve as independent and larger cluster samples.
+Another approach to increase the statistics of the measurements would 
+be to increase the redshift range in which clusters are being considered. 
+We chose $0.03 \leq z \leq 0.33$ in order to keep the analysis comparable 
+to \citet{more2016detection}. However, this cut reduces the cluster sample 
+size. Increasing the redshift range has its own limitations, though. 
+It would be required to use a brighter magnitude limit for galaxies, 
+which reduces the number of galaxies that can be used to infer the 
+cross-correlation signal. This results in a trade-off which could be investigated
+to find the optimal redshift range. Alternatively, other cluster samples that do 
+not rely on optical cluster finding such as Xray based surveys might 
+serve as independent and larger cluster samples. 
 Another plausible approach would be to consider a smaller region of
-the sky, meaning also less clusters but with a deeper field of view,
+the sky, resulting in less clusters but with a deeper field of view,
 such as in the case of the Hyper Suprime-Cam at Subaru Telescope,
@@
 signals are steeper than $-3$, and would hence be poorly fit by the
-NFW profile. We associate this feature with the splashback feature.
+NFW profile. We associate this steepening with the splashback feature.
 \item The location of the inferred splashback radius is $r_{\rm
-sp}=1.81_{-0.33}^{+0.28}$ $\mpch$, which is consistent with expectations
+sp}=1.85_{-0.30}^{+0.26}$ $\mpch$, which is consistent with expectations
 from numerical simulations for
@@
 quenched during their first orbit through the halo.
-\item We also detect a sharp increase in the fraction of red
+\item We also detect an increase in the fraction of red
 galaxies associated with the splashback radius. 
@@
 Our curated galaxy catalogs from the Pan-STARRS survey for different
-depths and the corresponding masks are available and can be send
+depths and the corresponding masks are available and can be sent
 upon request.
@@
 Society for Promotion of Science (JSPS), grant number 16H01089.
+
 The Pan-STARRS1 Surveys (PS1) and the PS1 public science archive
@@
 \appendix
+
+\section{Modelling cluster mis-centering}
+\label{sec:mis-centering}
+As described in \citet{baxter2017halo} mis-centering of the central cluster positions are not expected to change the location of the splashback feature but might decrease the significance of the finding.
+Therefore, we modelled the effects of mis-centering on the correlation function and its influence on the results.
+
+The mass dependence of the exact mis-centering fractions are not
+well understood and mis-centering effects are therefore difficult to model \citep{Skibba:2011, Hoshino:2015}.
+We follow the approach outlined in \citet{baxter2017halo} to take the effects of a possible mis-centering of a fraction of the cluster positions
+into account by modelling the influence on the two-dimensional correlation function.
+
+Denoting the fraction of mis-centered clusters in the sample with $f_{\rm mis}$ we relate
+the correlation function $\xi'_{\rm 2D}(R)$ that is affected by the mis-centering of the clusters to the correlation function
+unaffected by mis-centering Equation~\ref{eq:surface} by
+
+\begin{equation} 
+\xi'_{\rm 2D}(R) = (1-f_{\rm mis})\xi_{\rm 2D}(R)+f_{\rm mis}\xi_{\rm (2D,mis)}(R)
+\label{eq:full}
+\end{equation}
+
+where the contribution of the mis-centered clusters to the correlation function is captured by $\xi_{\rm (2D,mis)}$. 
+We model the mis-centered component $\xi_{\rm (2D,mis)}$ as
+
+\begin{equation}
+\xi_{\rm (2D,mis)}(R)=\int_0^\infty \mathrm{d}R_{\rm mis} P(R_{\rm mis})\xi_{\rm (2D,mis)}(R|R_{\rm mis})
+\end{equation}
+
+where we assign a probability $P(R_{\rm mis})$ that a cluster is mis-centered by a comoving distance $R_{\rm mis}$.
+The contribution $\xi_{\rm (2D,mis)}(R|R_{\rm mis})$ from a cluster mis-centered by a distance $R_{\rm mis}$ 
+relates to the unaffected correlation function $\xi_{\rm 2D}$ as
+
+\begin{equation}
+\xi_{\rm (2D,mis)}(R|R_{\rm mis})=\int_0^{2\pi}\frac{\mathrm{d}\theta}{2\pi}\xi_{\rm 2D}\left(\sqrt{R^2+R_{\rm mis}^2+2RR_{\rm mis}\cos{\theta}}\right)
+\end{equation}
+
+according to \citet{yang2006weak} and \citet{johnston2007cross}. Following \citet{simet2016weak} we model the mis-centering probability 
+$P(R_{\rm mis})$ as a Rayleigh distribution:
+
+\begin{equation}
+P(R_{\rm mis})=\frac{R_{\rm mis}}{\sigma^2}\exp{\left( -\frac{R_{\rm mis}^2}{2\sigma^2}\right)}
+\end{equation}
+
+Therefore, the mis-centered contribution is fully characterized by the two parameters $f_{\rm mis}$ and the witdh 
+of the mis-centering probability distribution $\sigma$.
+
+To find the priors for the two mis-centering paramters $f_{\rm mis}$ and $\sigma$ we cross-match our SZ selected cluster sample with the X-Ray selected ACCEPT cluster sample \citep{cavagnolo2009vizier}.
+Assuming the ACCEPT clusters to lay at the true gravitational cluster centers we construct Gaussian priors
+for the two mis-centering model parameters $f_{\rm mis}$ and $\sigma$ from the comparison of the 
+two samples with central values 0.15, 0.41 and scales 0.21, 0.3 for $f_{\rm mis}$ and $\sigma$, respectively.
+
+To study the influence of mis-centering on our findings we repeat the MCMC model fitting using our new model including mis-centering given in Equation~\ref{eq:full}, which now includes two more model parameters.
+
+\begin{table}
+    \centering
+    \caption{Listing of the splashback radii inferred by including the effects of mis-centering of the central cluster positions. }
+    \label{tab:mis_splash}
+    \begin{tabular}{ccc}
+    \hline 
+gal cat &  $R_{\mathrm{sp}}^{\mathrm{2D}}$ & $r_{\mathrm{sp}}^{\mathrm{3D}}$ \\
+\hline 
+\hline 
+PS 21 &$1.35_{-0.12}^{+0.13}$ & $1.76_{-0.33}^{+0.29}$\\
+\hline
+PS 21.5 & $1.30_{-0.10}^{+0.10}$&$1.81_{-0.33}^{+0.28}$\\
+\hline
+PS 22 &$1.33_{-0.17}^{+0.13}$ & $1.96_{-0.45}^{+0.37}$\\
+\hline
+PS 21.5 (R) & $1.45_{-0.11}^{+0.12}$ & $2.23_{-0.26}^{+0.27}$ \\
+\hline
+PS 21.5 (B) & $1.42_{-0.25}^{+0.20}$ & $2.39_{-0.39}^{+0.39}$ \\
+\hline
+    \end{tabular} 
+\end{table}
+
+We find that due to the use of a projected mis-centering model the error bands of the MCMC estimate of the projected cross-correlation signal are increased by $\sim 25$\%.
+However, the effect is barely noticeable in the three-dimensional profiles.
+The inclusion of mis-centering is reflected as a small increase of the inferred errors of the projected and three-dimensional splashback radii as shown in Table~\ref{tab:mis_splash}.
+A small shift of the inferred central values of the splashback radii is recorded additionally.
+However, the shift is not systematic nor statistically significant.
 

### 2018-10-15 Paper_new/RSP_paper_new.tex
Added contamination estimate to paper

@@
 
-We exploit the XXX SDSS galaxy sample to calibrate our color cut (cite ???).
-The SDSS galaxy sample is divided into a red and a blue galaxy population
-using the color cut XXX (cite???). By cross matching the sample with our Pan-STARRS
-catalog we can identify parts of the Pan-STARRS galaxies as red and blue galaxies,
-respectively. Additionally, we assign the photometric redshifts from the SDSS sample to
-the matched Pan-STARRS galaxies. The redshift dependent 
-$g_{\mathrm{P1}}-r_{\mathrm{P1}}$ color cut is then calibrated to exclude
-red galaxies from being characterized as blue galaxies at a confidence level of 3$\sigma$.
+We bin the galaxies into narrow redshift bins and produce a histogram of
+the $g_{\mathrm{P1}}-r_{\mathrm{P1}}$ colors of the galaxies in each bin. Due to
+the Lyman-$\alpha$-break present in the red galaxy population, the two galaxy populations
+separate in such a histogram and we fit a double Gaussian distribution to it.
+Based on the fitted distribution we put a cut in color such that we can exclude a contamination
+of the blue population by incorrectly characterized red galaxies with a confidence of 3$\sigma$.
+Repeating this proceduce for each redshift bin we end up with a redshift dependent color cut that
+separates the red from the blue population minimizing the contamination of the blue population by
+red galaxies. Although being much simpler and faster than calculating the individual k-corrections
+for each galaxy this procedure has its own shortcomings as discussed in Appendix~\ref{sec:Errors}.
 
@@
 
+We note that, in principle it is possible that the blue galaxy population does not posses
+a splashback feature but that due to our separation procedure outlined in Section~\ref{sec:Color}
+some of the red galaxies are identified as blue ones and are contaminating the correlation function
+of the blue population. Such a contamination could be caused by a scattering of some of the red galaxies
+into the blue population due to the large photometric errors of the Pan-STARRS galaxies at faint magnitudes.
+We tried to investigate the possiblity of that happening as outlined in 
+Appendix~\ref{sec:Errors}. Unfortunately, we established that at the current state of the data we cannot
+exclude such a contamination and the results derived using the color separated galaxy populations
+should be used with caution therefore.
+
 \section{Future work}
@@
 depth of 26.2 magnitudes \citep{takada2010subaru}.
+
+The separation of the blue and red galaxy populations as described in 
+Section~\ref{sec:Color} is prone to photometric errors. In order to 
+assure our finding of a splashback feature in the blue galaxy population
+a deeper galaxy catalog would be desirable. Again, the future survey
+conducted with the Hyper Suprime-Cam could come to rescue.
 
@@
 
+\section{Estimating the contamination of the blue galaxy population}
+\label{sec:Errors}
+In our separation procedure of the blue from the red galaxy population 
+we assume the photometric magnitudes of the Pan-STARRS galaxies to be exact.
+However, photometric errors could cause red galaxies to scatter into the blue
+population which contaminates the correlation function and might be the cause 
+for the splashback feature observed in the blue population. Therefore, we 
+investigate the possiblity of such a contamination.
+
+Firstly, we need to know how high such a contamination would have to be in order
+to reproduce the splashback signal as seen in the observations given that the actual
+blue poulation does not posses such a signal at all. We assume a simple $r^{-1.5}$ power 
+law for the correlation signal of the blue population which by construction cannot cause a splashback feature. Then,
+we simulate a contamination of the population by adding some of the accordingly rescaled 
+correlation signal of the red population, which does posses a splashback feature.
+We find that a contamination of at least 20\% is necessary to reproduce the observed
+splashback signal.
+
+Next we estimate the photometric errors of the Pan-STARRS galaxies in each one of the used
+bands (namely $i_{PS}, g_{PS}, r_{PS}$). Since we chose galaxies with $15.0 \leq i_{PS} \leq 21.5$
+for our analysis we consider the $i_{PS}$ errors as given in the Pan-STARRS survey of only 
+the galaxies in this magnitude range. We fit a Gaussian to their distribution and use a conservative $3\sigma$ confidence
+estimate for the photometric error in the $i_{PS}$ band. We repeat the same analysis for the
+$g_{PS}$ and $r_{PS}$ bands, but using magnitude ranges which are shifted by the mean magnitude
+differences between the $i_{PS}$ band and the $g_{PS}$ and $r_{PS}$ bands, respectively.
+The histograms of the errors as well as the estimated photometric errors are shown in
+Figure~\ref{fig:photoerrors}. We find similar photometric errors in the $i_{PS}$ (63 mmag)
+and $r_{PS}$ band (64 mmag) but a larger error in the $g_{PS}$ band of 81 mmag.
+
+\begin{figure}
+\centering{
+    \includegraphics[scale=0.6]{errors.pdf}}
+\caption{Histograms of the photometric errors in the used $i_{PS}, g_{PS}, r_{PS}$ bands.
+The errors were taken dirrectly from the Pan-STARRS survey and sampled for galaxy type 
+objects in the magniude range $15.0 \leq i_{PS} \leq 21.5$, $16.3 \leq g_{PS} \leq 22.8$ and $15.4 \leq r_{PS} \leq 21.9$, respectively. 
+The upper photometric error limits at $3\sigma$
+confidence are listed in the upper right of the figure.}
+    \label{fig:photoerrors}•
+\end{figure}
+
+Finally, we estimate the contamination of the blue galaxy population given the cut in $g_{PS} - r_{PS}$
+color that we used to separate the two populations. We start the same way as we established the cut:
+By taking narrow redshift bins and then by binning the $g_{PS} - r_{PS}$ colors of the galaxies in each
+redshift bin. Then we proceed by fitting a double Gaussian to the color distribution in each redshift bin
+(indicated by the solid, accordingly colored lines in Figure~\ref{fig:histogram}). We put the cut which
+separates the two distributions from each other at a $g_{PS} - r_{PS}$ color such that red galaxies are
+excluded from being incorrectly characterized as blue galaxies at a confidence level of $3\sigma$ (indicated
+by the solid, vertical, black line). At that point the fractional contribution of the red population reads 
+$\sim 40\%$ which corresponds to a free field galaxy sample. In order to model the distribution inside of 
+the cluster region we rescale the red distribution such that we end up with a fractional contribution of 
+the red population of $65\%$. We do now take into account the estimated photometric errors in the $g_{PS}$ and
+$r_{PS}$ bands by broadening the Gaussian distributions accordingly. The contamination is then estimated as:
+\begin{equation}
+\sum_{z=0.03}^{0.33} \int_{-\infty}^{cut(z)} 1 + \frac{\mathcal{N}_r(g-r)}{\mathcal{N}_b(g-r)} \mathrm{d}(g-r)
+\end{equation}
+where the sum runs over all redshift bins, the integration is performed over the $g_{PS} - r_{PS}$ color up 
+to the redshift dependent cut $cut(z)$ separating the two distributions and $\mathcal{N}_r(g-r)$ and $\mathcal{N}_b(g-r)$
+representing the broadened Gaussian distributions of the red and blue population, respectively
+(dashed, accordingly colored curves). With the described analysis we calculate a contamination of 24\%, which would
+be high enough to explain the observed splashback signal of the blue galaxy population solely by red galaxies
+that scattered into the blue population. However, this cannot be taken as disproof of the existence of a splashback
+feature in the blue galaxy population. The contamination estimate strongly depenends on two factors: Firstly, on the 
+confidence at which one wants to exclude red galaxies from being misidentified as blue galaxies and secondly on the
+method one uses to estimate the photometric errors (magnitude range and the conservatism of the error estimate).
+Depending on the approach we got contamination estimates ranging from 0.0001\% to 60\%. Therefore, at the current
+state it cannot be concisely established if the observed splashback feature stems from a contamination of red
+galaxies or not. A deeper galaxy catalog with smaller photometric errors, especially in the $g_{PS}$ band is
+required to shed light on this matter.
+
+\begin{figure}
+\centering{
+    \includegraphics[scale=0.6]{best_hist_58.pdf}}
+\caption{Histogram of the $g_{PS} - r_{PS}$ colors of the galaxies in a certain redshift bin for illustration
+of the contamination estimation. The solid, colored curves indicate the initially fitted Gaussian distributions,
+whereas the dashed curves represent the Gaussian distributions broadened by the photometric errors of the Pan-STARRS
+survey. The black, vertical line indicates the cut, separating the two galaxy populations as inferred from the original
+distributions. The cut excludes red galaxies from being characterized as blue galaxies at $3/sigma$ confidence.}
+    \label{fig:histogram}•
+\end{figure}
+
 \section{Modelling cluster mis-centering}
 \label{sec:mis-centering}
-As described in \citet{baxter2017halo} mis-centering of the central cluster positions are not expected to change the location of the splashback feature but might decrease the significance of the finding.
-Therefore, we modelled the effects of mis-centering on the correlation function and its influence on the results.
+As described in \citet{baxter2017halo} mis-centering of the central cluster 
+positions are not expected to change the location of the splashback feature 
+but might decrease the significance of the finding. Therefore, we modelled the 
+effects of mis-centering on the correlation function and its influence on the results.
 
 The mass dependence of the exact mis-centering fractions are not
-well understood and mis-centering effects are therefore difficult to model \citep{Skibba:2011, Hoshino:2015}.
-We follow the approach outlined in \citet{baxter2017halo} to take the effects of a possible mis-centering of a fraction of the cluster positions
-into account by modelling the influence on the two-dimensional correlation function.
+well understood and mis-centering effects are therefore difficult to 
+model \citep{Skibba:2011, Hoshino:2015}. We follow the approach outlined 
+in \citet{baxter2017halo} to take the effects of a possible mis-centering of a fraction 
+of the cluster positions into account by modelling the influence on the two-dimensional correlation function.
 

### 2018-10-15 splashpipe/build/lib.linux-x86_64-2.7/splashback.py

@@ -1,13 +1,22 @@
 # This file was automatically generated by SWIG (http://www.swig.org).
-# Version 2.0.10
+# Version 3.0.12
 #
 # Do not make changes to this file unless you know what you are doing--modify
 # the SWIG interface file instead.
 
-
-
-from sys import version_info
-if version_info >= (2,6,0):
+from sys import version_info as _swig_python_version_info
+if _swig_python_version_info >= (2, 7, 0):
+    def swig_import_helper():
+        import importlib
+        pkg = __name__.rpartition('.')[0]
+        mname = '.'.join((pkg, '_splashback')).lstrip('.')
+        try:
+            return importlib.import_module(mname)
+        except ImportError:
+            return importlib.import_module('_splashback')
+    _splashback = swig_import_helper()
+    del swig_import_helper
+elif _swig_python_version_info >= (2, 6, 0):
     def swig_import_helper():
         from os.path import dirname
         import imp
@@ -17,55 +26,74 @@ if version_info >= (2,6,0):
         except ImportError:
             import _splashback
             return _splashback
-        if fp is not None:
-            try:
-                _mod = imp.load_module('_splashback', fp, pathname, description)
-            finally:
+        try:
+            _mod = imp.load_module('_splashback', fp, pathname, description)
+        finally:
+            if fp is not None:
                 fp.close()
-            return _mod
+        return _mod
     _splashback = swig_import_helper()
     del swig_import_helper
 else:
     import _splashback
-del version_info
+del _swig_python_version_info
+
 try:
     _swig_property = property
 except NameError:
-    pass # Python < 2.2 doesn't have 'property'.
-def _swig_setattr_nondynamic(self,class_type,name,value,static=1):
-    if (name == "thisown"): return self.this.own(value)
+    pass  # Python < 2.2 doesn't have 'property'.
+
+try:
+    import builtins as __builtin__
+except ImportError:
+    import __builtin__
+
+def _swig_setattr_nondynamic(self, class_type, name, value, static=1):
+    if (name == "thisown"):
+        return self.this.own(value)
     if (name == "this"):
         if type(value).__name__ == 'SwigPyObject':
             self.__dict__[name] = value
             return
-    method = class_type.__swig_setmethods__.get(name,None)
-    if method: return method(self,value)
[…]

### 2018-10-15 splashpipe/src/splashback.h

@@ -7,7 +7,7 @@
 #include <ctime>
 #include <cmath>
 #include <fstream>
-#include "cosmology.h"
+//#include "cosmology.h"
 #include "kdtree2.h"
 #include <vector>
 #include <ctime>

### 2018-10-15 splashpipe/src/splashback_wrap.cpp

@@ -1,14 +1,18 @@
 /* ----------------------------------------------------------------------------
  * This file was automatically generated by SWIG (http://www.swig.org).
- * Version 2.0.10
- * 
- * This file is not intended to be easily readable and contains a number of 
+ * Version 3.0.12
+ *
+ * This file is not intended to be easily readable and contains a number of
  * coding conventions designed to improve portability and efficiency. Do not make
- * changes to this file unless you know what you are doing--modify the SWIG 
- * interface file instead. 
+ * changes to this file unless you know what you are doing--modify the SWIG
+ * interface file instead.
  * ----------------------------------------------------------------------------- */
 
+
+#ifndef SWIGPYTHON
 #define SWIGPYTHON
+#endif
+
 #define SWIG_PYTHON_DIRECTOR_NO_VTABLE
 
 
@@ -66,28 +70,28 @@ template <typename T> T SwigValueInit() {
 #ifndef SWIGUNUSED
 # if defined(__GNUC__)
 #   if !(defined(__cplusplus)) || (__GNUC__ > 3 || (__GNUC__ == 3 && __GNUC_MINOR__ >= 4))
-#     define SWIGUNUSED __attribute__ ((__unused__)) 
+#     define SWIGUNUSED __attribute__ ((__unused__))
 #   else
 #     define SWIGUNUSED
 #   endif
 # elif defined(__ICC)
-#   define SWIGUNUSED __attribute__ ((__unused__)) 
+#   define SWIGUNUSED __attribute__ ((__unused__))
 # else
-#   define SWIGUNUSED 
+#   define SWIGUNUSED
 # endif
 #endif
 
 #ifndef SWIG_MSC_UNSUPPRESS_4505
 # if defined(_MSC_VER)
 #   pragma warning(disable : 4505) /* unreferenced local function has been removed */
-# endif 
+# endif
 #endif
 
 #ifndef SWIGUNUSEDPARM
 # ifdef __cplusplus
 #   define SWIGUNUSEDPARM(p)
 # else
-#   define SWIGUNUSEDPARM(p) p SWIGUNUSED 
+#   define SWIGUNUSEDPARM(p) p SWIGUNUSED
 # endif
 #endif
 
@@ -102,9 +106,11 @@ template <typename T> T SwigValueInit() {
 #endif
 
 /* exporting methods */
[…]

### 2018-10-29 Paper_new/RSP_paper_new.tex
some comments

@@
 $M_i-5\log h=-19.44$, and is present at a consistent location in
-both red and blue galaxy populations. The presence of the splashback radius in
-color-separated galaxy distributions could potentially be used to put lower limits on the
-quenching timescales for galaxies. Further, we record an increase 
-in the fraction of red galaxies that is associated with the splashback radius.
+galaxy populations divided by color. The presence of the splashback radius in
+the blue galaxy population could potentially be used to put lower limits on the
+quenching timescales for galaxies. However, these results need further
+verification with deeper datasets, as photometric errors could cause
+contamination of blue galaxies with red galaxies.
 
@@
 radius. There is a possibility that the aperture used to select the
-cluster catalogs could be imprinted in a non-trivial way on the
-measured number density profiles of clusters.
+cluster catalogs could be imprinted in a non-trivial way on the measured number
+density profiles of clusters. {\bf Add citation to the more recent Xray paper
+by Henk Hoekstra and collaborators as well.}
 
@@
 comoving projected separation $R$. The subtraction of the signal
-around random cluster positions gets rid of the uncorrelated pairs
-and allows us to estimate the projected cross-correlation.
+around random cluster positions gets rid of the uncorrelated pairs and allows
+us to estimate the projected cross-correlation. The uncertainty in the galaxy
+distribution masks prevents us from using the Landy-Szalay estimator. {\bf Cite
+Landy-Szalay paper.}
 
@@
 
-We bin the galaxies into narrow redshift bins and produce a histogram of
-the $g_{\mathrm{P1}}-r_{\mathrm{P1}}$ colors of the galaxies in each bin. Due to
-the Lyman-$\alpha$-break present in the red galaxy population, the two galaxy populations
-separate in such a histogram and we fit a double Gaussian distribution to it.
-Based on the fitted distribution we put a cut in color such that we can exclude a contamination
-of the blue population by incorrectly characterized red galaxies with a confidence of 3$\sigma$.
-Repeating this proceduce for each redshift bin we end up with a redshift dependent color cut that
-separates the red from the blue population minimizing the contamination of the blue population by
-red galaxies. Although being much simpler and faster than calculating the individual k-corrections
-for each galaxy this procedure has its own shortcomings as discussed in Appendix~\ref{sec:Errors}.
-
-Depending upon the cluster redshift
-under consideration the same galaxy may be considered red or blue. Our
-method avoids the use of uncertain photometric redshifts to derive
-k-corrections \citep[cf.][]{baxter2017halo}. We will study the
-cross-correlations to derive the splashback radii for these galaxy
-populations separately, as well as the fractional
-contributions of the red and the blue galaxies to the total density profile
-as a function of radius.
+In order to compute the color cut to be used, we first match spectroscopic
+galaxies in the Sloan digital Sky Survey ({\bf which data release?}) to their
+Pan-STARRS photometry. We bin these galaxies in narrow redshift bins and
+produce a histogram of the $g_{\mathrm{P1}}-r_{\mathrm{P1}}$ colors of the
+galaxies in each bin. Due to the presence of the $4000\AA$-break present in the
+red galaxy population, the two galaxy populations separate in such histograms
+into two populations and we fit a double Gaussian distribution to it.  Based on
+the fitted distribution we put a cut in color to exclude a contamination of the
+blue population by incorrectly characterized red galaxies with a confidence of
+3$\sigma$. We repeat this procedure for each redshift bin, to obtain a redshift
+dependent color cut that separates the red from the blue population minimizing
+the contamination of the blue population by red galaxies. Although being much
+simpler and faster than calculating the individual k-corrections for each
+galaxy, this procedure has its own shortcomings as discussed in
+Appendix~\ref{sec:Errors}, in particular due to the photometric errors of red
+galaxies. We would therefore exercise appropriate caution while interpreting
+the results obtained by dividing galaxies in to color bins.
+
+In our analysis, the same galaxy may be considered red or blue depending upon
+the cluster redshift under consideration. Our method avoids the use of
+uncertain photometric redshifts to derive k-corrections
+\citep[cf.][]{baxter2017halo}. We will study the cross-correlations to derive
+the splashback radii for these galaxy populations separately, as well as the
+fractional contributions of the red and the blue galaxies to the total density
+profile as a function of radius. The caveats in the interpretation of these
+results are mentioned in the Appendix~\ref{sec:Errors}.
 
@@
 magnitude limit is changed, even though we use a sample which is one
-magnitude deeper than $M_{\rm i}-5\log h=-19.44$. The 68\%
+magnitude brighter than $M_{\rm i}-5\log h=-19.44$. The 68\%
 confidence interval of the location of the steepest slope is
@@
 i}-5\log h=-19.44$. Our measurements have an accuracy of $\sim$15\%.
+
+{\bf Dominik, we need to add in the first and second derivative of just the one
+halo term to these plots $\rho_{\rm in}\,f_{\rm trans}$. Also highlight that
+the slope is dropping down precipitously within a factor 2 in radius. Mention
+that in the next paragraph. Add in Figure~\ref{fig:derivatives}, the second
+derivative posterior as well. In fact you can leave out the current left hand
+panel and just plot the the first and second derivatives of $\log\rho_{\rm
+in}\,f_{\rm trans}$.}
 

### 2018-11-01 Paper_new/RSP_paper_new.tex
Added one halo derivative profiles. Made small changes

@@
 
-\citet{umetsu2017lensing} used Xray selected clusters to look for
-the splashback radius using the weak lensing signal, however
+\citet{umetsu2017lensing} as well as \citet{contigiani2018weak} 
+used Xray selected clusters to look for the splashback radius 
+using the weak lensing signal, however
 stacking issues and the low signal-to-noise ratio remains a significant
-hurdle. \citet{chang2017splashback} found evidence for the splashback
+hurdle for both of them. \citet{chang2017splashback} found evidence for the splashback
 radius in the weak lensing signal, but their analysis was again done
@@
 us to estimate the projected cross-correlation. The uncertainty in the galaxy
-distribution masks prevents us from using the Landy-Szalay estimator. {\bf Cite
-Landy-Szalay paper.}
+distribution masks prevents us from using the Landy-Szalay estimator \citep{landy1993bias}. 
+{\bf Cite Landy-Szalay paper.}
 
@@
 In order to compute the color cut to be used, we first match spectroscopic
-galaxies in the Sloan digital Sky Survey ({\bf which data release?}) to their
+galaxies in the Sloan digital Sky Survey (DR 13) ({\bf which data release?}) to their
 Pan-STARRS photometry. We bin these galaxies in narrow redshift bins and
@@
 rightmost column shows the second derivative profiles in matching color.
+The grey curves show the corresponding, estimated first and second derivatives of the 
+one-halo term (namely $\rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r)$ in Equation~\ref{eq:dk14}).
 For comparison, the location of the $r_{\mathrm{200m}}$ radius as calculated 
@@
 \begin{figure*}
-    \includegraphics[scale=0.75]{color_separated_3D_with_spline_no_mc.pdf}
+    \includegraphics[scale=0.76]{color_separated_3D_with_spline_no_mc.pdf}
 \caption{We show the three-dimensional cross-correlations as
@@
 splashback radii (indicated by the colored, vertical bands) and
-their first and second order derivative profiles. Here, the black, dashed lines indicate
-upper and lower bounds of the three-dimensional splashback radius
-corresponding to the full PS 21.5 galaxy sample.}
+their first and second order derivative profiles. The light-colored 
+curves show the corresponding first and second derivatives of the one-halo
+term (namely $\rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r)$ in Equation~\ref{eq:dk14})
+Here, the black, dashed lines indicate upper and lower bounds of the 
+three-dimensional splashback radius corresponding to the full PS 21.5 galaxy sample.}
    \label{fig:color_curve_3D} 
@@
 without the presence of the outer 2-halo term. This provides
-evidence for the existence of the splashback feature.
+evidence for the existence of the splashback feature. From the second
+derivative profiles we also note that the drop in the cross-correlation
+signal is very sharp and happens within a factor 2 in radius.
 

### 2018-11-14 Paper_new/RSP_paper_new.tex
edited affiliations

@@
 Dominik Zürcher \altaffilmark{1, 2}
-Surhud More \altaffilmark{1, 3}, 
+Surhud More \altaffilmark{3, 1}, 
 }
 \affil{
-$^{1}$Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), \\ 
+$^{1}$Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), 5-1-5 Kashiwanoha, Kashiwa, Chiba 277-8583, Japan \\ 
 $^{2}$Department of Physics, ETH Zurich, Wolfgang Pauli Strasse 27, 8093 Zurich, Switzerland\\
-$^{3}$The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa, Chiba 277-8583\\
+$^{4}$The Inter-University Centre for Astronomy and Astrophysics, Post Bag 4, Ganeshkhind, Pune 411007, India
 }
@@
 \begin{abstract}
-We present evidence for the existence of the splashback radius
-in galaxy clusters selected using the Sunyaev-Zeldovich effect.
-We show that the deprojected cross-correlation of galaxy clusters
-found in the Planck survey with galaxies detected photometrically in
-the Pan-STARRS survey, shows a sharp steepening feature (a
-logarithmic slope steeper than $-3$), which we associate with the
-splashback radius.  We infer the three-dimensional splashback radius
-for the SZ cluster sample to be $r_{\rm sp}=1.85_{-0.30}^{+0.26}$ $\mpch$,
-where the cluster sample has an average halo mass $M_{\rm
-500c}=3.0\times10^{14}\msunh$ at an average redshift of $z=0.18$.
-The inferred value of the splashback radius is consistent with the
-expected location for dark matter halos in the standard cold dark
-matter paradigm. However, given the limited precision of our
-measurements, we cannot conclusively rule out the smaller splashback
-radius measured so far in the literature for photometrically
-selected galaxy clusters. We show that the splashback radius does
-not depend upon the galaxy magnitude for galaxies fainter than
+We present evidence for the existence of the splashback radius in
+galaxy clusters selected using the Sunyaev-Zeldovich effect.  We show
+that the deprojected cross-correlation of galaxy clusters found in the
+Planck survey with galaxies detected photometrically in the Pan-STARRS
+survey, shows a sharp steepening feature (a logarithmic slope steeper
+than $-3$), which we associate with the splashback radius. We infer
+the three-dimensional splashback radius for the SZ cluster sample to
+be $r_{\rm sp}=1.85_{-0.30}^{+0.26}$ $\mpch$, where the cluster sample
+has an average halo mass $M_{\rm 500c}=3.0\times10^{14}\msunh$ at an
+average redshift of $z=0.18$.  The inferred value of the splashback
+radius is consistent with the expected location for dark matter halos
+in the standard cold dark matter paradigm. However, given the limited
+precision of our measurements, we cannot conclusively rule out the
+smaller splashback radius measured so far in the literature for
+optically selected galaxy clusters. We show that the splashback radius
+does not depend upon the galaxy magnitude for galaxies fainter than
 $M_i-5\log h=-19.44$, and is present at a consistent location in
-galaxy populations divided by color. The presence of the splashback radius in
-the blue galaxy population could potentially be used to put lower limits on the
-quenching timescales for galaxies. However, these results need further
-verification with deeper datasets, as photometric errors could cause
-contamination of blue galaxies with red galaxies.
+galaxy populations divided by color. The presence of the splashback
+radius in the star-forming galaxy population could potentially be used
+to put lower limits on the quenching timescales for galaxies. However,
+these results need further verification with deeper datasets, as
+photometric errors could cause contamination of the star-forming
+galaxies by quenched galaxies.
 

### 2018-11-15 Paper_new/RSP_paper_new.tex
many many edits

@@
 average redshift of $z=0.18$. The inferred value of the splashback
-radius is consistent with the expected location for dark matter halos
+radius appears consistent with the expected location for dark matter halos
 in the standard cold dark matter paradigm. However, given the limited
@@
 photometric errors could cause contamination of the star-forming
-galaxies by quenched galaxies.
+galaxy sample by quenched galaxies.
 
@@
 
-The recent study of \citet{diemer2014dependence} has sparked a
-renewed interest in understanding the structure of dark matter halos
-on scales beyond the typical virial radii.
-\citet{diemer2014dependence} investigated the outskirts of dark
-matter halos in numerical simulations and found the existence of a
-physical feature, namely a sharp steepening in the density
-distributions of dark matter halos, which is not captured by
-commonly used functional forms such as the NFW profile. They showed
-that even for halos of the same mass, the position of the feature
-changes depending upon the mass accretion rate of the halos. A simple
-theoretical toy model to explain this feature was presented by
-\citet{adhikari2014splashback}. They showed that the feature
-observed by \citet{diemer2014dependence} results from the  piling up
-of recently accreted dark matter particles at the apocenters of
-their orbits, and its location corresponds to the last density
+The recent study of \citet{diemer2014dependence} has sparked a renewed
+interest in understanding the structure of dark matter halos on scales
+beyond the typical virial radii.  \citet{diemer2014dependence}
+investigated the outskirts of dark matter halos in numerical
+simulations and found the existence of a physical feature, namely a
+sharp steepening in the density distributions of dark matter halos,
+which is not captured by commonly used functional forms such as the
+NFW profile. They showed that even for halos of the same mass, the
+position of the feature changes depending upon the mass accretion rate
+of the halos. A simple theoretical toy model to explain this feature
+was presented by \citet{adhikari2014splashback}. They showed that the
+feature observed by \citet{diemer2014dependence} results from the
+piling up of recently accreted dark matter particles at the apocenters
+of their orbits, and its location corresponds to the last density
 caustic in the self-similar models of secondary infall
 \citep{fillmore1984self, bertschinger1985self, lithwick2011self}.
-They coined the term ``splashback radius`` for this feature. Their
-toy model also naturally explains the accretion rate dependence --
-faster accreting halos have smaller splashback radii.
+They coined the term ``splashback radius`` for this feature. Their toy
+model also naturally explains the accretion rate dependence -- faster
+accreting halos have smaller splashback radii. Subsequently,
+\citet{more2015splashback} suggested the use of the splashback radius
+as a natural boundary for dark matter halos and explored its
+consequences for the inferred boundaries and growth rates of the
+halos. Depending on the accretion rate of the halo, the splashback
+radius can lie well beyond the commonly used virial radius
+\citep{diemer2014dependence, more2015splashback}.
 
@@
 
-Subsequently, \citet{more2015splashback} studied the
-growth rate of dark matter halos at low redshift and showed that
-pseudo-evolution, caused by the ill-definition of the halo boundary
-through the virial radius, accounts for nearly all of the apparent
-growth of galaxy-sized halos and can also account for a substantial
-fraction of the growth of cluster-sized halos
-\citep{diemer2013pseudo}. They suggested the use of the splashback
-radius as a natural boundary for dark matter halos and explored its
-consequences for the inferred boundaries and growth rates of the
-halos.  It was found that depending on the accretion rate of the
-halo, the splashback radius may lie well beyond the commonly used
-virial radius. For quickly accreting halos the splashback radius is
-expected to occur at $\approx 0.8-1$ $r_{\mathrm{200m}}$ and at
-$\approx 1.5$ $r_{\mathrm{200m}}$ for slowly accreting halos
-\citep{more2015splashback}.
-
 Given the mass of the halo, the location of the splashback radius
 constitutes a direct probe of the halo accretion rate. Motivated by
-these studies, \citet{more2016detection} tried to detect this
+these studies, \citet{more2016detection} attempted to detect this
 feature in observations. Using the optically selected Sloan Digital
@@
 for the steepening of the dark matter density profile, and therefore
-the splashback radius of this sample of galaxy clusters (later
+the splashback radius of this sample of galaxy clusters (further
 corroborated by including further models for mis-centering by
-\citet{baxter2017halo}). Somewhat surprisingly,
+\citet{baxter2017halo} and in the Dark Energy Survey data by
+\citet{chang2017splashback}). Somewhat surprisingly,
 \citet{more2016detection} found that the location of the splashback
@@
 \citet{umetsu2017lensing} as well as \citet{contigiani2018weak}
-used Xray selected clusters to look for the splashback radius 
-using the weak lensing signal, however
-stacking issues and the low signal-to-noise ratio remains a significant
-hurdle for both of them. \citet{chang2017splashback} found evidence for the splashback
-radius in the weak lensing signal, but their analysis was again done
-using optically selected clusters in the Dark energy survey
+recently used Xray selected clusters to look for the splashback radius
+using the weak lensing signal, however stacking issues and the low
+signal-to-noise ratio remains a significant hurdle for both of them.
+\citet{chang2017splashback} found evidence for the splashback radius
+in the weak lensing signal, but their analysis was again done using
+optically selected clusters in the Dark energy survey
 \citep{dark2005dark}. Regardless of the projection issues present in
@@
 cluster catalogs could be imprinted in a non-trivial way on the measured number
-density profiles of clusters. {\bf Add citation to the more recent Xray paper
-by Henk Hoekstra and collaborators as well.}
+density profiles of clusters.
 
@@
 cluster selection is performed is much smaller than the expected
-location of the splashback radius. Therefore, we do not expect major
-systematic biases due to the selection process. We use this sample
-to explore the evidence for the splashback radius in observations.
-Due to the low signal-to-noise ratio of the weak lensing signal, we
-perform our analysis using cross-correlation of galaxies with
-clusters instead. The SDSS sample used by \citet{more2016detection}
-was deep enough such that biases in the location of the splashback
-radius due to dynamical friction effects were expected to be small.
-Nevertheless, we use galaxy samples, which are even fainter by
-$0.5-1$ magnitudes compared to those used by
+location of the splashback radius (typically $R_{\rm 500c}$). We use
+this sample to explore the evidence for the splashback radius in
+observations.  Due to the low signal-to-noise ratio of the weak
+lensing signal, we perform our analysis using cross-correlation of
+galaxies with clusters.  The SDSS sample used by
+\citet{more2016detection} was deep enough such that biases in the
+location of the splashback radius due to dynamical friction effects
+were expected to be small.  Nevertheless, we use galaxy samples, which
+are even fainter by $0.5-1$ magnitudes compared to those used by
 \citet{more2016detection}.
@@
 the observations of the splashback radius can be used to study a
-variety of galaxy formation questions. Such as questions 
-regarding the timescales and the spatial scales within
-which star forming galaxies quench after they fall into the cluster
-potential. Answers to those questions are important to understand 
-the evolution of satellite galaxies in massive galaxy clusters. 
-If blue galaxies quench before
-they complete a single orbit, then they are not expected to show a
-splashback feature in their density distribution. In pursuit of this
-question, we also explore the dependence of the cluster-galaxy
-cross-correlations separately for the red and blue galaxy populations 
-and explore their relative contributions to the overall density profile.
-
-This paper is organized as follows: Section~\ref{sec:Methods} starts
-by introducing the data, namely the cluster and the galaxy catalogs
-as well as the methods that are used to derive the results which are
-presented in visual and tabular form and  discussed in
-Section~\ref{sec:Results}. We outline the steps that will be taken
-in future works in Section~\ref{sec:Future} and finally we summarize
-our findings in Section~\ref{sec:Conclusions} and provide a short
-outlook on what needs yet to be done. Throughout the paper, we use a
-flat $\Lambda$CDM cosmology with $\Omega_{\rm m}=0.27$ to convert
-redshifts and angles into cosmological distances. Also, we denote 
-three-dimensional distances by $r$ and projected distances by $R$.
-
-\section{Data and Methods}
-\label{sec:Methods}
-The methodology we adopt for locating the splashback radius closely
-follows \citet{more2016detection}. We perform a cross-correlation
-between SZ selected galaxy clusters with photometric galaxies in
-order to assess the existence and location of the splashback radius.
-We describe the data sets we use and our methodology in this
-section.
+variety of galaxy formation questions. Questions regarding the
+timescales and the spatial scales within which star forming galaxies
+quench after they fall into the cluster potential are of particular
+interest to understand the fate of star formation in satellite
+galaxies. In particular, if star forming galaxies quench before they
+reach the apocenters of their orbit after infall, then they are not
+expected to show a splashback feature in their density distribution.
+In pursuit of this question, we also explore the dependence of the
+cluster-galaxy cross-correlations separately for star forming and
+quenched galaxy populations separated by color.
+
+This paper is organized as follows. We introduce the observational
+data sets we use in Section~\ref{sec:data}, namely the cluster and the
+galaxy catalogs. We describe the methods and analysis procedures we
+use in Section~\ref{sec:estimators}. We present and discuss our
+results in Section~\ref{sec:Results}. Finally, we summarize our
+findings in Section~\ref{sec:Conclusions} and discuss possible future
+directions. Throughout the paper, we use a flat $\Lambda$CDM cosmology
+with $\Omega_{\rm m}=0.27$ to convert redshifts and angles into
+cosmological distances. Also, we denote three-dimensional distances by
+$r$ and projected distances by $R$.
+
+\section{Data}
+\label{sec:data}
 
@@
 and the estimated purity of the catalog has a lower limit of 83\%
-(probability that a detection corresponds to a real object). The
-integrated Compton Y-parameter $Y_{500c}$ of each of the clusters
-are also provided. Based on the scaling relation between $Y_{500c}$
-and $M_{500c}$ \citep{ade2014planck} the mass estimates $M_{500c}$
-of the clusters are calculated
-\citep{adam2016planck,collaboration2016planck}. The PSZ2 union
-cluster catalog is publicly available from the \fnurl{\textit{Planck
-Legacy Archive}}{https://pla.esac.esa.int/pla/\# home}.
-
-We restrict ourselves to the redshift range $0.03 \leq z \leq 0.33$
-in order to mimic the redshift range used by
-\citet{more2016detection}. Due to the large beam size of the Planck
+\citep{ade2016psclusters}. The integrated Compton Y-parameter
+$Y_{500c}$ of each of the clusters are also provided. The mass
+estimates $M_{500c}$ provided by the Planck collaboration are based on
+the scaling relation between $Y_{500c}$ and $M_{500c}$
+\citep{ade2014planck,adam2016planck,collaboration2016planck}. The PSZ2
+union cluster catalog is publicly available from the
+\fnurl{\textit{Planck Legacy Archive}}{https://pla.esac.esa.int/pla/\#
+home}.
+
+We restrict ourselves to the redshift range $0.03 \leq z \leq 0.33$ in
+order to have a similar redshift range used in
+\citet{more2016detection}. Due to the larger beam size of the Planck
 satellite, the cluster positions as reported in the catalog may be
@@
 For the visual inspection and centering of the clusters, we use the
-Pan-Starrs $gri$ \textit{stack} images around each cluster position.
+Pan-STARRS $gri$ \textit{stack} images around each cluster position.
 The galaxy catalog is obtained from the  \textit{StackObjectThin}
@@
 The magnitudes of the selected objects are then corrected for the
-extinction caused by the dust present in the Milky Way. This is done
+extinction caused by dust present in the Milky Way. This is done
 using the \fnurl{mwdust}{https://github.com/jobovy/mwdust} Python
@@
 $i_{\mathrm{P1}}$ band Kron magnitude brighter than 22.0 are
-selected from the catalog. This results in a galaxy catalog
-consisting out of 1'155'285'728 objects. Starting from this catalog
-three different sub-catalogs named PS 21, PS 21.5 and PS 22 with a
-survey depth of 21.0, 21.5 and 22.0 magnitudes, respectively are
-constructed.
+selected from the catalog. Starting from this catalog we construct
+three different sub-catalogs corresponding to survey depths of 21.0,
+21.5 and 22.0 magnitudes, and we name these catalogs PS 21, PS 21.5
+and PS 22, respectively.
 
@@
 to avoid choosing objects in shallow regions of the survey the
-minimal observed Kron magnitude in the $i_{\mathrm{P1}}$ band in
+maximum observed Kron magnitude in the $i_{\mathrm{P1}}$ band in
 each \textit{skycell} is recorded and only objects in skycells with
-a minimal observed Kron magnitude of 21.0, 21.5 and 22.0 or brighter
+a maximum observed Kron magnitude of 21.0, 21.5 and 22.0 or brighter
 are selected depending on the corresponding catalog. Since most of
@@
 
-\subsection{Estimation of the spatial density profile}
+\section{Methods}
 \label{sec:estimators}
-
-We use the Davis-Peebles estimator \citep{davis1983survey} to
-compute the cross-correlation between our galaxy clusters and
-galaxies. This estimator can be written as
+The methodology we adopt for locating the splashback radius closely
+follows that of \citet{more2016detection}. We perform a
+cross-correlation between SZ selected galaxy clusters with photometric
+galaxies in order to assess the existence and location of the
+splashback radius. We use the Davis-Peebles estimator
+\citep{davis1983survey} to compute the cross-correlation between our
+galaxy clusters and galaxies. This estimator can be written as
 \begin{equation}
@@
 distribution masks prevents us from using the Landy-Szalay estimator \citep{landy1993bias}.
-{\bf Cite Landy-Szalay paper.}
 
@@
 
-The splashback radius for galaxy cluster scale halos is consistent
+The splashback radius for halos on galaxy cluster scales is consistent
 with the location of the steepest logarithmic slope of the density
 profile. We estimate the steepest slope of both the two-dimensional
-and the three-dimensional cross-correlation function. The two
-locations of the steepest slope are expected to be different by
+and the three-dimensional cross-correlation function. The
+locations of the steepest slope in the two-dimensional and the
+three-dimensional case are expected to be different by
 about 20\% for typical cluster halo parameters
@@
 
-Mis-centering of the central cluster positions can heavily affect 
-the small-scale correlation function on scales smaller than the typical mis-centering distance. 
-Although, the splashback radius is located at much larger scales, 
-the change of the inner part of the correlation function can alter the model fit significantly. 
-Mis-centering effects are not expected to change the location of the splashback feature 
-but they can in principle decrease the significance of the evidence for the splashback feature \citep{baxter2017halo}.
-We discuss the modelling of mis-centering and its effects on the inferred splashback radii in Appendix~\ref{sec:mis-centering}.
+Mis-centering of the central cluster positions can affect the
+small-scale correlation function on scales smaller than the typical
+mis-centering distance.  Although, the splashback radius is located at
+much larger scales, the change of the inner part of the correlation
+function can alter the model fit significantly.  Mis-centering effects
+are not expected to change the location of the splashback feature but
+they can in principle decrease the significance of the evidence for
+the splashback feature \citep{baxter2017halo}.  We discuss the
+modelling of mis-centering and its effects on the inferred splashback
+radii in Appendix~\ref{sec:mis-centering}.
+
 \subsection{Separation of red and blue galaxies}
@@
 In order to compute the color cut to be used, we first match spectroscopic
-galaxies in the Sloan digital Sky Survey (DR 13) ({\bf which data release?}) to their
+galaxies in the Sloan digital Sky Survey (DR 13) to their
 Pan-STARRS photometry. We bin these galaxies in narrow redshift bins and
@@
 galaxies in each bin. Due to the presence of the $4000\AA$-break present in the
-red galaxy population, the two galaxy populations separate in such histograms
-into two populations and we fit a double Gaussian distribution to it.  Based on
-the fitted distribution we put a cut in color to exclude a contamination of the
-blue population by incorrectly characterized red galaxies with a confidence of
-3$\sigma$. We repeat this procedure for each redshift bin, to obtain a redshift
+quenched galaxy population, the two galaxy populations separate in such histograms
+into two populations and we fit a double Gaussian distribution to it.
+Based on the fitted distribution we use a cut in color to exclude a
+contamination to the star-forming galaxy population with a confidence
+of 3$\sigma$. We repeat this procedure for each redshift bin, to obtain a redshift
 dependent color cut that separates the red from the blue population minimizing
@@
 with their 68\% confidence intervals are listed in
-Table~\ref{tab:fit_parameters} along with their minimal, reduced
-$\chi^2$ values. The two-dimensional posterior distributions for
-each pair of parameters are shown in Figures~\ref{fig:corner_21},
-\ref{fig:corner_21.5} and \ref{fig:corner_22} for the three absolute
-magnitude limits, respectively.
+Table~\ref{tab:fit_parameters} along with the corresponding reduced
+$\chi^2$ values for the best fit. The two-dimensional posterior
+distributions for each pair of parameters are shown in
+Figures~\ref{fig:corner_21}, \ref{fig:corner_21.5} and
+\ref{fig:corner_22} for the three absolute magnitude limits,
+respectively.
 
@@
 \end{figure*}
-\begin{figure}
-    \includegraphics[width= \columnwidth]{color_fraction_with_spline_no_mc.pdf}
-\caption{Fractional contributions of the red and blue galaxy
-populations to the total galaxy number density. We show the
-locations of the splashback radii associated with the two subsamples
-with the colored, vertical bands and the upper and lower bounds of
-the splashback radius obtained from the full PS 21.5 catalog with
-the black, dashed lines.}
-   \label{fig:color_fraction} 
-\end{figure}
+%\begin{figure}
+%    \includegraphics[width= \columnwidth]{color_fraction_with_spline_no_mc.pdf}
+%\caption{Fractional contributions of the red and blue galaxy
+%populations to the total galaxy number density. We show the
+%locations of the splashback radii associated with the two subsamples
+%with the colored, vertical bands and the upper and lower bounds of
+%the splashback radius obtained from the full PS 21.5 catalog with
+%the black, dashed lines.}
+%   \label{fig:color_fraction} 
+%\end{figure}
 The right panels in Figure~\ref{fig:2D_graphs} show the
@@
 i}-5\log h=-19.44$. Our measurements have an accuracy of $\sim$15\%.
-
-{\bf Dominik, we need to add in the first and second derivative of just the one
-halo term to these plots $\rho_{\rm in}\,f_{\rm trans}$. Also highlight that
-the slope is dropping down precipitously within a factor 2 in radius. Mention
-that in the next paragraph. Add in Figure~\ref{fig:derivatives}, the second
-derivative posterior as well. In fact you can leave out the current left hand
-panel and just plot the the first and second derivatives of $\log\rho_{\rm
-in}\,f_{\rm trans}$.}
 
@@
 as evidence for the existence of the splashback feature in both galaxy populations.
-The finding of the splashback feature in the blue population implicates that
-there needs to be a reasonable fraction of blue galaxies that fall
-into the cluster and continue to stay blue even after reaching their
-apocenters. Star forming galaxies in models which quench their star
-formation on a timescale shorter than the orbital time scale are
-not expected to show presence of the splashback feature. A
-quantitative exploration of the implications is beyond the scope of
-this work, but will be followed up in the future.
-
-In Figure~\ref{fig:color_fraction}, we show the fractional
-contributions of the red and blue galaxies to the total,
-three-dimensional cross-correlation \footnote{The fractions are
-obtained by performing an appropriate number density weighting.}.
-The red galaxies dominate the central parts of the galaxy clusters
-but become less dominant as we move further away from the cluster center.
-We see an increase of the fractional contribution of
-red galaxies below the splashback radius. On scales larger than the
-splashback radius, the fractional contributions of the two populations become
-very similar.
-
-We note that, in principle it is possible that the blue galaxy population does not posses
-a splashback feature but that due to our separation procedure outlined in Section~\ref{sec:Color}
-some of the red galaxies are identified as blue ones and are contaminating the correlation function
-of the blue population. Such a contamination could be caused by a scattering of some of the red galaxies
-into the blue population due to the large photometric errors of the Pan-STARRS galaxies at faint magnitudes.
-We tried to investigate the possiblity of that happening as outlined in 
-Appendix~\ref{sec:Errors}. Unfortunately, we established that at the current state of the data we cannot
-exclude such a contamination and the results derived using the color separated galaxy populations
-should be used with caution therefore.
-
-\section{Future work}
-\label{sec:Future}
-
-As it can be seen from Table~\ref{tab:snr}, the signal-to-noise
-ratio of our measurement is lower when using the PS 22 catalog
-compared to the other two estimates. This has two causes: Firstly,
-the sky-coverage of the PS 22 catalog is $\approx$ 25\% lower than
-for PS 21 and PS 21.5 since more regions had to be excluded due to
-the survey depth being too low in those regions. Therefore, some
-clusters from the PSZ2 catalog are missed when the PS 22 catalog is
-exploited, which reduces the statistics. Secondly, as we consider
-fainter galaxies, the contamination from background galaxies is
-increased. This requires a better estimate of the uncorrelated
-background component. A more precise estimation of the uncorrelated
-background contamination would be possible by using a random galaxy
-catalog in addition to the random cluster sample. This would allow
-to use the more sophisticated Landy \& Szalay estimator
-\citep{landy1993bias} to perform the background subtraction.
-
-Another approach to increase the statistics of the measurements would 
-be to increase the redshift range in which clusters are being considered. 
-We chose $0.03 \leq z \leq 0.33$ in order to keep the analysis comparable 
-to \citet{more2016detection}. However, this cut reduces the cluster sample 
-size. Increasing the redshift range has its own limitations, though. 
-It would be required to use a brighter magnitude limit for galaxies, 
-which reduces the number of galaxies that can be used to infer the 
-cross-correlation signal. This results in a trade-off which could be investigated
-to find the optimal redshift range. Alternatively, other cluster samples that do 
-not rely on optical cluster finding such as Xray based surveys might 
-serve as independent and larger cluster samples. 
-Another plausible approach would be to consider a smaller region of
-the sky, resulting in less clusters but with a deeper field of view,
-such as in the case of the Hyper Suprime-Cam at Subaru Telescope,
-which will survey $\approx 1400$ deg$^2$ of the sky and achieve a
-depth of 26.2 magnitudes \citep{takada2010subaru}.
-
-The separation of the blue and red galaxy populations as described in 
-Section~\ref{sec:Color} is prone to photometric errors. In order to 
-assure our finding of a splashback feature in the blue galaxy population
-a deeper galaxy catalog would be desirable. Again, the future survey
-conducted with the Hyper Suprime-Cam could come to rescue.
-
-Lastly, but most importantly, the investigation of any systematics
-which might originate from the SZ selection of the Planck clusters
-is beyond the scope of the current work. We caution that there may
-be residual systematics in the selection which could affect the
-interpretation of our measurements. We will investigate such
-selection systematics with the help of hydrodynamical simulations.
-
-\section{Conclusions}
+Taken at face value, our finding of the splashback feature in the blue
+population would imply that there needs to be a reasonable fraction of
+blue galaxies that fall into the cluster and continue to stay blue
+even after reaching their apocenters.
+
+% Star forming galaxies in models
+% which quench their star formation on a timescale shorter than the
+% orbital time scale are not expected to show presence of the splashback
+% feature. A quantitative exploration of the implications is beyond the
+% scope of this work, but will be followed up in the future.
+
+% In Figure~\ref{fig:color_fraction}, we show the fractional
+% contributions of the red and blue galaxies to the total,
+% three-dimensional cross-correlation \footnote{The fractions are
+% obtained by performing an appropriate number density weighting.}.
+% The red galaxies dominate the central parts of the galaxy clusters
+% but become less dominant as we move further away from the cluster center.
+% We see an increase of the fractional contribution of
+% red galaxies below the splashback radius. On scales larger than the
+% splashback radius, the fractional contributions of the two populations become
+% very similar.
+
+We caution however that the cut we use to define our samples was
+defined based on spectroscopic galaxies, which tend to be brighter
+than the typical galaxies we use for the cross-correlation. As we use
+galaxies at fainter magnitudes for the cross-correlation, the
+photometric errors increase dramatically and can scatter many more of
+the red galaxy population into the blue galaxy sample. We report on
+our investigations in Appendix~\ref{sec:Errors} as a cautionary tale,
+and to guide future efforts to establish the splashback radius in the
+blue galaxy population. We show that given the current state of the
+data we cannot exclude a contamination of the correlation function of
+blue galaxies from the red galaxy population and appropriate caution
+be warranted in the interpretation or use of the results derived using
+the color separated galaxy populations.
+
+\section{Conclusions and future directions}
 \label{sec:Conclusions}
@@
 galaxies with the clusters, we present evidence for the presence of
-the splashback feature in both populations. This implies that the
-star formation of a sizable number of blue galaxies does not get
-quenched during their first orbit through the halo.
-\item We also detect an increase in the fraction of red
-galaxies associated with the splashback radius. 
+the splashback feature in both populations. The existence of the
+splashback radius for the 
+star forming galaxy population could be of significance for the
+models of satellite quenching in galaxy clusters. However, photometric
+errors hinder a clean interpretation of the signal.
 \end{itemize}
 
+The signal-to-noise ratio of the current measurement is a result of
+the limited depth of the Pan-STARRS catalog, as well as the limited
+number of galaxy clusters detected using the SZ effect. As we consider
+fainter galaxy catalogs, the sky fraction in which the Pan-STARRS
+galaxy catalogs are complete reduces. Furthermore, the contamination
+from background galaxies is expected to increase at deeper magnitudes
+as well. A more precise estimation of the
+uncorrelated component would be possible by using a random galaxy
+catalog in addition to the random cluster sample. The masking
+information in Pan-STARRS is not currently easily accessible, which
+prevents the use of the more sophisticated Landy \& Szalay estimator. 
+Increasing the redshift range of clusters could potentially yield a
+bigger cluster sample, but would require us to use a sample of
+galaxies with a brighter absolute magnitude limit for galaxies, 
+which reduces the number of galaxies that can be used to infer the
+cross-correlation signal. We are exploring the use of alternative
+cluster catalogs such as those detected from Xray surveys.
+
+% As it can be seen from Table~\ref{tab:snr}, the signal-to-noise
+% ratio of our measurement is lower when using the PS 22 catalog
+% compared to the other two estimates. This has two causes: Firstly,
+% the sky-coverage of the PS 22 catalog is $\approx$ 25\% lower than
+% for PS 21 and PS 21.5 since more regions had to be excluded due to
+% the survey depth being too low in those regions. Therefore, some
+% clusters from the PSZ2 catalog are missed when the PS 22 catalog is
+% exploited, which reduces the statistics. Secondly, as we consider
+% fainter galaxies, the contamination from background galaxies
+% increases. This requires a better estimate of the uncorrelated
+% background component. A more precise estimation of the uncorrelated
+% background contamination would be possible by using a random galaxy
+% catalog in addition to the random cluster sample. This would allow
+% to use the more sophisticated Landy \& Szalay estimator
+% \citep{landy1993bias} to perform the background subtraction.
+
+% Another approach to increase the statistics of the measurements would 
+% be to increase the redshift range in which clusters are being considered. 
+% We chose $0.03 \leq z \leq 0.33$ in order to keep the analysis comparable 
+% to \citet{more2016detection}. However, this cut reduces the cluster sample 
+% size. Increasing the redshift range has its own limitations, though. 
+% It would be required to use a brighter magnitude limit for galaxies, 
+% which reduces the number of galaxies that can be used to infer the 
+% cross-correlation signal. This results in a trade-off which could be investigated
+% to find the optimal redshift range. Alternatively, other cluster samples that do 
+% not rely on optical cluster finding such as Xray based surveys might 
+% serve as independent and larger cluster samples. 
+% Another plausible approach would be to consider a smaller region of
+% the sky, resulting in less clusters but with a deeper field of view,
+% such as in the case of the Hyper Suprime-Cam at Subaru Telescope,
+% which will survey $\approx 1400$ deg$^2$ of the sky and achieve a
+% depth of 26.2 magnitudes \citep{takada2010subaru}.
+
+The separation of the blue and red galaxy populations as described in
+Section~\ref{sec:Color} is prone to photometric errors as explored in
+the Appendix. A deeper galaxy catalog would be required in order to
+confirm or rule out the existence of the splashback feature in the
+blue galaxy population. The ongoing deep galaxy surveys such as the
+Hyper Suprime-Cam (HSC) and the Dark Energy Survey (DES) would be able
+to provide such data sets, albeit in a limited area. The Large
+Synoptic Survey telescope (LSST) would eventually provide deep as well
+as wide galaxy catalogs to eventually establish the locations of the
+splashback radius at high significance.
+
+Lastly, but most importantly, the investigation of any systematics
+which might originate from the SZ selection of the Planck clusters
+is beyond the scope of the current work. We caution that there may
+be residual systematics in the selection which could affect the
+interpretation of our measurements. We plan to investigate such
+selection systematics with the help of hydrodynamical simulations.
+
 Our curated galaxy catalogs from the Pan-STARRS survey for different
-depths and the corresponding masks are available and can be sent
-upon request.
+depths and the corresponding masks are available upon request.
+
+While this work was in preparation, we became aware of a related study
+by Shin et al. (2018). Our results are complementary to theirs given
+the different data samples and cluster catalogs.
 
 \section*{Acknowledgements}
-DZ is grateful to Kavli IPMU for its hospitality during this
-research project. SM is supported by a grant-in-aid by the Japan
-Society for Promotion of Science (JSPS), grant number 16H01089.
+DZ is grateful to Kavli IPMU for its hospitality during this research
+project. SM is supported by a grant-in-aid by the Japan Society for
+Promotion of Science (JSPS), grant number 16H01089. We acknowledge
+useful discussions regarding this work with Benedikt Diemer, Neal
+Dalal, Bhuvnesh Jain, Andrey Kravtsov, as well as participants of the
+KITP UCSB workshop on the Galaxy-Halo connection in 2017. SM was
+supported in part by the National Science Foundation under Grant No.
+NSF PHY-1125915 during this workshop.
 
@@
 
-\section{Estimating the contamination of the blue galaxy population}
-\label{sec:Errors}
-In our separation procedure of the blue from the red galaxy population 
-we assume the photometric magnitudes of the Pan-STARRS galaxies to be exact.
-However, photometric errors could cause red galaxies to scatter into the blue
-population which contaminates the correlation function and might be the cause 
-for the splashback feature observed in the blue population. Therefore, we 
-investigate the possiblity of such a contamination.
-
-Firstly, we need to know how high such a contamination would have to be in order
-to reproduce the splashback signal as seen in the observations given that the actual
-blue poulation does not posses such a signal at all. We assume a simple $r^{-1.5}$ power 
-law for the correlation signal of the blue population which by construction cannot cause a splashback feature. Then,
-we simulate a contamination of the population by adding some of the accordingly rescaled 
-correlation signal of the red population, which does posses a splashback feature.
-We find that a contamination of at least 20\% is necessary to reproduce the observed
-splashback signal.
-
-Next we estimate the photometric errors of the Pan-STARRS galaxies in each one of the used
-bands (namely $i_{PS}, g_{PS}, r_{PS}$). Since we chose galaxies with $15.0 \leq i_{PS} \leq 21.5$
-for our analysis we consider the $i_{PS}$ errors as given in the Pan-STARRS survey of only 
-the galaxies in this magnitude range. We fit a Gaussian to their distribution and use a conservative $3\sigma$ confidence
-estimate for the photometric error in the $i_{PS}$ band. We repeat the same analysis for the
-$g_{PS}$ and $r_{PS}$ bands, but using magnitude ranges which are shifted by the mean magnitude
-differences between the $i_{PS}$ band and the $g_{PS}$ and $r_{PS}$ bands, respectively.
-The histograms of the errors as well as the estimated photometric errors are shown in
-Figure~\ref{fig:photoerrors}. We find similar photometric errors in the $i_{PS}$ (63 mmag)
-and $r_{PS}$ band (64 mmag) but a larger error in the $g_{PS}$ band of 81 mmag.
-
-\begin{figure}
-\centering{
-    \includegraphics[scale=0.6]{errors.pdf}}
-\caption{Histograms of the photometric errors in the used $i_{PS}, g_{PS}, r_{PS}$ bands.
-The errors were taken dirrectly from the Pan-STARRS survey and sampled for galaxy type 
-objects in the magniude range $15.0 \leq i_{PS} \leq 21.5$, $16.3 \leq g_{PS} \leq 22.8$ and $15.4 \leq r_{PS} \leq 21.9$, respectively. 
-The upper photometric error limits at $3\sigma$
-confidence are listed in the upper right of the figure.}
-    \label{fig:photoerrors}•
-\end{figure}
-
-Finally, we estimate the contamination of the blue galaxy population given the cut in $g_{PS} - r_{PS}$
-color that we used to separate the two populations. We start the same way as we established the cut:
-By taking narrow redshift bins and then by binning the $g_{PS} - r_{PS}$ colors of the galaxies in each
-redshift bin. Then we proceed by fitting a double Gaussian to the color distribution in each redshift bin
-(indicated by the solid, accordingly colored lines in Figure~\ref{fig:histogram}). We put the cut which
-separates the two distributions from each other at a $g_{PS} - r_{PS}$ color such that red galaxies are
-excluded from being incorrectly characterized as blue galaxies at a confidence level of $3\sigma$ (indicated
-by the solid, vertical, black line). At that point the fractional contribution of the red population reads 
-$\sim 40\%$ which corresponds to a free field galaxy sample. In order to model the distribution inside of 
-the cluster region we rescale the red distribution such that we end up with a fractional contribution of 
-the red population of $65\%$. We do now take into account the estimated photometric errors in the $g_{PS}$ and
-$r_{PS}$ bands by broadening the Gaussian distributions accordingly. The contamination is then estimated as:
-\begin{equation}
-\sum_{z=0.03}^{0.33} \int_{-\infty}^{cut(z)} 1 + \frac{\mathcal{N}_r(g-r)}{\mathcal{N}_b(g-r)} \mathrm{d}(g-r)
-\end{equation}
-where the sum runs over all redshift bins, the integration is performed over the $g_{PS} - r_{PS}$ color up 
-to the redshift dependent cut $cut(z)$ separating the two distributions and $\mathcal{N}_r(g-r)$ and $\mathcal{N}_b(g-r)$
-representing the broadened Gaussian distributions of the red and blue population, respectively
-(dashed, accordingly colored curves). With the described analysis we calculate a contamination of 24\%, which would
-be high enough to explain the observed splashback signal of the blue galaxy population solely by red galaxies
-that scattered into the blue population. However, this cannot be taken as disproof of the existence of a splashback
-feature in the blue galaxy population. The contamination estimate strongly depenends on two factors: Firstly, on the 
-confidence at which one wants to exclude red galaxies from being misidentified as blue galaxies and secondly on the
-method one uses to estimate the photometric errors (magnitude range and the conservatism of the error estimate).
-Depending on the approach we got contamination estimates ranging from 0.0001\% to 60\%. Therefore, at the current
-state it cannot be concisely established if the observed splashback feature stems from a contamination of red
-galaxies or not. A deeper galaxy catalog with smaller photometric errors, especially in the $g_{PS}$ band is
-required to shed light on this matter.
-
-\begin{figure}
-\centering{
-    \includegraphics[scale=0.6]{best_hist_58.pdf}}
-\caption{Histogram of the $g_{PS} - r_{PS}$ colors of the galaxies in a certain redshift bin for illustration
-of the contamination estimation. The solid, colored curves indicate the initially fitted Gaussian distributions,
-whereas the dashed curves represent the Gaussian distributions broadened by the photometric errors of the Pan-STARRS
-survey. The black, vertical line indicates the cut, separating the two galaxy populations as inferred from the original
-distributions. The cut excludes red galaxies from being characterized as blue galaxies at $3/sigma$ confidence.}
-    \label{fig:histogram}•
-\end{figure}
-
-\section{Modelling cluster mis-centering}
-\label{sec:mis-centering}
-As described in \citet{baxter2017halo} mis-centering of the central cluster 
-positions are not expected to change the location of the splashback feature 
-but might decrease the significance of the finding. Therefore, we modelled the 
-effects of mis-centering on the correlation function and its influence on the results.
-
-The mass dependence of the exact mis-centering fractions are not
-well understood and mis-centering effects are therefore difficult to 
-model \citep{Skibba:2011, Hoshino:2015}. We follow the approach outlined 
-in \citet{baxter2017halo} to take the effects of a possible mis-centering of a fraction 
-of the cluster positions into account by modelling the influence on the two-dimensional correlation function.
-
-Denoting the fraction of mis-centered clusters in the sample with $f_{\rm mis}$ we relate
-the correlation function $\xi'_{\rm 2D}(R)$ that is affected by the mis-centering of the clusters to the correlation function
-unaffected by mis-centering Equation~\ref{eq:surface} by
-
-\begin{equation} 
-\xi'_{\rm 2D}(R) = (1-f_{\rm mis})\xi_{\rm 2D}(R)+f_{\rm mis}\xi_{\rm (2D,mis)}(R)
-\label{eq:full}
-\end{equation}
-
-where the contribution of the mis-centered clusters to the correlation function is captured by $\xi_{\rm (2D,mis)}$. 
-We model the mis-centered component $\xi_{\rm (2D,mis)}$ as
-
-\begin{equation}
-\xi_{\rm (2D,mis)}(R)=\int_0^\infty \mathrm{d}R_{\rm mis} P(R_{\rm mis})\xi_{\rm (2D,mis)}(R|R_{\rm mis})
-\end{equation}
-
-where we assign a probability $P(R_{\rm mis})$ that a cluster is mis-centered by a comoving distance $R_{\rm mis}$.
-The contribution $\xi_{\rm (2D,mis)}(R|R_{\rm mis})$ from a cluster mis-centered by a distance $R_{\rm mis}$ 
-relates to the unaffected correlation function $\xi_{\rm 2D}$ as
-
-\begin{equation}
-\xi_{\rm (2D,mis)}(R|R_{\rm mis})=\int_0^{2\pi}\frac{\mathrm{d}\theta}{2\pi}\xi_{\rm 2D}\left(\sqrt{R^2+R_{\rm mis}^2+2RR_{\rm mis}\cos{\theta}}\right)
-\end{equation}
-
-according to \citet{yang2006weak} and \citet{johnston2007cross}. Following \citet{simet2016weak} we model the mis-centering probability 
-$P(R_{\rm mis})$ as a Rayleigh distribution:
-
-\begin{equation}
-P(R_{\rm mis})=\frac{R_{\rm mis}}{\sigma^2}\exp{\left( -\frac{R_{\rm mis}^2}{2\sigma^2}\right)}
-\end{equation}
-
-Therefore, the mis-centered contribution is fully characterized by the two parameters $f_{\rm mis}$ and the witdh 
-of the mis-centering probability distribution $\sigma$.
-
-To find the priors for the two mis-centering paramters $f_{\rm mis}$ and $\sigma$ we cross-match our SZ selected cluster sample with the X-Ray selected ACCEPT cluster sample \citep{cavagnolo2009vizier}.
-Assuming the ACCEPT clusters to lay at the true gravitational cluster centers we construct Gaussian priors
-for the two mis-centering model parameters $f_{\rm mis}$ and $\sigma$ from the comparison of the 
-two samples with central values 0.15, 0.41 and scales 0.21, 0.3 for $f_{\rm mis}$ and $\sigma$, respectively.
-
-To study the influence of mis-centering on our findings we repeat the MCMC model fitting using our new model including mis-centering given in Equation~\ref{eq:full}, which now includes two more model parameters.
-
-\begin{table}
-    \centering
-    \caption{Listing of the splashback radii inferred by including the effects of mis-centering of the central cluster positions. }
-    \label{tab:mis_splash}
-    \begin{tabular}{ccc}
-    \hline 
-gal cat &  $R_{\mathrm{sp}}^{\mathrm{2D}}$ & $r_{\mathrm{sp}}^{\mathrm{3D}}$ \\
-\hline 
-\hline 
-PS 21 &$1.35_{-0.12}^{+0.13}$ & $1.76_{-0.33}^{+0.29}$\\
-\hline
-PS 21.5 & $1.30_{-0.10}^{+0.10}$&$1.81_{-0.33}^{+0.28}$\\
-\hline
-PS 22 &$1.33_{-0.17}^{+0.13}$ & $1.96_{-0.45}^{+0.37}$\\
-\hline
-PS 21.5 (R) & $1.45_{-0.11}^{+0.12}$ & $2.23_{-0.26}^{+0.27}$ \\
-\hline
-PS 21.5 (B) & $1.42_{-0.25}^{+0.20}$ & $2.39_{-0.39}^{+0.39}$ \\
-\hline
-    \end{tabular} 
-\end{table}
-
-We find that due to the use of a projected mis-centering model the error bands of the MCMC estimate of the projected cross-correlation signal are increased by $\sim 25$\%.
-However, the effect is barely noticeable in the three-dimensional profiles.
-The inclusion of mis-centering is reflected as a small increase of the inferred errors of the projected and three-dimensional splashback radii as shown in Table~\ref{tab:mis_splash}.
-A small shift of the inferred central values of the splashback radii is recorded additionally.
-However, the shift is not systematic nor statistically significant.
-
 \section{Sky maps}
@@
 We present the sky locations of the SZ selected clusters from the PSZ2
-catalog that were used in our study in Figure~\ref{fig:planck_fig}.
-The purple areas mark the masked out regions as defined by the union
-selection function of the PSZ2 catalog. The sky maps in
-Figure~\ref{fig:heal_map} show the survey masks of our three galaxy
-catalogs. All sky maps presented in this section use the ICRS
-coordinate system.
+catalog that we used in our study. The purple areas mark the masked
+out regions as defined by the union selection function of the PSZ2
+catalog. The sky maps in Figure~\ref{fig:heal_map} show the survey
+masks of our three galaxy catalogs.  All sky maps presented in this
+section use the ICRS coordinate system.
 
@@
 \end{figure*}
+
+\section{Modelling cluster mis-centering}
+\label{sec:mis-centering}
+As can be seen for the analysis and results in \citet{baxter2017halo},
+the mis-centering of the central cluster positions in optical clusters
+were not large enough to change the location of the steepest slope in
+the cluster-galaxy cross-correlations. They do however decrease the
+significance of the finding. Therefore, we explore the effects of
+mis-centering on the correlation function and its influence on the
+results.
+
+The mass dependence of the exact mis-centering fractions (for the
+brightest galaxy to be the central) are not well understood and
+mis-centering effects are therefore difficult to model
+\citep{Skibba:2011, Hoshino:2015}. We follow the approach outlined in
+\citet{baxter2017halo} to take the effects of a possible mis-centering
+of a fraction of the cluster positions into account by modelling the
+influence on the two-dimensional correlation function.
+
+If a fraction $f_{\rm mis}$ of the galaxy clusters in our sample are
+mis-centered, then the measured correlation function $\xi'_{\rm
+2D}(R)$ is given by
+% 
+%Denoting the fraction of mis-centered clusters in the sample with
+%$f_{\rm mis}$ we relate the correlation function $\xi'_{\rm 2D}(R)$
+%that is affected by the mis-centering of the clusters to the
+%correlation function unaffected by mis-centering
+%Equation~\ref{eq:surface} by
+%
+\begin{equation} 
+\xi'_{\rm 2D}(R) = (1-f_{\rm mis})\xi_{\rm 2D}(R)+f_{\rm mis}\xi_{\rm
+(2D,mis)}(R)\\,
+\label{eq:full}
+\end{equation}
+where $\xi_{\rm (2D,mis)}$ denotes the contribution of the
+mis-centered clusters to the correlation function, and $\xi_{\rm
+2D}(R)$ corresponds to the contribution of the correctly centered
+clusters. We model the mis-centered component $\xi_{\rm (2D,mis)}$ as
+\begin{equation}
+\xi_{\rm (2D,mis)}(R)=\int_0^\infty \mathrm{d}R_{\rm mis} P(R_{\rm
+mis})\xi_{\rm (2D,mis)}(R|R_{\rm mis})\,,
+\end{equation}
+where $P(R_{\rm mis})$ denotes the probability that a cluster is
+centered at a comoving distance $R_{\rm mis}$ from the brightest
+galaxy. The contribution $\xi_{\rm (2D,mis)}(R|R_{\rm mis})$ is
+related to the correlation function of the correctly centered clusters
+$\xi_{\rm 2D}$ as
+\begin{equation}
+\xi_{\rm (2D,mis)}(R|R_{\rm
+mis})=\int_0^{2\pi}\frac{\mathrm{d}\theta}{2\pi}\xi_{\rm
+2D}\left(\sqrt{R^2+R_{\rm mis}^2+2RR_{\rm mis}\cos{\theta}}\right)\,,
+\end{equation}
+according to \citet{yang2006weak} and \citet{johnston2007cross}. We
+model the mis-centering probability $P(R_{\rm mis})$ as a Rayleigh
+distribution,
+\begin{equation}
+P(R_{\rm mis})=\frac{R_{\rm mis}}{\sigma^2}\exp{\left( -\frac{R_{\rm
+mis}^2}{2\sigma^2}\right)}\,,
+\end{equation}
+Thus, the mis-centered contribution is fully characterized by the
+two parameters $f_{\rm mis}$ and the witdh of the mis-centering
+probability distribution $\sigma$.
+
+To find the priors for the two mis-centering paramters $f_{\rm mis}$
+and $\sigma$ we cross-match our SZ selected cluster sample with the
+X-Ray selected ACCEPT cluster sample \citep{cavagnolo2009vizier}.
+Assuming the ACCEPT clusters to lie at the minimum of the
+gravitational potential, we infer Gaussian priors for the two
+mis-centering model parameters $f_{\rm mis}=0.15\pm0.21$ and
+$\sigma=0.41\pm0.30$.
+
+To study the influence of mis-centering on our findings we repeat the
+MCMC model fitting using our new model including mis-centering given
+in Equation~\ref{eq:full}, which now includes two more model
+parameters. 
+\begin{table}
+    \centering
+    \caption{Listing of the splashback radii inferred by including the effects of mis-centering of the central cluster positions. }
+    \label{tab:mis_splash}
+    \begin{tabular}{ccc}
+    \hline 
+gal cat &  $R_{\mathrm{sp}}^{\mathrm{2D}}$ & $r_{\mathrm{sp}}^{\mathrm{3D}}$ \\
+\hline 
+\hline 
+PS 21 &$1.35_{-0.12}^{+0.13}$ & $1.76_{-0.33}^{+0.29}$\\
+\hline
+PS 21.5 & $1.30_{-0.10}^{+0.10}$&$1.81_{-0.33}^{+0.28}$\\
+\hline
+PS 22 &$1.33_{-0.17}^{+0.13}$ & $1.96_{-0.45}^{+0.37}$\\
+\hline
+PS 21.5 (R) & $1.45_{-0.11}^{+0.12}$ & $2.23_{-0.26}^{+0.27}$ \\
+\hline
+PS 21.5 (B) & $1.42_{-0.25}^{+0.20}$ & $2.39_{-0.39}^{+0.39}$ \\
+\hline
+    \end{tabular} 
+\end{table}
+
+We find that the use of a projected mis-centering model increases the
+errorbars on the predicted confidence intervals for the projected
+cross-correlation signal by $\sim 25$\%. However, the effect is barely
+noticeable in the three-dimensional profiles.  The inclusion of
+mis-centering is reflected as a small increase in the inferred errors
+of the projected and three-dimensional splashback radii as seen in
+Table~\ref{tab:mis_splash}. Although we notice shifts in the inferred
+central values of the splashback radii, none of these shifts appear
+systematic or significant given the errors.
 
@@
 the fitting parameters corresponding to the functional
-form in Equation~\ref{eq:full}. We cross-correlated PSZ2 galaxy clusters with
-galaxies form the PS 21 galaxy catalog to establish this figure.}
+form in Equation~\ref{eq:full} for the PS 21 sample. 
+}
    \label{fig:corner_21} 
@@
 the fitting parameters corresponding to the functional
-form in Equation~\ref{eq:full}. We cross-correlated PSZ2 galaxy clusters with
-galaxies form the PS 21.5 galaxy catalog to establish this figure.}
+form in Equation~\ref{eq:full} for the PS 21.5 sample.
+}
    \label{fig:corner_21.5} 
@@
 \caption{The two-dimensional posterior distributions of each pair of
-the fitting parameters corresponding to the functional
-form in Equation~\ref{eq:full}. We cross-correlated PSZ2 galaxy clusters with
-galaxies form the PS 22 galaxy catalog to establish this figure.}
+the fitting parameters corresponding to the functional form in
+Equation~\ref{eq:full} for the PS 22 sample.}
    \label{fig:corner_22} 
@@
 \caption{The two-dimensional posterior distributions of each pair of
-the fitting parameters corresponding to the functional
-form in Equation~\ref{eq:full}. We cross-correlated PSZ2 galaxy clusters with
-galaxies form the PS 21.5 galaxy catalog. Only the galaxies labeled
-as red were used.}
+the fitting parameters corresponding to the functional form in
+Equation~\ref{eq:full} for the PS 21 sample, where we restricted our
+cross-correlatoin analysis to the red galaxy population.
+}
    \label{fig:cornerred} 
@@
 \caption{The two-dimensional posterior distributions of each pair of
-the fitting parameters corresponding to the functional
-form in Equation~\ref{eq:full}. We cross-correlated PSZ2 galaxy clusters with
-galaxies form the PS 21 galaxy catalog. Only the galaxies labeled as
-blue were used.}
+the fitting parameters corresponding to the functional form in
+Equation~\ref{eq:full} for the PS 21 sample, where we restricted our
+cross-correlatoin analysis to the blue galaxy population. 
+}
    \label{fig:cornerblue} 
@@
 
+\section{Estimating the contamination of the blue galaxy population}
+\label{sec:Errors}
+{\bf Add figures to this appendix}.
+
+To infer the color cut to separate star forming galaxies from the
+quenched galaxy population, we cross-matched the SDSS spectroscopic
+sample to its Pan-STARRS photometry. In Figure~\ref{xx}, we show the
+plot of the Pan-STARRS $(g-r)$ color as a function of redshift, and
+the color cut we use in our analysis. The SDSS spectroscopic sample is
+however quite shallow, and thus consists of galaxies that are brighter
+than the Pan-STARRS galaxies that we wish to cross-correlate. At
+fainter magnitudes, we can expect photometric errors to scatter red
+galaxies into the blue population, potentially contaminating the
+correlation function measurement. This could erroneously cause for the
+splashback feature observed in the blue population. Therefore, we
+need to assess the possiblity of such a contamination.
+
+In Figure~\ref{}, we show the photometric errors of the Pan-STARRS
+galaxies as a function of magnitude in each of the bands we use. The
+galaxies that we use in our cross-correlation for the red/blue
+analysis have an absolute magnitude of $M_{i}-5\log h=-18.94$. This
+corresponds to a different apparent magnitude limit at each redshift.
+For each spectroscopically matched galaxy, we figure out how faint the
+apparent magnitude limit in the $i$ band is compared to the actual
+apparent magnitude of the galaxy. We assume that the populations of
+galaxies that we use to cross-correlate with clusters have the same
+intrinsic colors, but are just fainter. This gives us the true
+intrinsic magnitude of the galaxies that we cross-correlate in the
+$g$ and the $r$ band. We perturb these magnitudes by the expected
+errors at that magnitude as seen in Figure~\ref{}.
+
+Next, we compute the fraction of galaxies which were intrinsically red
+that now enter the blue population as defined using the same color
+cut, but based on the perturbed magnitudes as a result of photometric
+errors. We find such contamination of intrinsically red galaxies to
+the blue population to be about 5 percent. This value would apply in
+the field. Given that the red fraction is higher in clusters ($\sim
+60$ percent in the whole cluster) than in the field ($\sim 40$ percent),
+we expect there to be a larger proportion of red galaxies which could
+potentially contaminate the blue galaxies due to photometric errors.
+This would roughly double the contamination to be about 10 percent.
+
+This is a conservative estimate of the contamination, because the
+spectroscopic galaxy sample we use has a large incompleteness at the
+blue end at redshifts beyond $0.2$, where SDSS targetted the luminous
+red galaxy population. Thus we are missing a lot of the blue galaxy
+population in the highest redshift bins in our spectroscopic sample.
+Nevertheless we estimate what a roughly 10 percent contamination would
+mean for the cross-correlation signal found for the blue galaxies.
+
+% \begin{figure}
+% \centering{
+%     \includegraphics[scale=0.6]{errors.pdf}}
+% \caption{Histograms of the photometric errors in the used $i_{PS}, g_{PS}, r_{PS}$ bands.
+% The errors were taken dirrectly from the Pan-STARRS survey and sampled for galaxy type 
+% objects in the magniude range $15.0 \leq i_{PS} \leq 21.5$, $16.3 \leq g_{PS} \leq 22.8$ and $15.4 \leq r_{PS} \leq 21.9$, respectively. 
+% The upper photometric error limits at $3\sigma$
+% confidence are listed in the upper right of the figure.}
+%     \label{fig:photoerrors}•
+% \end{figure}
+
+The null hypothesis that we would like to establish or rule out is
+that the blue galaxies just consist of the infall population and show
+no splashback feature. We assume a simple $r^{-1.5}$ power law for the
+cross-correlation of the blue population with clusters consistent with
+an infalling population, and the inferred 3d cross-correlation
+function of the red galaxy population from our analysis.  Given these
+cross-correlation functions we can estimate the cross-correlation of
+the blue population when contaminated with a given amount of red
+galaxies. We find that in order to reproduce the observed
+cross-correlation function of blue galaxies, we need a contamination
+of about 20\%. While our conservatively estimated contamination is
+smaller than this value, a proper modeling of this contamination is
+warranted before definitive conclusions can be drawn. Larger galaxy
+surveys with better photometry such as the HSC or LSST would be of
+significant help in alleviating these issues.
+
+% \begin{figure}
+% \centering{
+%     \includegraphics[scale=0.6]{best_hist_58.pdf}}
+% \caption{Histogram of the $g_{PS} - r_{PS}$ colors of the galaxies in a certain redshift bin for illustration
+% of the contamination estimation. The solid, colored curves indicate the initially fitted Gaussian distributions,
+% whereas the dashed curves represent the Gaussian distributions broadened by the photometric errors of the Pan-STARRS
+% survey. The black, vertical line indicates the cut, separating the two galaxy populations as inferred from the original
+% distributions. The cut excludes red galaxies from being characterized as blue galaxies at $3/sigma$ confidence.}
+%     \label{fig:histogram}•
+% \end{figure}
+
 \label{lastpage}

### 2018-11-15 Paper_new/RSP_paper_new.tex
minor edits

@@
 $^{2}$Department of Physics, ETH Zurich, Wolfgang Pauli Strasse 27, 8093 Zurich, Switzerland\\
-$^{4}$The Inter-University Centre for Astronomy and Astrophysics, Post Bag 4, Ganeshkhind, Pune 411007, India
+$^{3}$The Inter-University Centre for Astronomy and Astrophysics, Post Bag 4, Ganeshkhind, Pune 411007, India
 }

### 2018-11-15 Paper_new/RSP_paper_new.tex
Added graphs in appendix and made some changes to appendix D

@@
 \label{sec:Errors}
-{\bf Add figures to this appendix}.
-
-To infer the color cut to separate star forming galaxies from the
-quenched galaxy population, we cross-matched the SDSS spectroscopic
-sample to its Pan-STARRS photometry. In Figure~\ref{xx}, we show the
-plot of the Pan-STARRS $(g-r)$ color as a function of redshift, and
-the color cut we use in our analysis. The SDSS spectroscopic sample is
-however quite shallow, and thus consists of galaxies that are brighter
-than the Pan-STARRS galaxies that we wish to cross-correlate. At
-fainter magnitudes, we can expect photometric errors to scatter red
-galaxies into the blue population, potentially contaminating the
-correlation function measurement. This could erroneously cause for the
+
+\begin{figure*}
+    \includegraphics[width= \textwidth]{color_vs_z.pdf}
+\caption{Scatter plot showing the $(g_{\mathrm{PS}}-r_{\mathrm{PS}})$ colors
+of the matched galaxies versus their redshifts, where the red dots correspond
+to galaxies identified as red from the SDSS spectroscopic colors and blue dots
+correspond to galaxies identified as blue, respectively. The black, solid line
+indicates the spline cut separating the two populations and excluding the red 
+galaxies from the blue population at a confidence level of $3 \sigma$.}
+   \label{fig:g-r_vs_z} 
+\end{figure*}
+
+To infer the color cut which separates star forming (blue) galaxies from the
+quenched (red) galaxy population, we cross-matched the SDSS spectroscopic
+sample to its Pan-STARRS photometry. In Figure~\ref{fig:g-r_vs_z}, we show the
+plot of the Pan-STARRS $(g_{\mathrm{PS}}-r_{\mathrm{PS}})$ color as a 
+function of redshift, and the color cut we use in our analysis. 
+The SDSS spectroscopic sample is however quite shallow, 
+and thus consists of galaxies that are brighter than the Pan-STARRS 
+galaxies that we wish to cross-correlate. At fainter magnitudes, we can 
+expect red galaxies to scatter into the blue population 
+due to photometric errors, potentially contaminating the
+correlation function measurement. This could erroneously cause the
 splashback feature observed in the blue population. Therefore, we
@@
 
-In Figure~\ref{}, we show the photometric errors of the Pan-STARRS
+\begin{figure*}
+    \includegraphics[width= \textwidth]{mag_errors.pdf}
+\caption{Shown are the photometric errors of the Pan-STARRS galaxies versus
+their magnitude in each of the used band. The dashed curves indicate the running
+median of the photometric error.}
+   \label{fig:mag_errors} 
+\end{figure*}
+
+In Figure~\ref{fig:mag_errors}, we show the photometric errors of the Pan-STARRS
 galaxies as a function of magnitude in each of the bands we use. The
-galaxies that we use in our cross-correlation for the red/blue
-analysis have an absolute magnitude of $M_{i}-5\log h=-18.94$. This
+galaxies that we use in our cross-correlation analysis for the red/blue
+galaxy population have an upper absolute magnitude limit of $M_{i}-5\log h=-18.94$. This
 corresponds to a different apparent magnitude limit at each redshift.
 For each spectroscopically matched galaxy, we figure out how faint the
-apparent magnitude limit in the $i$ band is compared to the actual
-apparent magnitude of the galaxy. We assume that the populations of
+apparent magnitude limit in the $i_{\mathrm{PS}}$ band is compared to the actual
+apparent magnitude of the galaxy, recorded by Pan-STARRS. Aassume that the populations of
 galaxies that we use to cross-correlate with clusters have the same
-intrinsic colors, but are just fainter. This gives us the true
+intrinsic colors, but are just fainter we infer the true
 intrinsic magnitude of the galaxies that we cross-correlate in the
-$g$ and the $r$ band. We perturb these magnitudes by the expected
-errors at that magnitude as seen in Figure~\ref{}.
+$g_{\mathrm{PS}}$ and the $r_{\mathrm{PS}}$ band. We randomly perturb these magnitudes 
+by the expected photmometric errors at that magnitude as reported in Figure~\ref{fig:mag_errors}.
 
 Next, we compute the fraction of galaxies which were intrinsically red
-that now enter the blue population as defined using the same color
-cut, but based on the perturbed magnitudes as a result of photometric
-errors. We find such contamination of intrinsically red galaxies to
-the blue population to be about 5 percent. This value would apply in
-the field. Given that the red fraction is higher in clusters ($\sim
-60$ percent in the whole cluster) than in the field ($\sim 40$ percent),
+that now entered the blue population by the perturbation. Where we
+defined the separation of the populations using the same color
+cut. We find such a contamination of intrinsically red galaxies to
+the blue population to be about 5 \%. This value would apply for a galaxy population
+measured in the field. Given that the red fraction is higher in clusters ($\sim
+60$ \% in the whole cluster) than in the field ($\sim 40$ \%),
 we expect there to be a larger proportion of red galaxies which could
 potentially contaminate the blue galaxies due to photometric errors.
-This would roughly double the contamination to be about 10 percent.
+This would roughly double the contamination to be about 10 \%.
 
@@
 blue end at redshifts beyond $0.2$, where SDSS targetted the luminous
-red galaxy population. Thus we are missing a lot of the blue galaxy
+red galaxy population, recording only very few blue galaxies. 
+Thus we are missing a lot of the blue galaxy
 population in the highest redshift bins in our spectroscopic sample.
-Nevertheless we estimate what a roughly 10 percent contamination would
-mean for the cross-correlation signal found for the blue galaxies.
+Nevertheless we estimate if a $\sim 10$ \% contamination could
+cause the splashback signal found in the cross-correlation for the blue galaxies.
 
@@
 no splashback feature. We assume a simple $r^{-1.5}$ power law for the
-cross-correlation of the blue population with clusters consistent with
-an infalling population, and the inferred 3d cross-correlation
-function of the red galaxy population from our analysis.  Given these
+3D cross-correlation of the blue population consistent for clusters with
+an infalling population, and a 3D cross-correlation equal to the signal
+found for the red galaxy population in our analysis. Given these
 cross-correlation functions we can estimate the cross-correlation of
 the blue population when contaminated with a given amount of red
-galaxies. We find that in order to reproduce the observed
-cross-correlation function of blue galaxies, we need a contamination
+galaxies, by considering a weighted sum of the two signals. 
+We find that in order to reproduce the observed
+cross-correlation function of the blue galaxies, we need a contamination
 of about 20\%. While our conservatively estimated contamination is

### 2018-11-15 Paper_new/RSP_paper_new.tex
Minor changes in appendix

@@
 apparent magnitude limit in the $i_{\mathrm{PS}}$ band is compared to the actual
-apparent magnitude of the galaxy, recorded by Pan-STARRS. Aassume that the populations of
+apparent magnitude of the galaxy, recorded by Pan-STARRS. Assuming that the populations of
 galaxies that we use to cross-correlate with clusters have the same
-intrinsic colors, but are just fainter we infer the true
+intrinsic colors, but are just fainter, we infer the true
 intrinsic magnitude of the galaxies that we cross-correlate in the
 $g_{\mathrm{PS}}$ and the $r_{\mathrm{PS}}$ band. We randomly perturb these magnitudes 
-by the expected photmometric errors at that magnitude as reported in Figure~\ref{fig:mag_errors}.
+by the expected photometric errors at that magnitude as reported in Figure~\ref{fig:mag_errors}.
 
 Next, we compute the fraction of galaxies which were intrinsically red
-that now entered the blue population by the perturbation. Where we
+that now entered the blue population by the perturbation, where we
 defined the separation of the populations using the same color
@@
 60$ \% in the whole cluster) than in the field ($\sim 40$ \%),
-we expect there to be a larger proportion of red galaxies which could
+we expect there to be a larger proportion of red galaxies in the cluster which could
 potentially contaminate the blue galaxies due to photometric errors.
@@
 population in the highest redshift bins in our spectroscopic sample.
-Nevertheless we estimate if a $\sim 10$ \% contamination could
+Nevertheless we assess if a $\sim 10$ \% contamination could
 cause the splashback signal found in the cross-correlation for the blue galaxies.

### 2018-11-15 Paper_new/RSP_paper_new.tex
minor edits

@@
 for the steepening of the dark matter density profile, and therefore
-the splashback radius of this sample of galaxy clusters (further
+the splashback radius of this sample of galaxy clusters. This was 
 corroborated by including further models for mis-centering by
 \citet{baxter2017halo} and in the Dark Energy Survey data by
-\citet{chang2017splashback}). Somewhat surprisingly,
-\citet{more2016detection} found that the location of the splashback
-radius was inconsistent with that expected from numerical
-simulations of dark matter by about $20\pm5$\%. Although they
+\citet{chang2017splashback} using optically selected clusters. Somewhat surprisingly,
+\citet{more2016detection} found that the location of the splashback radius was
+inconsistent with that expected from numerical simulations of dark matter by
+about $20\pm5$\% (see also \citet{baxter2017halo, chang2017splashback}).
+Although they
 investigated potential systematic issues, they did not have access

### 2018-11-15 Paper_new/RSP_paper_new.tex
Added planck figure and downsized color vs z
some more minor edits

@@
 in the weak lensing signal, but their analysis was again done using
-optically selected clusters in the Dark energy survey
-\citep{dark2005dark}. Regardless of the projection issues present in
-the optical cluster catalog, there is some inherent circularity
-present in the logic of using photometric galaxies to select
-clusters as over-densities in a given aperture, and then using the
-same photometric sample of galaxies to look for the splashback
-radius. There is a possibility that the aperture used to select the
-cluster catalogs could be imprinted in a non-trivial way on the measured number
-density profiles of clusters.
+optically selected clusters in the Dark energy survey. Regardless of the
+projection issues present in the optical cluster catalog, there is some
+inherent circularity present in the logic of using photometric galaxies to
+select clusters as over-densities in a given aperture, and then using the same
+photometric sample of galaxies to look for the splashback radius. There is a
+possibility that the aperture used to select the cluster catalogs could be
+imprinted in a non-trivial way on the measured number density profiles of
+clusters.
 
@@
 \label{sec:clusters}
+
+\begin{figure}
+    \includegraphics[scale=0.55]{Planck_summary.pdf}
+\caption{The distribution of the masses and redshifts of the galaxy clusters
+from the PSZ2 catalog that we use in our analysis. The histograms on the right
+hand side and the bottom show the distribution in mass and redshift,
+respectively.}
+   \label{fig:planck_summary}
+\end{figure}
+
 The baryonic component of a galaxy cluster is dominated by the hot,
@@
 
-We restrict ourselves to the redshift range $0.03 \leq z \leq 0.33$ in
-order to have a similar redshift range used in
-\citet{more2016detection}. Due to the larger beam size of the Planck
+We restrict ourselves to the redshift range $0.03 \leq z \leq 0.33$ in order to
+have a similar redshift range used in \citet{more2016detection}. The mass and
+the redshift distribution of the Planck clusters we use is shown in
+Fig.~\ref{fig:planck_summary}. Due to the larger beam size of the Planck
 satellite, the cluster positions as reported in the catalog may be
@@
     \centering
-    \caption{We list our findings for the fitting parameters obtained from cross-correlating the galaxy cluster sample with the different galaxy catalogs.
+    \caption{The table presents the posterior distribution of the parameters obtained from fitting the cross-correlation of the galaxy cluster sample with the different galaxy catalogs.
 For each parameter estimate the median as well as the 16\% and 84\% quantiles of the posterior distribution are given.
-We also list the estimated locations of the steepening feature in the two-dimensional cross-correlation signal ($R_{\mathrm{sp}}^{\mathrm{2D}}$) as well as the three-dimensional splashback radius ($r_{\mathrm{sp}}^{\mathrm{3D}}$).
-In the last column the minimal, reduced $\chi^2$ value of the model fit is indicated.
+We also list the estimated locations of the steepening feature in the two-dimensional cross-correlation signal ($R_{\mathrm{sp}}^{\mathrm{2D}}$), as well as the three-dimensional splashback radius ($r_{\mathrm{sp}}^{\mathrm{3D}}$).
+In the last column the minimum, reduced $\chi^2$ value of the model fit is indicated.
 The two-dimensional posterior distributions of the fitting parameters are displayed in
@@
   \includegraphics[scale=0.8]{derivatives_with_spline_no_mc.pdf}}
-\caption{We show the distributions of the logarithmic derivatives of
+\caption{The distributions of the logarithmic derivatives of
 the three-dimensional cross-correlation signals at the location of
-the splashback radius. In the left panel the distributions of the
+the splashback radius are shown. In the left panel the distributions of the
 derivatives of the full profiles are shown, whereas only the inner
 halo term (namely $\rho_{\mathrm{in}}f_{\mathrm{trans}}$) is
-considered in the right panel.}
+shown in the right panel.}
    \label{fig:derivatives} 
@@
     \includegraphics[scale=0.8]{splashback_with_spline_no_mc.pdf}}
-\caption{Shown are the posterior distributions of the inferred
+\caption{The posterior distributions of the inferred
 locations of steepest slope of the two- and three dimensional
-cross-correlation signals. On the left side the distributions of the
+cross-correlation signals. The distributions of the
 locations of the two-dimensional steepening feature
-($R_{\mathrm{sp}}^{\mathrm{2D}}$) are shown, whereas the
+($R_{\mathrm{sp}}^{\mathrm{2D}}$) are shown in the left panel, while the
 distributions of the three-dimensional counterparts
@@
 \label{sec:mis-centering}
-As can be seen for the analysis and results in \citet{baxter2017halo},
+As can be seen from the analysis and results in \citet{baxter2017halo},
 the mis-centering of the central cluster positions in optical clusters
@@
 \begin{figure*}
-    \includegraphics[width= \textwidth]{color_vs_z.pdf}
+    \includegraphics[width= 0.5\textwidth]{color_vs_z.pdf}
 \caption{Scatter plot showing the $(g_{\mathrm{PS}}-r_{\mathrm{PS}})$ colors
@@
 \begin{figure*}
+\centering{
     \includegraphics[width= \textwidth]{mag_errors.pdf}
@@
    \label{fig:mag_errors} 
+}
 \end{figure*}

### 2018-11-15 Paper_new/RSP_paper_new.tex
Dominiks changes

--- 2018-11-15 Paper_new/RSP_paper_new.tex
@@
 cluster-galaxy cross-correlations separately for star forming and
-quenched galaxy populations separated by color.
+quenched galaxy populations as separated by their color.
 
@@
 directions. Throughout the paper, we use a flat $\Lambda$CDM cosmology
-with $\Omega_{\rm m}=0.27$ to convert redshifts and angles into
+with $\Omega_{\rm m}=0.27$ and a dimensionless Hubble parameter of $h=0.7$ 
+to convert redshifts and angles into
 cosmological distances. Also, we denote three-dimensional distances by
@@
 \label{sec:clusters}
+
+\begin{figure}
+    \includegraphics[scale=0.55]{Planck_summary.pdf}
+\caption{Visualization of the distribution of the masses and redshifts of the used
+clusters from the PSZ2 catalog.}
+   \label{fig:placnk_summary}
+\end{figure}
+
 The baryonic component of a galaxy cluster is dominated by the hot,
@@
 We restrict ourselves to the redshift range $0.03 \leq z \leq 0.33$ in
-order to have a similar redshift range used in
+order to have a similar redshift range as used in
 \citet{more2016detection}. Due to the larger beam size of the Planck
@@
 the main properties of the cluster catalog used in this work to that
-used by \citet{more2016detection}. A map of the sky positions of the clusters
+used by \citet{more2016detection}. Additionaly, Figure~\ref{fig:placnk_summary}
+visualizes the distribution of the masses and redshifts of the used clusters.
+A map of the sky positions of the clusters
 can be found in Figure~\ref{fig:planck_fig} in
@@
 In order to compute the color cut to be used, we first match spectroscopic
-galaxies in the Sloan digital Sky Survey (DR 13) to their
+galaxies in the Sloan Digital Sky Survey (DR 8) to their
 Pan-STARRS photometry. We bin these galaxies in narrow redshift bins and
@@
 galaxies. We would therefore exercise appropriate caution while interpreting
-the results obtained by dividing galaxies in to color bins.
+the results obtained by dividing galaxies into color bins.
 
@@
 \citep[cf.][]{baxter2017halo}. We will study the cross-correlations to derive
-the splashback radii for these galaxy populations separately, as well as the
-fractional contributions of the red and the blue galaxies to the total density
-profile as a function of radius. The caveats in the interpretation of these
+the splashback radii for these galaxy populations separately. 
+The caveats in the interpretation of these
 results are mentioned in the Appendix~\ref{sec:Errors}.
@@
 their first and second order derivative profiles. The light-colored 
-curves show the corresponding first and second derivatives of the one-halo
-term (namely $\rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r)$ in Equation~\ref{eq:dk14})
+curves show the corresponding first and second order derivatives of the one-halo
+term (namely $\rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r)$ in Equation~\ref{eq:dk14}).
 Here, the black, dashed lines indicate upper and lower bounds of the 
@@
 Following \citet{baxter2017halo}, we also present the values of the
-logarithmic derivatives at the location of the steepest slope for
+first and second order logarithmic derivatives at the location of the steepest slope for
 the total three-dimensional cross-correlations, as well as those for
-the inner halo term in the left and right hand panels of
+the inner halo term in the middle and right hand panels of
 Figure~\ref{fig:derivatives}, respectively. The logarithmic slope of the 
@@
 evidence for the existence of the splashback feature. From the second
-derivative profiles we also note that the drop in the cross-correlation
+order derivative profiles we also note that the drop in the cross-correlation
 signal is very sharp and happens within a factor 2 in radius.
@@
 
-Next we present our measurements of the projected and
+Next, we present our measurements of the projected and
 three-dimensional cross-correlations of the red and blue galaxy populations
@@
 photometric errors increase dramatically and can scatter many more of
-the red galaxy population into the blue galaxy sample. We report on
+the red galaxies into the blue galaxy sample. We report on
 our investigations in Appendix~\ref{sec:Errors} as a cautionary tale,
@@
 be warranted in the interpretation or use of the results derived using
-the color separated galaxy populations.
+the color-separated galaxy populations.
 
@@
 Section~\ref{sec:Color} is prone to photometric errors as explored in
-the Appendix. A deeper galaxy catalog would be required in order to
+ Appendix~\ref{sec:Errors}. A deeper galaxy catalog would be required in order to
 confirm or rule out the existence of the splashback feature in the
@@
     \includegraphics[width= \textwidth]{color_vs_z.pdf}
-\caption{Scatter plot showing the $(g_{\mathrm{PS}}-r_{\mathrm{PS}})$ colors
+\caption{Scatter plot showing the $(g_{\mathrm{P1}}-r_{\mathrm{P1}})$ colors
 of the matched galaxies versus their redshifts, where the red dots correspond
@@
 sample to its Pan-STARRS photometry. In Figure~\ref{fig:g-r_vs_z}, we show the
-plot of the Pan-STARRS $(g_{\mathrm{PS}}-r_{\mathrm{PS}})$ color as a 
+plot of the Pan-STARRS $(g_{\mathrm{P1}}-r_{\mathrm{P1}})$ color as a 
 function of redshift, and the color cut we use in our analysis. 
@@
 For each spectroscopically matched galaxy, we figure out how faint the
-apparent magnitude limit in the $i_{\mathrm{PS}}$ band is compared to the actual
+apparent magnitude limit in the $i_{\mathrm{P1}}$ band is compared to the actual
 apparent magnitude of the galaxy, recorded by Pan-STARRS. Assuming that the populations of
@@
 intrinsic magnitude of the galaxies that we cross-correlate in the
-$g_{\mathrm{PS}}$ and the $r_{\mathrm{PS}}$ band. We randomly perturb these magnitudes 
+$g_{\mathrm{P1}}$ and the $r_{\mathrm{P1}}$ band. We randomly perturb these magnitudes 
 by the expected photometric errors at that magnitude as reported in Figure~\ref{fig:mag_errors}.
@@
 cut. We find such a contamination of intrinsically red galaxies to
-the blue population to be about 5 \%. This value would apply for a galaxy population
+the blue population to be about 5\%. This value would apply for a galaxy population
 measured in the field. Given that the red fraction is higher in clusters ($\sim
-60$ \% in the whole cluster) than in the field ($\sim 40$ \%),
+60$\% in the whole cluster) than in the field ($\sim 40$\%),
 we expect there to be a larger proportion of red galaxies in the cluster which could
 potentially contaminate the blue galaxies due to photometric errors.
-This would roughly double the contamination to be about 10 \%.
+This would roughly double the contamination to be about 10\%.
 
@@
 population in the highest redshift bins in our spectroscopic sample.
-Nevertheless we assess if a $\sim 10$ \% contamination could
+Nevertheless we assess if a $\sim 10$\% contamination could
 cause the splashback signal found in the cross-correlation for the blue galaxies.

### 2018-11-15 Paper_new/RSP_paper_new.tex

@@
     \includegraphics[scale=0.55]{Planck_summary.pdf}
-\caption{Visualization of the distribution of the masses and redshifts of the used
-clusters from the PSZ2 catalog.}
-   \label{fig:placnk_summary}
+\caption{The distribution of the masses and redshifts of the galaxy clusters
+from the PSZ2 catalog that we use in our analysis. The histograms on the right
+hand side and the bottom show the distribution in mass and redshift,
+respectively.}
+   \label{fig:planck_summary}
 \end{figure}
@@
 
-We restrict ourselves to the redshift range $0.03 \leq z \leq 0.33$ in
-order to have a similar redshift range as used in
-\citet{more2016detection}. Due to the larger beam size of the Planck
+We restrict ourselves to the redshift range $0.03 \leq z \leq 0.33$ in order to
+have a similar redshift range used in \citet{more2016detection}. The mass and
+the redshift distribution of the Planck clusters we use is shown in
+Fig.~\ref{fig:planck_summary}. Due to the larger beam size of the Planck
 satellite, the cluster positions as reported in the catalog may be
@@
 \begin{figure*}
+
     \includegraphics[width= \textwidth]{color_vs_z.pdf}

### 2018-11-15 Paper_new/RSP_paper_new.tex
minor edits

--- 2018-11-15 Paper_new/RSP_paper_new.tex
@@
 galaxy populations divided by color. The presence of the splashback
-radius in the star-forming galaxy population could potentially be used
-to put lower limits on the quenching timescales for galaxies. However,
-these results need further verification with deeper datasets, as
-photometric errors could cause contamination of the star-forming
-galaxy sample by quenched galaxies.
+radius in the star-forming galaxy population could potentially be used to put
+lower limits on the quenching timescales for galaxies. We can marginally rule
+out the contamination of the star-forming galaxy sample by quenched galaxies,
+but the results would need further verification with deeper datasets.
 
@@
 location, under the assumption that the BCG is located at the true,
-gravitational center. Due to this crude assumption, we additionally 
+gravitational center. Due to this assumption, we additionally 
 study the effects of a possible, remaining mis-centering of the 
@@
 in this paper has an average redshift of 0.177, and an average
-cluster mass $M_{500c}$ of about $3.0 \cdot 10^{14}
+cluster mass $M_{500c}$ of about $3.0 \times 10^{14}
 h^{-1}$M$_{\sun}$. In Table~\ref{tab:cluster_catalogs} we compare
@@
 make the assumption that the galaxies reside at the redshift of the
-cluster in question. The used magnitude limits are (-19.44, -18.94
-and -18.44) for the catalogs PS 21, PS 21.5 and PS 22, respectively.
+cluster in question. The magnitude limits we use are -19.44, -18.94 and -18.44
+and name the corresponding catalogs PS 21, PS 21.5 and PS 22, respectively.
 
@@
 \citep[cf.][]{baxter2017halo}. We will study the cross-correlations to derive
-the splashback radii for these galaxy populations separately, as well as the
-fractional contributions of the red and the blue galaxies to the total density
-profile as a function of radius. The caveats in the interpretation of these
-results are mentioned in the Appendix~\ref{sec:Errors}.
+the splashback radii for these galaxy populations separately. The caveats in
+the interpretation of these results due to photometric errors are discussed in the
+Appendix~\ref{sec:Errors}.
 
@@
 magnitude limit is changed, even though we use a sample which is one
-magnitude brighter than $M_{\rm i}-5\log h=-19.44$. The 68\%
+magnitude fainter than $M_{\rm i}-5\log h=-19.44$. The 68\%
 confidence interval of the location of the steepest slope is
@@
 blue galaxy population. We show that given the current state of the
-data we cannot exclude a contamination of the correlation function of
-blue galaxies from the red galaxy population and appropriate caution
-be warranted in the interpretation or use of the results derived using
-the color separated galaxy populations.
+data we can marginally exclude a contamination of the correlation
+function of blue galaxies from the red galaxy population but
+appropriate caution is warranted in the interpretation or use of the
+results derived using the color separated galaxy populations.
 
@@
 Section~\ref{sec:Color} is prone to photometric errors as explored in
-the Appendix. A deeper galaxy catalog would be required in order to
+the Appendix~\ref{sec:Errors}. A deeper galaxy catalog would be required in order to
 confirm or rule out the existence of the splashback feature in the
@@
 \begin{figure*}
-    \includegraphics[width= 0.5\textwidth]{color_vs_z.pdf}
+\centering{
+    \includegraphics[width= 0.5\textwidth]{color_vs_z.pdf}}
 \caption{Scatter plot showing the $(g_{\mathrm{PS}}-r_{\mathrm{PS}})$ colors
@@
 \centering{
-    \includegraphics[width= \textwidth]{mag_errors.pdf}
+    \includegraphics[width= \textwidth]{mag_errors.png}
 \caption{Shown are the photometric errors of the Pan-STARRS galaxies versus

### 2018-11-15 Paper_new/RSP_paper_new.tex

--- 2018-11-15 Paper_new/RSP_paper_new.tex
@@
 \citep[cf.][]{baxter2017halo}. We will study the cross-correlations to derive
-the splashback radii for these galaxy populations separately. 
-The caveats in the interpretation of these
-results are mentioned in the Appendix~\ref{sec:Errors}.
+the splashback radii for these galaxy populations separately. The caveats in
+the interpretation of these results due to photometric errors are discussed in the
+Appendix~\ref{sec:Errors}.
 
@@
 blue galaxy population. We show that given the current state of the
-data we cannot exclude a contamination of the correlation function of
-blue galaxies from the red galaxy population and appropriate caution
-be warranted in the interpretation or use of the results derived using
-the color-separated galaxy populations.
+data we can marginally exclude a contamination of the correlation
+function of blue galaxies from the red galaxy population but
+appropriate caution is warranted in the interpretation or use of the
+results derived using the color separated galaxy populations.
 
@@
 Section~\ref{sec:Color} is prone to photometric errors as explored in
- Appendix~\ref{sec:Errors}. A deeper galaxy catalog would be required in order to
+the Appendix~\ref{sec:Errors}. A deeper galaxy catalog would be required in order to
 confirm or rule out the existence of the splashback feature in the
@@
 \begin{figure*}
-
+\centering{
     \includegraphics[width= \textwidth]{color_vs_z.pdf}

### 2018-11-15 Paper_new/RSP_paper_new.tex
more changes

@@
 \documentclass[iop, apjl, twocolappendix, numberedappendix]{emulateapj}
-%\usepackage{newtxtext,newtxmath}
 \usepackage[T1]{fontenc}
-%\usepackage{ae,aecompl}
 \usepackage{float}
@@
 \usepackage[colorlinks=true,urlcolor=blue,linkcolor=blue,citecolor=blue]{hyperref}
-%\usepackage{nccmath}
 \usepackage[utf8]{inputenc}
@@
 
+\thanks{This work was submitted and defended as a Masters thesis by Dominik
+Zuercher at the DPHYS in ETH Zurich in June 2018.}
+
 \author{
-Dominik Zürcher \altaffilmark{1, 2}
+Dominik Zürcher \altaffilmark{1, 2, 4}
 Surhud More \altaffilmark{3, 1}, 
@@
 $^{2}$Department of Physics, ETH Zurich, Wolfgang Pauli Strasse 27, 8093 Zurich, Switzerland\\
-$^{3}$The Inter-University Centre for Astronomy and Astrophysics, Post Bag 4, Ganeshkhind, Pune 411007, India
+$^{3}$The Inter-University Centre for Astronomy and Astrophysics, Post Bag 4, Ganeshkhind, Pune 411007, India\\
+$^{4}$ dominikz@phys.ethz.ch
 }
@@
 
-%\begin{keywords}
-%galaxies:clusters:general -- galaxies:halos -- methods:observational -- cosmology:dark matter -- cosmology:large-scale structure of Universe -- cosmology:observations
-%\end{keywords}
+% \begin{keywords}
+% galaxies:clusters:general -- galaxies:halos -- methods:observational -- cosmology:dark matter -- cosmology:large-scale structure of Universe -- cosmology:observations
+% \end{keywords}
 
@@
 the main properties of the cluster catalog used in this work to that
-used by \citet{more2016detection}. Additionaly, Figure~\ref{fig:placnk_summary}
+used by \citet{more2016detection}. Additionaly, Figure~\ref{fig:planck_summary}
 visualizes the distribution of the masses and redshifts of the used clusters.
@@
 \end{figure*}
-%\begin{figure}
-%    \includegraphics[width= \columnwidth]{color_fraction_with_spline_no_mc.pdf}
-%\caption{Fractional contributions of the red and blue galaxy
-%populations to the total galaxy number density. We show the
-%locations of the splashback radii associated with the two subsamples
-%with the colored, vertical bands and the upper and lower bounds of
-%the splashback radius obtained from the full PS 21.5 catalog with
-%the black, dashed lines.}
-%   \label{fig:color_fraction} 
-%\end{figure}
 The right panels in Figure~\ref{fig:2D_graphs} show the
@@
 
-% Star forming galaxies in models
-% which quench their star formation on a timescale shorter than the
-% orbital time scale are not expected to show presence of the splashback
-% feature. A quantitative exploration of the implications is beyond the
-% scope of this work, but will be followed up in the future.
-
-% In Figure~\ref{fig:color_fraction}, we show the fractional
-% contributions of the red and blue galaxies to the total,
-% three-dimensional cross-correlation \footnote{The fractions are
-% obtained by performing an appropriate number density weighting.}.
-% The red galaxies dominate the central parts of the galaxy clusters
-% but become less dominant as we move further away from the cluster center.
-% We see an increase of the fractional contribution of
-% red galaxies below the splashback radius. On scales larger than the
-% splashback radius, the fractional contributions of the two populations become
-% very similar.
-
 We caution however that the cut we use to define our samples was
@@
 
-% As it can be seen from Table~\ref{tab:snr}, the signal-to-noise
-% ratio of our measurement is lower when using the PS 22 catalog
-% compared to the other two estimates. This has two causes: Firstly,
-% the sky-coverage of the PS 22 catalog is $\approx$ 25\% lower than
-% for PS 21 and PS 21.5 since more regions had to be excluded due to
-% the survey depth being too low in those regions. Therefore, some
-% clusters from the PSZ2 catalog are missed when the PS 22 catalog is
-% exploited, which reduces the statistics. Secondly, as we consider
-% fainter galaxies, the contamination from background galaxies
-% increases. This requires a better estimate of the uncorrelated
-% background component. A more precise estimation of the uncorrelated
-% background contamination would be possible by using a random galaxy
-% catalog in addition to the random cluster sample. This would allow
-% to use the more sophisticated Landy \& Szalay estimator
-% \citep{landy1993bias} to perform the background subtraction.
-
-% Another approach to increase the statistics of the measurements would 
-% be to increase the redshift range in which clusters are being considered. 
-% We chose $0.03 \leq z \leq 0.33$ in order to keep the analysis comparable 
-% to \citet{more2016detection}. However, this cut reduces the cluster sample 
-% size. Increasing the redshift range has its own limitations, though. 
-% It would be required to use a brighter magnitude limit for galaxies, 
-% which reduces the number of galaxies that can be used to infer the 
-% cross-correlation signal. This results in a trade-off which could be investigated
-% to find the optimal redshift range. Alternatively, other cluster samples that do 
-% not rely on optical cluster finding such as Xray based surveys might 
-% serve as independent and larger cluster samples. 
-% Another plausible approach would be to consider a smaller region of
-% the sky, resulting in less clusters but with a deeper field of view,
-% such as in the case of the Hyper Suprime-Cam at Subaru Telescope,
-% which will survey $\approx 1400$ deg$^2$ of the sky and achieve a
-% depth of 26.2 magnitudes \citep{takada2010subaru}.
-
 The separation of the blue and red galaxy populations as described in
@@
 blue galaxy population. The ongoing deep galaxy surveys such as the
-Hyper Suprime-Cam (HSC) and the Dark Energy Survey (DES) would be able
+Hyper Suprime-Cam \citep{Aihara2018} and the Dark Energy Survey \citep{Abbott2018} would be able
 to provide such data sets, albeit in a limited area. The Large
-Synoptic Survey telescope (LSST) would eventually provide deep as well
+Synoptic Survey telescope \citep{LSST2009} would eventually provide deep as well
 as wide galaxy catalogs to eventually establish the locations of the
@@
 \centering{
-    \includegraphics[width= \textwidth]{color_vs_z.pdf}
+    \includegraphics[width= \textwidth]{color_vs_z.pdf}}
 \caption{Scatter plot showing the $(g_{\mathrm{P1}}-r_{\mathrm{P1}})$ colors

### 2018-12-13 Paper_v2/RSP_paper_new.tex
Adding second version of paper

--- 2018-11-15 Paper_new/RSP_paper_new.tex
@@
 optical cluster catalog in the context of halo assembly bias was 
-also demonstrated by \citet{zu2016level}.
-
-\citet{umetsu2017lensing} as well as \citet{contigiani2018weak}
-recently used Xray selected clusters to look for the splashback radius
-using the weak lensing signal, however stacking issues and the low
-signal-to-noise ratio remains a significant hurdle for both of them.
-\citet{chang2017splashback} found evidence for the splashback radius
-in the weak lensing signal, but their analysis was again done using
-optically selected clusters in the Dark energy survey. Regardless of the
+also demonstrated by \citet{zu2016level}. Regardless of the
 projection issues present in the optical cluster catalog, there is some
@@
 
-In this work, we move away from the optical cluster selection and
-explore the use of SZ selected cluster catalogs. While the SZ
+\textbf{Trying to avoid the problems which complicate the unbiased detction
+of the splashback signal in opical samples some recent studies searched
+for the signature of the splashback effect using non-optical cluster samples.}
+\citet{umetsu2017lensing} as well as \citet{contigiani2018weak}
+used Xray selected clusters to look for the splashback radius
+using the weak lensing signal, however stacking issues and the low
+signal-to-noise ratio remains a significant hurdle for both of them.
+Also \citet{chang2017splashback} found evidence for the splashback feature
+in the weak lensing signal, but their analysis was again done using
+optically selected clusters in the Dark energy survey suffering from 
+the before mentioned issus again.
+
+\textbf{In this work, we explore yet another non-optical cluster sample. 
+Namely, SZ selected clusters.} While the SZ
 selected clusters can also be susceptible to systematic selection
@@
 lensing signal, we perform our analysis using cross-correlation of
-galaxies with clusters.  The SDSS sample used by
-\citet{more2016detection} was deep enough such that biases in the
+galaxies with clusters.
+
+\textbf{Dynamcial friction is expected to decrease the observed splashback radius in 
+massive clusters. It causes a
+slow-down of the massive subhalos, hosting many of the observed galaxies, 
+which in return decreases the apocentric
+radius of their orbits and therefore the measured splashback radius of the host cluster. 
+Since the rate of dynamical friction scales
+with the mass of the moving object the effect is stronger for more
+massive subhalos. Therefore, one expects the decrease in the splashback
+radius to scale with the amount of massive subhalos in the host cluster and
+with its mass \citep{adhikari2016observing}. This bias can be limited by choosing a deep enough
+galaxy sample such that a large enough amount of low mass subhalos can be
+observed.} The SDSS sample used by
+\citet{more2016detection} was already deep enough such that biases in the
 location of the splashback radius due to dynamical friction effects
-were expected to be small.  Nevertheless, we use galaxy samples, which
+were expected to be small. 
+Nevertheless, we use galaxy samples, which
 are even fainter by $0.5-1$ magnitudes compared to those used by
@@
 \label{sec:clusters}
-
-\begin{figure}
-    \includegraphics[scale=0.55]{Planck_summary.pdf}
-\caption{The distribution of the masses and redshifts of the galaxy clusters
-from the PSZ2 catalog that we use in our analysis. The histograms on the right
-hand side and the bottom show the distribution in mass and redshift,
-respectively.}
-   \label{fig:planck_summary}
-\end{figure}
 
@@
     \hline 
-    eff. area [deg$^2$] & $\approx$ 10'000 & 21'148 & 20'586 & 15'689\\ 
-    \hline 
-    \# objects & 57'181'113 & 93'772'329 & 123'188'529 & 105'809'113 \\
+    eff. area [deg$^2$] & $\approx$ 10,000 & 21,148 & 20,586 & 15,689\\ 
+    \hline 
+    \# objects & 57,181,113 & 93,772,329 & 123,188,529 & 105,809,113 \\
     \hline
     objects/deg$^2$ & 5718 & 4434 & 5984 & 6744\\ 
-    \hline
-    \end{tabular} 
-\end{table*}
-\begin{table*}
-    \centering
-    \caption{Summary of the priors used in the MCMC sampling
-procedure. The MCMC chains are constrained using flat priors or
-normal priors on some of the fitting parameters. This table lists
-the ranges of the flat priors and the central positions as well as
-the scales of the normal priors ( format: center | scale ),
-respectively.}
-    \label{tab:priors}
-    \begin{tabular}{ccccccccc}
-    \hline 
-    & $\log_{10}(\rho_{\mathrm{s}})$ & $\log_{10}(\alpha)$ & $\log_{10}(r_{\mathrm{s}})$ & $\rho_0$ & $s_{\mathrm{e}}$ & $\log_{10}(r_{\mathrm{t}})$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ \\ 
-    \hline 
-    Prior Type & None & Normal & Flat & None & None & Flat & Normal & Normal\\ 
-    \hline 
-    Prior Range & - & $\log_{10}(0.2)| 1.2$ & [0.1,5.0] & - & - & [0.1,5.0] & $\log_{10}(6.0) | 0.4$ & $\log_{10}(4.0) | 0.4$ \\
     \hline
@@
 
-We restrict ourselves to the redshift range $0.03 \leq z \leq 0.33$ in order to
-have a similar redshift range used in \citet{more2016detection}. The mass and
-the redshift distribution of the Planck clusters we use is shown in
-Fig.~\ref{fig:planck_summary}. Due to the larger beam size of the Planck
+We restrict ourselves to the redshift range $0.03 \leq z \leq 0.33$ in 
+order to have a similar redshift range as used in \citet{more2016detection}. 
+Due to the larger beam size of the Planck
 satellite, the cluster positions as reported in the catalog may be
@@
 visualizes the distribution of the masses and redshifts of the used clusters.
-A map of the sky positions of the clusters
-can be found in Figure~\ref{fig:planck_fig} in
-Appendix~\ref{sec:figures}.
+A map of the sky positions of the clusters as well as a visualization of their redshift and mass distributions
+can be found in Appendix~\ref{sec:figures}.
 
@@
 HEALPix maps showing the excluded areas on the sky can be found in
-Figure~\ref{fig:heal_map}. We further disregard objects in bad
+Appendix~\ref{sec:figures}. We further disregard objects in bad
 pixel regions as indicated by the $i_{\mathrm{P1}}$ band
@@
 implemented in the parallel python package {\it emcee} by
-\citet{foreman2013emcee}. We adopt priors similar to
-\citet{more2016detection} on some of our parameters based on the
-expectations of their values from numerical simulations, but double
-the scales of the normal priors compared to their work (see
-Table~\ref{tab:priors}). The central value for the prior on $\alpha$
-is deduced from mass estimates \citep{gao2008redshift}, whereas the
-central values on the priors of $\beta$ and $\gamma$ were
-recommended by \citet{diemer2014dependence}.
-
-The splashback radius for halos on galaxy cluster scales is consistent
-with the location of the steepest logarithmic slope of the density
-profile. We estimate the steepest slope of both the two-dimensional
+\citet{foreman2013emcee}. 
+\textbf{We keep the parameters $\rho_{\mathrm{s}}$, $\rho_0$ and $s_{\mathrm{e}}$ 
+as free parameters during the fitting procedure. Similarly to \citet{more2016detection} 
+we put flat priors on $\log_{10}(r_{\mathrm{s}})$ and $\log_{10}(r_{\mathrm{t}})$ but double 
+their ranges to $[0.1,5.0]$ compared to their work. In contrast, 
+we use a normal prior with a central value of $\log_{10}(0.2)$ and a scale of 1.2 
+for $\log_{10}(\alpha)$ as deduced from mass estimates \citep{gao2008redshift}. 
+For the parameters $\log_{10}(\beta)$ and $\log_{10}(\gamma)$ we also use normal 
+priors with central values $\log_{10}(6.0)$ and $\log_{10}(4.0)$, respectively 
+and scale 0.4 as recommended by \citet{diemer2014dependence}.}
+
+\textbf{It has been a common concern that the profile in Equation~\ref{eq:model} might introduce
+a splashback feature simply by its functional from and without its presence in the data.
+However, \citet{baxter2017halo} showed that this is not the case by using a Bayesian odds 
+ratio approach to asses that the data is described significantly better by the general 
+profile in Equation~\ref{eq:model} (with the splashback feature)
+rather than by the same profile with fixed $f_{trans} = 1$ (without splashback feature).
+The same conclusion was made by \citet{umetsu2017lensing} who conducted a similar study but
+using weak lensing data.}
+%\begin{table*}
+%    \centering
+%    \caption{Summary of the priors used in the MCMC sampling
+%procedure. The MCMC chains are constrained using flat priors or
+%normal priors on some of the fitting parameters. This table lists
+%the ranges of the flat priors and the central positions as well as
+%the scales of the normal priors ( format: center | scale ),
+%respectively.}
+%    \label{tab:priors}
+%    \begin{tabular}{ccccccccc}
+%    \hline 
+%    & $\log_{10}(\rho_{\mathrm{s}})$ & $\log_{10}(\alpha)$ & $\log_{10}%(r_{\mathrm{s}})$ & $\rho_0$ & $s_{\mathrm{e}}$ & $\log_{10}(r_{\mathrm{t}})$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ \\ 
+%    \hline 
+%    Prior Type & None & Normal & Flat & None & None & Flat & Normal & Normal\\ 
+%    \hline 
+%    Prior Range & - & $\log_{10}(0.2)| 1.2$ & [0.1,5.0] & - & - & [0.1,5.0] & $%\log_{10}(6.0) | 0.4$ & $\log_{10}(4.0) | 0.4$ \\
+%    \hline
+%    \end{tabular} 
+%\end{table*}
+
+\textbf{While there have been other suggestions for defining the location of the
+splashback radius (see \citet{adhikari2014splashback, shi2016outer, 
+mansfield2017splashback, diemer2017splashback}) we adopt the 
+definition given by \citet{more2015splashback}, who define
+the location of the splashback radius for halos on galaxy cluster scales to 
+be consistent with the location of the steepest logarithmic slope of the density
+profile, due to its easy accessibility in data.}
+
+We estimate the steepest slope of both the two-dimensional
 and the three-dimensional cross-correlation function. The
@@
 \label{sec:Results}
-\subsection{Cluster-galaxy cross-correlations}
 The measurements of the two-dimensional cluster-galaxy
 cross-correlations are shown as black points with error bars in the
-left column of Figure~\ref{fig:2D_graphs}. The different rows
+first row of Figure~\ref{fig:all_graphs}. The different columns
 correspond to the three different absolute magnitude limits that we
@@
 cross-correlations. The cross-correlation signal is clearly detected
-in all three measurements and the corresponding signal-to-noise
-ratios of the measurements are listed in Table~\ref{tab:snr}.
+in all three measurements. \textbf{The signal to noise ratios of the 
+three different estimates of the two-dimensional cross-correlation 
+signals amount to 42.4, 43.3 and 30.9 for the galaxy samples PS 21, 
+PS 21.5 and PS 22, respectively. For comparison: 
+The SNR achieved by \citet{more2016detection} is 263. It is much higher
+due to size of the cluster sample used in their study.}
 
@@
 Table~\ref{tab:fit_parameters} along with the corresponding reduced
-$\chi^2$ values for the best fit. The two-dimensional posterior
-distributions for each pair of parameters are shown in
-Figures~\ref{fig:corner_21}, \ref{fig:corner_21.5} and
-\ref{fig:corner_22} for the three absolute magnitude limits,
-respectively.
-
-\begin{figure}
-    \includegraphics[scale=0.65]{2D_graphs_with_spline_no_mc.pdf}
-\caption{The estimates of the two-dimensional cross-correlation
-signals (black dots) are shown in the left column. The colored
+$\chi^2$ values for the best fit.
+
+\textbf{We show the two-dimensional posterior
+distributions for each pair of parameters for the PS 21.5 sample in 
+Figure~\ref{fig:corner_21.5}. Since the posterior distributions for 
+the other datasetsare very similar we refrain from showing them as well. 
+It is observed that there are some strong degeneracies present between 
+parameters describing the same part of the model in Equation~\ref{eq:model} 
+(namely $\rho_{\mathrm{in}}$, $f_{\mathrm{trans}}$ and $\rho_{\mathrm{out}}$).
+This is not unexpected since certain combinations of parameter values can 
+very well result in the same functional shape of the different parts of 
+the model. This degeneracy also leads to some of the parameters not being 
+constrained tightly (especially $\rho_s$ and $r_s$ due to their strong degeneracy 
+with $\alpha$). On the other hand, it is important to note that there is 
+no degeneracy present between parameters describing different parts of the 
+model, which means that the overall shape of the profile is well constrained. 
+Note also that, since the location of the splashback radius only depends on 
+the overall shape of the profile the uncertainties of the individual parameters 
+within the independent parts of the profile do not translate
+into an uncertainty of the location of the splashback feature directly.}
+
+\begin{figure*}
+	\centering{
+    \includegraphics[scale=0.85]{MAIN_results_with_spline_no_mc.pdf}}
+\caption{The main results of the study are presented in this Figure.
+The first two rows show the inferred two-dimensional cross-correlation
+signals as well as its derivatives.
+The three different columns correspond to the three different galaxy
+samples cross-correlated with the cluster sample.
+The magnitude limit applied to the galaxy catalog is indicated in 
+each tile of the first row along with the signal-to-noise ratio (SNR).
+The measurements of the two-dimensional cross-correlation
+signals (black dots) are shown in the first row as well. There, the colored
 curves show the two-dimensional model fits of the functional
-form in Equation~\ref{eq:surface}. The magnitude limit applied to the galaxy
-catalog is indicated in each row along with the signal-to-noise ratio (SNR). 
-The vertical, shaded regions indicate the estimates of the locations of 
-steepest slope of the profiles as estimated from the corresponding minima of the
-derivative profiles, which are shown in the right column. For
-comparison, the location of the $r_{\mathrm{200m}}$ radius as
-calculated from the average cluster sample properties is indicated
-by the black, dotted lines.}
-   \label{fig:2D_graphs}
-\end{figure}
-
-\begin{figure*}
-    \centering
-    \includegraphics[scale=0.85]{3D_graphs_with_spline_no_mc.pdf}
-\caption{The estimates of the three-dimensional cross-correlation
-signals are shown in the leftmost column. The colored curves show the
-model fits of the functional form in Equation~\ref{eq:model}. The magnitude
-limit applied on the galaxy catalog is indicated in each row along with 
-the signal-to-noise ratio (SNR). The vertical, shaded regions indicate the 
+form in Equation~\ref{eq:surface}. The vertical, shaded regions indicate 
+the estimates of the locations of steepest slope of the profiles as estimated from the corresponding minima of the two-dimensional
+derivative profiles, which are shown in the second row. 
+Rows three to five show the corresponding three-dimensional model fit
+with the functional form Equation~\ref{eq:model} as well as its first and
+second order derivatives.
+In rows three to five the vertical, shaded regions indicate the 
 estimates of the splashback radii as estimated from the corresponding minima 
-of the derivative profiles, which are shown in the column in the middle. The
-rightmost column shows the second derivative profiles in matching color.
+of the three-dimensional derivative profiles.
 The grey curves show the corresponding, estimated first and second derivatives of the 
-one-halo term (namely $\rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r)$ in Equation~\ref{eq:dk14}).
+one-halo term (namely $\rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r)$ in Equation~\ref{eq:model}).
 For comparison, the location of the $r_{\mathrm{200m}}$ radius as calculated 
@@
 lines.}
-   \label{fig:3D_graphs} 
+   \label{fig:all_graphs}
 \end{figure*}
 
-\begin{table}
-    \centering
-    \caption{We list the signal to noise ratios (SNRs) of our
-different estimates of the two-dimensional cross-correlation
-obtained by using the different galaxy samples. For comparison: The SNR
-achieved by \citet{more2016detection} is 263. It is much higher
-due to size of the cluster sample used in their study.}
-    \label{tab:snr}
-    \begin{tabular}{cccc}
-    \hline
-    gal cat & PS 21 & PS 21.5 & PS 22 \\ 
-    \hline
-    \hline
-   SNR & 42.4 & 43.3 & 30.9 \\
-    \hline
-    \end{tabular} 
-\end{table}
+%\begin{table}
+%    \centering
+%    \caption{We list the signal to noise ratios (SNRs) of our
+%different estimates of the two-dimensional cross-correlation
+%obtained by using the different galaxy samples. For comparison: The SNR
+%achieved by \citet{more2016detection} is 263. It is much higher
+%due to size of the cluster sample used in their study.}
+%    \label{tab:snr}
+%    \begin{tabular}{cccc}
+%    \hline
+%    gal cat & PS 21 & PS 21.5 & PS 22 \\ 
+%    \hline
+%    \hline
+%   SNR & 42.4 & 43.3 & 30.9 \\
+%    \hline
+%    \end{tabular} 
+%\end{table}
 
@@
     \centering
-    \caption{The table presents the posterior distribution of the parameters obtained from fitting the cross-correlation of the galaxy cluster sample with the different galaxy catalogs.
+    \caption{The Table presents the posterior distribution of the parameters obtained from fitting the cross-correlation of the galaxy cluster sample with the different galaxy catalogs.
 For each parameter estimate the median as well as the 16\% and 84\% quantiles of the posterior distribution are given.
 We also list the estimated locations of the steepening feature in the two-dimensional cross-correlation signal ($R_{\mathrm{sp}}^{\mathrm{2D}}$), as well as the three-dimensional splashback radius ($r_{\mathrm{sp}}^{\mathrm{3D}}$).
-In the last column the minimum, reduced $\chi^2$ value of the model fit is indicated.
-The two-dimensional posterior distributions of the fitting parameters are displayed in
-Figure~\ref{fig:corner_21} up to Figure~\ref{fig:cornerblue}.}
+In the last column the minimum, reduced $\chi^2$ value of the model fit is indicated.}
     \label{tab:fit_parameters}
@@
 \begin{figure*}
-\centering{
-  \includegraphics[scale=0.8]{derivatives_with_spline_no_mc.pdf}}
-\caption{The distributions of the logarithmic derivatives of
-the three-dimensional cross-correlation signals at the location of
-the splashback radius are shown. In the left panel the distributions of the
-derivatives of the full profiles are shown, whereas only the inner
-halo term (namely $\rho_{\mathrm{in}}f_{\mathrm{trans}}$) is
-shown in the right panel.}
-   \label{fig:derivatives} 
+    \includegraphics[width= \textwidth]{corner215.pdf}
+\caption{The two-dimensional posterior distributions of each pair of
+the fitting parameters corresponding to the functional
+form in Equation~\ref{eq:model} for the PS 21.5 sample.
+}
+   \label{fig:corner_21.5} 
 \end{figure*}
+
 \begin{figure*}
 \centering{
-    \includegraphics[scale=0.8]{splashback_with_spline_no_mc.pdf}}
-\caption{The posterior distributions of the inferred
-locations of steepest slope of the two- and three dimensional
-cross-correlation signals. The distributions of the
+  \includegraphics[scale=0.8]{HISTOGRAMS.pdf}}
+\caption{The posterior distributions of the
 locations of the two-dimensional steepening feature
-($R_{\mathrm{sp}}^{\mathrm{2D}}$) are shown in the left panel, while the
+($R_{\mathrm{sp}}^{\mathrm{2D}}$) are shown in the leftmost panel, while the
 distributions of the three-dimensional counterparts
-($r_{\mathrm{sp}}^{\mathrm{3D}}$) are shown on the right. The
-magnitude limit applied to the galaxy catalogs is indicated for each
+($r_{\mathrm{sp}}^{\mathrm{3D}}$) are shown in the middle one. 
+For comparison, the location of the virial
+radius $r_{\mathrm{200m}}$ as calculated from the average cluster
+sample properties is indicated by the black, dotted lines.
+Additionally, the distributions of the logarithmic derivatives of
+the three-dimensional cross-correlation signals at the location of
+the splashback radius are shown in the rightmost panel.
+The magnitude limit applied to the galaxy catalogs is indicated for each
 distribution. Note that the colors of the distributions match with
-the colors used in Figure~\ref{fig:2D_graphs} and
-Figure~\ref{fig:3D_graphs}. For comparison, the location of the virial
-radius $r_{\mathrm{200m}}$ as calculated from the average cluster
-sample properties is indicated by the black, dotted lines.}
-   \label{fig:splashback} 
+the colors used in Figure~\ref{fig:all_graphs}. }
+   \label{fig:histograms} 
 \end{figure*}
+
 \begin{figure}
-    \includegraphics[scale=0.65]{color_separated_2D_with_spline_no_mc.pdf}
-\caption{The two-dimensional cross-correlations
+	\centering{
+    \includegraphics[scale=0.75]{MAIN_color_results_with_spline_no_mc.pdf}}
+\caption{We present the cross-correlations inferred for the color-separated
+galaxy samples. The two-dimensional cross-correlations
 of the red and blue galaxy populations as inferred by
@@
 subsamples that were extracted from the PS 21.5 galaxy catalog are
-shown in the left panel, whereas the associated derivative profiles
-are shown on the right. The vertical, shaded bands indicate the
-locations of steepest slope of the cross-correlation signal as
-inferred from the two subsamples, whereas the black, dashed lines
+shown in the top panel, whereas the associated derivative profiles
+are shown in the second one. The vertical, shaded bands indicate the
+locations of steepest slope of the two-dimensional cross-correlation signal 
+as inferred from the two subsamples, whereas the black, dashed lines
 indicate the upper and lower bounds of the same feature but as
-estimated from the full PS 21.5 galaxy catalog. }
-   \label{fig:color_curve_2D} 
-\end{figure}
-\begin{figure*}
-    \includegraphics[scale=0.76]{color_separated_3D_with_spline_no_mc.pdf}
-\caption{We show the three-dimensional cross-correlations as
-inferred by cross-correlating the cluster sample with the
-color-separated galaxy subsamples, as well as the corresponding
+estimated from the full PS 21.5 galaxy catalog.
+Panels three to five show the corresponding three-dimensional 
+cross-correlations, as well as the corresponding
 splashback radii (indicated by the colored, vertical bands) and
@@
 curves show the corresponding first and second order derivatives of the one-halo
-term (namely $\rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r)$ in Equation~\ref{eq:dk14}).
-Here, the black, dashed lines indicate upper and lower bounds of the 
+term (namely $\rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r)$ in Equation~\ref{eq:model}). Here, the black, dashed lines indicate upper and lower bounds of the 
 three-dimensional splashback radius corresponding to the full PS 21.5 galaxy sample.}
-   \label{fig:color_curve_3D} 
-\end{figure*}
-The right panels in Figure~\ref{fig:2D_graphs} show the
+   \label{fig:color_curve_all} 
+\end{figure}
+
+The second row in Figure~\ref{fig:all_graphs} shows the
 corresponding analytical derivatives of the two-dimensional
@@
 derivatives. These inferences along with the corresponding 68\%
-confidence intervals are presented in Figure~\ref{fig:3D_graphs},
-maintaining the same color scheme as in Figure~\ref{fig:2D_graphs}
-for ease of comparison. The three-dimensional cross-correlations
+confidence intervals are presented in the last three rows of 
+Figure~\ref{fig:all_graphs}. The three-dimensional cross-correlations
 also show significant steepening in each of the cases that we have
@@
 two-dimensional and three-dimensional cross-correlations can be
-found in the left hand and the right hand panels of
-Figure~\ref{fig:splashback}, respectively. The estimates of the splashback radii
+found in the left hand and middle panels of
+Figure~\ref{fig:histograms}, respectively. The estimates of the splashback radii
 for each of the samples are listed in Table~\ref{tab:fit_parameters}
@@
 Following \citet{baxter2017halo}, we also present the values of the
-first and second order logarithmic derivatives at the location of the steepest slope for
-the total three-dimensional cross-correlations, as well as those for
-the inner halo term in the middle and right hand panels of
-Figure~\ref{fig:derivatives}, respectively. The logarithmic slope of the 
+first order logarithmic derivatives at the location of the steepest slope for
+the total three-dimensional cross-correlations in the right hand panel of
+Figure~\ref{fig:histograms}. The logarithmic slope of the 
 cross-correlation is significantly steeper than $-3$ at the location 
@@
 estimate to $M_{\rm 200m}=6.2\times10^{14}$ $\msunh$ using the average
-concentration mass relation of halos following
-\citet{HuKravtsov:2003}. Given the average mass and redshift of our
+concentration mass relation of halos assuming an NFW profile
+\citep{HuKravtsov:2003}. Given the average mass and redshift of our
 cluster sample, we calculate the expected splashback radius to be
@@
 satisfying $M_{i}-5\log h<-18.94$ with our SZ-selected cluster
-sample. The projected cross-correlations are presented in Figure~\ref{fig:color_curve_2D},
-whereas the three-dimensional counterparts are shown in 
-Figure~\ref{fig:color_curve_3D}. The shaded regions show
+sample. The projected cross-correlations as well as the three-dimensional 
+counterparts are shown in Figure~\ref{fig:color_curve_all}. The shaded regions show
 the 68\% confidence intervals from our fits. The vertical, shaded
@@
 
-\section{Sky maps}
+\section{Visualization of the Data}
 \label{sec:figures}
-We present the sky locations of the SZ selected clusters from the PSZ2
-catalog that we used in our study. The purple areas mark the masked
-out regions as defined by the union selection function of the PSZ2
-catalog. The sky maps in Figure~\ref{fig:heal_map} show the survey
-masks of our three galaxy catalogs.  All sky maps presented in this
-section use the ICRS coordinate system.
+
+We visualize some of the main properties of the used data catalogs.
+In Fig.~\ref{fig:planck_summary} we show the mass and
+the redshift distribution of the Planck clusters.
+In Figure~\ref{fig:skymaps} we present the sky locations of the SZ selected clusters from the PSZ2 catalog that we used in our study (red points).
+The purple areas mark the masked out regions of the galaxy catalogs.
+All sky maps presented use the ICRS coordinate system.
 
@@
 \centering{
-    \includegraphics[scale=0.8]{Planck_pres.png}}
-\caption{Sky map showing the sky positions of the used clusters as
+    \includegraphics[scale=0.55]{Planck_summary.pdf}}
+\caption{The distribution of the masses and redshifts of the galaxy clusters
+from the PSZ2 catalog that we use in our analysis. The histograms on the right
+hand side and the bottom show the distribution in mass and redshift,
+respectively.}
+   \label{fig:planck_summary}
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=\textwidth]{skymaps.pdf}
+\caption{Sky maps showing the sky positions of the used clusters as
 selected from the PSZ2 catalog. In total 596 clusters have been
-selected. The purple areas mark the regions that are excluded by the
-union survey selection function. Note that all clusters with
+selected. The purple areas mark the masked out regions of the used
+galaxy catalogs extracted from the Pan-STARRS 3$\pi$ Steradian
+survey. Note that all clusters with
 $\delta<-31\degr$ have been removed since this region is not covered
@@
 system is used.}
-    \label{fig:planck_fig} 
+   \label{fig:skymaps} 
 \end{figure}
-
-\begin{figure*}
-    \includegraphics[width= \textwidth]{heal_maps.png}
-\caption{Sky maps displaying the masked out regions of the used
-galaxy catalogs extracted from the Pan-STARRS 3$\pi$ Steradian
-survey in purple. The ICRS coordinate system is used.}
-   \label{fig:heal_map} 
-\end{figure*}
 
@@
 parameters.
+
 \begin{table}
     \centering
-    \caption{Listing of the splashback radii inferred by including the effects of mis-centering of the central cluster positions. }
+    \caption{Listing of the splashback radii inferred by including the effects of mis-centering of the central cluster positions (labeled with subsrcipt 'mis') as well as the fiducial results for comparison.}
     \label{tab:mis_splash}
-    \begin{tabular}{ccc}
-    \hline 
-gal cat &  $R_{\mathrm{sp}}^{\mathrm{2D}}$ & $r_{\mathrm{sp}}^{\mathrm{3D}}$ \\
-\hline 
-\hline 
-PS 21 &$1.35_{-0.12}^{+0.13}$ & $1.76_{-0.33}^{+0.29}$\\
-\hline
-PS 21.5 & $1.30_{-0.10}^{+0.10}$&$1.81_{-0.33}^{+0.28}$\\
-\hline
-PS 22 &$1.33_{-0.17}^{+0.13}$ & $1.96_{-0.45}^{+0.37}$\\
-\hline
-PS 21.5 (R) & $1.45_{-0.11}^{+0.12}$ & $2.23_{-0.26}^{+0.27}$ \\
-\hline
-PS 21.5 (B) & $1.42_{-0.25}^{+0.20}$ & $2.39_{-0.39}^{+0.39}$ \\
+    \begin{tabular}{ccc|cc}
+    \hline 
+gal cat &  $R_{\mathrm{sp, mis}}^{\mathrm{2D}}$ & $r_{\mathrm{sp, mis}}^{\mathrm{3D}}$ &  $R_{\mathrm{sp}}^{\mathrm{2D}}$ & $r_{\mathrm{sp}}^{\mathrm{3D}}$\\
+\hline 
+\hline 
+PS 21 &$1.35_{-0.12}^{+0.13}$ & $1.76_{-0.33}^{+0.29}$ & $1.384_{-0.096}^{+0.088}$ &$1.86_{-0.26}^{+0.25}$\\
+\hline
+PS 21.5 & $1.30_{-0.10}^{+0.10}$&$1.81_{-0.33}^{+0.28}$ & $1.323_{-0.086}^{+0.080}$&$1.85_{-0.30}^{+0.26}$\\
+\hline
+PS 22 &$1.33_{-0.17}^{+0.13}$ & $1.96_{-0.45}^{+0.37}$ & $1.31_{-0.14}^{+0.11}$ &$1.90_{-0.40}^{+0.32} $\\ 
+\hline
+PS 21.5 (R) & $1.45_{-0.11}^{+0.12}$ & $2.23_{-0.26}^{+0.27}$ & $1.437_{-0.089}^{+0.099}$ & $2.13_{-0.21}^{+0.22}$\\
+\hline
+PS 21.5 (B) & $1.42_{-0.25}^{+0.20}$ & $2.39_{-0.39}^{+0.39}$ & $1.43_{-0.13}^{+0.12}$ & $2.34_{-0.34}^{+0.33}$ \\
 \hline
@@
 
-\section{Cornerplots}
-\label{sec:cornerplots}
-In Figures \ref{fig:corner_21} to \ref{fig:cornerblue} we present
-the two-dimensional posterior distributions for each pair of the
-fitting parameters corresponding to the functional
-form in Equation~\ref{eq:full}. We obtained the distributions by  using the
-affine invariant Markov Chain Monte Carlo sampler of
-\citet{goodman2010ensemble} as implemented in the parallel python
-package {\it emcee} by \citet{foreman2013emcee}.
-\begin{figure*}
-    \includegraphics[width= \textwidth]{corner21.pdf}
-\caption{The two-dimensional posterior distributions of each pair of
-the fitting parameters corresponding to the functional
-form in Equation~\ref{eq:full} for the PS 21 sample. 
-}
-   \label{fig:corner_21} 
-\end{figure*}
-\begin{figure*}
-    \includegraphics[width= \textwidth]{corner215.pdf}
-\caption{The two-dimensional posterior distributions of each pair of
-the fitting parameters corresponding to the functional
-form in Equation~\ref{eq:full} for the PS 21.5 sample.
-}
-   \label{fig:corner_21.5} 
-\end{figure*}
-\begin{figure*}
-    \includegraphics[width= \textwidth]{corner22.pdf}
-\caption{The two-dimensional posterior distributions of each pair of
-the fitting parameters corresponding to the functional form in
-Equation~\ref{eq:full} for the PS 22 sample.}
-   \label{fig:corner_22} 
-\end{figure*}
-\begin{figure*}
-    \includegraphics[width= \textwidth]{cornerred.pdf}
-\caption{The two-dimensional posterior distributions of each pair of
-the fitting parameters corresponding to the functional form in
-Equation~\ref{eq:full} for the PS 21 sample, where we restricted our
-cross-correlatoin analysis to the red galaxy population.
-}
-   \label{fig:cornerred} 
-\end{figure*}
-\begin{figure*}
-    \includegraphics[width= \textwidth]{cornerblue.pdf}
-\caption{The two-dimensional posterior distributions of each pair of
-the fitting parameters corresponding to the functional form in
-Equation~\ref{eq:full} for the PS 21 sample, where we restricted our
-cross-correlatoin analysis to the blue galaxy population. 
-}
-   \label{fig:cornerblue} 
-\end{figure*}
-
 \section{Estimating the contamination of the blue galaxy population}
@@
 
-\begin{figure*}
-\centering{
-    \includegraphics[width= \textwidth]{color_vs_z.pdf}}
-\caption{Scatter plot showing the $(g_{\mathrm{P1}}-r_{\mathrm{P1}})$ colors
-of the matched galaxies versus their redshifts, where the red dots correspond
-to galaxies identified as red from the SDSS spectroscopic colors and blue dots
-correspond to galaxies identified as blue, respectively. The black, solid line
-indicates the spline cut separating the two populations and excluding the red 
-galaxies from the blue population at a confidence level of $3 \sigma$.}
-   \label{fig:g-r_vs_z} 
-\end{figure*}
+%\begin{figure*}
+%\centering{
+%    \includegraphics[width= 0.5\textwidth]{color_vs_z.pdf}}
+%\caption{Scatter plot showing the $(g_{\mathrm{P1}}-r_{\mathrm{P1}})$ colors
+%of the matched galaxies versus their redshifts, where the red dots correspond
+%to galaxies identified as red from the SDSS spectroscopic colors and blue dots
+%correspond to galaxies identified as blue, respectively. The black, solid line
+%indicates the spline cut separating the two populations and excluding the red 
+%galaxies from the blue population at a confidence level of $3 \sigma$.}
+%   \label{fig:g-r_vs_z} 
+%\end{figure*}
 
@@
 quenched (red) galaxy population, we cross-matched the SDSS spectroscopic
-sample to its Pan-STARRS photometry. In Figure~\ref{fig:g-r_vs_z}, we show the
-plot of the Pan-STARRS $(g_{\mathrm{P1}}-r_{\mathrm{P1}})$ color as a 
-function of redshift, and the color cut we use in our analysis. 
+sample to its Pan-STARRS photometry. 
 The SDSS spectroscopic sample is however quite shallow, 
@@
 
-\begin{figure*}
-\centering{
-    \includegraphics[width= \textwidth]{mag_errors.png}
-\caption{Shown are the photometric errors of the Pan-STARRS galaxies versus
-their magnitude in each of the used band. The dashed curves indicate the running
-median of the photometric error.}
-   \label{fig:mag_errors} 
-}
-\end{figure*}
-
-In Figure~\ref{fig:mag_errors}, we show the photometric errors of the Pan-STARRS
-galaxies as a function of magnitude in each of the bands we use. The
-galaxies that we use in our cross-correlation analysis for the red/blue
+%\begin{figure*}
+%\centering{
+%    \includegraphics[width= \textwidth]{mag_errors.png}
+%\caption{Shown are the photometric errors of the Pan-STARRS galaxies versus
+%their magnitude in each of the used band. The dashed curves indicate the running
+%median of the photometric error.}
+%   \label{fig:mag_errors} 
+%}
+%\end{figure*}
+
+The galaxies that we use in our cross-correlation analysis for the red/blue
 galaxy population have an upper absolute magnitude limit of $M_{i}-5\log h=-18.94$. This
@@
 $g_{\mathrm{P1}}$ and the $r_{\mathrm{P1}}$ band. We randomly perturb these magnitudes 
-by the expected photometric errors at that magnitude as reported in Figure~\ref{fig:mag_errors}.
+by the expected photometric errors at that magnitude.
 

### 2018-12-13 plot_sky_maps.py
Merging with remote

@@ -1,0 +1,38 @@
+import healpy as hp
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import pandas as pd
+import numpy as np
+cat_path = "/work/dominik.zuercher/DataStore/Planck-SZ/Catalogs/21_bins/Planck_21_bins.csv"
+
+planck = pd.read_csv(cat_path)
+planck = planck[(planck['REDSHIFT'] <= 0.33) & (planck['REDSHIFT'] >= 0.03)]
+ra = np.asarray(planck["RA"].values)
+dec = np.asarray(planck["DEC"].values)
+
+f, axarr = plt.subplots(ncols=3, nrows=1, figsize=(18,6))
+
+sky1 = hp.read_map("/work/dominik.zuercher/Output/depth_analysis/bads_21.fits")
+plt.axes(axarr[0])
+hp.mollview(sky1, hold=True, cbar=False, title="PS 21")
+hp.projscatter(ra, dec, lonlat=True, s = 1, c = 'r')
+#hp.projscatter(rand_ra, rand_dec, lonlat=True, s = 3, c = 'b')
+hp.graticule()
+
+sky1 = hp.read_map("/work/dominik.zuercher/Output/depth_analysis/bads_21.5.fits")
+plt.axes(axarr[1])
+hp.mollview(sky1, hold=True, cbar=False, title="PS 21.5")
+hp.projscatter(ra, dec, lonlat=True, s = 1, c = 'r')
+#hp.projscatter(rand_ra, rand_dec, lonlat=True, s = 3, c = 'b')
+hp.graticule()
+
+sky1 = hp.read_map("/work/dominik.zuercher/Output/depth_analysis/bads_22.fits")
+plt.axes(axarr[2])
+hp.mollview(sky1, hold=True, cbar=False, title="PS 22")
+hp.projscatter(ra, dec, lonlat=True, s = 1, c = 'r')
+#hp.projscatter(rand_ra, rand_dec, lonlat=True, s = 3, c = 'b')
+hp.graticule()
+
+plt.subplots_adjust(wspace=0.5)
+f.savefig("/work/dominik.zuercher/Output/skymaps.pdf")

### 2018-12-13 splashpipe/make_plots_v2.py

@@ -1,0 +1,735 @@
+import pandas as pd
+import numpy as np
+import matplotlib
+matplotlib.use("Agg")
+import matplotlib.pyplot as plt
+import palettable 
+cm=palettable.colorbrewer.qualitative.Dark2_8.mpl_colors
+
+
+def assign_color(i,idx):
+    return cm[i]
+
+def assign_color_xr(i):
+    return cm[i*2]
+
+def curve_graphs(types):
+    f, axarr = plt.subplots(ncols=3,nrows=5,figsize=(9,12))
+    i=0
+    shifts=np.asarray([1,1,1])
+    for type_ in types:
+	print("Doing %s",type_)
+	dr_dat = np.genfromtxt("%s/%s/xi_2d.dat" % (splash_directory, type_))
+        
+        if mc == False:
+            type_ += "_no_mc"
+
+	idx = (dr_dat[:,0] > 0.1) & (dr_dat[:,0] < 10.0)
+	rr=dr_dat[idx,0]
+	rrange=np.linspace(rr[0],rr[-1],rsteps)
+
+	dr_plotdat=pd.read_csv("%s/%s/plotsave.dat" % (est_directory, type_),sep=' ',header=None)
+	dr_plotdat=np.asarray(dr_plotdat.values)
+	dr_sigmas=dr_plotdat[0:rsteps,:]
+	dr_rhos=dr_plotdat[rsteps:rsteps*2,:]
+	dr_devs=dr_plotdat[rsteps*2:rsteps*3,:]
+	dr_rhodevs=dr_plotdat[rsteps*3:rsteps*4,:]
+	dr_rhodevs2=dr_plotdat[rsteps*4:rsteps*5,:]
+	dr_innerrhodevs=dr_plotdat[rsteps*5:rsteps*6,:]
+	dr_innerrhodevs2=dr_plotdat[rsteps*6:rsteps*7,:]
+
+	dr_splashdat=pd.read_csv("%s/%s/values.dat" % (est_directory, type_), sep=' ',header=None)
+	dr_splashdat=np.asarray(dr_splashdat.values)
+	dr_rsp2ds=dr_splashdat[0,:]
+	dr_rsp3ds=dr_splashdat[1,:]
+        
+        print("Data read")
+        print("Plotting...")
+
+	#Plot 2D data
[…]

### 2019-01-09 Paper_v2/RSP_paper_new.tex
Some more corrections by Dominik in regard of referee report

@@
 
-We caution however that the cut we use to define our samples was
+\textbf{This result is in contradiction to the findings of \citet{baxter2017halo}, who find no splashback feature in the blue galaxy population.
+At the current state it is not clear how those different results emerge.
+It might be that, in contrast to our SZ selected cluster sample, there is simply no splashback feature present in the galaxy cluster sample used by \citet{baxter2017halo}, which was constructed using the REDMAPPER algorithm on SDSS data.
+Further, the separation of the galaxies by color used by \citet{baxter2017halo} is fundamentaly different from our approach.
+They use K-corrected magnitudes from the SDSS dataset, whereas we avoid using K-corrections but instead use a redshift dependent color cut.}
+
+We caution that the cut we use to define our color-separated samples was
 defined based on spectroscopic galaxies, which tend to be brighter
@@
 
-%\begin{figure*}
-%\centering{
-%    \includegraphics[width= 0.5\textwidth]{color_vs_z.pdf}}
-%\caption{Scatter plot showing the $(g_{\mathrm{P1}}-r_{\mathrm{P1}})$ colors
-%of the matched galaxies versus their redshifts, where the red dots correspond
-%to galaxies identified as red from the SDSS spectroscopic colors and blue dots
-%correspond to galaxies identified as blue, respectively. The black, solid line
-%indicates the spline cut separating the two populations and excluding the red 
-%galaxies from the blue population at a confidence level of $3 \sigma$.}
-%   \label{fig:g-r_vs_z} 
-%\end{figure*}
-
 To infer the color cut which separates star forming (blue) galaxies from the
 quenched (red) galaxy population, we cross-matched the SDSS spectroscopic
-sample to its Pan-STARRS photometry. 
+sample to its Pan-STARRS photometry. In Figure~\ref{fig:g-r_vs_z}, we show the
+plot of the Pan-STARRS $(g_{\mathrm{P1}}-r_{\mathrm{P1}})$ color as a 
+function of redshift, and the color cut we use in our analysis. 
 The SDSS spectroscopic sample is however quite shallow, 
@@
 
+\begin{figure*}
+\centering{
+    \includegraphics[width= 0.5\textwidth]{color_vs_z.pdf}}
+\caption{Scatter plot showing the $(g_{\mathrm{P1}}-r_{\mathrm{P1}})$ colors
+of the matched galaxies versus their redshifts, where the red dots correspond
+to galaxies identified as red from the SDSS spectroscopic colors and blue dots
+correspond to galaxies identified as blue, respectively. The black, solid line
+indicates the spline cut separating the two populations and excluding the red 
+galaxies from the blue population at a confidence level of $3 \sigma$.}
+   \label{fig:g-r_vs_z} 
+\end{figure*}
 % \begin{figure}

### 2019-01-24 Paper_v2/RSP_paper_new.tex
Some edits

@@
 
-\textbf{Trying to avoid the problems which complicate the unbiased detction
-of the splashback signal in opical samples some recent studies searched
-for the signature of the splashback effect using non-optical cluster samples.}
-\citet{umetsu2017lensing} as well as \citet{contigiani2018weak}
-used Xray selected clusters to look for the splashback radius
-using the weak lensing signal, however stacking issues and the low
-signal-to-noise ratio remains a significant hurdle for both of them.
-Also \citet{chang2017splashback} found evidence for the splashback feature
-in the weak lensing signal, but their analysis was again done using
-optically selected clusters in the Dark energy survey suffering from 
-the before mentioned issus again.
-
-\textbf{In this work, we explore yet another non-optical cluster sample. 
-Namely, SZ selected clusters.} While the SZ
-selected clusters can also be susceptible to systematic selection
-effects, the scales on which the SZ signal is measured and the
-cluster selection is performed is much smaller than the expected
-location of the splashback radius (typically $R_{\rm 500c}$). We use
-this sample to explore the evidence for the splashback radius in
-observations.  Due to the low signal-to-noise ratio of the weak
-lensing signal, we perform our analysis using cross-correlation of
-galaxies with clusters.
-
-\textbf{Dynamcial friction is expected to decrease the observed splashback radius in 
-massive clusters. It causes a
-slow-down of the massive subhalos, hosting many of the observed galaxies, 
-which in return decreases the apocentric
-radius of their orbits and therefore the measured splashback radius of the host cluster. 
-Since the rate of dynamical friction scales
-with the mass of the moving object the effect is stronger for more
-massive subhalos. Therefore, one expects the decrease in the splashback
-radius to scale with the amount of massive subhalos in the host cluster and
-with its mass \citep{adhikari2016observing}. This bias can be limited by choosing a deep enough
-galaxy sample such that a large enough amount of low mass subhalos can be
-observed.} The SDSS sample used by
+\textbf{To avoid optical cluster selection effects, there have been some
+previous efforts to use X-ray selected cluster samples to look for the
+splashback radius using the weak lensing signal\{umetsu2017lensing,
+contigiani2018weak}}.  However stacking issues and the low signal-to-noise
+ratio remains a significant hurdle for both of them. \textbf{The use of weak
+lensing in these studies could get around the biased nature of the galaxy
+distribution by directly probing the dark matter distribution. Along those
+lines,} \citet{chang2017splashback} found evidence for the splashback feature
+in the weak lensing signal, but their analysis was again done using optically
+selected clusters in the Dark energy survey that suffer from the
+afore-mentioned issues.
+
+\textbf{In this work, we explore clusters selected using the SZ effect.} While
+the SZ selected clusters can also be susceptible to systematic selection
+effects, the scales on which the SZ signal is measured and the cluster
+selection is performed is much smaller than the expected location of the
+splashback radius (typically $R_{\rm 500c}$). We use this sample to explore the
+evidence for the splashback radius in observations.  Due to the low
+signal-to-noise ratio of the weak lensing signal, we perform our analysis using
+cross-correlation of galaxies with clusters.
+
+\textbf{Dynamical friction is expected to slow down massive subhalos, hosting
+galaxies that are orbiting the galaxy cluster XXXX{Cite paper by Chandrasekhar
+here}XXXX. If a majority of the observed galaxies are hosted by these massive
+subhalos, the slow down due to dynamical friction would reduce the apocenters
+of their orbits, in turn, biasing the measured splashback radius of the host
+cluster XXX{Cite More2016 and papers on Benedikt's SPARTA}XXX. As dynamical
+friction timescales are inversely proportional to the mass of the subhalos,
+this effect is stronger for more massive subhalos. Therefore, one expects the
+splashback radius to decrease for more massive subhalos
+\citep{adhikari2016observing}.  This bias can be limited by choosing a faint
+galaxy sample such that majority of the galaxies reside in low mass subhalos,
+unaffected by dynamical friction.} The SDSS sample used by
 \citet{more2016detection} was already deep enough such that biases in the
-location of the splashback radius due to dynamical friction effects
-were expected to be small. 
-Nevertheless, we use galaxy samples, which
-are even fainter by $0.5-1$ magnitudes compared to those used by
-\citet{more2016detection}.
+location of the splashback radius due to dynamical friction effects were
+expected to be small. Nevertheless, we use galaxy samples, which are fainter by
+$0.5-1$ magnitudes compared to those used by \citet{more2016detection}.
 
@@
 \citet{foreman2013emcee}. 
-\textbf{We keep the parameters $\rho_{\mathrm{s}}$, $\rho_0$ and $s_{\mathrm{e}}$ 
-as free parameters during the fitting procedure. Similarly to \citet{more2016detection} 
-we put flat priors on $\log_{10}(r_{\mathrm{s}})$ and $\log_{10}(r_{\mathrm{t}})$ but double 
-their ranges to $[0.1,5.0]$ compared to their work. In contrast, 
-we use a normal prior with a central value of $\log_{10}(0.2)$ and a scale of 1.2 
-for $\log_{10}(\alpha)$ as deduced from mass estimates \citep{gao2008redshift}. 
-For the parameters $\log_{10}(\beta)$ and $\log_{10}(\gamma)$ we also use normal 
-priors with central values $\log_{10}(6.0)$ and $\log_{10}(4.0)$, respectively 
-and scale 0.4 as recommended by \citet{diemer2014dependence}.}
-
-\textbf{It has been a common concern that the profile in Equation~\ref{eq:model} might introduce
-a splashback feature simply by its functional from and without its presence in the data.
-However, \citet{baxter2017halo} showed that this is not the case by using a Bayesian odds 
-ratio approach to asses that the data is described significantly better by the general 
-profile in Equation~\ref{eq:model} (with the splashback feature)
-rather than by the same profile with fixed $f_{trans} = 1$ (without splashback feature).
-The same conclusion was made by \citet{umetsu2017lensing} who conducted a similar study but
-using weak lensing data.}
+\textbf{We let the parameters $\rho_{\mathrm{s}}$, $\rho_0$ and
+$s_{\mathrm{e}}$ vary freely during our fitting procedure. Similar to
+\citet{more2016detection} we put flat priors on $\log_{10}(r_{\mathrm{s}})$ and
+$\log_{10}(r_{\mathrm{t}})$ but double their ranges to $[0.1,5.0]$ compared to
+their work. In contrast to \citet{more2016detection}, we use a normal prior
+with a central value of $\log_{10}(0.2)$ and a scale of 1.2 for
+$\log_{10}(\alpha)$ as deduced from mass estimates \citep{gao2008redshift}.
+For the parameters $\log_{10}(\beta)$ and $\log_{10}(\gamma)$ we also use
+normal priors with central values $\log_{10}(6.0)$ and $\log_{10}(4.0)$,
+respectively and scale 0.4 as recommended by \citet{diemer2014dependence}.}
+
+\textbf{It has been a common concern that the profile in
+Equation~\ref{eq:model} introduces a point of minimum slope in the logarithmic
+derivative profile simply due to the functional form. However,
+\citet{baxter2017halo} used a Bayesian evidence approach to assess that the
+data is described significantly better by the general profile in
+Equation~\ref{eq:model} (with the splashback feature) rather than by the same
+profile with fixed $f_{trans} = 1$ (without splashback feature).  The same
+conclusion was made by \citet{umetsu2017lensing} who conducted a similar study
+but using weak lensing data.}
 %\begin{table*}
@@
 
-\textbf{While there have been other suggestions for defining the location of the
-splashback radius (see \citet{adhikari2014splashback, shi2016outer, 
-mansfield2017splashback, diemer2017splashback}) we adopt the 
-definition given by \citet{more2015splashback}, who define
-the location of the splashback radius for halos on galaxy cluster scales to 
-be consistent with the location of the steepest logarithmic slope of the density
-profile, due to its easy accessibility in data.}
+\textbf{The location of the splashback radius can be identified in various
+ways, e.g., as the radius of the outermost shell in theoretical models of
+spherical symmetric collapse \citep{adhikari2014splashback, shi2016outer}, or
+using non-spherical shells of density jumps \citet{ mansfield2017splashback},
+or the average location of the apocenter of particles falling in the cluster
+potential \citet{diemer2017splashback}. Although these definitions have subtle
+differences, they all follow the general trend of a decreasing splashback
+radius with increasing rate of accretion XXX{Cite Benedikt and Phils paper for
+these comparisons}. In this paper, we adopt the convention of
+\citet{more2015splashback}, who define the location of the splashback radius
+for halos on galaxy cluster scales to be the location of the steepest
+logarithmic slope of the radially averaged density profile, due to its ease of
+accessibility in data.}
 
@@
 in all three measurements. \textbf{The signal to noise ratios of the 
-three different estimates of the two-dimensional cross-correlation 
-signals amount to 42.4, 43.3 and 30.9 for the galaxy samples PS 21, 
-PS 21.5 and PS 22, respectively. For comparison: 
-The SNR achieved by \citet{more2016detection} is 263. It is much higher
-due to size of the cluster sample used in their study.}
+three different estimates of the two-dimensional cross-correlation signals
+amount to 42.4, 43.3 and 30.9 for the galaxy samples PS 21, PS 21.5 and PS 22,
+respectively. For comparison, the detection SNR in \citet{more2016detection}
+was 263, a much higher number due to the size of the cluster sample used in
+their study.}
 
@@
 
-\textbf{We show the two-dimensional posterior
-distributions for each pair of parameters for the PS 21.5 sample in 
-Figure~\ref{fig:corner_21.5}. Since the posterior distributions for 
-the other datasetsare very similar we refrain from showing them as well. 
+\textbf{We show the two-dimensional posterior distributions for each pair of
+parameters for the PS 21.5 sample in Figure~\ref{fig:corner_21.5}. The
+posterior distributions for the other datasets show similar degeneracies and
+are not included in the paper for brevity.
 It is observed that there are some strong degeneracies present between 
@@
 (namely $\rho_{\mathrm{in}}$, $f_{\mathrm{trans}}$ and $\rho_{\mathrm{out}}$).
-This is not unexpected since certain combinations of parameter values can 
+This is expected since certain combinations of parameter values can 
 very well result in the same functional shape of the different parts of 
@@
 with $\alpha$). On the other hand, it is important to note that there is
-no degeneracy present between parameters describing different parts of the 
-model, which means that the overall shape of the profile is well constrained. 
-Note also that, since the location of the splashback radius only depends on 
-the overall shape of the profile the uncertainties of the individual parameters 
-within the independent parts of the profile do not translate
-into an uncertainty of the location of the splashback feature directly.}
+little-to-no degeneracy present between parameters describing different parts
+of the model, which means that the overall shape of the profile is well
+constrained.  Note also that, since the location of the splashback radius only
+depends on the overall shape of the profile, the uncertainties of the
+individual parameters within the independent parts of the profile do not
+translate into a huge uncertainty on the location of the splashback feature.}
 
@@
 
-\textbf{This result is in contradiction to the findings of \citet{baxter2017halo}, who find no splashback feature in the blue galaxy population.
-At the current state it is not clear how those different results emerge.
-It might be that, in contrast to our SZ selected cluster sample, there is simply no splashback feature present in the galaxy cluster sample used by \citet{baxter2017halo}, which was constructed using the REDMAPPER algorithm on SDSS data.
-Further, the separation of the galaxies by color used by \citet{baxter2017halo} is fundamentaly different from our approach.
-They use K-corrected magnitudes from the SDSS dataset, whereas we avoid using K-corrections but instead use a redshift dependent color cut.}
+\textbf{This result seem to be at odds with the findings presented by
+\citet{baxter2017halo}, who find no splashback feature in the blue galaxy
+population. Our investigations suggest that the splashback feature gets less
+prominent as we proceed to look at galaxies which are progressively bluer in
+color. Given that \citet{baxter2017halo}, consider the last quartile of the
+blue population, it is imaginable that they see no evidence for the splashback
+feature in their dataset. The approach used by \citet{baxter2017halo} used to
+separate galaxies into red or blue is also fundamentally different from our
+approach. While \citet{baxter2017halo} use K-corrected magnitudes from SDSS
+relying on the photometric redshifts of galaxies (which could have different
+uncertainties for the red and the blue population), we rely on a color cut
+which depends upon the redshift of the cluster under consideration.}
 

### 2019-01-25 Paper_v2/RSP_paper_new.tex
Reviewing Surhuds corrections

@@
 previous efforts to use X-ray selected cluster samples to look for the
-splashback radius using the weak lensing signal\{umetsu2017lensing,
+splashback radius using the weak lensing signal \citep{umetsu2017lensing,
 contigiani2018weak}}. However stacking issues and the low signal-to-noise
 ratio remains a significant hurdle for both of them. \textbf{The use of weak
-lensing in these studies could get around the biased nature of the galaxy
+lensing data in these studies could get around the biased nature of the galaxy
 distribution by directly probing the dark matter distribution. Along those
@@
 \textbf{Dynamical friction is expected to slow down massive subhalos, hosting
-galaxies that are orbiting the galaxy cluster XXXX{Cite paper by Chandrasekhar
-here}XXXX. If a majority of the observed galaxies are hosted by these massive
+galaxies that are orbiting the galaxy cluster \citep{chandrasekhar1943dynamical}.
+If a majority of the observed galaxies are hosted by these massive
 subhalos, the slow down due to dynamical friction would reduce the apocenters
-of their orbits, in turn, biasing the measured splashback radius of the host
-cluster XXX{Cite More2016 and papers on Benedikt's SPARTA}XXX. As dynamical
+of their orbits, and in turn, biasing the measured splashback radius of the host
+cluster \citep{more2016detection, diemer2017sparta}. As dynamical
 friction timescales are inversely proportional to the mass of the subhalos,
@@
 \citep{adhikari2016observing}.  This bias can be limited by choosing a faint
-galaxy sample such that majority of the galaxies reside in low mass subhalos,
+galaxy sample such that the majority of the galaxies reside in low mass subhalos,
 unaffected by dynamical friction.} The SDSS sample used by
@@
 spherical symmetric collapse \citep{adhikari2014splashback, shi2016outer}, or
-using non-spherical shells of density jumps \citet{ mansfield2017splashback},
+using non-spherical shells of density jumps \citep{ mansfield2017splashback},
 or the average location of the apocenter of particles falling in the cluster
@@
 differences, they all follow the general trend of a decreasing splashback
-radius with increasing rate of accretion XXX{Cite Benedikt and Phils paper for
-these comparisons}. In this paper, we adopt the convention of
+radius with increasing rate of accretion \citep{diemer2017splashback}.
+In this paper, we adopt the convention of
 \citet{more2015splashback}, who define the location of the splashback radius

### 2019-02-13 Paper_v2/Reply_to_referee.txt
Reply to referee added

We thank the referee for the very detailed and useful report. We have made the
changes based on the referee's detailed suggestions, and these changes should
have improved the readability of the paper. We hope the revised manuscript is
in an acceptable format. In our response below, the referees comments have been
quoted, and our response indicated by Reply.

Please let us know if there are any further concerns.

Cheers,
Dominik and Surhud

> Referee Report
> 
> In previous work, the splashback radius of dark matter halos was detected by
> optically selecting galaxy clusters and measuring the galaxy (or lensing mass)
> distribution around them. In this paper, the authors propose an entirely new
> method, namely selecting clusters in Planck SZ maps. The main advantage is to
> avoid the troubling systematics in optical selection that have recently been
> discovered.
> 
> The paper represents a highly valuable contribution to the field, and will
> certainly spark many follow-up studies using other datasets. Overall, the paper
> is already in good shape: the results and the method by which they were
> obtained are clear and sensible, and the writing is (mostly) clear. I do,
> however, fear that the current version is somewhat cluttered with too many
> figures and tables that might confuse the reader and lessen the paper's impact.
> Moreover, some of the writing assumes a fair amount of previous knowledge of
> the subject, meaning that readers unfamiliar with splashback might be turned
> off.
> 
> I will be happy to recommend the paper for publication once the major points
> below have been addressed. I emphasize that many of my suggestions are just
> that: writing, figure design, and the flow of a paper are, to a large extent, a
> matter of taste. I hope that you will find my suggestions helpful.
> 
> Congratulations on this really important result.

Reply: We thank the referee for a careful reading of the manuscript and the
detailed suggestions which have helped improve the paper.

> 
> 
> 1) The main points of the paper are somewhat hidden in a wealth of 16 figures
> and 6 tables, some of which seem detail-oriented and make the paper harder to
> digest than it needs to be. The suggestions below would drastically reduce the
> number of figures, without losing any essential information.
> 
> a) Figure 1: It is not clear why the sky maps of the selected clusters are
> buried in the appendix while the mass-redshift distribution is shown in Figure
> 1. Both figures are relatively technical. My recommendation would be to shift
> Figure 1 into Appendix A, which could be renamed from "Sky maps" to "Properties
> of the SZ sample" or something like that.

Reply: Our original motivation to keep Figure 1 in the beginning was to show the
average redshift of the sample and the mass range, since that goes in our
theoretical expectation. However since this is indicated in the Table, we have
now moved Figure 1 to the appendix based on the referee's suggestion.

> 
> b) Figures 2 and 3 show very similar things, namely the 2D and 3D density
> profiles. However, because the figures are split and because the panels come
> out much larger in Figure 3, it is not immediately apparent that the actual
> measured results are shown in Figure 2. I have a somewhat radical suggestion: I
> would combine both figures by stacking the panels vertically instead of
> horizontally, i.e., combining the 2D and 3D profiles into one column of five
> panels that shows all aspects of the modeling (data, inferred 2D, 2D slope, 3D
> etc). Then, the three samples would be three columns that could easily be fit
> next to each other, particularly as the y-labels would not need to be repeated
> in each column. The disadvantage is that it would become harder to compare the
> location of Rsp in the three samples, but as stated in the text, they all agree
> anyway. The advantage would be that one could directly compare the inferred 2D
> and 3D radii -- to me, that is more informative. Most importantly, it would be
> very clear that the combined figure represents the main result of the paper.
> The same could be done for Figures 6 and 7 which, again, appear somewhat
> disconnected to the reader even though they are highly connected.

Reply: We thank the referee for this suggestion. We have now combined Figure 2
and Figure 3 in the original manuscript into one. However, since the upper two
panels have the projected radius as the abscissa while the bottom three have
the 3-dimensional radius instead, we have included the labels at the bottom of
row 2, and row 5 separately. {\bf TBD: We have also included a label Rsp^{\rm
2d} and Rsp^{\rm 3d} to indicate the two and three dimensional locations of the
steepest slopes.} We have similarly combined Figure 6 and 7 into the new Figure
4.

> 
> c) Tables 3 and 4 contain so little data that they could easily be put into
> words and added to the text.

Reply: We agree and have described this table in the text instead.

> 
> d) Figures 4 and 5 could easily be combined into one figure, perhaps with
> clear, large labels inside the panels explaining what the different
> distributions represent.

Reply: We apologize that the right panel in Figure 4 was inadvertently included
in the original manuscript. We have now removed that part and combined Figure 4
and 5 into a single one and included large labels inside the panels explaining
what each of the distribution corresponds to.

> 
> e) Figures 8 and 9 could be combined by showing the clusters on top of the
> masks. That way, the masks would be more useful because the reader could
> immediately see how many clusters are masked out.

Reply: We agree and have changed the figure as suggested.

> 
> f) Showing the corner plots in Figures 10 to 14 is laudable in terms of
> absolute completeness of the information presented, but frankly, I am not sure
> they are necessary. In particular, Figures 10-12 are virtually impossible to
> distinguish by eye, and Figures 13-14 are difficult to digest. I had to stare
> at these figures quite hard to derive any meaningful takeaway messages. My
> suggestions would be to omit all of these figures except perhaps one for one of
> the PanStarrs samples. That figure could then even be put into the main body of
> the paper instead of an appendix.

Reply: We agree with the referee's suggestion and have included one of the
corner plots in the main manuscript and the others have been removed from the
appendix. We have also included some messages that we want the reader to take
from these plots in the text describing this figure.

> 
> g) I am not sure that figures 15 and 16 are necessary. I found the written
> explanation of the checks on color scatter perfectly adequate and convincing
> without the figures.

Reply: We agree that the figure XX corresponding to the error as a function of
magnitude may not be necessary, but we would like to show the color cut we use
for reproducibility purposes. We hope the referee will be ok with this.

> 
> 2) Throughout the paper, I found that the writing supposed the reader to
> possess a high level of knowledge about the specifics of the splashback radius
> and its detection. It would be good to add some gentle explanations as well as
> smoother transitions between different sections and arguments. I give some
> examples below.
> 
> a) In the abstract, an introductory sentence would help. What has been done so
> far, why move from optical to SZ selection? A comment to this effect would also
> be good in Section 2.1, some readers are probably confused as to the purpose of
> the SZ sample (which is used only to find clusters but not to constrain their
> profiles).

Reply: We have now included sentences to this effect in the {\bf abstract},
the introduction as well as just before Section 2.1.

> 
> b) Throughout the paper, it is implicitly assumed that the definition of the
> splashback radius is the radius where the 3D slope of density is steepest, but
> that is only one of many definitions. It was defined this way in More+15 as the
> most easily measurable quantity, but one can also use the radius of the
> outermost shell in theoretical models (Adhikari+14, Shi 16), non-spherical
> shells (Mansfield+17), or the apocenter radii of particles (Diemer 17). To be
> clear, this comment is not intended as a sneaky citation request. I do,
> however, feel that there is already a lot of confusion as to "what the
> splashback radius actually is", and any splashback paper should try to
> alleviate this confusion.

Reply: We would like to apologize for missing these citations. We have now
pointed out these alternative ways of defining the splashback radius in the
Methods section, along with the relevant citations.

> 
> c) It is assumed that the reader understands the connection between the
> limiting magnitude of galaxy samples and dynamical friction, but that
> connection is far from obvious! Please explain that dynamical friction can
> reduce Rsp, that this effect is mass-dependent, and that selecting more massive
> galaxy samples can thus put limits on the effect. In this context, it would
> also be good to cite Adhikari+16 who measure and model the magnitude of
> dynamical friction in SDSS.

Reply: We have now added comments relevant to dynamical friction effects in the
introduction itself now.

> 
> d) One common concern is that the profile fitting function might introduce a
> splashback scale simply due to its functional form. This was shown not to be
> the case in Baxter+ and Umetsu & Diemer 17, it would be good to explain that.

Reply: We have now added the relevant comments in the methods section.

> 
> e) The corner plots in Figures 10-14, whether they remain in the paper or not,
> would benefit from some explanation. These plots are hard to read: which
> parameters are well-constrained, which are not? Which are dominated by priors?
> Are there important degeneracies? What does all of this mean for the inferred
> splashback radii?

Reply: We have now kept only one of the corner plots, and have written the main
takeaways from the plot in the Results section of the text.

> 
> 3) Some results seem incompatible with results in Baxter+17, and (if real)
> those differences should be discussed.

{\bf Still to be done?}

> a) The right panel of Figure 4 seems puzzling, should these slopes not be much
> steeper? Compare to Figure 4 in Baxter+17.

Reply: This was an erroneous plot, we apologize for not noticing this before,
and thank the referee for noticing it.

> 
> b) In Section 4, you explain that the splashback radius seen in the blue
> population may be due to contamination of the blue sample, but the conclusion
> remains a little unclear in the main text. I would refer to Baxter+17 Figure 5,
> saying that they found no splashback in the blue population, and make a firm
> statement on whether there is any evidence that this is wrong (given the issues
> with contamination).  -refer to baxter and explain why we find something
> different
> 
> 4) I have some smaller comments and questions regarding the text and figures.
> 
> a) In Table 2, it looks like "'" were used instead of "." in large numbers.

Reply: We have corrected this.

> 
> b) The derivatives in figures 2, 3 etc look somewhat noisy, even though the
> profile measure is smooth as it is inferred from the profile fitting function.
> My expectation would be that the derivatives should look smooth too?

Reply: Not corrected since this would require evaluating function on many more
points -> large computational cost

> c) Section 4.1 is the only sub-section of Section 4, and thus makes no sense. I
> would either remove the 4.1 section title or add more sub-sections.

Reply: Done

> d) In Section 4, you state that you are using an "average concentration-mass
> relation" to convert M500c to M200m. Which model of the concentration-mass
> relation was used?

Reply: We now mention the model of concentration-mass relation we use.

> 
> e) In Figures 4 and 5, y-labels are missing (even though they are fairly
> obvious). Moreover, it would be good to increase the size of the inset labels
> that state what each panel is showing.

Reply: We have added the y-labels and increased the size of the inset labels.

> 
> f) Figure 8 looks like a low-resolution pixel graphic. Is there a reason not to
> show it as a vector graphic?

Reply: We have now edited this.

> g) Table 6 would be more useful if it showed the Rsp values computed without
> miscentering for comparison.

### 2019-02-13 Paper_v2/RSP_paper_new.tex
edits to paper

@@
 \begin{abstract}
-We present evidence for the existence of the splashback radius in
-galaxy clusters selected using the Sunyaev-Zeldovich effect.  We show
-that the deprojected cross-correlation of galaxy clusters found in the
-Planck survey with galaxies detected photometrically in the Pan-STARRS
-survey, shows a sharp steepening feature (a logarithmic slope steeper
-than $-3$), which we associate with the splashback radius. We infer
-the three-dimensional splashback radius for the SZ cluster sample to
-be $r_{\rm sp}=1.85_{-0.30}^{+0.26}$ $\mpch$, where the cluster sample
-has an average halo mass $M_{\rm 500c}=3.0\times10^{14}\msunh$ at an
-average redshift of $z=0.18$. The inferred value of the splashback
-radius appears consistent with the expected location for dark matter halos
-in the standard cold dark matter paradigm. However, given the limited
-precision of our measurements, we cannot conclusively rule out the
-smaller splashback radius measured so far in the literature for
-optically selected galaxy clusters. We show that the splashback radius
-does not depend upon the galaxy magnitude for galaxies fainter than
-$M_i-5\log h=-19.44$, and is present at a consistent location in
-galaxy populations divided by color. The presence of the splashback
-radius in the star-forming galaxy population could potentially be used to put
-lower limits on the quenching timescales for galaxies. We can marginally rule
-out the contamination of the star-forming galaxy sample by quenched galaxies,
-but the results would need further verification with deeper datasets.
+We present evidence for the existence of the splashback radius in galaxy
+clusters selected using the Sunyaev-Zeldovich effect, a sample unaffected by
+systematics related to cluster finding in the optical wavelength range. We show
+that the deprojected cross-correlation of galaxy clusters found in the Planck
+survey with galaxies detected photometrically in the Pan-STARRS survey, shows a
+sharp steepening feature (a logarithmic slope steeper than $-3$), which we
+associate with the splashback radius. We infer the three-dimensional splashback
+radius for the SZ cluster sample to be $r_{\rm sp}=1.85_{-0.30}^{+0.26}$
+$\mpch$, where the cluster sample has an average halo mass $M_{\rm
+500c}=3.0\times10^{14}\msunh$ at an average redshift of $z=0.18$.  The inferred
+value of the splashback radius appears consistent with the expected location
+for dark matter halos in the standard cold dark matter paradigm. However, given
+the limited precision of our measurements, we cannot conclusively confirm or
+rule out the smaller splashback radius measured so far in the literature for
+optically selected galaxy clusters. We show that the splashback radius does not
+depend upon the galaxy magnitude for galaxies fainter than $M_i-5\log
+h=-19.44$, and is present at a consistent location in galaxy populations
+divided by color. The presence of the splashback radius in the star-forming
+galaxy population could potentially be used to put lower limits on the
+quenching timescales for galaxies. We can marginally rule out the contamination
+of the star-forming galaxy sample by quenched galaxies, but the results would
+need further verification with deeper datasets.
 
@@
 
-\textbf{To avoid optical cluster selection effects, there have been some
+\textbf{To avoid such optical cluster selection effects, there have been some
 previous efforts to use X-ray selected cluster samples to look for the
@@
 \label{sec:data}
+
+In order to avoid optical cluster selection effects, the aim of this paper is
+to find observational evidence for the existence of the splashback radius in
+galaxy clusters which have not been selected using optical photometry. To move
+away from the optical selection we use galaxy clusters selected using the
+Sunyaev-Zeldovich effect. We describe the data we use in this section.
 

### 2019-02-13 Paper_v2/Reply_to_referee.txt
more edits

@@
 
-Reply: We have now included sentences to this effect in the {\bf abstract},
-the introduction as well as just before Section 2.1.
+Reply: We have now included sentences to this effect in the abstract, the
+introduction as well as just before Section 2.1.
 
@@
 
-{\bf Still to be done?}
+Reply: We have now added a note discussing our results with those in Baxter et
+al. 2017.
 
@@
 > miscentering for comparison.
+
+Reply: We have added the Rsp values computed without miscentering in Table 6, as suggested.

### 2019-02-13 Paper_v2/Reply_to_referee.txt
added last reply in refree_reply

--- 2019-02-13 Paper_v2/Reply_to_referee.txt
@@
 
-Reply: We agree that the figure XX corresponding to the error as a function of
+Reply: We agree that the figure 15 corresponding to the error as a function of
 magnitude may not be necessary, but we would like to show the color cut we use
@@
 
-{\bf Still to be done?}
+{\bf Still to be done?} Should be done in paragraph starting with: This result
+seems to be at odds with the findings ....
 
@@
 > miscentering for comparison.
+
+Reply: We have added the values computed without miscentering as suggested

### 2019-02-13 Paper_v2/RSP_paper_new.tex

@@
 
-\textbf{This result seem to be at odds with the findings presented by
-\citet{baxter2017halo}, who find no splashback feature in the blue galaxy
-population. Our investigations suggest that the splashback feature gets less
-prominent as we proceed to look at galaxies which are progressively bluer in
-color. Given that \citet{baxter2017halo}, consider the last quartile of the
-blue population, it is imaginable that they see no evidence for the splashback
-feature in their dataset. The approach used by \citet{baxter2017halo} used to
-separate galaxies into red or blue is also fundamentally different from our
+\textbf{At face value, this result seems to be at odds with the findings
+presented by \citet{baxter2017halo}, who find no splashback feature in the blue
+galaxy population. Our independent investigations suggest that the splashback
+feature gets less prominent as we cross-correlate the galaxy clusters with
+galaxies which are progressively bluer in color. In their paper,
+\citet{baxter2017halo} considered the last quartile of the blue population.
+Therefore, it is conceivable that they see no evidence for the splashback
+feature in their dataset in the bluest population of galaxies. We would also
+like to note that the approach used by \citet{baxter2017halo} used to separate
+galaxies into red and blue populations is also fundamentally different from our
 approach. While \citet{baxter2017halo} use K-corrected magnitudes from SDSS

### 2019-02-14 Paper_v2/RSP_paper_new.tex
Smoothend plots and minor fixes
affiliation changed

@@
 $^{1}$Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), 5-1-5 Kashiwanoha, Kashiwa, Chiba 277-8583, Japan \\
-$^{2}$Department of Physics, ETH Zurich, Wolfgang Pauli Strasse 27, 8093 Zurich, Switzerland\\
+$^{2}$Institute for Particle Physics and Astrophysics, Department of Physics, ETH Zurich, Wolfgang Pauli Strasse 27, 8093 Zurich, Switzerland\\
 $^{3}$The Inter-University Centre for Astronomy and Astrophysics, Post Bag 4, Ganeshkhind, Pune 411007, India\\
-$^{4}$ dominikz@phys.ethz.ch
+$^{4}$ dominik.zuercher@phys.ethz.ch
 }
@@
 supported in part by the National Science Foundation under Grant No.
-NSF PHY-1125915 during this workshop.
+NSF PHY-1125915 during this workshop. Further, we also thank the anonymous
+referee for helpful comments and suggestions during the development of this 
+manuscript.
 

### 2019-02-14 Paper_v2/Reply_to_referee.txt

@@
 the 3-dimensional radius instead, we have included the labels at the bottom of
-row 2, and row 5 separately. {\bf TBD: We have also included a label Rsp^{\rm
-2d} and Rsp^{\rm 3d} to indicate the two and three dimensional locations of the
-steepest slopes.} We have similarly combined Figure 6 and 7 into the new Figure
-4.
+row 2, and row 5 separately. We have also included a label Rsp^{\rm 2d} and
+Rsp^{\rm 3d} to indicate the two and three dimensional locations of the
+steepest slopes, since it could be confusing. We have similarly combined Figure
+6 and 7 into the new Figure 4.
 
@@
 
-Reply: Not corrected since this would require evaluating function on many more
-points -> large computational cost
+Reply: The noisy looking derivatives were a result of us avoiding the large
+computational cost of storing the derivatives at a large number of radial
+points at every MCMC step. We have now taken the computed points, and plotted
+the spline instead and are displaying it in the Figure to avoid this noise in
+the derivative figure.
 

### 2019-02-14 Paper_v2/RSP_paper_new.tex
more edits

@@
 We present evidence for the existence of the splashback radius in galaxy
-clusters selected using the Sunyaev-Zeldovich effect, a sample unaffected by
-systematics related to cluster finding in the optical wavelength range. We show
+clusters selected using the Sunyaev-Zeldovich effect, {\bf a sample unaffected by
+systematics related to cluster finding in the optical wavelength range.} We show
 that the deprojected cross-correlation of galaxy clusters found in the Planck
@@
 subhalos, the slow down due to dynamical friction would reduce the apocenters
-of their orbits, and in turn, biasing the measured splashback radius of the host
+of their orbits, and in turn, bias the measured splashback radius of the host
 cluster \citep{more2016detection, diemer2017sparta}. As dynamical
@@
 this effect is stronger for more massive subhalos. Therefore, one expects the
-splashback radius to decrease for more massive subhalos
-\citep{adhikari2016observing}.  This bias can be limited by choosing a faint
-galaxy sample such that the majority of the galaxies reside in low mass subhalos,
-unaffected by dynamical friction.} The SDSS sample used by
+splashback radius to be biased low as measured for more massive subhalos
+\citep{adhikari2016observing}.  This bias can be overcome by choosing a faint
+enough galaxy sample such that the majority of the galaxies reside in low mass
+subhalos, unaffected by dynamical friction.} The SDSS sample used by
 \citet{more2016detection} was already deep enough such that biases in the
@@
 $\log_{10}(r_{\mathrm{t}})$ but double their ranges to $[0.1,5.0]$ compared to
-their work. In contrast to \citet{more2016detection}, we use a normal prior
-with a central value of $\log_{10}(0.2)$ and a scale of 1.2 for
-$\log_{10}(\alpha)$ as deduced from mass estimates \citep{gao2008redshift}.
-For the parameters $\log_{10}(\beta)$ and $\log_{10}(\gamma)$ we also use
-normal priors with central values $\log_{10}(6.0)$ and $\log_{10}(4.0)$,
-respectively and scale 0.4 as recommended by \citet{diemer2014dependence}.}
+their work in order to stay conservative. We also use a normal prior with a
+central value of $\log_{10}(0.2)$ for $\log_{10}(\alpha)$ as deduced from mass
+estimates \citep{gao2008redshift}. To be conservative, we once again double the
+scale of the prior to be 1.2 compared to \citet{more2016detection}. For the
+parameters $\log_{10}(\beta)$ and $\log_{10}(\gamma)$ we also use normal priors
+with central values $\log_{10}(6.0)$ and $\log_{10}(4.0)$, respectively and
+scale 0.4 as recommended by \citet{diemer2014dependence}.}
 
@@
 using non-spherical shells of density jumps \citep{ mansfield2017splashback},
-or the average location of the apocenter of particles falling in the cluster
+or the average location of the apocenter of particles falling into the cluster
 potential \citet{diemer2017splashback}. Although these definitions have subtle
@@
 cross-correlations. The cross-correlation signal is clearly detected
-in all three measurements. \textbf{The signal to noise ratios of the
+in all three measurements. \textbf{The signal-to-noise ratios of the
 three different estimates of the two-dimensional cross-correlation signals
 amount to 42.4, 43.3 and 30.9 for the galaxy samples PS 21, PS 21.5 and PS 22,
-respectively. For comparison, the detection SNR in \citet{more2016detection}
-was 263, a much higher number due to the size of the cluster sample used in
-their study.}
+respectively. For comparison, the detection signal-to-noise ratio in
+\citet{more2016detection} was 263, a much higher number due to the size of the
+cluster sample used in their study.}
 
@@
 little-to-no degeneracy present between parameters describing different parts
-of the model, which means that the overall shape of the profile is well
-constrained.  Note also that, since the location of the splashback radius only
-depends on the overall shape of the profile, the uncertainties of the
-individual parameters within the independent parts of the profile do not
-translate into a huge uncertainty on the location of the splashback feature.}
+of the model, which means that the location of the transition region is well
+constrained. Therefore, the uncertainties of the individual parameters within
+the independent parts of the profile do not directly translate into an
+uncertainty in the location of the splashback feature.}
 
@@
 	\centering{
-    \includegraphics[scale=0.85]{MAIN_results_with_spline_no_mc.pdf}}
+    \includegraphics[scale=0.75]{MAIN_results_with_spline_no_mc.pdf}}
 \caption{The main results of the study are presented in this Figure.

### 2019-02-14 Paper_v2/RSP_paper_new.tex
small edit

@@
 	\centering{
-    \includegraphics[scale=0.75]{MAIN_results_with_spline_no_mc.pdf}}
+    \includegraphics[trim = 0mm 2mm 0mm 0mm, clip, scale=0.8]{MAIN_results_with_spline_no_mc_1.pdf}
+    \includegraphics[trim = 0mm 2mm 0mm 0mm, clip, scale=0.8]{MAIN_results_with_spline_no_mc_2.pdf}
+}
 \caption{The main results of the study are presented in this Figure.
@@
 galaxies which are progressively bluer in color. In their paper,
-\citet{baxter2017halo} considered the last quartile of the blue population.
+\citet{baxter2017halo} considered the bluest quartile of the galaxy population.
 Therefore, it is conceivable that they see no evidence for the splashback

### 2019-02-14 Paper_v2/Reply_to_referee.txt
finalizing edits

@@
 
-Reply: Our original motivation to keep Figure 1 in the beginning was to show the
-average redshift of the sample and the mass range, since that goes in our
-theoretical expectation. However since this is indicated in the Table, we have
-now moved Figure 1 to the appendix based on the referee's suggestion.
+Reply: Our original motivation to keep Figure 1 in the beginning was to show
+the average redshift of the sample and the mass range, since that goes in our
+theoretical expectation. However since this is indicated in Table 1, we have
+now moved Figure 1 to the appendix based on the referee's suggestion. We have
+renamed the appendix to "Properties of the SZ clusters and the PS galaxy
+sample".
 
@@
 pointed out these alternative ways of defining the splashback radius in the
-Methods section, along with the relevant citations.
+Methods section, along with the relevant citations. We have also highlighted
+the common thread connecting these different definitions, and mentioned the
+reason we adopt a particular definition in the paper.
 
@@
 Reply: We have now added comments relevant to dynamical friction effects in the
-introduction itself now.
+introduction itself.
 
@@
 > statement on whether there is any evidence that this is wrong (given the issues
-> with contamination).  -refer to baxter and explain why we find something
-> different
->
+> with contamination).
+
+Reply: We now refer to Baxter et al. 2017, explain the differences between our
+results. We refrain from making a strong statement given that the analysis
+methods are different and the difference between which galaxies we consider
+blue compared to what Baxter et al. adopt in their paper.
+
 > 4) I have some smaller comments and questions regarding the text and figures.
@@
 
-Reply: We have corrected this.
+Reply: We have now corrected this.
 
@@
 points at every MCMC step. We have now taken the computed points, and plotted
-the spline instead and are displaying it in the Figure to avoid this noise in
+a spline instead and are displaying it in the Figure to avoid this noise in
 the derivative figure.
@@
 
-Reply: Done
+Reply: Agreed, we have now changed this.
 
@@
 
-Reply: We now mention the model of concentration-mass relation we use.
+Reply: We now mention the model of concentration-mass relation we use (Diemer
+and Kravtsov 2015).
 
@@
 
-Reply: We have now edited this.
+Reply: We had included a png file, and now we have changed it to a pdf.
 
@@
 
-Reply: We have added the Rsp values computed without miscentering in Table 6, as suggested.
+Reply: We have added the Rsp values computed without miscentering in Table 6,
+as suggested.

### 2019-02-14 Paper_v2/RSP_paper_new.tex
more edits
finalizing edits

@@
 	\centering{
-    \includegraphics[scale=0.75]{MAIN_color_results_with_spline_no_mc.pdf}}
+    \includegraphics[trim = 0mm 2mm 0mm 0mm, clip,scale=0.75]{MAIN_color_results_with_spline_no_mc_1.pdf}
+    \includegraphics[trim = 0mm 2mm 0mm 0mm, clip,scale=0.75]{MAIN_color_results_with_spline_no_mc_2.pdf}}
 \caption{We present the cross-correlations inferred for the color-separated
@@
 estimate to $M_{\rm 200m}=6.2\times10^{14}$ $\msunh$ using the average
-concentration mass relation of halos assuming an NFW profile
+concentration mass relation of halos \citep{Diemer2015} assuming an NFW profile
 \citep{HuKravtsov:2003}. Given the average mass and redshift of our
@@
 uncertainties for the red and the blue population), we rely on a color cut
-which depends upon the redshift of the cluster under consideration.}
+which depends upon the redshift of the cluster under consideration. The
+differences in our conclusions therefore need to be carefully examined given
+these analysis differences.}
 
@@
 NSF PHY-1125915 during this workshop. Further, we also thank the anonymous
-referee for helpful comments and suggestions during the development of this 
+referee for helpful comments and suggestions which helped improve the
 manuscript.
@@
 
-\section{Visualization of the Data}
+\section{Properties of the SZ clusters and the PS galaxy sample}
 \label{sec:figures}
 
-We visualize some of the main properties of the used data catalogs.
-In Fig.~\ref{fig:planck_summary} we show the mass and
-the redshift distribution of the Planck clusters.
-In Figure~\ref{fig:skymaps} we present the sky locations of the SZ selected clusters from the PSZ2 catalog that we used in our study (red points).
-The purple areas mark the masked out regions of the galaxy catalogs.
-All sky maps presented use the ICRS coordinate system.
+We present the main properties of the data catalogs we have used in our
+analysis. In Fig.~\ref{fig:planck_summary}, we show the mass and the redshift
+distribution of the Planck SZ clusters. In Figure~\ref{fig:skymaps}, we present
+the sky locations of the SZ selected clusters from the PSZ2 catalog that we
+used in our study (red points). The purple areas mark the regions which have
+been masked out from the galaxy catalogs. All sky maps presented use the ICRS
+coordinate system.
 

### 2019-02-20 Paper_v2/RSP_paper_new.tex
small typo edit

@@
 scale of the prior to be 1.2 compared to \citet{more2016detection}. For the
-parameters $\log_{10}(\beta)$ and $\log_{10}(\gamma)$ we also use normal priors
-with central values $\log_{10}(6.0)$ and $\log_{10}(4.0)$, respectively and
-scale 0.4 as recommended by \citet{diemer2014dependence}.}
+parameters $\log_{10}(\beta)$ and $\log_{10}(\gamma)$ we also use
+normal priors with central values $\log_{10}(6.0)$ and
+$\log_{10}(4.0)$, respectively. The scale of the priors is again
+doubled compared to \citet{more2016detection} and set equal to 0.4.}
 

### 2019-03-06 Paper_v2/RSP_paper_new.tex
changes in cornerplot
Corrections regarding proof of paper

@@
 \caption{The two-dimensional posterior distributions of each pair of
-the fitting parameters corresponding to the functional
-form in Equation~\ref{eq:model} for the PS 21.5 sample.
+the fitting parameters corresponding to the functional form in
+Equation~\ref{eq:model} for the PS 21.5 sample. The dark and light magenta
+contours represent the 68\% and 95\% confidence regions for the posterior
+distribution of our parameters.
 }
@@
 While this work was in preparation, we became aware of a related study
-by Shin et al. (2018). Our results are complementary to theirs given
+namely, \citet{shin2018des}. Our results are complementary to theirs given
 the different data samples and cluster catalogs.

### 2019-03-13 Paper_v2/RSP_paper_new.tex
Fixed the COLLOSUS issue

@@
     \hline
-    $M_{\mathrm{500c}}$ [$h^{-1}10^{14} $M$_{\sun}$] & 0.9 & 3.0 \\
-    \hline
-    $M_{\mathrm{200m}}$ [$h^{-1}10^{14} $M$_{\sun}$] & 1.8 & 6.2\\
-    \hline
-    $r^{\mathrm{3D,theo}}_{\mathrm{sp}}$ [$h^{-1}$ Mpc] & 1.37 & 1.89 \\
+    $M_{\mathrm{500c}}$ [$h^{-1}10^{14} $M$_{\sun}$] & 1.0 & 3.0 \\
+    \hline
+    $M_{\mathrm{200m}}$ [$h^{-1}10^{14} $M$_{\sun}$] & 1.9 & 6.1\\
+    \hline
+    $r^{\mathrm{3D,theo}}_{\mathrm{sp}}$ [$h^{-1}$ Mpc] & 1.6 & 2.2 \\
     \hline
@@
 is $M_{\rm 500c}=3.0\times10^{14}$ $\msunh$. We convert this mass
-estimate to $M_{\rm 200m}=6.2\times10^{14}$ $\msunh$ using the average
+estimate to $M_{\rm 200m}=6.1\times10^{14}$ $\msunh$ using the average
 concentration mass relation of halos \citep{Diemer2015} assuming an NFW profile
@@
 cluster sample, we calculate the expected splashback radius to be
-$1.89$ $\mpch$. We base this estimate on the fitting functions
+$2.2$ $\mpch$. We base this estimate on the fitting functions
 presented in \citet{more2015splashback}. The splashback radius we
-find for the three samples is consistent with this expectation,
-although we can not rule out $\sim 15\%$ deviations in either directions,
-given our large error bars.
+find for the three samples is marginally consistent with this expectation
+but on the lower side. Given our large error bars further investigation is
+warranted.
 
@@
 \item The location of the inferred splashback radius is $r_{\rm
-sp}=1.85_{-0.30}^{+0.26}$ $\mpch$, which is consistent with expectations
-from numerical simulations for
+sp}=1.85_{-0.30}^{+0.26}$ $\mpch$, which is marginally consistent 
+with expectations from numerical simulations for
 halos of an average mass $M_{\rm 500c}=3.0\times10^{14}\msunh$ at an
 average redshift of $z=0.18$ in a collision-less dark matter Universe.
-However, given the errors we cannot
-currently rule out $\sim15\%$ deviations from these expectations.
+However, given the errors further investigation is warranted.
 \item We find that the location of the steepest slope does not

### 2019-03-13 change_mass.py

@@ -6,28 +6,31 @@ import colossus.halo.splashback as sb
 
 h = 0.7 #Hubble parameter
 cosmology.setCosmology('bolshoi')
+mass_definition = '500c'
 
-
-def calc_stats(mass, redshift, mass_definition = "200m"):
+def calc_stat(mass, redshift, mass_definition = "200m"):
     if mass_definition == "200m":
         M200m = mass
         c200m = concentration.concentration(M200m, mass_definition, redshift)
+        M200m, R200m, c200m = changeMassDefinition(M200m, c200m, redshift,'200m', '200m')
         M500c, R500c, c500c = changeMassDefinition(M200m, c200m, redshift,'200m', '500c', profile = 'nfw')
     elif mass_definition == "500c":
         M500c = mass
 	c500c = concentration.concentration(M500c, '500c', redshift)
         M200m, R200m, c200m = changeMassDefinition(M500c, c500c, redshift,'500c', '200m')
 
-    Rsp = sb.splashbackRadius(redshift, '200m', M = M200m)[0]*(1 + redshift)
+    Rsp = sb.splashbackRadius(redshift, '200m', M = M200m, model='more15')[0]*(1 + redshift)
+    R200m = R200m*(1 + redshift)
     return M200m, M500c, R200m, Rsp
 
 
 if __name__=="__main__":
    
     #RedMaPPer
-    mass = 1.8e14
+    mass = 1.9e14
     redshift = 0.24
-    M200m, M500c, R200m = calc_stat(mass, redshift, mass_defintion)
+
+    M200m, M500c, R200m, Rsp = calc_stat(mass, redshift, "200m")
     print("RedMaPPer:")
     print("######################################")
     print("R200m is: %E kpc/h" % R200m)
@@ -38,7 +41,7 @@ if __name__=="__main__":
     #SZ
     mass = 4.3e14*h
     redshift = 0.177
-    M200m, M500c, R200m = calc_stat(mass, redshift, mass_defintion)
+    M200m, M500c, R200m , Rsp = calc_stat(mass, redshift, "500c")
     print("SZ:")
     print("######################################")
     print("R200m is: %E kpc/h" % R200m)
@@ -49,7 +52,7 @@ if __name__=="__main__":
     #XR
     mass = 2.3e14*h
     redshift = 0.186
-    M200m, M500c, R200m = calc_stat(mass, redshift, mass_defintion)
+    M200m, M500c, R200m , Rsp = calc_stat(mass, redshift, mass_definition)
[…]

### 2019-03-13 Paper_v2/RSP_paper_new.tex
soften the abstract further

@@
 500c}=3.0\times10^{14}\msunh$ at an average redshift of $z=0.18$.  The inferred
-value of the splashback radius appears consistent with the expected location
+value of the splashback radius appears marginally consistent with the expected location
 for dark matter halos in the standard cold dark matter paradigm. However, given

### 2019-03-13 Paper_v2/RSP_paper_new.tex
changed bibliography

@@
 cosmological distances. Also, we denote three-dimensional distances by
-$r$ and projected distances by $R$.
+$r$ and projected distances by $R$. All distance measurements in this 
+paper are given in comoving units.
 
@@
 While this work was in preparation, we became aware of a related study
-namely, \citet{shin2018des}. Our results are complementary to theirs given
+by \citet{shin2018des}. Our results are complementary to theirs given
 the different data samples and cluster catalogs.
@@
 Canada.  Some of the results in this paper have been derived using
-the HEALPix (K.M. Górski et al., 2005, ApJ, 622, p759) package
+the HEALPix package \citep{gorski2005}
 

### 2019-03-13 Paper_v2/RSP_paper_new.tex
make changes bold

--- 2019-03-13 Paper_v2/RSP_paper_new.tex
@@
 We present evidence for the existence of the splashback radius in galaxy
-clusters selected using the Sunyaev-Zeldovich effect, {\bf a sample unaffected by
-systematics related to cluster finding in the optical wavelength range.} We show
+clusters selected using the Sunyaev-Zeldovich effect, a sample unaffected by
+systematics related to cluster finding in the optical wavelength range. We show
 that the deprojected cross-correlation of galaxy clusters found in the Planck
@@
 $\mpch$, where the cluster sample has an average halo mass $M_{\rm
-500c}=3.0\times10^{14}\msunh$ at an average redshift of $z=0.18$.  The inferred
-value of the splashback radius appears consistent with the expected location
-for dark matter halos in the standard cold dark matter paradigm. However, given
+500c}=3.0\times10^{14}\msunh$ at an average redshift of $z=0.18$. {\bf The inferred
+value of the splashback radius appears marginally consistent with the expected location
+for dark matter halos in the standard cold dark matter paradigm}. However, given
 the limited precision of our measurements, we cannot conclusively confirm or
@@
 
-\textbf{To avoid such optical cluster selection effects, there have been some
+To avoid such optical cluster selection effects, there have been some
 previous efforts to use X-ray selected cluster samples to look for the
 splashback radius using the weak lensing signal \citep{umetsu2017lensing,
-contigiani2018weak}}. However stacking issues and the low signal-to-noise
-ratio remains a significant hurdle for both of them. \textbf{The use of weak
+contigiani2018weak}. However stacking issues and the low signal-to-noise
+ratio remains a significant hurdle for both of them. The use of weak
 lensing data in these studies could get around the biased nature of the galaxy
 distribution by directly probing the dark matter distribution. Along those
-lines,} \citet{chang2017splashback} found evidence for the splashback feature
+lines, \citet{chang2017splashback} found evidence for the splashback feature
 in the weak lensing signal, but their analysis was again done using optically
@@
 
-\textbf{In this work, we explore clusters selected using the SZ effect.} While
+In this work, we explore clusters selected using the SZ effect. While
 the SZ selected clusters can also be susceptible to systematic selection
@@
 
-\textbf{Dynamical friction is expected to slow down massive subhalos, hosting
+Dynamical friction is expected to slow down massive subhalos, hosting
 galaxies that are orbiting the galaxy cluster \citep{chandrasekhar1943dynamical}.
@@
 enough galaxy sample such that the majority of the galaxies reside in low mass
-subhalos, unaffected by dynamical friction.} The SDSS sample used by
+subhalos, unaffected by dynamical friction. The SDSS sample used by
 \citet{more2016detection} was already deep enough such that biases in the
@@
 cosmological distances. Also, we denote three-dimensional distances by
-$r$ and projected distances by $R$.
+$r$ and projected distances by $R$. {\bf All distance measurements in this 
+paper are given in comoving units.}
 
@@
 \citet{foreman2013emcee}.
-\textbf{We let the parameters $\rho_{\mathrm{s}}$, $\rho_0$ and
+We let the parameters $\rho_{\mathrm{s}}$, $\rho_0$ and
 $s_{\mathrm{e}}$ vary freely during our fitting procedure. Similar to
@@
 $\log_{10}(4.0)$, respectively. The scale of the priors is again
-doubled compared to \citet{more2016detection} and set equal to 0.4.}
-
-\textbf{It has been a common concern that the profile in
+doubled compared to \citet{more2016detection} and set equal to 0.4.
+
+It has been a common concern that the profile in
 Equation~\ref{eq:model} introduces a point of minimum slope in the logarithmic
@@
 conclusion was made by \citet{umetsu2017lensing} who conducted a similar study
-but using weak lensing data.}
+but using weak lensing data.
 %\begin{table*}
@@
 
-\textbf{The location of the splashback radius can be identified in various
+The location of the splashback radius can be identified in various
 ways, e.g., as the radius of the outermost shell in theoretical models of
@@
 logarithmic slope of the radially averaged density profile, due to its ease of
-accessibility in data.}
+accessibility in data.
 
@@
 cross-correlations. The cross-correlation signal is clearly detected
-in all three measurements. \textbf{The signal-to-noise ratios of the
+in all three measurements. The signal-to-noise ratios of the
 three different estimates of the two-dimensional cross-correlation signals
@@
 \citet{more2016detection} was 263, a much higher number due to the size of the
-cluster sample used in their study.}
+cluster sample used in their study.
 
@@
 
-\textbf{We show the two-dimensional posterior distributions for each pair of
+We show the two-dimensional posterior distributions for each pair of
 parameters for the PS 21.5 sample in Figure~\ref{fig:corner_21.5}. The
@@
 the independent parts of the profile do not directly translate into an
-uncertainty in the location of the splashback feature.}
+uncertainty in the location of the splashback feature.
 
@@
 the PSZ2 clusters as estimated from the Sunyaev-Zeldovich signal
-is $M_{\rm 500c}=3.0\times10^{14}$ $\msunh$. We convert this mass
+is $M_{\rm 500c}=3.0\times10^{14}$ $\msunh$. {\bf We convert this mass
 estimate to $M_{\rm 200m}=6.1\times10^{14}$ $\msunh$ using the average
@@
 cluster sample, we calculate the expected splashback radius to be
-$2.2$ $\mpch$. We base this estimate on the fitting functions
-presented in \citet{more2015splashback}. The splashback radius we
+$2.2$ $\mpch$.} We base this estimate on the fitting functions
+presented in \citet{more2015splashback}. {\bf The splashback radius we
 find for the three samples is marginally consistent with this expectation
 but on the lower side. Given our large error bars further investigation is
-warranted.
+warranted.}
 
@@
 
-\textbf{At face value, this result seems to be at odds with the findings
+At face value, this result seems to be at odds with the findings
 presented by \citet{baxter2017halo}, who find no splashback feature in the blue
@@
 differences in our conclusions therefore need to be carefully examined given
-these analysis differences.}
+these analysis differences.
 
@@
 NFW profile. We associate this steepening with the splashback feature.
-\item The location of the inferred splashback radius is $r_{\rm
+\item {\bf The location of the inferred splashback radius is $r_{\rm
 sp}=1.85_{-0.30}^{+0.26}$ $\mpch$, which is marginally consistent 
@@
 average redshift of $z=0.18$ in a collision-less dark matter Universe.
-However, given the errors further investigation is warranted.
+However, given the errors further investigation is warranted.}
 \item We find that the location of the steepest slope does not
@@
 
-While this work was in preparation, we became aware of a related study
-namely, \citet{shin2018des}. Our results are complementary to theirs given
-the different data samples and cluster catalogs.
+{\bf While this work was in preparation, we became aware of a related study
+by \citet{shin2018des}. Our results are complementary to theirs given
+the different data samples and cluster catalogs.}
 
@@
 
-Based on observations obtained with Planck
+{\bf Based on observations obtained with Planck
 (http://www.esa.int/Planck), an ESA science mission with instruments
@@
 Canada.  Some of the results in this paper have been derived using
-the HEALPix (K.M. Górski et al., 2005, ApJ, 622, p759) package
+the HEALPix package \citep{gorski2005}}
 
